### 2018-12-02 apjl.tex
Add files via upload

%%
%% Beginning of file 'sample62.tex'
%%
%% Modified 2018 January
%%
%% This is a sample manuscript marked up using the
%% AASTeX v6.2 LaTeX 2e macros.
%%
%% AASTeX is now based on Alexey Vikhlinin's emulateapj.cls 
%% (Copyright 2000-2015).  See the classfile for details.

%% AASTeX requires revtex4-1.cls (http://publish.aps.org/revtex4/) and
%% other external packages (latexsym, graphicx, amssymb, longtable, and epsf).
%% All of these external packages should already be present in the modern TeX 
%% distributions.  If not they can also be obtained at www.ctan.org.

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style  which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%%
%% using aastex version 6.2
\documentclass{aastex62}

%% The default is a single spaced, 10 point font, single spaced article.
%% There are 5 other style options available via an optional argument. They
%% can be envoked like this:
%%
%% \documentclass[argument]{aastex62}
%% 
%% where the layout options are:
%%
%%  twocolumn   : two text columns, 10 point font, single spaced article.
%%                This is the most compact and represent the final published
%%                derived PDF copy of the accepted manuscript from the publisher
%%  manuscript  : one text column, 12 point font, double spaced article.
%%  preprint    : one text column, 12 point font, single spaced article.  
%%  preprint2   : two text columns, 12 point font, single spaced article.
%%  modern      : a stylish, single text column, 12 point font, article with
%% 		  wider left and right margins. This uses the Daniel
%% 		  Foreman-Mackey and David Hogg design.
%%  RNAAS       : Preferred style for Research Notes which are by design 
%%                lacking an abstract and brief. DO NOT use \begin{abstract}
%%                and \end{abstract} with this style.
%%
%% Note that you can submit to the AAS Journals in any of these 6 styles.
%%
%% There are other optional arguments one can envoke to allow other stylistic
%% actions. The available options are:
%%
%%  astrosymb    : Loads Astrosymb font and define \astrocommands. 
%%  tighten      : Makes baselineskip slightly smaller, only works with 
%%                 the twocolumn substyle.
%%  times        : uses times font instead of the default
%%  linenumbers  : turn on lineno package.
%%  trackchanges : required to see the revision mark up and print its output
%%  longauthor   : Do not use the more compressed footnote style (default) for 
%%                 the author/collaboration/affiliations. Instead print all
%%                 affiliation information after each name. Creates a much
%%                 long author list but may be desirable for short author papers
%%
%% these can be used in any combination, e.g.
%%
%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex62}
%%
%% AASTeX v6.* now includes \hyperref support. While we have built in specific
%% defaults into the classfile you can manually override them with the
%% \hypersetup command. For example,
%%
%%\hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
%%
%% will change the color of the internal links to red, the links to the
%% bibliography to green, the file links to cyan, and the external links to
%% magenta. Additional information on \hyperref options can be found here:
%% https://www.tug.org/applications/hyperref/manual.html#x1-40003
%%
%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}

%% Reintroduced the \received and \accepted commands from AASTeX v5.2
\received{January 1, 2018}
\revised{January 7, 2018}
\accepted{\today}
%% Command to document which AAS Journal the manuscript was submitted to.
%% Adds "Submitted to " the arguement.
\submitjournal{ApJ}

%% Mark up commands to limit the number of authors on the front page.
%% Note that in AASTeX v6.2 a \collaboration call (see below) counts as
%% an author in this case.
%
%\AuthorCollaborationLimit=3
%
%% Will only show Schwarz, Muench and "the AAS Journals Data Scientist 
%% collaboration" on the front page of this example manuscript.
%%
%% Note that all of the author will be shown in the published article.
%% This feature is meant to be used prior to acceptance to make the
%% front end of a long author article more manageable. Please do not use
%% this functionality for manuscripts with less than 20 authors. Conversely,
%% please do use this when the number of authors exceeds 40.
%%
%% Use \allauthors at the manuscript end to show the full author list.
%% This command should only be used with \AuthorCollaborationLimit is used.

%% The following command can be used to set the latex table counters.  It
%% is needed in this document because it uses a mix of latex tabular and
%% AASTeX deluxetables.  In general it should not be needed.
%\setcounter{table}{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% The following section outlines numerous optional output that
%% can be displayed in the front matter or as running meta-data.
%%
%% If you wish, you may supply running head information, although
%% this information may be modified by the editorial offices.
\shorttitle{Compact Binaries of BS Twins from Stellar Triples}
\shortauthors{Leigh \& Portegies Zwart}
%%
%% You can add a light gray and diagonal water-mark to the first page 
%% with this command:
% \watermark{text}
%% where "text", e.g. DRAFT, is the text to appear.  If the text is 
%% long you can control the water-mark size with:
%  \setwatermarkfontsize{dimension}
%% where dimension is any recognized LaTeX dimension, e.g. pt, in, etc.
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% This is the end of the preamble.  Indicate the beginning of the
%% manuscript itself with \begin{document}.

\begin{document}

\title{A Triple Origin for Twin Blue Stragglers in Compact Binaries}

%% LaTeX will automatically break titles if they run longer than
%% one line. However, you may use \\ to force a line break if
%% you desire. In v6.2 you can include a footnote in the title.

%% A significant change from earlier AASTEX versions is in the structure for 
%% calling author and affilations. The change was necessary to implement 
%% autoindexing of affilations which prior was a manual process that could 
%% easily be tedious in large author manuscripts.
%%
%% The \author command is the same as before except it now takes an optional
%% arguement which is the 16 digit ORCID. The syntax is:
%% \author[xxxx-xxxx-xxxx-xxxx]{Author Name}
%%
%% This will hyperlink the author name to the author's ORCID page. Note that
%% during compilation, LaTeX will do some limited checking of the format of
%% the ID to make sure it is valid.
%%
%% Use \affiliation for affiliation information. The old \affil is now aliased
%% to \affiliation. AASTeX v6.2 will automatically index these in the header.
%% When a duplicate is found its index will be the same as its previous entry.
%%
%% Note that \altaffilmark and \altaffiltext have been removed and thus 
%% can not be used to document secondary affiliations. If they are used latex
%% will issue a specific error message and quit. Please use multiple 
%% \affiliation calls for to document more than one affiliation.
%%
%% The new \altaffiliation can be used to indicate some secondary information
%% such as fellowships. This command produces a non-numeric footnote that is
%% set away from the numeric \affiliation footnotes.  NOTE that if an
%% \altaffiliation command is used it must come BEFORE the \affiliation call,
%% right after the \author command, in order to place the footnotes in
%% the proper location.
%%
%% Use \email to set provide email addresses. Each \email will appear on its
%% own line so you can put multiple email address in one \email call. A new
%% \correspondingauthor command is available in V6.2 to identify the
%% corresponding author of the manuscript. It is the author's responsibility
%% to make sure this name is also in the author list.
%%
%% While authors can be grouped inside the same \author and \affiliation
%% commands it is better to have a single author for each. This allows for
%% one to exploit all the new benefits and should make book-keeping easier.
%%
%% If done correctly the peer review system will be able to
%% automatically put the author and affiliation information from the manuscript
%% and save the corresponding author the trouble of entering it by hand.

\correspondingauthor{Nathan W. C. Leigh}
\email{nleigh@amnh.org}

\author{Nathan W. C. Leigh}
\affil{American Museum of Natural History \\
Department of Astrophysics \\
79th Street at Central Park West \\
New York, NY 10024-5192, USA}
\affil{Stony Brook University \\
Department of Physics and Astronomy\\
Stony Brook, NY 11794-3800, USA}
\affil{Departamento de Astronom\'ia \\ 
Facultad de Ciencias F\'isicas y Matem\'aticas \\ 
Universidad de Concepci\'on \\ 
Concepci\'on, Chile}

\author{Simon Portegies Zwart}
\affiliation{Leiden Observatory \\
Leiden University \\
PO Box 9513, 2300 RA \\
Leiden, the Netherlands}

%% Note that the \and command from previous versions of AASTeX is now
%% depreciated in this version as it is no longer necessary. AASTeX 
%% automatically takes care of all commas and "and"s between authors names.

%% AASTeX 6.2 has the new \collaboration and \nocollaboration commands to
%% provide the collaboration status of a group of authors. These commands 
%% can be used either before or after the list of corresponding authors. The
%% argument for \collaboration is the collaboration identifier. Authors are
%% encouraged to surround collaboration identifiers with ()s. The 
%% \nocollaboration command takes no argument and exists to indicate that
%% the nearby authors are not part of surrounding collaborations.

%\newcommand{\mnras}{\textrm{MNRAS}}
%\newcommand{\apj}{\textrm{ApJ}}
%\newcommand{\aap}{\textrm{A\&A}}
%\newcommand{\apjl}{\textrm{ApJ}}

\begin{abstract}
In this Letter, we propose a potential formation mechanism for twin blue stragglers in compact binaries that involves mass transfer from an evolved outer tertiary companion on to the inner binary via a circumbinary disk.  We apply our hypothetical scenario to the observed double blue straggler system Binary 7782 in the old open cluster NGC 188, and show that its observed properties are easily and even naturally reproduced within the context our proposed model.  Within the context of the hypothetical formation mechanism proposed here, the presented work predicts the following properties for the post-mass transfer double BS tertiary:  (1)  For the outer tertiary orbit, the orbital period should lie between 220 days $\lesssim$ P$_{\rm out}$ $\lesssim$ 1100 days, assuming initial masses for the inner binary components of m$_{\rm 1} =$ 1.1 M$_{\odot}$ and m$_{\rm 2} =$ 0.9 M$_{\odot}$ and an outer tertiary mass of m$_{\rm 3} =$ 1.4 M$_{\odot}$. (2)  Larger final WD masses, and hence core masses for the donor at the time of mass transfer, should correspond to larger final outer orbital periods for the tertiary. (3)  For the inner binary, the rotational axes of the BSs should be aligned with each other and the orbital plane of the outer tertiary WD. (4)  The BSs in the inner binary should have roughly equal masses, independent of their initial masses.  This predicts that the initially lower mass MS star should accrete the most, and should hence be polluted more significantly by any accreted material.  This could be observable in the surface layers of a radiative star (i.e., He, C and O if the donor is an RGB star, and/or s-process elements if the donor is an AGB star). (5) Twin BSs in compact binaries formed from the proposed mechanism should be more frequent in younger clusters with ages $\lesssim$ 4-6 Gyr, since the donor will have  radiative envelope.

\end{abstract}

\keywords{stars: blue stragglers -- binaries: general -- globular clusters: general -- scattering}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction} \label{intro}

Blue straggler (BS) stars appear brighter and bluer than the main-sequence turn-off (MSTO) in a cluster colour-magnitude diagram (CMD) \citep[e.g.][]{simunovic14,simunovic16}.  Two primary channels for BS formation have been proposed; mass transfer from an evolved donor on to a main-sequence star in a binary star system \citep[e.g.][]{mccrea64,knigge09,mathieu09,leigh11,geller11,geller12,gosnell14,gosnell15}, and direct stellar collisions involving main-sequence stars mediated via direct interactions involving binaries \citep[e.g.][]{hills75,shara97,leigh07,leigh11,leigh13,hypki13}.  Other possible, albeit related, formation mechanisms include mergers of compact MS-MS binaries, and mergers of the inner MS-MS binaries of hierarchical triple star systems induced by Lidov-Kozai oscillations coupled with tidal damping \citep[e.g.][]{perets09}.

In spite of these specific predictions for the expected properties of BSs formed from each of the above production mechanisms, there exist many BSs with observed properties that defy these simple scenarios.  For example, in the old open cluster M67, there lurks a candidate triple system that is posited to host \textit{two} BSs \citep{vandenberg01,sandquist03}.  The observations suggest that the outer tertiary is itself a BS, with a mass $\sim$ 1.7 M$_{\odot}$ and orbiting the inner binary with a period of 1188.5 days \citep{sandquist03}.  The inner binary has a period of only 1.068 days \citep{vandenberg01}, and hosts a BS of mass 2.52 M$_{\odot}$.  Thus, in order to form this system after convolving its observed properties with its host cluster age, we require at least five stars in order to conserve the total system mass \citep{leigh11}.  As explained in \citet{leigh11}, this is strongly indicative of a dynamical origin for the system, and a single direct interaction involving a binary and a triple that resulted in two separate collision events is the most probable explanation for its origin (i.e., a single interaction involving two multiples with two or more stars is a more likely scenario to produce this system than two back-to-back direct binary-binary interactions).

Even more curious, there exists in the old open cluster NGC 188 a double BS binary, called Binary 7782.  Specifically, \citet{mathieu09} observed a compact and mildly eccentric (i.e., e $\sim$ 0.1) binary star system with an orbital period of $\sim$ 10 days hosting \textit{two} blue stragglers.  During a given binary-binary interaction, the probability that not one but \textit{two} direct MS-MS collisions occur is less than a percent \citep{leonard89,leigh11,leigh12}.  Typically, such binaries are very wide with long orbital periods.  Thus, dynamically, it is very difficult to form a compact binary composed of two collision products during a single direct interaction in a star cluster.  So, how did Binary 7782 form?  MENTION BIMODAL P-E DISTRIBUTION, AND HOW THIS COULD BE SUGGESTIVE OF A TRIPLE ORIGIN FOR SOME OF THE SUBSET OF OBSERVED BSs.

In this Letter, we propose a potential formation channel for Binary 7782, and compact double BS binaries in general, which involves mass transfer from an outer tertiary companion on to an inner MS-MS binary.  In section~\ref{dyn}, we constrain the range of present-day orbital parameters for a hypothetical outer tertiary companion, using a combination of dynamical and stellar evolution-based constraints.  In Section~\ref{sims} we present the numerical simulations used to study the mass transfer process in our hypothetical triple system, computed using the \texttt{AMUSE} software package, in order to study the evolution of the inner and outer orbital parameters during mass transfer.  We summarize and discuss the implications of our results for compact double BS binaries and, more generally, mass transfer in stellar triples in Section~\ref{discussion}.

\section{Constraints on the present-day orbital parameters for a hypothesized tertiary companion in the compact BS Binary 7782} \label{dyn}

Consider a hierarchical triple system with component masses m$_{\rm 1}$ and m$_{\rm 2}$ for the inner binary, and mass m$_{\rm 3}$ for the outer tertiary companion.  The inner and outer binary orbital semi-major axes are denoted a$_{\rm in}$ and a$_{\rm out}$, respectively.  We assume circular orbits for both the inner and outer orbits.

We consider a scenario where the outer tertiary companion is filling its Roche lobe and is hence transferring mass to the inner binary.  Using conservation of angular momentum, we can equate the specific angular momentum of the accreted mass at the inner Lagrangian point of the donor star to the final specific angular momentum of the accretion stream at the circularization radius about the inner binary:
\begin{equation}
\label{eqn:specangmom1}
v_{\rm orb,3}(a_{\rm out} - r_{\rm L}) = v_{\rm orb,c}a_{\rm c},
\end{equation}
where R$_{\rm L}$ is the radius of the Roche lobe of the outer tertiary companion, a$_{\rm c}$ is the semi-major axis of the orbit about the inner binary corresponding to the circularization radius and v$_{\rm orb,c}$ is the orbital velocity at a$_{\rm c}$.  The distance from the center of mass corresponding to the outer tertiary companion defined by the Roche lobe is given by \citep{eggleton83}: 
\begin{equation}
\label{eqn:roche}
R_{\rm L} = \frac{0.49q^{2/3}}{0.6q^{2/3} + {\rm ln}(1 + q^{1/3})}a_{\rm out},
\end{equation}
where the mass ratio q is defined as q $=$ m$_{\rm 3}$/(m$_{\rm 1} +$ m$_{\rm 2}$).  Combining Equation~\ref{eqn:roche} with Equation~\ref{eqn:specangmom1}, we can solve for the circularization radius as a function of a$_{\rm out}$ and the assumed stellar masses:
\begin{equation}
\label{eqn:ac}
a_{\rm c} = a_{\rm out}(1 - R_{\rm L}).
\end{equation}
In order for a circumbinary disk to form around the inner binary, we require that a$_{\rm in} <$ a$_{\rm c}$.

Figure~\ref{fig:fig1} shows the parameter space in the P$_{\rm out}$-P$_{\rm in}$-plane for Binary 7782.  We assume initial component masses of m$_{\rm 1} =$ 1.1 M$_{\rm \odot}$ and m$_{\rm 2} =$ 0.9 M$_{\rm \odot}$ for the inner binary components, and m$_{\rm 3} =$ 1.4 M$_{\rm \odot}$ for the outer tertiary.  We compare the circularization radius to the semi-major axis of the inner binary, for which we require a$_{\rm c} >$ a$_{\rm in}$, after folding in all constraints from the requirements for dynamical stability, an outer tertiary that is Roche lobe-filling, and a dynamically hard outer tertiary orbit.  Note that the range of plotted orbital periods P$_{\rm in}$ corresponding to a contact state for the inner binary, assuming R$_{\rm 1} =$ R$_{\rm 2} =$ 1 R$_{\odot}$, lies outside the range of plotted values for P$_{\rm in}$, since it does not contribute significantly to constraining the outer orbital properties of a hypothesized outer WD tertiary.  The thick horizontal solid red line shows the allowed range of outer semi-major axes, after folding in all of the aforementioned criteria.  As is clear, this makes a relatively narrow prediction for the allowed ranges of outer tertiary orbits, namely 2.2 $\times$ 10$^{2}$ days $\le$ P$_{\rm out}$ $\le$ 1.1 $\times$ 10$^3$ days, for our assumed final donor mass.

\begin{figure}[ht!]
\plotone{fig1.eps}
\caption{Parameter space in the P$_{\rm out}$-P$_{\rm in}$-plane allowed for the hypothetical outer tertiary orbit of Binary 7782.  The solid diagonal black lines show the period corresponding to the circularization radius a$_{\rm c}$ for the mass transfer stream coming from the outer tertiary, for different values of the mass ratio, namely q $=$ 0.1, 0.7, 1, 2 and 10.  We assume initial component masses of m$_{\rm 1}$ = 1.1 M$_{\rm \odot}$ and m$_{\rm 2}$ = 0.9 M$_{\rm \odot}$ for the inner binary components, and m$_{\rm 3}$ is computed for the outer tertiary according to our assumed mass ratio (with our fiducial case corresponding to q $=$ 0.7.  We assume completely conservative mass transfer for this exercise, and a final mass for the outer tertiary of 0.6 M$_{\rm \odot}$ once it has become a WD.  The dashed diagonal black line shows a rough criterion for dynamical stability in the triple, approximately following \citet{mardling99} (i.e., a$_{\rm in} <$ 0.1a$_{\rm out}$ is required for long-term dynamical stability in equal-mass co-planar triples).  The vertical solid red lines show the outer orbital periods corresponding to the hard-soft boundary assuming central velocity dispersions of $\sigma =$ 1, 5 and 10 km s$^{-1}$.  The vertical dashed black lines show the maximum outer orbital period P$_{\rm out}$ for which the outer tertiary companion is Roche lobe-filling, assuming a stellar radius of R$_{\rm 3} =$ 200 R$_{\odot}$ (CHANGE, POSSIBLY USING MESA CALCULATIONS?!).  The horizontal dashed red line shows the observed orbital period for Binary 7782, using its observed orbital period and our assumed final inner companion masses (i.e., m$_{\rm 1} =$ m$_{\rm 2} =$ 1.4 M$_{\odot}$).  Finally, the thick solid horizontal red line shows the parameter space for P$_{\rm out}$ allowed after considering all of the aforementioned criteria.
\label{fig:fig1}}
\end{figure}

\section{Numerical Simulations} \label{sims}

\subsection{AMUSE} \label{amuse}

We use smoothed-particle hydrodynamics (SPH) simulations to compute the time evolution of the mass transfer process.

\subsection{Initial Conditions} \label{ICs}

In this section, we describe and justify our choice of initial conditions for both our analytic calculations and smoothed-particle hydrodynamics simulations.

We adopt initial component masses of m$_{\rm 1}$ = 1.1 M$_{\rm \odot}$ and m$_{\rm 2}$ = 0.9 M$_{\rm \odot}$ for the inner binary components, and m$_{\rm 3}$ = 1.4 M$_{\rm \odot}$ for the outer tertiary.  This choice for the initial mass of the outer tertiary is critical since it ensures that the donor star during the mass transfer process will have a radiative envelope \citep[e.g.][]{maeder09}.  In turn, this ensures that the mass transfer will be maximally conservative, such that the accretion stream will be maximally stable, accreting at a stable and constant rate \citep[e.g.][]{iben91}.

\section{Results} \label{results}

\section{Summary and Discussion} \label{discussion}

In this Letter, we have proposed a formation scenario for double BS equal-mass compact binaries, as observed for Binary 7782 in the old open cluster NGC 188.  The proposed scenario involves mass transfer from an evolved outer tertiary companion, which is accreted by the inner binary via a circumbinary disk.  Our scenario makes several predictions for the observed properties of a hypothetical outer triple companion, now a WD.  These are:

\begin{enumerate}

\item For the predicted outer tertiary orbit, the present-day semi-major axis should lie between 220 days $\lesssim$ P$_{\rm out}$ $\lesssim$ 1100 days, assuming initial masses for the inner binary components of m$_{\rm 1} =$ 1.1 M$_{\odot}$ and m$_{\rm 2} =$ 0.9 M$_{\odot}$ and an outer tertiary mass of m$_{\rm 3} =$ 1.4 M$_{\odot}$.

\item Larger final WD masses, and hence core masses for the donor at the time of mass transfer, should correspond to larger final outer orbital periods for the tertiary.  This is because the Roche radius is larger for larger outer orbital periods, such that the donor must evolve to larger radii, and hence core masses, before the onset of mass transfer.

\item For the inner binary, the rotational axes of the BSs should be aligned with each other and the orbital plane of the outer tertiary WD.  This is because accretion onto the BS progenitors proceeds via an accretion disk, that forms at the circularization radius and that has an orbital plane aligned with that of the outer tertiary.

\item The BSs in the inner binary should have roughly equal masses, independent of their initial masses.  This is because it is the lowest mass object that typically accretes the fastest, since its orbital velocity and distance relative to the circumbinary disk is typically the lowest.  This quickly brings the mass ratio toward unity.  This predicts that the initially lower mass MS star should accrete the most, and should hence be polluted more significantly by any accreted material.  This could be observable in the surface layers of a radiative star.  If the donor is an RGB star, the accretor will be enriched in mostly carbon, oxygen and helium.  If the accretor is an AGB star, it will be enriched in mostly s-process elements.

\item Twin BSs in compact binaries formed from the proposed mechanism should be more frequent in younger clusters with ages $\lesssim$ 4-6 Gyr.  This is because clusters with a main-sequence turn-off mass $\lesssim$ 1.2 M$_{\odot}$ have convective envelopes \citep[e.g.][]{iben91,maedoer09}, and a radiative envelope for the donor in a mass transferring binary ensures stable accretion on to the accretor.

WHAT ELSE?  SOMETHING RELATED TO TIMESCALES AND THE PROBABiLitY OF OBSERVING THE WD?

\end{enumerate}

\acknowledgments

N.W.C.L. acknowledges support from a Kalbfleisch Fellowship at the American Museum of Natural History.

\begin{thebibliography}{}

%\bibitem[\protect\citeauthoryear{Anderson et al.}{2008}]{anderson08}
% Anderson J.,  Sarajedini A., Bedin L. R., King I. R., Piotto G.,
%  Reid I. N., Siegel M., Majewski S. R., Paust N. E. Q., Aparicio A.,
%  Milone A. P., Chaboyer B., Rosenberg A. 2008, AJ, 135, 2055
%\bibitem[\protect\citeauthoryear{Artymowicz et al.}{1993}]{artymowicz93} Artymowicz P., Lin D. N. C., Wampler E. J. 1993, ApJ, 409, 592 
%\bibitem[\protect\citeauthoryear{Bartos et al.}{2017}]{Bartos17} Bartos I., Kocsis B., Haiman Z. \& M\'{a}rka S., 2017, ApJ, 835, 165
%\bibitem[\protect\citeauthoryear{Bartko et al.}{2009}]{Bartko09} Bartko H., Martins F., Trippe S., Fritz T. K., Genzel R., Ott T., Eisenhauer F., Gillessen S., Paumard T., Alexander T., Dodds-Eden K., Gerhard O., Levin Y., Mascetti L., Nayakshin S., Perets H. B., Perrin G., Pfuhl O., Reid M. J., Rouan D., Sternberg A., Trippe S., 2009, ApJ, 697, 1741
%\bibitem[\protect\citeauthoryear{Bartko et al.}{2010}]{Bartko10} Bartko H., Martins F., Fritz T. K., Genzel R., Levin Y., Perets H. B., Paumard T., Nayakshin S., Gerhard O., Alexander T., Dodds-Eden K., Eisenhauer F., Gillessen S., Mascetti L., Ott T., Perrin G., Pfuhl O., Reid M. J., Rouan D., Zilka M., Sternberg A., 2010, ApJ, 708, 834
%\bibitem[\protect\citeauthoryear{Baruteau et al.}{2011}]{Baruteau11} Baruteau C., Cuadra J. \& Lin D.N.C., 2011, ApJ, 726, 28
%\bibitem[\protect\citeauthoryear{Bedin et al.}{2010}]{bedin10} Bedin L. R., Cassisi S., Castelli F., Piotto G., Anderson J., Salaris M., Momany Y., Pietrinferni A. 2010, MNRAS 357, 1038
%\bibitem[\protect\citeauthoryear{Bender et al.}{2005}]{bender05} Bender R., Kormendy J., Bower G., et al. 2005, ApJ, 631, 280
%\bibitem[\protect\citeauthoryear{Bruzual \& Charlot}{2003}]{bruzual03} Bruzual G., Charlot S. 2003, MNRAS, 344, 1000 
%\bibitem[\protect\citeauthoryear{Casassus et al.}{2013}]{casassus13} Casassus S., Hales A., de Gregorio I., Dent B., Belloche A., G\"usten R., M\'enard F., Hughes A. M., Wilner D., Salinas V. 2013, A\&A, 553, 64 
%\bibitem[\protect\citeauthoryear{Ceillier et al.}{2017}]{ceillier17} Ceillier T., Tayar J., Mathur S., Salabert D., Garc\'ia R. A., Stello D., Pinsonneault M. H., van Sanders J., Beck P. G., Bloemen S. 2017, A\& A, 605, 111 
\bibitem[\protect\citeauthoryear{Chatterjee et al.}{2013}]{chatterjee13} Chatterjee S., Rasio F. A., Sills A., Glebbeek E. 2013, ApJ, 777, 106  
%\bibitem[\protect\citeauthoryear{Chen \& Amaro-Seoane}{2015}]{chen15} Chen X., Amaro-Seoane P. 2015, Classical and Quantum Gravity, 32, 6 
%\bibitem[\protect\citeauthoryear{Dotter et al.}{2010}]{dotter10} Dotter, A., Sarajedini A., Anderson J., Aparicio A., Bedin L. R., Chaboyer B., Majewski S., Marin-Franch A., Milone A., Paust N., Piotto G., Reid N., Rosenberg A., Siegel M. 2010, ApJ 708, 698 
%\bibitem[\protect\citeauthoryear{Dalessandro et al.}{2013}]{dalessandro13} Dalessandro E., Ferraro F. R., Massari D., Lanzoni B., Miocchi R. P., Beccari G., Bellini A., Sills A., Sigurdsson S., Mucciarelli A., Lovisi L. 2013, ApJ, 778, 135
%\bibitem[\protect\citeauthoryear{Eggleton}{1983}]{eggleton83} Eggleton P. P. 1983, ApJ, 268, 368 
%\bibitem[\protect\citeauthoryear{Flock et al.}{2015}]{flock15} Flock M., Ruge J. P., Dzyurkevich N., Henning Th., Klahr H., Wolf S. 2015, A\&A, 574, 68
%\bibitem[\protect\citeauthoryear{Ferraro et al.}{1997}]{ferraro97}
%  Ferraro F. R., Paltrinieri B., Fusi Pecci F., Cacciari C., Dorman
%  B., Rood R. T., Buonanno R., Corsi C. E., Burgarella D., Laget
%  M. 1997, A\&A, 324, 915
%\bibitem[\protect\citeauthoryear{Ferraro et al.}{1999}]{ferraro99}
%  Ferraro F. R., Paltrinieri B., Rood R. T., Dorman B. 1999, ApJ, 522,
%  983
%\bibitem[\protect\citeauthoryear{Ferraro et al.}{2004}]{ferraro04}
%  Ferraro F. R., Beccari G., Rood, R. T., Bellazzini M., Sills A.,
%  Sabbi E. 2004, ApJ, 603, 127
%\bibitem[\protect\citeauthoryear{Ferraro, Valenti \& Origlia}{2006}]{ferraro06} Ferraro F. R., Valenti E., Origlia L. 2006, ApJ, 649, 243
%\bibitem[\protect\citeauthoryear{Ferraro et al.}{2009}]{ferraro09} Ferraro F. R., Beccari G., Dalessandro E., Lanzoni B., Sills A., Rood R. T., Pecci F. F., Karakas A. I., Miocchi P., Bovinelli S. 2009, Nature, 462, 1028  
%\bibitem[\protect\citeauthoryear{Fregeau et al.}{2004}]{fregeau04} Fregeau J. M., Cheung P.,
%  Portegies Zwart S. F., Rasio F. A. 2004, MNRAS, 352, 1
%\bibitem[\protect\citeauthoryear{Fregeau, Ivanova \& Rasio}{2009}]{fregeau09} Fregeau J. M., Ivanova N.,
%  Rasio F. A. 2009, ApJ, 707, 1533
%\bibitem[\protect\citeauthoryear{Geller at al.}{2009}]{geller09}
%  Geller A. M., Mathieu R. D., Harris H. C., McClure R. D., 2009,
%  AJ, 137, 3743
\bibitem[\protect\citeauthoryear{Geller \& Mathieu}{2011}]{geller11}
  Geller A. M., Mathieu R. D. 2011, Nature, 478, 356
\bibitem[\protect\citeauthoryear{Geller \& Mathieu}{2012}]{geller12} Geller A. M., Mathieu R. D. 2012, AJ, 144, 54
\bibitem[\protect\citeauthoryear{Geller et al.}{2013a}]{geller13a} Geller A. M.,
de Grijs R., Li C., Hurley J. R. 2013, ApJ, 779, 30
\bibitem[\protect\citeauthoryear{Geller et al.}{2013b}]{geller13b} Geller A. M., Hurley J. R., Mathieu R. D. 2013, AJ, 145, 8
\bibitem[\protect\citeauthoryear{Geller \& Leigh}{2015}]{geller15} Geller A. M., Leigh W. W. C. 2015, ApJL, 808, L25 
%\bibitem[\protect\citeauthoryear{Ghez}{2008}]{ghez08} Ghez A. M., Salim S., Weinberg N. N., Lu J. R., Do T., Dunn J. K., Matthews K, Morris M. R., Yelda S., Becklin E. E., Kremenek T., Milosavlevic M., Naiman J., ApJ, 2008, 689, 1044 
%\bibitem[\protect\citeauthoryear{Ghez}{2008}]{ghez08}
\bibitem[\protect\citeauthoryear{Gosnell et al.}{2014}]{gosnell14} Gosnell N. M., Mathieu R. D., Geller A. M., Sills A., Leigh N. W. C., Knigge C. 2014, ApJ, 783, 8
\bibitem[\protect\citeauthoryear{Gosnell et al.}{2015}]{gosnell15} Gosnell N. M., Mathieu R. D., Geller A. M., Sills A., Leigh N. W. C., Knigge C. 2015, ApJ, 814, 163
%\bibitem[\protect\citeauthoryear{Graham \& Spitler}{2009}]{Graham09} Graham A.W. \& Spitler L.R., 2009, MNRAS, 397, 2148
%\bibitem[\protect\citeauthoryear{Harris et al.}{1996; 2010 update}]{harris96} Harris W. E. 1996, AJ, 112,
%  1487; 2010 update
%\bibitem[\protect\citeauthoryear{Heggie}{1975}]{heggie75} Heggie D. C. 1975, MNRAS, 173, 729
%\bibitem[\protect\citeauthoryear{Heggie \& Hut}{2003}]{heggie03}
%  Heggie D. C., Hut P. 2003, The Gravitational Million-Body Problem:
%  A Multidisciplinary Approach to Sar Cluster Dynamics (Cambridge:
%  Cambridge University Press)
\bibitem[\protect\citeauthoryear{Hills}{1975}]{hills75} Hills J. G. 1975, AJ, 80, 809
%\bibitem[\protect\citeauthoryear{Hurley et al.}{2005}]{hurley05}
%  Hurley J. R., Pols O. R., Aarseth S. J., Tout C. A. 2005, MNRAS,
%  363, 293
%\bibitem[\protect\citeauthoryear{Hurley, Aarseth \&
%    Shara}{2007}]{hurley07} Hurley J. R., Aarseth S. J., Shara M. M. 2007, ApJ, 665, 707
%\bibitem[\protect\citeauthoryear{Hut \& Bahcall}{1983}]{hut83} Hut P., Bahcall J. N. 1983, ApJ,
%  268, 319
%\bibitem[\protect\citeauthoryear{Howarth}{1983}]{howarth83} Howarth I. D. 1983, MNRAS, 203, 301
\bibitem[\protect\citeauthoryear{Hypki \& Giersz}{2013}]{hypki13} Hypki A., Giersz M. 2013,
MNRAS, 429, 1221
\bibitem[\protect\citeauthoryear{Iben}{1991}]{iben91}  Iben I., Jr. 1991, ApJS, 76, 55
\bibitem[\protect\citeauthoryear{Knigge, Leigh \& Sills}{2009}]{knigge09} Knigge C., Leigh
  N., Sills A. 2009, Nature, 457, 288
%\bibitem[\protect\citeauthoryear{Laidler et al.}{2008}]{laidler08} Laidler et al. 2008, ``Synphot Data User's Guide'' (Baltimore, STScI)
%\bibitem[\protect\citeauthoryear{Lanzoni et al.}{2007}]{lanzoni07} Lanzoni B., Dalessandro E., Ferraro F. R., Valenti E., Beccari G., Schiavon R. P., Rood R. T., Mapelli M., Sigurdsson S. 2007, ApJ, 663, 1040
%\bibitem[\protect\citeauthoryear{Kaluzny et al.}{1998}]{kaluzny98} Kaluzny J., Hilditch R. W., Clement C., Rucinski S. M. 1998, MNRAS, 296, 347
%\bibitem[\protect\citeauthoryear{Kaluzny et al.}{2015}]{kaluzny15} Kaluzny J., Thompson I. B., Narloch W., Pych W., Rozyczka M. 2015, Acta Astronomica, 65, 267 
\bibitem[\protect\citeauthoryear{Leigh, Sills \& Knigge}{2007}]{leigh07} Leigh
  N. W. C., Sills A., Knigge C. 2007, ApJ, 661, 210
%\bibitem[\protect\citeauthoryear{Leigh, Sills \& Knigge}{2008}]{leigh08} Leigh
%  N. W., Sills A., Knigge C. 2008, ApJ, 678, 564
%\bibitem[\protect\citeauthoryear{Leigh, Sills \& Knigge}{2009}]{leigh09} Leigh
%  N. W., Sills A., Knigge C. 2009, MNRAS, 399, L179
\bibitem[\protect\citeauthoryear{Leigh \& Sills}{2011}]{leigh11} Leigh N. W. C., Sills A. 2011, MNRAS, 410, 2370
\bibitem[\protect\citeauthoryear{Leigh et al.}{2012}]{leigh12} Leigh N. W. C., Umbreit S.,
Sills A., Knigge C., De Marchi G., Glebbeek E., Sarajedini A. 2012, MNRAS, 422, 1592
\bibitem[\protect\citeauthoryear{Leigh et al.}{2013}]{leigh13} Leigh N. W. C., Knigge C.,
Sills A., Perets H. B., Sarajedini A., Glebbeek E. 2013, MNRAS, 428, 897
%\bibitem[\protect\citeauthoryear{Leigh et al.}{2014}]{leigh14} Leigh N. W. C., L\"utzgendorf N., 
%Geller A. M., Maccarone T. J., Heinke C., Sesana A. 2014, MNRAS, 444, 29
%\bibitem[\protect\citeauthoryear{Leigh et al.}{2016a}]{leigh16a} Leigh N. W. C., Antonini F., Stone N. C., Shara M. M., Merritt D. 2016a, MNRAS, 463, 1605
%\bibitem[\protect\citeauthoryear{Leigh et al.}{2016b}]{leigh16b} Leigh N. W. C., Stone N. C., Geller A. M., Shara M. M., Muddu H., Solano-Oropeza D., Thomas Y. 2016b, MNRAS, 463, 3311 
%\bibitem[\protect\citeauthoryear{Leigh et al.}{2016c}]{leigh16c} Leigh N. W. C., Geller A. M., Toonen S. 2016c, ApJ, 818, 21
%\bibitem[\protect\citeauthoryear{Leigh et al.}{2016d}]{leigh16d} Leigh N. W. C., Shara M. M., Geller A. M. 2016d, MNRAS, 459, 1242
\bibitem[\protect\citeauthoryear{Leonard}{1989}]{leonard89} Leonard
  P. J. T. 1989, AJ, 98, 217
%\bibitem[\protect\citeauthoryear{Leonard \& Linnell}{1992}]{leonard92}
%  Leonard P. J. T., Linnell A. P. 1992, AJ, 103, 1928
%\bibitem[\protect\citeauthoryear{Leonard \& Livio}{1995}]{leonard95} Leonard P. J. T., Livio M. 1995,
%  ApJ, 447, L121
%\bibitem[\protect\citeauthoryear{Lim, Diaz \& Laidler}{2015}]{lim15} Lim P. L., Diaz R. L., Laidler V. 2015, PySynphot User's Guide (Baltimore, MD: STScI)
%\bibitem[\protect\citeauthoryear{Lovisi et al.}{2012}]{lovisi12} Lovisi L., Mucciarelli A., Lanzoni B., Ferraro F. R., Gratton R., Dalessandro E., Contreras R. R. 2012, ApJ, 754, 91
\bibitem[\protect\citeauthoryear{Maeder}{2009}]{maeder09} Maeder A. 2009, 
Physics, Formation and Evolution of Rotating Stars. Berlin: Springer-Verlag
\bibitem[\protect\citeauthoryear{Mardling \& Aarseth}{1999}]{mardling99} Mardling R. A., Aarseth S. J. 1999, ASIC, 522, 385  
%\bibitem[\protect\citeauthoryear{Mapelli et al.}{2006}]{mapelli06}
%  Mapelli M., Sigurdsson S., Ferraro F. R., Colpi M., Possenti A., Lanzoni B. 2006,
%  MNRAS, 373, 361
\bibitem[\protect\citeauthoryear{Mathieu \& Geller}{2009}]{mathieu09}
  Mathieu R. D., Geller A. R. 2009, Nature, 462, 1032
\bibitem[\protect\citeauthoryear{McCrea}{1964}]{mccrea64} McCrea
  W. H. 1964, MNRAS, 128, 147
%\bibitem[\protect\citeauthoryear{Milone et al.}{2008}]{milone08}
%  Milone A. P., Piotto G., Bedin L. R., Sarajedini A. 2008, MmSAI, 79,
%  623
%\bibitem[\protect\citeauthoryear{Milone et al.}{2012}]{milone12} Milone A. P., Piotto G.,
%Bedin L. R., Aparicio A., Anderson J., Sarajedini A., Marino A. F., Moretti A.,
%Davies M. B., Chaboyer B., Dotter A., Hempel M., Marin-Franch A., Majewski S.,
%Paust N. E. Q., Reid I. N., Rosenberg A., Siegel M. 2012, A\&A, 540, 16
\bibitem[\protect\citeauthoryear{Perets \& Fabrycky}{2009}]{perets09} Perets H. B., Fabrycky D. C. 2009, ApJ, 697, 1048
%\bibitem[\protect\citeauthoryear{Pickles}{1998}]{pickles98} Pickles A. J. 1998, PASP, 110, 863
\bibitem[\protect\citeauthoryear{Piotto et al.}{2004}]{piotto04}
  Piotto G., De Angeli F., King I. R., Djorgovski S. G., Bono G.,
  Cassisi S., Meylan G., Recio-Blanco A., Rich R. M., Davies M. B. 2004,
  ApJ, 604, L109
%\bibitem[\protect\citeauthoryear{Piotto et al.}{2007}]{piotto07}
%Piotto G., Bedin L. R., Anderson J., King I. R., Cassisi S., Milone A. P., Villanova S., Pietrinferni A., Renzini A. 2007, ApJ, 661, L53
%\bibitem[\protect\citeauthoryear{Piotto et al.}{2015}]{piotto15}
%  Piotto G., Milone A. P., Bedin L. R., Anderson J., King I. R., Marino A. F., Nardiello D., Aparicio A., Barbuy B., Bellini A., Brown T. M., Cassisi S., Cool A. M., Cunial A., Dalessandro E., D'Antona F., Ferraro F. R., Hidalgo S., Lanzoni B., Monelli M., Ortolani S., Renzini A., Sarajedini A., van der Marel R. P., Vesperini E., Zoccali M. 2015, AJ, 149, 91
%\bibitem[\protect\citeauthoryear{Raghavan et al.}{2010}]{raghavan10} Raghavan D., McAlister H. A., Henry T. J, et al. 2010, ApJS, 190, 1 
\bibitem[\protect\citeauthoryear{Sandquist et al.}{2003}]{sandquist03} Sandquist E. L., Latham D. W., Shetrone M. D., Milone A. A. E. 2003, AJ, 125, 810
%\bibitem[\protect\citeauthoryear{Sarajedini et al.}{2007}]{sarajedini07}
%  Sarajedini A., Bedin L. R., Chaboyer B., Dotter  A., Siegel M.,
%  Anderson J., Aparicio A., King I., Majewski S., Marin-Franch A.,
%  Piotto G., Reid  I. N., Rosenberg A., Steven M. 2007, AJ, 133, 1658
%\bibitem[\protect\citeauthoryear{Sigurdsson \& Phinney}{1993}]{sigurdsson93} Sigurdsson S. \& Phinney S.L. 1993, ApJ, 415, 631 
%\bibitem[\protect\citeauthoryear{Shara et al.}{1995}]{shara95} Shara
%  M. M., Drissen L., Bergeron L. E.,  Paresce F. 1995, ApJ, 441, 617
\bibitem[\protect\citeauthoryear{Shara, Saffer \&
    Livio}{1997}]{shara97} Shara M. M., Saffer R. A., Livio M. 1997,
  ApJ, 489, L59
\bibitem[\protect\citeauthoryear{Sills et al.}{1997}]{sills97} Sills A., Lombardi J. C. Jr.,
Bailyn C. D., Demarque P., Rasio F. A., Shapiro S. L. 1997, ApJ, 487, 290
\bibitem[\protect\citeauthoryear{Sills \& Bailyn}{1999}]{sills99} Sills A., Bailyn C. D. 1999,
  ApJ, 513, 428
\bibitem[\protect\citeauthoryear{Sills et al.}{2001}]{sills01} Sills A. R., Faber J. A.,
  Lombardi J. C., Rasio F. A., Waren A. R. 2001, ApJ, 548, 323
\bibitem[\protect\citeauthoryear{Simunovic, Puzia \& Sills}{2014}]{simunovic14} Simunovic, M., Puzia, T. H., Sills, A. 2014, ApJL, 795, L10
\bibitem[\protect\citeauthoryear{Simunovic \& Puzia}{2016}]{simunovic16} Simunovic M., Puzia T. H. 2016, MNRAS 462, 3401
%\bibitem[\protect\citeauthoryear{Sirianni et al.}{2005}]{sirianni05} Sirianni M., Jee M. J., Benitez N., Blakeslee J. P., Martel A. R., Meurer G., Clampin M., De Marchi G., Ford H. C., Gilliland R., Hartig G. F., Illingworth G. D., Mack J., McCann W. J. 2005, PASP, 117, 1049
%\bibitem[\protect\citeauthoryear{Sollima et al.}{2007}]{sollima07}
%  Sollima A., Beccari G., Ferraro F. R., Fusi Pecci F., Sarajedini
%  A. 2008, MNRAS, 380, 781
%\bibitem[\protect\citeauthoryear{Sollima et al.}{2008}]{sollima08}
%  Sollima A., Beccari G., Ferraro F. R., Fusi Pecci F., Sarajedini
%  A. 2007, A\&A, 481, 701
%\bibitem[\protect\citeauthoryear{Soto et al.}{2017}]{soto17} Soto M., Belloni A., Anderson J., Piotto G., Bedin L. R., van der Marel R. P., Milone A. P., Brown T. M., Cool A. M., King I. R., Sarajedini A., Granata V., Cassisi S., Aparicio A., Hidalgo S., Ortolani S., Nardiello D. 2017, AJ, 153, 19
%\bibitem[\protect\citeauthoryear{Spitzer}{1969}]{spitzer69} Spitzer
%  L. Jr. 1969, ApJ, 168, L139
%\bibitem[\protect\citeauthoryear{Spitzer}{1987}]{spitzer87} Spitzer L. 1987, Dynamical Evolution of Globular Clusters (Princeton: Princeton University Press)
%\bibitem[\protect\citeauthoryear{Tout et al.}{1996}]{tout96} Tout C. A., Pols O. R., Eggleton P. P., Han Z. 1996, MNRAS, 281, 257
\bibitem[\protect\citeauthoryear{van den Berg et al.}{2001}]{vandenberg01} van den Berg M., Orosz J., Verbunt F., Stassun K. 2001, A\&A, 375, 375

\end{thebibliography}

\end{document}

### 2018-12-02 mn.tex
Add files via upload

--- 2018-12-02 apjl.tex
@@
-%%
-%% Beginning of file 'sample62.tex'
-%%
-%% Modified 2018 January
-%%
-%% This is a sample manuscript marked up using the
-%% AASTeX v6.2 LaTeX 2e macros.
-%%
-%% AASTeX is now based on Alexey Vikhlinin's emulateapj.cls 
-%% (Copyright 2000-2015).  See the classfile for details.
+%mm4 comments/revisions on v8 labeled with %mm4
+%mm5 revisions on v10 labeled with %mm5
+%
+\documentclass[useAMS,usenatbib]{mnras}
+\topmargin -1cm
+\usepackage{graphicx}
+\usepackage{textcomp}
+\usepackage{amssymb}\usepackage{hyperref}
+\usepackage{amsmath,alltt}                                                                                                                     
+\usepackage{multirow}
+\usepackage{rotating}
+\usepackage{lscape}
+\usepackage{times}
+\usepackage{hyperref}
+\usepackage{pdflscape}
+\usepackage{supertabular}
 
-%% AASTeX requires revtex4-1.cls (http://publish.aps.org/revtex4/) and
-%% other external packages (latexsym, graphicx, amssymb, longtable, and epsf).
-%% All of these external packages should already be present in the modern TeX 
-%% distributions.  If not they can also be obtained at www.ctan.org.
+%%%%% AUTHORS - PLACE YOUR OWN MACROS HERE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%% The first piece of markup in an AASTeX v6.x document is the \documentclass
-%% command. LaTeX will ignore any data that comes before this command. The 
-%% documentclass can take an optional argument to modify the output style.
-%% The command below calls the preprint style  which will produce a tightly 
-%% typeset, one-column, single-spaced document.  It is the default and thus
-%% does not need to be explicitly stated.
-%%
-%%
-%% using aastex version 6.2
-\documentclass{aastex62}
+\newcommand\lsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
+        \raise1pt\hbox{$<$}}}
+\newcommand\gsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
+        \raise1pt\hbox{$>$}}}
+\newcommand{\be}{\begin{equation}}
+\newcommand{\ba}{\begin{eqnarray}}
+%\newcommand{\baa}{\begin{align}}
+\newcommand{\ee}{\end{equation}}
+\newcommand{\ea}{\end{eqnarray}}
+%\newcommand{\eaa}{\end{align}}
 
-%% The default is a single spaced, 10 point font, single spaced article.
-%% There are 5 other style options available via an optional argument. They
-%% can be envoked like this:
-%%
-%% \documentclass[argument]{aastex62}
-%% 
-%% where the layout options are:
-%%
-%%  twocolumn   : two text columns, 10 point font, single spaced article.
-%%                This is the most compact and represent the final published
-%%                derived PDF copy of the accepted manuscript from the publisher
-%%  manuscript  : one text column, 12 point font, double spaced article.
-%%  preprint    : one text column, 12 point font, single spaced article.  
-%%  preprint2   : two text columns, 12 point font, single spaced article.
-%%  modern      : a stylish, single text column, 12 point font, article with
-%% 		  wider left and right margins. This uses the Daniel
-%% 		  Foreman-Mackey and David Hogg design.
-%%  RNAAS       : Preferred style for Research Notes which are by design 
-%%                lacking an abstract and brief. DO NOT use \begin{abstract}
-%%                and \end{abstract} with this style.
-%%
-%% Note that you can submit to the AAS Journals in any of these 6 styles.
-%%
-%% There are other optional arguments one can envoke to allow other stylistic
-%% actions. The available options are:
-%%
-%%  astrosymb    : Loads Astrosymb font and define \astrocommands. 
-%%  tighten      : Makes baselineskip slightly smaller, only works with 
-%%                 the twocolumn substyle.
-%%  times        : uses times font instead of the default
-%%  linenumbers  : turn on lineno package.
-%%  trackchanges : required to see the revision mark up and print its output
-%%  longauthor   : Do not use the more compressed footnote style (default) for 
-%%                 the author/collaboration/affiliations. Instead print all
-%%                 affiliation information after each name. Creates a much
-%%                 long author list but may be desirable for short author papers
-%%
-%% these can be used in any combination, e.g.
-%%
-%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex62}
-%%
-%% AASTeX v6.* now includes \hyperref support. While we have built in specific
-%% defaults into the classfile you can manually override them with the
-%% \hypersetup command. For example,
-%%
-%%\hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
-%%
-%% will change the color of the internal links to red, the links to the
-%% bibliography to green, the file links to cyan, and the external links to
-%% magenta. Additional information on \hyperref options can be found here:
-%% https://www.tug.org/applications/hyperref/manual.html#x1-40003
-%%
-%% If you want to create your own macros, you can do so
-%% using \newcommand. Your macros should appear before
-%% the \begin{document} command.
-%%
-\newcommand{\vdag}{(v)^\dagger}
-\newcommand\aastex{AAS\TeX}
-\newcommand\latex{La\TeX}
+%\newcommand{\mnras}{\textrm{MNRAS}}
+%\newcommand{\apj}{\textrm{ApJ}}
+%\newcommand{\aap}{\textrm{A\&A}}
+%\newcommand{\apjl}{\textrm{ApJ}}
+%\newcommand{\prd}{\textrm{Phys Rev D}}
 
-%% Reintroduced the \received and \accepted commands from AASTeX v5.2
-\received{January 1, 2018}
-\revised{January 7, 2018}
-\accepted{\today}
-%% Command to document which AAS Journal the manuscript was submitted to.
-%% Adds "Submitted to " the arguement.
-\submitjournal{ApJ}
-
-%% Mark up commands to limit the number of authors on the front page.
-%% Note that in AASTeX v6.2 a \collaboration call (see below) counts as
-%% an author in this case.
-%
-%\AuthorCollaborationLimit=3
-%
-%% Will only show Schwarz, Muench and "the AAS Journals Data Scientist 
-%% collaboration" on the front page of this example manuscript.
-%%
-%% Note that all of the author will be shown in the published article.
-%% This feature is meant to be used prior to acceptance to make the
-%% front end of a long author article more manageable. Please do not use
-%% this functionality for manuscripts with less than 20 authors. Conversely,
-%% please do use this when the number of authors exceeds 40.
-%%
-%% Use \allauthors at the manuscript end to show the full author list.
-%% This command should only be used with \AuthorCollaborationLimit is used.
-
-%% The following command can be used to set the latex table counters.  It
-%% is needed in this document because it uses a mix of latex tabular and
-%% AASTeX deluxetables.  In general it should not be needed.
-%\setcounter{table}{1}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%
-%% The following section outlines numerous optional output that
-%% can be displayed in the front matter or as running meta-data.
-%%
-%% If you wish, you may supply running head information, although
-%% this information may be modified by the editorial offices.
-\shorttitle{Compact Binaries of BS Twins from Stellar Triples}
-\shortauthors{Leigh \& Portegies Zwart}
-%%
-%% You can add a light gray and diagonal water-mark to the first page 
-%% with this command:
-% \watermark{text}
-%% where "text", e.g. DRAFT, is the text to appear.  If the text is 
-%% long you can control the water-mark size with:
-%  \setwatermarkfontsize{dimension}
-%% where dimension is any recognized LaTeX dimension, e.g. pt, in, etc.
-%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% This is the end of the preamble.  Indicate the beginning of the
-%% manuscript itself with \begin{document}.
-
-\begin{document}
-
-\title{A Triple Origin for Twin Blue Stragglers in Compact Binaries}
-
-%% LaTeX will automatically break titles if they run longer than
-%% one line. However, you may use \\ to force a line break if
-%% you desire. In v6.2 you can include a footnote in the title.
-
-%% A significant change from earlier AASTEX versions is in the structure for 
-%% calling author and affilations. The change was necessary to implement 
-%% autoindexing of affilations which prior was a manual process that could 
-%% easily be tedious in large author manuscripts.
-%%
-%% The \author command is the same as before except it now takes an optional
-%% arguement which is the 16 digit ORCID. The syntax is:
-%% \author[xxxx-xxxx-xxxx-xxxx]{Author Name}
-%%
-%% This will hyperlink the author name to the author's ORCID page. Note that
-%% during compilation, LaTeX will do some limited checking of the format of
-%% the ID to make sure it is valid.
-%%
-%% Use \affiliation for affiliation information. The old \affil is now aliased
-%% to \affiliation. AASTeX v6.2 will automatically index these in the header.
-%% When a duplicate is found its index will be the same as its previous entry.
-%%
-%% Note that \altaffilmark and \altaffiltext have been removed and thus 
-%% can not be used to document secondary affiliations. If they are used latex
-%% will issue a specific error message and quit. Please use multiple 
-%% \affiliation calls for to document more than one affiliation.
-%%
-%% The new \altaffiliation can be used to indicate some secondary information
-%% such as fellowships. This command produces a non-numeric footnote that is
-%% set away from the numeric \affiliation footnotes.  NOTE that if an
-%% \altaffiliation command is used it must come BEFORE the \affiliation call,
-%% right after the \author command, in order to place the footnotes in
-%% the proper location.
-%%
-%% Use \email to set provide email addresses. Each \email will appear on its
-%% own line so you can put multiple email address in one \email call. A new
-%% \correspondingauthor command is available in V6.2 to identify the
-%% corresponding author of the manuscript. It is the author's responsibility
-%% to make sure this name is also in the author list.
-%%
-%% While authors can be grouped inside the same \author and \affiliation
-%% commands it is better to have a single author for each. This allows for
-%% one to exploit all the new benefits and should make book-keeping easier.
-%%
-%% If done correctly the peer review system will be able to
-%% automatically put the author and affiliation information from the manuscript
-%% and save the corresponding author the trouble of entering it by hand.
-
-\correspondingauthor{Nathan W. C. Leigh}
-\email{nleigh@amnh.org}
-
-\author{Nathan W. C. Leigh}
-\affil{American Museum of Natural History \\
-Department of Astrophysics \\
-79th Street at Central Park West \\
-New York, NY 10024-5192, USA}
-\affil{Stony Brook University \\
-Department of Physics and Astronomy\\
-Stony Brook, NY 11794-3800, USA}
-\affil{Departamento de Astronom\'ia \\ 
-Facultad de Ciencias F\'isicas y Matem\'aticas \\ 
-Universidad de Concepci\'on \\ 
-Concepci\'on, Chile}
-
-\author{Simon Portegies Zwart}
-\affiliation{Leiden Observatory \\
-Leiden University \\
-PO Box 9513, 2300 RA \\
-Leiden, the Netherlands}
-
-%% Note that the \and command from previous versions of AASTeX is now
-%% depreciated in this version as it is no longer necessary. AASTeX 
-%% automatically takes care of all commas and "and"s between authors names.
-
-%% AASTeX 6.2 has the new \collaboration and \nocollaboration commands to
-%% provide the collaboration status of a group of authors. These commands 
-%% can be used either before or after the list of corresponding authors. The
-%% argument for \collaboration is the collaboration identifier. Authors are
-%% encouraged to surround collaboration identifiers with ()s. The 
-%% \nocollaboration command takes no argument and exists to indicate that
-%% the nearby authors are not part of surrounding collaborations.
+\newcommand{\comment}{\bf}
+\newcommand{\pont}{{\,^\ast\!}R\,R}
+\newcommand{\red}{\color{red}}
+\newcommand{\blue}{\color{blue}}
+\newcommand{\green}{\color{green}}
+\newcommand{\black}{\color{black}}
+\newcommand{\Scri}{{\mathcal I}}
+\newcommand{\re}{{\textrm{real}}}
+\newcommand{\eff}{{\textrm{eff}}}
+\newcommand{\p}{{\textrm{pole}}}
+\newcommand{\lf}{{\textrm{log-fac}}}
+\newcommand{\SMBH}{\bullet}
+\newcommand{\SCO}{\star}
+\newcommand{\GW}{{\mbox{\tiny GW}}}
+\newcommand{\vac}{{\mbox{\tiny vac}}}
+\newcommand{\SPA}{{\mbox{\tiny SPA}}}
+\newcommand{\Tot}{{\mbox{\tiny tot}}}
+\newcommand{\Bondi}{{\mbox{\tiny Bondi}}}
+\newcommand{\Ho}{{\mbox{\tiny Hor}}}
+\newcommand{\Pa}{{\mbox{\tiny Pade}}}
+\newcommand{\pd}{{\mbox{\tiny PD}}}
+\newcommand{\Newt}{{\mbox{\tiny Newt}}}
+\newcommand{\Pert}{{\mbox{\tiny Pert}}}
+\newcommand{\Ta}{{\mbox{\tiny Tay.}}}
+\newcommand{\lfac}{{\mbox{\tiny log-fac}}}
+\newcommand{\NS}{{\mbox{\tiny NS}}}
+\newcommand{\Edd}{{\mbox{\tiny Edd}}}
+\newcommand{\Sp}{{\mbox{\tiny S}}}
+\newcommand{\ISCO}{{\mbox{\tiny ISCO}}}
+\newcommand{\initial}{{\mbox{\tiny Initial}}}
+\newcommand{\final}{{\mbox{\tiny Final}}}
+\newcommand{\mock}{{\mbox{\tiny mock}}}
+\newcommand{\ny}[1]{\textcolor{red}{\it{\textbf{ny: #1}}} }
+\newcommand{\sah}[1]{\textcolor{magenta}{\it{\textbf{sah: #1}}} }
+\newcommand{\bk}[1]{\textcolor{blue}{\it{\textbf{bk: #1}}} }
+\newcommand{\OrbitalFreq}{\Omega}
+\newcommand{\Sm}{{\mbox{\tiny S}}}
+\newcommand{\La}{{\mbox{\tiny L}}}
+\newcommand{\EOB}{{\mbox{\tiny EOB}}}
+\newcommand{\Msun}{\,{\rm M_\odot}}
+\newcommand{\yr}{\,{\rm yr}}
+\newcommand{\cm}{\,{\rm cm}}
+\newcommand{\gm}{\,{\rm g}}
+\newcommand{\I}{\mathcal{J}}
+\newcommand{\D}{\mathrm{d}}
+\newcommand{\orb}{\mathrm{orb}}
+\newcommand{\R}{{\bar{r}}}
+\newcommand{\Ls}{\ell}
+\newcommand{\gas}{\mathrm{gas}}
+\newcommand{\gap}{\mathrm{gap}}
+\newcommand{\dL}{d_{\rm L}}
 
@@
 
+\title[Compact Binaries of BS Twins from Stellar Triples]{A Triple Origin for Twin Blue Stragglers in Compact Binaries}
+
+\author[N. W. C. Leigh \& S. Portegies Zwart]{N. W. C. Leigh$^{1,2,3}$, S. Portegies Zwart$^{4}$ \\
+$^{1}$Department of Astrophysics, American Museum of Natural History, New York, NY 10024, USA\\
+$^{2}$Department of Physics and Astronomy, Stony Brook University, Stony Brook, NY 11794-3800, USA\\
+$^{3}$Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Avenue, New York, NY 10010, USA\\
+$^{4}$Leiden Observatory, }
+
+\begin{document}
+
+\date{Accepted. Received; in original form}
+
+\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2008}
+
+\maketitle
+
+\label{firstpage}
+
 \begin{abstract}
@@
 We apply our hypothetical scenario to the observed double blue straggler system Binary 7782 in the old open cluster NGC 188, and show that its observed properties are easily and even naturally reproduced within the context our proposed model.
-Within the context of the hypothetical formation mechanism proposed here, the presented work predicts the following properties for the post-mass transfer double BS tertiary:  (1)  For the outer tertiary orbit, the orbital period should lie between 220 days $\lesssim$ P$_{\rm out}$ $\lesssim$ 1100 days, assuming initial masses for the inner binary components of m$_{\rm 1} =$ 1.1 M$_{\odot}$ and m$_{\rm 2} =$ 0.9 M$_{\odot}$ and an outer tertiary mass of m$_{\rm 3} =$ 1.4 M$_{\odot}$.
+Within the context of the hypothetical formation mechanism proposed here, the presented work predicts the following properties for the post-mass transfer double BS tertiary:  (1)  For the outer tertiary orbit, the semi-major axis should lie between 2 AU $\lesssim$ a$_{\rm out}$ $\lesssim$ 5 AU, assuming initial masses for the inner binary components of m$_{\rm 1} =$ 1.1 M$_{\odot}$ and m$_{\rm 2} =$ 0.9 M$_{\odot}$ and an outer tertiary mass of m$_{\rm 3} =$ 1.4 M$_{\odot}$.
 (2)  Larger final WD masses, and hence core masses for the donor at the time of mass transfer, should correspond to larger final outer orbital periods for the tertiary.
@@
 
-\keywords{stars: blue stragglers -- binaries: general -- globular clusters: general -- scattering}
+\begin{keywords}
+stars: blue stragglers -- binaries: general -- globular clusters: general -- scattering. 
+\end{keywords}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction} \label{intro}
+\section{Introduction}
 
-Blue straggler (BS) stars appear brighter and bluer than the main-sequence turn-off (MSTO) in a cluster colour-magnitude diagram (CMD) \citep[e.g.][]{simunovic14,simunovic16}.
-Two primary channels for BS formation have been proposed; mass transfer from an evolved donor on to a main-sequence star in a binary star system \citep[e.g.][]{mccrea64,knigge09,mathieu09,leigh11,geller11,geller12,gosnell14,gosnell15}, and direct stellar collisions involving main-sequence stars mediated via direct interactions involving binaries \citep[e.g.][]{hills75,shara97,leigh07,leigh11,leigh13,hypki13}.
+Blue straggler (BS) stars appear brighter and bluer than the main-sequence turn-off (MSTO) in a cluster colour-magnitude diagram (CMD).
+Two primary channels for BS formation have been proposed; mass transfer from an evolved donor on to a main-sequence star in a binary star system \citep[e.g.][]{mccrea64,knigge09,leigh11,gosnell14,gosnell15}, and direct stellar collisions involving main-sequence stars mediated via direct interactions involving binaries \citep[e.g.][]{hills75,shara97,leigh13,hypki13}.
 Other possible, albeit related, formation mechanisms include mergers of compact MS-MS binaries, and mergers of the inner MS-MS binaries of hierarchical triple star systems induced by Lidov-Kozai oscillations coupled with tidal damping \citep[e.g.][]{perets09}.
@@
 
-Figure~\ref{fig:fig1} shows the parameter space in the P$_{\rm out}$-P$_{\rm in}$-plane for Binary 7782.
-We assume initial component masses of m$_{\rm 1} =$ 1.1 M$_{\rm \odot}$ and m$_{\rm 2} =$ 0.9 M$_{\rm \odot}$ for the inner binary components, and m$_{\rm 3} =$ 1.4 M$_{\rm \odot}$ for the outer tertiary.
-We compare the circularization radius to the semi-major axis of the inner binary, for which we require a$_{\rm c} >$ a$_{\rm in}$, after folding in all constraints from the requirements for dynamical stability, an outer tertiary that is Roche lobe-filling, and a dynamically hard outer tertiary orbit.
-Note that the range of plotted orbital periods P$_{\rm in}$ corresponding to a contact state for the inner binary, assuming R$_{\rm 1} =$ R$_{\rm 2} =$ 1 R$_{\odot}$, lies outside the range of plotted values for P$_{\rm in}$, since it does not contribute significantly to constraining the outer orbital properties of a hypothesized outer WD tertiary.
-The thick horizontal solid red line shows the allowed range of outer semi-major axes, after folding in all of the aforementioned criteria.
-As is clear, this makes a relatively narrow prediction for the allowed ranges of outer tertiary orbits, namely 2.2 $\times$ 10$^{2}$ days $\le$ P$_{\rm out}$ $\le$ 1.1 $\times$ 10$^3$ days, for our assumed final donor mass.
+Figure~\ref{fig:fig1} shows the parameter space in the a$_{\rm out}$-a$_{\rm in}$-plane for Binary 7782.
+We assume initial component masses of m$_{\rm 1}$ = 1.1 M$_{\rm \odot}$ and m$_{\rm 2}$ = 0.9 M$_{\rm \odot}$ for the inner binary components, and m$_{\rm 3}$ = 1.4 M$_{\rm \odot}$ for the outer tertiary.
+This choice is guided by the current turn-off mass of 1.1 M$_{\odot}$ in NGC 188 \citep{mathieu09} and a maximum BS age of a few Gyr \citep[e.g.][]{sills99,sills01}.
+After comparing the circularization radius to the semi-major axis of the inner binary and folding in all constraints from the requirements for dynamical stability, an outer tertiary that is Roche lobe-filling, and a dynamically hard outer tertiary orbit.
+The thick horizontal solid red line shows the allowed range of outer semi-major axes allowed, after folding in all of the aforementioned criteria.
+As is clear, this makes a relatively narrow prediction for the allowed ranges of outer tertiary orbits, namely 2 AU $\le$ a$_{\rm out} \le$ 5 AU.
 
-\begin{figure}[ht!]
-\plotone{fig1.eps}
-\caption{Parameter space in the P$_{\rm out}$-P$_{\rm in}$-plane allowed for the hypothetical outer tertiary orbit of Binary 7782.
-The solid diagonal black lines show the period corresponding to the circularization radius a$_{\rm c}$ for the mass transfer stream coming from the outer tertiary, for different values of the mass ratio, namely q $=$ 0.1, 0.7, 1, 2 and 10.
-We assume initial component masses of m$_{\rm 1}$ = 1.1 M$_{\rm \odot}$ and m$_{\rm 2}$ = 0.9 M$_{\rm \odot}$ for the inner binary components, and m$_{\rm 3}$ is computed for the outer tertiary according to our assumed mass ratio (with our fiducial case corresponding to q $=$ 0.7.
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{fig1.eps}
+\end{center}
+\caption[Parameter space in the a$_{\rm out}$-a$_{\rm in}$-plane allowed for the hypothetical outer tertiary orbit of Binary 7782.]{Parameter space in the a$_{\rm out}$-a$_{\rm in}$-plane allowed for the hypothetical outer tertiary orbit of Binary 7782.
+The solid diagonal black lines show the circularization radius a$_{\rm c}$ for the mass transfer stream coming from the outer tertiary, for different values of the mas ratio, namely q $=$ 0.1, 0.5, 1, 2 and 10.
+We assume initial component masses of m$_{\rm 1}$ = 1.1 M$_{\rm \odot}$ and m$_{\rm 2}$ = 0.9 M$_{\rm \odot}$ for the inner binary components, and m$_{\rm 3}$ = 1.4 M$_{\rm \odot}$ for the outer tertiary.
 We assume completely conservative mass transfer for this exercise, and a final mass for the outer tertiary of 0.6 M$_{\rm \odot}$ once it has become a WD.
-The dashed diagonal black line shows a rough criterion for dynamical stability in the triple, approximately following \citet{mardling99} (i.e., a$_{\rm in} <$ 0.1a$_{\rm out}$ is required for long-term dynamical stability in equal-mass co-planar triples).
-The vertical solid red lines show the outer orbital periods corresponding to the hard-soft boundary assuming central velocity dispersions of $\sigma =$ 1, 5 and 10 km s$^{-1}$.
-The vertical dashed black lines show the maximum outer orbital period P$_{\rm out}$ for which the outer tertiary companion is Roche lobe-filling, assuming a stellar radius of R$_{\rm 3} =$ 200 R$_{\odot}$ (CHANGE, POSSIBLY USING MESA CALCULATIONS?!).
-The horizontal dashed red line shows the observed orbital period for Binary 7782, using its observed orbital period and our assumed final inner companion masses (i.e., m$_{\rm 1} =$ m$_{\rm 2} =$ 1.4 M$_{\odot}$).
-Finally, the thick solid horizontal red line shows the parameter space for P$_{\rm out}$ allowed after considering all of the aforementioned criteria.
+The dashed diagonal black line shows a rough criterion for dynamical stability in the triple, roughly following \citet{mardling99} (i.e., a$_{\rm in} <$ 0.1a$_{\rm out}$ is required).
+The vertical solid red lines show the outer semi-major axes corresponding to the hard-soft boundary assuming central velocity dispersions of $\sigma =$ 1, 5 and 10 km s$^{-1}$.
+The vertical dashed black lines show the maximum outer semi-major axis a$_{\rm out}$ for which the outer tertiary companion is Roche lobe-filling, assuming a stellar radius of R$_{\rm 3} =$ 200 R$_{\odot}$ (CHANGE).
+The horizontal solid red line shows the semi-major axis corresponding to a contact state for the inner binary, assuming R$_{\rm 1} =$ R$_{\rm 2} =$ 1 R$_{\odot}$.
+The horizontal dashed red line shows the observed semi-major axis for Binary 7782, for our assumed final inner companion masses (i.e., m$_{\rm 1} =$ m$_{\rm 2} =$ 1.4 M$_{\odot}$).
+Finally, the thick solid horizontal red line shows the parameter space for a$_{\rm out}$ allowed after considering all of the aforementioned criteria.
 \label{fig:fig1}}
@@
 
-\item For the predicted outer tertiary orbit, the present-day semi-major axis should lie between 220 days $\lesssim$ P$_{\rm out}$ $\lesssim$ 1100 days, assuming initial masses for the inner binary components of m$_{\rm 1} =$ 1.1 M$_{\odot}$ and m$_{\rm 2} =$ 0.9 M$_{\odot}$ and an outer tertiary mass of m$_{\rm 3} =$ 1.4 M$_{\odot}$.
+\item For the outer tertiary orbit, the semi-major axis should lie between 2 AU $\lesssim$ a$_{\rm out}$ $\lesssim$ 5 AU, assuming initial masses for the inner binary components of m$_{\rm 1} =$ 1.1 M$_{\odot}$ and m$_{\rm 2} =$ 0.9 M$_{\odot}$ and an outer tertiary mass of m$_{\rm 3} =$ 1.4 M$_{\odot}$.
 
@@
 
-\acknowledgments
+\section{Acknowledgments}
 
-N.W.C.L. acknowledges support from a Kalbfleisch Fellowship at the American Museum of Natural History.
+N.W.C.L.
+acknowledges support from a Kalbfleisch Fellowship at the American Museum of Natural History.
+T.H.P.
+acknowledges the support through the FONDECYT Regular Project No.
+1161817 and the BASAL Center for Astrophysics and Associated Technologies (PFB-06).
 
-\begin{thebibliography}{}
+\begin{thebibliography}{99}
 
-%\bibitem[\protect\citeauthoryear{Anderson et al.}{2008}]{anderson08}
-% Anderson J.,  Sarajedini A., Bedin L. R., King I. R., Piotto G.,
-%  Reid I. N., Siegel M., Majewski S. R., Paust N. E. Q., Aparicio A.,
-%  Milone A. P., Chaboyer B., Rosenberg A. 2008, AJ, 135, 2055
-%\bibitem[\protect\citeauthoryear{Artymowicz et al.}{1993}]{artymowicz93} Artymowicz P., Lin D. N. C., Wampler E. J. 1993, ApJ, 409, 592 
+\bibitem[\protect\citeauthoryear{Anderson et al.}{2008}]{anderson08}
+  Anderson J.,  Sarajedini A., Bedin L. R., King I. R., Piotto G.,
+  Reid I. N., Siegel M., Majewski S. R., Paust N. E. Q., Aparicio A.,
+  Milone A. P., Chaboyer B., Rosenberg A. 2008, AJ, 135, 2055
+\bibitem[\protect\citeauthoryear{Artymowicz et al.}{1993}]{artymowicz93} Artymowicz P., Lin D. N. C., Wampler E. J. 1993, ApJ, 409, 592 
 %\bibitem[\protect\citeauthoryear{Bartos et al.}{2017}]{Bartos17} Bartos I., Kocsis B., Haiman Z. \& M\'{a}rka S., 2017, ApJ, 835, 165
@@
 %\bibitem[\protect\citeauthoryear{Baruteau et al.}{2011}]{Baruteau11} Baruteau C., Cuadra J. \& Lin D.N.C., 2011, ApJ, 726, 28
-%\bibitem[\protect\citeauthoryear{Bedin et al.}{2010}]{bedin10} Bedin L. R., Cassisi S., Castelli F., Piotto G., Anderson J., Salaris M., Momany Y., Pietrinferni A. 2010, MNRAS 357, 1038
+\bibitem[\protect\citeauthoryear{Bedin et al.}{2010}]{bedin10} Bedin L. R., Cassisi S., Castelli F., Piotto G., Anderson J., Salaris M., Momany Y., Pietrinferni A. 2010, MNRAS 357, 1038
 %\bibitem[\protect\citeauthoryear{Bender et al.}{2005}]{bender05} Bender R., Kormendy J., Bower G., et al. 2005, ApJ, 631, 280
-%\bibitem[\protect\citeauthoryear{Bruzual \& Charlot}{2003}]{bruzual03} Bruzual G., Charlot S. 2003, MNRAS, 344, 1000 
-%\bibitem[\protect\citeauthoryear{Casassus et al.}{2013}]{casassus13} Casassus S., Hales A., de Gregorio I., Dent B., Belloche A., G\"usten R., M\'enard F., Hughes A.
+\bibitem[\protect\citeauthoryear{Bruzual \& Charlot}{2003}]{bruzual03} Bruzual G., Charlot S. 2003, MNRAS, 344, 1000 
+\bibitem[\protect\citeauthoryear{Casassus et al.}{2013}]{casassus13} Casassus S., Hales A., de Gregorio I., Dent B., Belloche A., G\:usten R., M\'enard F., Hughes A.
 M., Wilner D., Salinas V.
 2013, A\&A, 553, 64
-%\bibitem[\protect\citeauthoryear{Ceillier et al.}{2017}]{ceillier17} Ceillier T., Tayar J., Mathur S., Salabert D., Garc\'ia R.
+\bibitem[\protect\citeauthoryear{Ceillier et al.}{2017}]{ceillier17} Ceillier T., Tayar J., Mathur S., Salabert D., Garc\'ia R.
 A., Stello D., Pinsonneault M.
@@
 %\bibitem[\protect\citeauthoryear{Chen \& Amaro-Seoane}{2015}]{chen15} Chen X., Amaro-Seoane P. 2015, Classical and Quantum Gravity, 32, 6 
-%\bibitem[\protect\citeauthoryear{Dotter et al.}{2010}]{dotter10} Dotter, A., Sarajedini A., Anderson J., Aparicio A., Bedin L.
+\bibitem[\protect\citeauthoryear{Dotter et al.}{2010}]{dotter10} Dotter, A., Sarajedini A., Anderson J., Aparicio A., Bedin L.
 R., Chaboyer B., Majewski S., Marin-Franch A., Milone A., Paust N., Piotto G., Reid N., Rosenberg A., Siegel M.
 2010, ApJ 708, 698
-%\bibitem[\protect\citeauthoryear{Dalessandro et al.}{2013}]{dalessandro13} Dalessandro E., Ferraro F.
+\bibitem[\protect\citeauthoryear{Dalessandro et al.}{2013}]{dalessandro13} Dalessandro E., Ferraro F.
 R., Massari D., Lanzoni B., Miocchi R.
@@
 2013, ApJ, 778, 135
-%\bibitem[\protect\citeauthoryear{Eggleton}{1983}]{eggleton83} Eggleton P. P. 1983, ApJ, 268, 368 
-%\bibitem[\protect\citeauthoryear{Flock et al.}{2015}]{flock15} Flock M., Ruge J. P., Dzyurkevich N., Henning Th., Klahr H., Wolf S. 2015, A\&A, 574, 68
-%\bibitem[\protect\citeauthoryear{Ferraro et al.}{1997}]{ferraro97}
-%  Ferraro F. R., Paltrinieri B., Fusi Pecci F., Cacciari C., Dorman
-%  B., Rood R. T., Buonanno R., Corsi C. E., Burgarella D., Laget
-%  M. 1997, A\&A, 324, 915
-%\bibitem[\protect\citeauthoryear{Ferraro et al.}{1999}]{ferraro99}
-%  Ferraro F. R., Paltrinieri B., Rood R. T., Dorman B. 1999, ApJ, 522,
-%  983
-%\bibitem[\protect\citeauthoryear{Ferraro et al.}{2004}]{ferraro04}
-%  Ferraro F. R., Beccari G., Rood, R. T., Bellazzini M., Sills A.,
-%  Sabbi E. 2004, ApJ, 603, 127
-%\bibitem[\protect\citeauthoryear{Ferraro, Valenti \& Origlia}{2006}]{ferraro06} Ferraro F. R., Valenti E., Origlia L. 2006, ApJ, 649, 243
-%\bibitem[\protect\citeauthoryear{Ferraro et al.}{2009}]{ferraro09} Ferraro F.
+\bibitem[\protect\citeauthoryear{Eggleton}{1983}]{eggleton83} Eggleton P. P. 1983, ApJ, 268, 368 
+\bibitem[\protect\citeauthoryear{Flock et al.}{2015}]{flock15} Flock M., Ruge J. P., Dzyurkevich N., Henning Th., Klahr H., Wolf S. 2015, A\&A, 574, 68
+\bibitem[\protect\citeauthoryear{Ferraro et al.}{1997}]{ferraro97}
+  Ferraro F. R., Paltrinieri B., Fusi Pecci F., Cacciari C., Dorman
+  B., Rood R. T., Buonanno R., Corsi C. E., Burgarella D., Laget
+  M. 1997, A\&A, 324, 915
+\bibitem[\protect\citeauthoryear{Ferraro et al.}{1999}]{ferraro99}
+  Ferraro F. R., Paltrinieri B., Rood R. T., Dorman B. 1999, ApJ, 522,
+  983
+\bibitem[\protect\citeauthoryear{Ferraro et al.}{2004}]{ferraro04}
+  Ferraro F. R., Beccari G., Rood, R. T., Bellazzini M., Sills A.,
+  Sabbi E. 2004, ApJ, 603, 127
+\bibitem[\protect\citeauthoryear{Ferraro, Valenti \& Origlia}{2006}]{ferraro06} Ferraro F. R., Valenti E., Origlia L. 2006, ApJ, 649, 243
+\bibitem[\protect\citeauthoryear{Ferraro et al.}{2009}]{ferraro09} Ferraro F.
 R., Beccari G., Dalessandro E., Lanzoni B., Sills A., Rood R.
@@
 2009, Nature, 462, 1028
-%\bibitem[\protect\citeauthoryear{Fregeau et al.}{2004}]{fregeau04} Fregeau J. M., Cheung P.,
-%  Portegies Zwart S. F., Rasio F. A. 2004, MNRAS, 352, 1
-%\bibitem[\protect\citeauthoryear{Fregeau, Ivanova \& Rasio}{2009}]{fregeau09} Fregeau J. M., Ivanova N.,
-%  Rasio F. A. 2009, ApJ, 707, 1533
+\bibitem[\protect\citeauthoryear{Fregeau et al.}{2004}]{fregeau04} Fregeau J. M., Cheung P.,
+  Portegies Zwart S. F., Rasio F. A. 2004, MNRAS, 352, 1
+\bibitem[\protect\citeauthoryear{Fregeau, Ivanova \& Rasio}{2009}]{fregeau09} Fregeau J. M., Ivanova N.,
+  Rasio F. A. 2009, ApJ, 707, 1533
 %\bibitem[\protect\citeauthoryear{Geller at al.}{2009}]{geller09}
@@
 %\bibitem[\protect\citeauthoryear{Graham \& Spitler}{2009}]{Graham09} Graham A.W. \& Spitler L.R., 2009, MNRAS, 397, 2148
-%\bibitem[\protect\citeauthoryear{Harris et al.}{1996; 2010 update}]{harris96} Harris W. E. 1996, AJ, 112,
-%  1487; 2010 update
+\bibitem[\protect\citeauthoryear{Harris et al.}{1996; 2010 update}]{harris96} Harris W. E. 1996, AJ, 112,
+  1487; 2010 update
 %\bibitem[\protect\citeauthoryear{Heggie}{1975}]{heggie75} Heggie D. C. 1975, MNRAS, 173, 729
-%\bibitem[\protect\citeauthoryear{Heggie \& Hut}{2003}]{heggie03}
-%  Heggie D. C., Hut P. 2003, The Gravitational Million-Body Problem:
-%  A Multidisciplinary Approach to Sar Cluster Dynamics (Cambridge:
-%  Cambridge University Press)
+\bibitem[\protect\citeauthoryear{Heggie \& Hut}{2003}]{heggie03}
+  Heggie D. C., Hut P. 2003, The Gravitational Million-Body Problem:
+  A Multidisciplinary Approach to Sar Cluster Dynamics (Cambridge:
+  Cambridge University Press)
 \bibitem[\protect\citeauthoryear{Hills}{1975}]{hills75} Hills J. G. 1975, AJ, 80, 809
-%\bibitem[\protect\citeauthoryear{Hurley et al.}{2005}]{hurley05}
-%  Hurley J. R., Pols O. R., Aarseth S. J., Tout C. A. 2005, MNRAS,
-%  363, 293
+\bibitem[\protect\citeauthoryear{Hurley et al.}{2005}]{hurley05}
+  Hurley J. R., Pols O. R., Aarseth S. J., Tout C. A. 2005, MNRAS,
+  363, 293
 %\bibitem[\protect\citeauthoryear{Hurley, Aarseth \&
@@
 %  268, 319
-%\bibitem[\protect\citeauthoryear{Howarth}{1983}]{howarth83} Howarth I. D. 1983, MNRAS, 203, 301
+\bibitem[\protect\citeauthoryear{Howarth}{1983}]{howarth83} Howarth I. D. 1983, MNRAS, 203, 301
 \bibitem[\protect\citeauthoryear{Hypki \& Giersz}{2013}]{hypki13} Hypki A., Giersz M. 2013,
@@
   N., Sills A. 2009, Nature, 457, 288
-%\bibitem[\protect\citeauthoryear{Laidler et al.}{2008}]{laidler08} Laidler et al. 2008, ``Synphot Data User's Guide'' (Baltimore, STScI)
-%\bibitem[\protect\citeauthoryear{Lanzoni et al.}{2007}]{lanzoni07} Lanzoni B., Dalessandro E., Ferraro F.
+\bibitem[\protect\citeauthoryear{Laidler et al.}{2008}]{laidler08} Laidler et al. 2008, ``Synphot Data User's Guide'' (Baltimore, STScI)
+\bibitem[\protect\citeauthoryear{Lanzoni et al.}{2007}]{lanzoni07} Lanzoni B., Dalessandro E., Ferraro F.
 R., Valenti E., Beccari G., Schiavon R.
@@
 \bibitem[\protect\citeauthoryear{Leigh, Sills \& Knigge}{2007}]{leigh07} Leigh
-  N. W. C., Sills A., Knigge C. 2007, ApJ, 661, 210
+  N. W., Sills A., Knigge C. 2007, ApJ, 661, 210
 %\bibitem[\protect\citeauthoryear{Leigh, Sills \& Knigge}{2008}]{leigh08} Leigh
@@
 %  N. W., Sills A., Knigge C. 2009, MNRAS, 399, L179
-\bibitem[\protect\citeauthoryear{Leigh \& Sills}{2011}]{leigh11} Leigh N. W. C., Sills A. 2011, MNRAS, 410, 2370
-\bibitem[\protect\citeauthoryear{Leigh et al.}{2012}]{leigh12} Leigh N. W. C., Umbreit S.,
+\bibitem[\protect\citeauthoryear{Leigh \& Sills}{2011}]{leigh11} Leigh N., Sills A. 2011, MNRAS, 410, 2370
+\bibitem[\protect\citeauthoryear{Leigh et al.}{2012}]{leigh12} Leigh N. W., Umbreit S.,
 Sills A., Knigge C., De Marchi G., Glebbeek E., Sarajedini A. 2012, MNRAS, 422, 1592
-\bibitem[\protect\citeauthoryear{Leigh et al.}{2013}]{leigh13} Leigh N. W. C., Knigge C.,
+\bibitem[\protect\citeauthoryear{Leigh et al.}{2013}]{leigh13} Leigh N. W., Knigge C.,
 Sills A., Perets H. B., Sarajedini A., Glebbeek E. 2013, MNRAS, 428, 897
@@
 %  ApJ, 447, L121
-%\bibitem[\protect\citeauthoryear{Lim, Diaz \& Laidler}{2015}]{lim15} Lim P. L., Diaz R. L., Laidler V. 2015, PySynphot User's Guide (Baltimore, MD: STScI)
-%\bibitem[\protect\citeauthoryear{Lovisi et al.}{2012}]{lovisi12} Lovisi L., Mucciarelli A., Lanzoni B., Ferraro F. R., Gratton R., Dalessandro E., Contreras R. R. 2012, ApJ, 754, 91
+\bibitem[\protect\citeauthoryear{Lim, Diaz \& Laidler}{2015}]{lim15} Lim P. L., Diaz R. L., Laidler V. 2015, PySynphot User's Guide (Baltimore, MD: STScI)
+\bibitem[\protect\citeauthoryear{Lovisi et al.}{2012}]{lovisi12} Lovisi L., Mucciarelli A., Lanzoni B., Ferraro F. R., Gratton R., Dalessandro E., Contreras R. R. 2012, ApJ, 754, 91
 \bibitem[\protect\citeauthoryear{Maeder}{2009}]{maeder09} Maeder A. 2009, 
@@
   W. H. 1964, MNRAS, 128, 147
-%\bibitem[\protect\citeauthoryear{Milone et al.}{2008}]{milone08}
-%  Milone A. P., Piotto G., Bedin L. R., Sarajedini A. 2008, MmSAI, 79,
-%  623
-%\bibitem[\protect\citeauthoryear{Milone et al.}{2012}]{milone12} Milone A. P., Piotto G.,
-%Bedin L. R., Aparicio A., Anderson J., Sarajedini A., Marino A. F., Moretti A.,
-%Davies M. B., Chaboyer B., Dotter A., Hempel M., Marin-Franch A., Majewski S.,
-%Paust N. E. Q., Reid I. N., Rosenberg A., Siegel M. 2012, A\&A, 540, 16
+\bibitem[\protect\citeauthoryear{Milone et al.}{2008}]{milone08}
+  Milone A. P., Piotto G., Bedin L. R., Sarajedini A. 2008, MmSAI, 79,
+  623
+\bibitem[\protect\citeauthoryear{Milone et al.}{2012}]{milone12} Milone A. P., Piotto G.,
+Bedin L. R., Aparicio A., Anderson J., Sarajedini A., Marino A. F., Moretti A.,
+Davies M. B., Chaboyer B., Dotter A., Hempel M., Marin-Franch A., Majewski S.,
+Paust N. E. Q., Reid I. N., Rosenberg A., Siegel M. 2012, A\&A, 540, 16
 \bibitem[\protect\citeauthoryear{Perets \& Fabrycky}{2009}]{perets09} Perets H. B., Fabrycky D. C. 2009, ApJ, 697, 1048
-%\bibitem[\protect\citeauthoryear{Pickles}{1998}]{pickles98} Pickles A. J. 1998, PASP, 110, 863
+\bibitem[\protect\citeauthoryear{Pickles}{1998}]{pickles98} Pickles A. J. 1998, PASP, 110, 863
 \bibitem[\protect\citeauthoryear{Piotto et al.}{2004}]{piotto04}
@@
   ApJ, 604, L109
-%\bibitem[\protect\citeauthoryear{Piotto et al.}{2007}]{piotto07}
-%Piotto G., Bedin L. R., Anderson J., King I. R., Cassisi S., Milone A. P., Villanova S., Pietrinferni A., Renzini A. 2007, ApJ, 661, L53
-%\bibitem[\protect\citeauthoryear{Piotto et al.}{2015}]{piotto15}
-%  Piotto G., Milone A.
+\bibitem[\protect\citeauthoryear{Piotto et al.}{2007}]{piotto07}
+Piotto G., Bedin L. R., Anderson J., King I. R., Cassisi S., Milone A. P., Villanova S., Pietrinferni A., Renzini A. 2007, ApJ, 661, L53
+\bibitem[\protect\citeauthoryear{Piotto et al.}{2015}]{piotto15}
+  Piotto G., Milone A.
 P., Bedin L.
@@
 2015, AJ, 149, 91
-%\bibitem[\protect\citeauthoryear{Raghavan et al.}{2010}]{raghavan10} Raghavan D., McAlister H. A., Henry T. J, et al. 2010, ApJS, 190, 1 
+\bibitem[\protect\citeauthoryear{Raghavan et al.}{2010}]{raghavan10} Raghavan D., McAlister H. A., Henry T. J, et al. 2010, ApJS, 190, 1 
 \bibitem[\protect\citeauthoryear{Sandquist et al.}{2003}]{sandquist03} Sandquist E. L., Latham D. W., Shetrone M. D., Milone A. A. E. 2003, AJ, 125, 810
-%\bibitem[\protect\citeauthoryear{Sarajedini et al.}{2007}]{sarajedini07}
-%  Sarajedini A., Bedin L. R., Chaboyer B., Dotter  A., Siegel M.,
-%  Anderson J., Aparicio A., King I., Majewski S., Marin-Franch A.,
-%  Piotto G., Reid  I. N., Rosenberg A., Steven M. 2007, AJ, 133, 1658
-%\bibitem[\protect\citeauthoryear{Sigurdsson \& Phinney}{1993}]{sigurdsson93} Sigurdsson S. \& Phinney S.L. 1993, ApJ, 415, 631 
+\bibitem[\protect\citeauthoryear{Sarajedini et al.}{2007}]{sarajedini07}
+  Sarajedini A., Bedin L. R., Chaboyer B., Dotter  A., Siegel M.,
+  Anderson J., Aparicio A., King I., Majewski S., Marin-Franch A.,
+  Piotto G., Reid  I. N., Rosenberg A., Steven M. 2007, AJ, 133, 1658
+\bibitem[\protect\citeauthoryear{Sigurdsson \& Phinney}{1993}]{sigurdsson93} Sigurdsson S. \& Phinney S.L. 1993, ApJ, 415, 631 
 %\bibitem[\protect\citeauthoryear{Shara et al.}{1995}]{shara95} Shara
@@
 \bibitem[\protect\citeauthoryear{Simunovic \& Puzia}{2016}]{simunovic16} Simunovic M., Puzia T. H. 2016, MNRAS 462, 3401
-%\bibitem[\protect\citeauthoryear{Sirianni et al.}{2005}]{sirianni05} Sirianni M., Jee M.
+\bibitem[\protect\citeauthoryear{Sirianni et al.}{2005}]{sirianni05} Sirianni M., Jee M.
 J., Benitez N., Blakeslee J.
@@
 %  A. 2007, A\&A, 481, 701
-%\bibitem[\protect\citeauthoryear{Soto et al.}{2017}]{soto17} Soto M., Belloni A., Anderson J., Piotto G., Bedin L.
+\bibitem[\protect\citeauthoryear{Soto et al.}{2017}]{soto17} Soto M., Belloni A., Anderson J., Piotto G., Bedin L.
 R., van der Marel R.
@@
 %\bibitem[\protect\citeauthoryear{Spitzer}{1987}]{spitzer87} Spitzer L. 1987, Dynamical Evolution of Globular Clusters (Princeton: Princeton University Press)
-%\bibitem[\protect\citeauthoryear{Tout et al.}{1996}]{tout96} Tout C. A., Pols O. R., Eggleton P. P., Han Z. 1996, MNRAS, 281, 257
+\bibitem[\protect\citeauthoryear{Tout et al.}{1996}]{tout96} Tout C. A., Pols O. R., Eggleton P. P., Han Z. 1996, MNRAS, 281, 257
 \bibitem[\protect\citeauthoryear{van den Berg et al.}{2001}]{vandenberg01} van den Berg M., Orosz J., Verbunt F., Stassun K. 2001, A\&A, 375, 375

### 2018-12-02 apjl.tex
Add files via upload

@@
 We apply our hypothetical scenario to the observed double blue straggler system Binary 7782 in the old open cluster NGC 188, and show that its observed properties are easily and even naturally reproduced within the context our proposed model.
-Within the context of the hypothetical formation mechanism proposed here, the presented work predicts the following properties for the post-mass transfer double BS tertiary:  (1)  For the outer tertiary orbit, the orbital period should lie between 220 days $\lesssim$ P$_{\rm out}$ $\lesssim$ 1100 days, assuming initial masses for the inner binary components of m$_{\rm 1} =$ 1.1 M$_{\odot}$ and m$_{\rm 2} =$ 0.9 M$_{\odot}$ and an outer tertiary mass of m$_{\rm 3} =$ 1.4 M$_{\odot}$.
+Within the context of the hypothetical formation mechanism proposed here, the presented work predicts the following properties for the post-mass transfer double BS tertiary:  (1)  For the outer tertiary orbit, the initial orbital period should lie between 220 days $\lesssim$ P$_{\rm out}$ $\lesssim$ 1100 days, assuming initial masses for the inner binary components of m$_{\rm 1} =$ 1.1 M$_{\odot}$ and m$_{\rm 2} =$ 0.9 M$_{\odot}$ and an outer tertiary mass of m$_{\rm 3} =$ 1.4 M$_{\odot}$.
 (2)  Larger final WD masses, and hence core masses for the donor at the time of mass transfer, should correspond to larger final outer orbital periods for the tertiary.
@@
 In this Letter, we propose a potential formation channel for Binary 7782, and compact double BS binaries in general, which involves mass transfer from an outer tertiary companion on to an inner MS-MS binary.
-In section~\ref{dyn}, we constrain the range of present-day orbital parameters for a hypothetical outer tertiary companion, using a combination of dynamical and stellar evolution-based constraints.
+In section~\ref{dyn}, we constrain the range of initial (i.e., pre-mass transfer) orbital parameters for a hypothetical outer tertiary companion, using a combination of dynamical and stellar evolution-based constraints.
 In Section~\ref{sims} we present the numerical simulations used to study the mass transfer process in our hypothetical triple system, computed using the \texttt{AMUSE} software package, in order to study the evolution of the inner and outer orbital parameters during mass transfer.
@@
 The inner and outer binary orbital semi-major axes are denoted a$_{\rm in}$ and a$_{\rm out}$, respectively.
-We assume circular orbits for both the inner and outer orbits.
+We assume circular orbits for both the inner and outer orbits, and co-planar triples only since this is what has been observed for low-mass tertiaries \citep[e.g.][]{moe18,tobin18}.
 
 We consider a scenario where the outer tertiary companion is filling its Roche lobe and is hence transferring mass to the inner binary.
+The mass transfer stream gathers at the circularization radius a$_{\rm c}$, and forms a circumbinary disk.
 Using conservation of angular momentum, we can equate the specific angular momentum of the accreted mass at the inner Lagrangian point of the donor star to the final specific angular momentum of the accretion stream at the circularization radius about the inner binary:
@@
 We use smoothed-particle hydrodynamics (SPH) simulations to compute the time evolution of the mass transfer process.
+We adopt the same initial particle masses as in Figure~\ref{fig:fig1}, namely initial component masses of m$_{\rm 1}$ = 1.1 M$_{\rm \odot}$ and m$_{\rm 2}$ = 0.9 M$_{\rm \odot}$ for the inner binary components, and m$_{\rm 3}$ is computed for the outer tertiary according to our assumed mass ratio, with our fiducial case corresponding to q $=$ 0.7.
+The initial orbital eccentricities are set to zero.
+The inner and outer binary orbital semi-major axes are set to 0.1 AU and 1 AU, respectively (CORRECT).
 
@@
 \item The BSs in the inner binary should have roughly equal masses, independent of their initial masses.
-This is because it is the lowest mass object that typically accretes the fastest, since its orbital velocity and distance relative to the circumbinary disk is typically the lowest.
+This is because it is the lowest mass object that typically accretes the fastest, since its orbital velocity and distance relative to the circumbinary disk is typically the lowest \citep[e.g.][]{haiman09,farris15,rafikov16,kelley17}.
 This quickly brings the mass ratio toward unity.
@@
 \bibitem[\protect\citeauthoryear{Chatterjee et al.}{2013}]{chatterjee13} Chatterjee S., Rasio F. A., Sills A., Glebbeek E. 2013, ApJ, 777, 106  
+\bibitem[\protect\citeauthoryear{Farris et al.}{2015}]{farris15} Farris B. D., Duffell P., MacFayden A. I., Haiman Z. 2014, ApJ, 783, 134 
 %\bibitem[\protect\citeauthoryear{Chen \& Amaro-Seoane}{2015}]{chen15} Chen X., Amaro-Seoane P. 2015, Classical and Quantum Gravity, 32, 6 
@@
 \bibitem[\protect\citeauthoryear{Gosnell et al.}{2015}]{gosnell15} Gosnell N. M., Mathieu R. D., Geller A. M., Sills A., Leigh N. W. C., Knigge C. 2015, ApJ, 814, 163
+\bibitem[\protect\citeauthoryear{Haiman et al.}{2009}]{haiman09} Haiman Z., Kocsis B., Menou K. 2009, ApJ, 700, 1952  
 %\bibitem[\protect\citeauthoryear{Graham \& Spitler}{2009}]{Graham09} Graham A.W. \& Spitler L.R., 2009, MNRAS, 397, 2148
@@
 \bibitem[\protect\citeauthoryear{Iben}{1991}]{iben91}  Iben I., Jr. 1991, ApJS, 76, 55
+\bibitem[\protect\citeauthoryear{Kelley et al.}{2017}]{kelley17} Kelley L. Z., Blecha L., Hernquist L. 2017, MNRAS, 464, 3131 
 \bibitem[\protect\citeauthoryear{Knigge, Leigh \& Sills}{2009}]{knigge09} Knigge C., Leigh
@@
   W. H. 1964, MNRAS, 128, 147
+\bibitem[\protect\citeauthoryear{Moe \& Kratter}{2018}]{moe18} Moe M., Kratter K. M. 2018, ApJ, 854, 44 
 %\bibitem[\protect\citeauthoryear{Milone et al.}{2008}]{milone08}
@@
   ApJ, 604, L109
+\bibitem[\protect\citeauthoryear{Rafikov}{2016}]{rafikov16} Rafikov R. R. 2016, ApJ, 827, 111 
 %\bibitem[\protect\citeauthoryear{Piotto et al.}{2007}]{piotto07}
@@
 \bibitem[\protect\citeauthoryear{Simunovic \& Puzia}{2016}]{simunovic16} Simunovic M., Puzia T. H. 2016, MNRAS 462, 3401
+\bibitem[\protect\citeauthoryear{Tobin et al.}{2018}]{tobin18} Tobin J.
+J., Looney L.
+W., Li Z.-Y., Sadavoy S.
+I., Dunham M.
+M.
+Segura-Cox D., Kratter K., Chandler C.
+J., Melis C., Harris R.
+J., Perez L.
+2018, ApJ, 867, 43
 %\bibitem[\protect\citeauthoryear{Sirianni et al.}{2005}]{sirianni05} Sirianni M., Jee M.

### 2018-12-04 apjl.tex
Add files via upload

@@
 We assume circular orbits for both the inner and outer orbits, and co-planar triples only since this is what has been observed for low-mass tertiaries \citep[e.g.][]{moe18,tobin18}.
+This initial configuration for our assumed formation scenario for Binary 7782, described below, is depicted in Figure~\ref{fig:fig1}.
+
+\begin{figure}[ht!]
+\plotone{fig1.eps}
+\caption{Cartoon depiction of our proposed scenario for the formation of Binary 7782, specifically mass transfer from an evolved outer tertiary companion on to a compact inner binary via a circumbinary disk.
+The outer tertiary component has mass m$_{\rm 3}$, whereas the inner binary components have masses m$_{\rm 1}$ and m$_{\rm 2}$.
+The inner and outer orbital separations are denoted by, respectively, a$_{\rm in}$ and a$_{\rm out}$.
+The circularization radius of the accretion stream is denoted a$_{\rm c}$, as calculated via Equation~\ref{eqn:ac}, and marks the mean separation of the circumbinary disk.
+\label{fig:fig1}}
+\end{figure}
 
@@
 
-Figure~\ref{fig:fig1} shows the parameter space in the P$_{\rm out}$-P$_{\rm in}$-plane for Binary 7782.
+Figure~\ref{fig:fig2} shows the parameter space in the P$_{\rm out}$-P$_{\rm in}$-plane for Binary 7782.
 We assume initial component masses of m$_{\rm 1} =$ 1.1 M$_{\rm \odot}$ and m$_{\rm 2} =$ 0.9 M$_{\rm \odot}$ for the inner binary components, and m$_{\rm 3} =$ 1.4 M$_{\rm \odot}$ for the outer tertiary.
@@
 \begin{figure}[ht!]
-\plotone{fig1.eps}
+\plotone{fig2.eps}
 \caption{Parameter space in the P$_{\rm out}$-P$_{\rm in}$-plane allowed for the hypothetical outer tertiary orbit of Binary 7782.
@@
 Finally, the thick solid horizontal red line shows the parameter space for P$_{\rm out}$ allowed after considering all of the aforementioned criteria.
-\label{fig:fig1}}
+\label{fig:fig2}}
 \end{figure}
@@
 We use smoothed-particle hydrodynamics (SPH) simulations to compute the time evolution of the mass transfer process.
-We adopt the same initial particle masses as in Figure~\ref{fig:fig1}, namely initial component masses of m$_{\rm 1}$ = 1.1 M$_{\rm \odot}$ and m$_{\rm 2}$ = 0.9 M$_{\rm \odot}$ for the inner binary components, and m$_{\rm 3}$ is computed for the outer tertiary according to our assumed mass ratio, with our fiducial case corresponding to q $=$ 0.7.
+We adopt the same initial particle masses as in Figure~\ref{fig:fig2}, namely initial component masses of m$_{\rm 1}$ = 1.1 M$_{\rm \odot}$ and m$_{\rm 2}$ = 0.9 M$_{\rm \odot}$ for the inner binary components, and m$_{\rm 3}$ is computed for the outer tertiary according to our assumed mass ratio, with our fiducial case corresponding to q $=$ 0.7.
 The initial orbital eccentricities are set to zero.
@@
 If the donor is an RGB star, the accretor will be enriched in mostly carbon, oxygen and helium.
-If the accretor is an AGB star, it will be enriched in mostly s-process elements.
+If the donor is an AGB star, it will be enriched in mostly s-process elements.
 

### 2018-12-06 apjl.tex
Add files via upload

@@
 
+Finally, in future work, we intend to explore the implications of the mechanism proposed here for other types of stellar triples.
+The results highlight that specific theoretical predictions can often be made.
+For example, if two white dwarfs form the inner compact binary, than circumbinary accretion could push one of them above the Chandrasekhar mass limit.
+Upon explosion, its WD companion would be ejected at roughly the orbital velocity at the time of explosion, producing a hypervelocity WD.
+This predicts hot hypervelocity WDs with masses very close to the Chandrasekhar mass limit for this scenario.
+Similarly, if the two WDs are replaced with two neutron stars (NSs), then one NS will likely accrete to surpass the critical supernova limit, upon which time it explodes to become a black hole and receives a strong natal kick.
+The NS companion would have a very comparable mass to the newly formed black hole progenitor at the time of explosion, and could potentially be used to constrain the maximum NS mass.
+
 \acknowledgments

### 2018-12-10 apjl.tex
Add files via upload
Added figures and update text

@@
 \newcommand\latex{La\TeX}
+
+\newcommand{\MSun}{\mbox{M$_\odot$}}
+\newcommand{\RSun}{\mbox{R$_\odot$}}
+\newcommand{\LSun}{\mbox{L$_\odot$}}
+
+\def\Simon#1{{\bf {\color{red}[#1 -- Simon]}}}
+\def\simon#1{{\bf {\color{red}[#1 -- Simon]}}}
+\def\del#1{{\bf {\sout{#1}}}}
+\def\replace#1#2{{\bf {\sout{#1} $\rightarrow$ {\bf #2}}}}
 
@@
 \begin{abstract}
-In this Letter, we propose a potential formation mechanism for twin blue stragglers in compact binaries that involves mass transfer from an evolved outer tertiary companion on to the inner binary via a circumbinary disk.
-We apply our hypothetical scenario to the observed double blue straggler system Binary 7782 in the old open cluster NGC 188, and show that its observed properties are easily and even naturally reproduced within the context our proposed model.
-Within the context of the hypothetical formation mechanism proposed here, the presented work predicts the following properties for the post-mass transfer double BS tertiary:  (1)  For the outer tertiary orbit, the initial orbital period should lie between 220 days $\lesssim$ P$_{\rm out}$ $\lesssim$ 1100 days, assuming initial masses for the inner binary components of m$_{\rm 1} =$ 1.1 M$_{\odot}$ and m$_{\rm 2} =$ 0.9 M$_{\odot}$ and an outer tertiary mass of m$_{\rm 3} =$ 1.4 M$_{\odot}$.
-(2)  Larger final WD masses, and hence core masses for the donor at the time of mass transfer, should correspond to larger final outer orbital periods for the tertiary.
-(3)  For the inner binary, the rotational axes of the BSs should be aligned with each other and the orbital plane of the outer tertiary WD.
-(4)  The BSs in the inner binary should have roughly equal masses, independent of their initial masses.
-This predicts that the initially lower mass MS star should accrete the most, and should hence be polluted more significantly by any accreted material.
-This could be observable in the surface layers of a radiative star (i.e., He, C and O if the donor is an RGB star, and/or s-process elements if the donor is an AGB star).
-(5) Twin BSs in compact binaries formed from the proposed mechanism should be more frequent in younger clusters with ages $\lesssim$ 4-6 Gyr, since the donor will have  radiative envelope.
+
+We propose a formation mechanism for twin blue stragglers in compact
+binaries that involves mass transfer from an evolved outer tertiary
+companion on to the inner binary via a circumbinary disk.  We apply
+our hypothetical scenario to the observed double blue straggler system
+Binary 7782 in the old open cluster NGC 188, and show that its
+observed properties are naturally reproduced within the context our
+proposed model.  Within the context of the hypothetical formation
+mechanism proposed here, the presented work predicts the following
+properties for the post-mass transfer double BS tertiary: (1) For the
+outer tertiary orbit, the initial orbital period should lie between
+220 days $\lesssim$ P$_{\rm out}$ $\lesssim$ 1100 days, assuming
+initial masses for the inner binary components of m$_{\rm 1} =$ 1.1
+M$_{\odot}$ and m$_{\rm 2} =$ 0.9 M$_{\odot}$ and an outer tertiary
+mass of m$_{\rm 3} =$ 1.4 M$_{\odot}$. (2) Larger final WD masses, and
+hence core masses for the donor at the time of mass transfer, should
+correspond to larger final outer orbital periods for the tertiary. (3)
+For the inner binary, the rotational axes of the BSs should be aligned
+with each other and the orbital plane of the outer tertiary WD. (4)
+The BSs in the inner binary should have roughly equal masses,
+independent of their initial masses.  This predicts that the initially
+lower mass MS star should accrete the most, and should hence be
+polluted more effectively by the accreted material.  This could be
+observable in the surface layers of a radiative star (i.e., He, C and
+O if the donor is an RGB star, and/or s-process elements if the donor
+is an AGB star). (5) Twin BSs in compact binaries formed from the
+proposed mechanism should be more frequent in younger clusters with
+ages $\lesssim$ 4-6 Gyr, since the donor will have radiative envelope.
 
@@
 
-Blue straggler (BS) stars appear brighter and bluer than the main-sequence turn-off (MSTO) in a cluster colour-magnitude diagram (CMD) \citep[e.g.][]{simunovic14,simunovic16}.
-Two primary channels for BS formation have been proposed; mass transfer from an evolved donor on to a main-sequence star in a binary star system \citep[e.g.][]{mccrea64,knigge09,mathieu09,leigh11,geller11,geller12,gosnell14,gosnell15}, and direct stellar collisions involving main-sequence stars mediated via direct interactions involving binaries \citep[e.g.][]{hills75,shara97,leigh07,leigh11,leigh13,hypki13}.
-Other possible, albeit related, formation mechanisms include mergers of compact MS-MS binaries, and mergers of the inner MS-MS binaries of hierarchical triple star systems induced by Lidov-Kozai oscillations coupled with tidal damping \citep[e.g.][]{perets09}.
+Blue straggler (BS) stars are brighter and bluer than the
+main-sequence turn-off (MSTO) in a cluster colour-magnitude diagram
+(CMD) \citep[e.g.][]{1953AJ.....58...61S,simunovic14,simunovic16}.
+Two primary channels for BS formation have been proposed; mass
+transfer from an evolved donor on to a main-sequence star in a binary
+star system
+\citep[e.g.][]{mccrea64,997A&A...328..143P,knigge09,mathieu09,leigh11,geller11,geller12,gosnell14,gosnell15},
+and direct stellar collisions involving main-sequence stars mediated
+via direct interactions involving binaries
+\citep[e.g.][]{hills75,1997A&A...328..130P,shara97,leigh07,leigh11,leigh13,hypki13,2018arXiv181100058P}.
+Other possible, albeit related, formation mechanisms include mergers
+of compact main-sequence binaries (ms, ms), and mergers of the inner
+binaries of hierarchical triple star systems induced by Lidov-Kozai
+oscillations coupled with tidal damping \citep[e.g.][]{perets09}.
 
-In spite of these specific predictions for the expected properties of BSs formed from each of the above production mechanisms, there exist many BSs with observed properties that defy these simple scenarios.
-For example, in the old open cluster M67, there lurks a candidate triple system that is posited to host \textit{two} BSs \citep{vandenberg01,sandquist03}.
-The observations suggest that the outer tertiary is itself a BS, with a mass $\sim$ 1.7 M$_{\odot}$ and orbiting the inner binary with a period of 1188.5 days \citep{sandquist03}.
-The inner binary has a period of only 1.068 days \citep{vandenberg01}, and hosts a BS of mass 2.52 M$_{\odot}$.
-Thus, in order to form this system after convolving its observed properties with its host cluster age, we require at least five stars in order to conserve the total system mass \citep{leigh11}.
-As explained in \citet{leigh11}, this is strongly indicative of a dynamical origin for the system, and a single direct interaction involving a binary and a triple that resulted in two separate collision events is the most probable explanation for its origin (i.e., a single interaction involving two multiples with two or more stars is a more likely scenario to produce this system than two back-to-back direct binary-binary interactions).
+In spite of these specific predictions for the expected properties of
+BSs formed from each of the above production mechanisms, there exist
+many BSs with observed properties that defy these simple scenarios.
+\del{For example, in the old open cluster M67, there lurks a candidate
+  triple system that is posited to host \textit{two} BSs
+  \citep{vandenberg01,sandquist03}.  The observations suggest that the
+  outer tertiary is itself a BS, with a mass $\sim$ 1.7 M$_{\odot}$
+  and orbiting the inner binary with a period of 1188.5 days
+  \citep{sandquist03}.  The inner binary has a period of only 1.068
+  days \citep{vandenberg01}, and hosts a BS of mass 2.52 M$_{\odot}$.}
+In order to form this system after convolving its observed properties
+with its host cluster age, we require at least five stars in order to
+conserve the total system mass \citep{leigh11}.  As explained in
+\citet{leigh11}, this is strongly indicative of a dynamical origin for
+the system, and a single direct interaction involving a binary and a
+triple that resulted in two separate collision events is the most
+probable explanation for its origin (i.e., a single interaction
+involving two multiples with two or more stars is a more likely
+scenario to produce this system than two back-to-back direct
+binary-binary interactions) \citep{2004MNRAS.350..615G}.
 
-Even more curious, there exists in the old open cluster NGC 188 a double BS binary, called Binary 7782.
-Specifically, \citet{mathieu09} observed a compact and mildly eccentric (i.e., e $\sim$ 0.1) binary star system with an orbital period of $\sim$ 10 days hosting \textit{two} blue stragglers.
-During a given binary-binary interaction, the probability that not one but \textit{two} direct MS-MS collisions occur is less than a percent \citep{leonard89,leigh11,leigh12}.
-Typically, such binaries are very wide with long orbital periods.
-Thus, dynamically, it is very difficult to form a compact binary composed of two collision products during a single direct interaction in a star cluster.
-So, how did Binary 7782 form?
-MENTION BIMODAL P-E DISTRIBUTION, AND HOW THIS COULD BE SUGGESTIVE OF A TRIPLE ORIGIN FOR SOME OF THE SUBSET OF OBSERVED BSs.
+Even more curious, there exists in the old open cluster NGC 188 a
+double BS binary, called Binary 7782.  Specifically, \citet{mathieu09}
+observed a compact and mildly eccentric (i.e., e $\sim$ 0.1) binary
+star system with an orbital period of $\sim$ 10 days hosting two blue
+stragglers.  During a given binary-binary interaction, the probability
+that not one but two direct (ms, ms) collisions occur is less than
+$10^{-2}$ \citep{leonard89,leigh11,leigh12}.  Typically, such binaries
+have long orbital periods. Dynamically, it difficult to form a
+short-period binary composed of two collision products during a
+collision interaction in a star cluster \citep{2011Sci...334.1380F}.
+So, how did Binary 7782 form?  MENTION BIMODAL P-E DISTRIBUTION, AND
+HOW THIS COULD BE SUGGESTIVE OF A TRIPLE ORIGIN FOR SOME OF THE SUBSET
+OF OBSERVED BSs.
 
-In this Letter, we propose a potential formation channel for Binary 7782, and compact double BS binaries in general, which involves mass transfer from an outer tertiary companion on to an inner MS-MS binary.
-In section~\ref{dyn}, we constrain the range of initial (i.e., pre-mass transfer) orbital parameters for a hypothetical outer tertiary companion, using a combination of dynamical and stellar evolution-based constraints.
-In Section~\ref{sims} we present the numerical simulations used to study the mass transfer process in our hypothetical triple system, computed using the \texttt{AMUSE} software package, in order to study the evolution of the inner and outer orbital parameters during mass transfer.
-We summarize and discuss the implications of our results for compact double BS binaries and, more generally, mass transfer in stellar triples in Section~\ref{discussion}.
+We propose a formation channel for Binary 7782, and compact double BS
+binaries in general, which involves mass transfer from an outer
+tertiary companion on to an inner MS-MS binary.  In section~\ref{dyn},
+we constrain the range of initial (i.e., pre-mass transfer) orbital
+parameters for a hypothetical outer tertiary companion, using a
+combination of dynamical and stellar evolution-based constraints.  In
+Section~\ref{sims} we present the numerical simulations used to study
+the mass transfer process in our hypothetical triple system, computed
+using the \texttt{AMUSE}\cite{AMUSE} software package, in order to
+study the evolution of the inner and outer orbital parameters during
+mass transfer.  We summarize and discuss the implications of our
+results for compact double BS binaries and, more generally, mass
+transfer in stellar triples in Section~\ref{discussion}.
 
@@
 
-Consider a hierarchical triple system with component masses m$_{\rm 1}$ and m$_{\rm 2}$ for the inner binary, and mass m$_{\rm 3}$ for the outer tertiary companion.
-The inner and outer binary orbital semi-major axes are denoted a$_{\rm in}$ and a$_{\rm out}$, respectively.
-We assume circular orbits for both the inner and outer orbits, and co-planar triples only since this is what has been observed for low-mass tertiaries \citep[e.g.][]{moe18,tobin18}.
-This initial configuration for our assumed formation scenario for Binary 7782, described below, is depicted in Figure~\ref{fig:fig1}.
+Consider a hierarchical triple system with component masses m$_{\rm
+  1}$ and m$_{\rm 2}$ for the inner binary, and mass m$_{\rm 3}$ for
+the outer tertiary companion.  The inner and outer binary orbital
+semi-major axes are denoted a$_{\rm in}$ and a$_{\rm out}$,
+respectively.  We assume circular orbits for both the inner and outer
+orbits, and co-planar triples only since this is what has been
+observed for low-mass tertiaries \cite{2010yCat..73890925T} \simon{I
+  think that {\em moe18} and {\em tobin18} are not the right
+  references}.  This initial configuration for our assumed formation
+scenario for Binary 7782, described below, is depicted in
+Figure~\ref{fig:fig1}.
 
@@
 \plotone{fig1.eps}
-\caption{Cartoon depiction of our proposed scenario for the formation of Binary 7782, specifically mass transfer from an evolved outer tertiary companion on to a compact inner binary via a circumbinary disk.
-The outer tertiary component has mass m$_{\rm 3}$, whereas the inner binary components have masses m$_{\rm 1}$ and m$_{\rm 2}$.
-The inner and outer orbital separations are denoted by, respectively, a$_{\rm in}$ and a$_{\rm out}$.
-The circularization radius of the accretion stream is denoted a$_{\rm c}$, as calculated via Equation~\ref{eqn:ac}, and marks the mean separation of the circumbinary disk.
+\caption{Cartoon depiction of our proposed scenario for the formation
+  of Binary 7782, specifically mass transfer from an evolved outer
+  tertiary companion on to a compact inner binary via a circumbinary
+  disk.  The outer tertiary component has mass m$_{\rm 3}$, whereas
+  the inner binary components have masses m$_{\rm 1}$ and m$_{\rm 2}$.
+  The inner and outer orbital separations are denoted by,
+  respectively, a$_{\rm in}$ and a$_{\rm out}$.  The circularization
+  radius of the accretion stream is denoted a$_{\rm c}$, as calculated
+  via Equation~\ref{eqn:ac}, and marks the mean separation of the
+  circumbinary disk.
 \label{fig:fig1}}
@@
 
-We consider a scenario where the outer tertiary companion is filling its Roche lobe and is hence transferring mass to the inner binary.
-The mass transfer stream gathers at the circularization radius a$_{\rm c}$, and forms a circumbinary disk.
-Using conservation of angular momentum, we can equate the specific angular momentum of the accreted mass at the inner Lagrangian point of the donor star to the final specific angular momentum of the accretion stream at the circularization radius about the inner binary:
+We consider a scenario where the outer star is filling its Roche lobe
+and is transfers mass to the inner binary.  The mass transfer stream
+gathers at the circularization radius a$_{\rm c}$, and forms a disk
+around the inner binary.  Using conservation of angular momentum, we
+equate the specific angular momentum of the accreted mass at the inner
+Lagrangian point of the (outer) donor star to the final specific
+angular momentum of the accretion stream at the circularization radius
+about the inner binary, this results in
+\simon{replaced lower case $r$ with upper case.}
 \begin{equation}
 \label{eqn:specangmom1}
-v_{\rm orb,3}(a_{\rm out} - r_{\rm L}) = v_{\rm orb,c}a_{\rm c},
+v_{\rm orb,3}(a_{\rm out} - R_{\rm L}) = v_{\rm orb,c}a_{\rm c},
 \end{equation}
-where R$_{\rm L}$ is the radius of the Roche lobe of the outer tertiary companion, a$_{\rm c}$ is the semi-major axis of the orbit about the inner binary corresponding to the circularization radius and v$_{\rm orb,c}$ is the orbital velocity at a$_{\rm c}$.
-The distance from the center of mass corresponding to the outer tertiary companion defined by the Roche lobe is given by \citep{eggleton83}:
+where R$_{\rm L}$ is the radius of the Roche lobe of the outer
+tertiary companion, a$_{\rm c}$ is the semi-major axis of the orbit
+about the inner binary corresponding to the circularization radius and
+v$_{\rm orb,c}$ is the orbital velocity at a$_{\rm c}$.  The distance
+from the center of mass corresponding to the outer tertiary companion
+defined by the Roche lobe is given by \citep{eggleton83}.
+\simon{Do we really need this eq?}
 \begin{equation}
@@
 \end{equation}
-where the mass ratio q is defined as q $=$ m$_{\rm 3}$/(m$_{\rm 1} +$ m$_{\rm 2}$).
-Combining Equation~\ref{eqn:roche} with Equation~\ref{eqn:specangmom1}, we can solve for the circularization radius as a function of a$_{\rm out}$ and the assumed stellar masses:
+where the mass ratio q is defined as q $=$ m$_{\rm 3}$/(m$_{\rm 1} +$
+m$_{\rm 2}$).  Combining Equation~\ref{eqn:roche} with
+Equation~\ref{eqn:specangmom1}, we can solve for the circularization
+radius as a function of a$_{\rm out}$ and the assumed stellar masses:
 \begin{equation}
@@
 \end{equation}
-In order for a circumbinary disk to form around the inner binary, we require that a$_{\rm in} <$ a$_{\rm c}$.
+In order for a circumbinary disk to form around the inner binary, we
+require that a$_{\rm in} <$ a$_{\rm c}$.
 
-Figure~\ref{fig:fig2} shows the parameter space in the P$_{\rm out}$-P$_{\rm in}$-plane for Binary 7782.
-We assume initial component masses of m$_{\rm 1} =$ 1.1 M$_{\rm \odot}$ and m$_{\rm 2} =$ 0.9 M$_{\rm \odot}$ for the inner binary components, and m$_{\rm 3} =$ 1.4 M$_{\rm \odot}$ for the outer tertiary.
-We compare the circularization radius to the semi-major axis of the inner binary, for which we require a$_{\rm c} >$ a$_{\rm in}$, after folding in all constraints from the requirements for dynamical stability, an outer tertiary that is Roche lobe-filling, and a dynamically hard outer tertiary orbit.
-Note that the range of plotted orbital periods P$_{\rm in}$ corresponding to a contact state for the inner binary, assuming R$_{\rm 1} =$ R$_{\rm 2} =$ 1 R$_{\odot}$, lies outside the range of plotted values for P$_{\rm in}$, since it does not contribute significantly to constraining the outer orbital properties of a hypothesized outer WD tertiary.
-The thick horizontal solid red line shows the allowed range of outer semi-major axes, after folding in all of the aforementioned criteria.
-As is clear, this makes a relatively narrow prediction for the allowed ranges of outer tertiary orbits, namely 2.2 $\times$ 10$^{2}$ days $\le$ P$_{\rm out}$ $\le$ 1.1 $\times$ 10$^3$ days, for our assumed final donor mass.
+Figure~\ref{fig:fig2} shows the parameter space in the P$_{\rm
+  out}$-P$_{\rm in}$-plane for Binary 7782.  We assume initial
+component masses of m$_{\rm 1} =$ 1.1 M$_{\rm \odot}$ and m$_{\rm 2}
+=$ 0.9 M$_{\rm \odot}$ for the inner binary components, and m$_{\rm 3}
+=$ 1.4 M$_{\rm \odot}$ for the outer tertiary.  We compare the
+circularization radius to the semi-major axis of the inner binary, for
+which we require a$_{\rm c} >$ a$_{\rm in}$, \del{after folding in all
+  constraints from the requirements for dynamical stability}\simon{can
+  we not simply state the constraints?}, an outer tertiary that is
+Roche lobe-filling, and a dynamically hard outer tertiary orbit.  Note
+that the range of plotted orbital periods P$_{\rm in}$ corresponding
+to a contact state for the inner binary, assuming \simon{This looks
+  weird:} R$_{\rm 1} =$ R$_{\rm 2} =$ 1 R$_{\odot}$, lies outside the
+range of plotted values for P$_{\rm in}$, since it does not contribute
+significantly to constraining the outer orbital properties of a
+hypothesized outer WD tertiary.  The thick horizontal solid red line
+shows the allowed range of outer semi-major axes, after folding in all
+of the aforementioned criteria.  As is clear, this makes a relatively
+narrow prediction for the allowed ranges of outer tertiary orbits,
+namely 2.2 $\times$ 10$^{2}$ days $\le$ P$_{\rm out}$ $\le$ 1.1
+$\times$ 10$^3$ days, for our assumed final donor mass.
 
@@
 \plotone{fig2.eps}
-\caption{Parameter space in the P$_{\rm out}$-P$_{\rm in}$-plane allowed for the hypothetical outer tertiary orbit of Binary 7782.
-The solid diagonal black lines show the period corresponding to the circularization radius a$_{\rm c}$ for the mass transfer stream coming from the outer tertiary, for different values of the mass ratio, namely q $=$ 0.1, 0.7, 1, 2 and 10.
-We assume initial component masses of m$_{\rm 1}$ = 1.1 M$_{\rm \odot}$ and m$_{\rm 2}$ = 0.9 M$_{\rm \odot}$ for the inner binary components, and m$_{\rm 3}$ is computed for the outer tertiary according to our assumed mass ratio (with our fiducial case corresponding to q $=$ 0.7.
-We assume completely conservative mass transfer for this exercise, and a final mass for the outer tertiary of 0.6 M$_{\rm \odot}$ once it has become a WD.
-The dashed diagonal black line shows a rough criterion for dynamical stability in the triple, approximately following \citet{mardling99} (i.e., a$_{\rm in} <$ 0.1a$_{\rm out}$ is required for long-term dynamical stability in equal-mass co-planar triples).
-The vertical solid red lines show the outer orbital periods corresponding to the hard-soft boundary assuming central velocity dispersions of $\sigma =$ 1, 5 and 10 km s$^{-1}$.
-The vertical dashed black lines show the maximum outer orbital period P$_{\rm out}$ for which the outer tertiary companion is Roche lobe-filling, assuming a stellar radius of R$_{\rm 3} =$ 200 R$_{\odot}$ (CHANGE, POSSIBLY USING MESA CALCULATIONS?!).
-The horizontal dashed red line shows the observed orbital period for Binary 7782, using its observed orbital period and our assumed final inner companion masses (i.e., m$_{\rm 1} =$ m$_{\rm 2} =$ 1.4 M$_{\odot}$).
-Finally, the thick solid horizontal red line shows the parameter space for P$_{\rm out}$ allowed after considering all of the aforementioned criteria.
+\caption{Parameter space in the P$_{\rm out}$-P$_{\rm in}$-plane
+  allowed for the hypothetical outer tertiary orbit of Binary 7782.
+  The solid diagonal black lines show the period corresponding to the
+  circularization radius a$_{\rm c}$ for the mass transfer stream
+  coming from the outer star, for different values of the mass ratio,
+  namely q $=$ 0.1, 0.7, 1, 2 and 10 \simon{before or after mass
+    transfer?}.  \simon{what is the purpose of extending q to 0.1 and
+    10?} We assume initial component masses of m$_{\rm 1}$ = 1.1
+  M$_{\rm \odot}$ and m$_{\rm 2}$ = 0.9 M$_{\rm \odot}$ for the inner
+  binary components, and m$_{\rm 3}$ is computed for the outer
+  tertiary according to our assumed mass ratio (with our fiducial case
+  corresponding to q $=$ 0.7.  We assume completely conservative mass
+  transfer for this exercise, and a final mass for the outer tertiary
+  of 0.6 M$_{\rm \odot}$ once it has become a WD.  The dashed diagonal
+  black line shows a rough criterion for dynamical stability in the
+  triple, approximately following \citet{mardling99} (i.e., a$_{\rm
+    in} <$ 0.1a$_{\rm out}$ is required for long-term dynamical
+  stability in equal-mass co-planar triples).  The vertical solid red
+  lines show the outer orbital periods corresponding to the hard-soft
+  boundary assuming central velocity dispersions of $\sigma =$ 1, 5
+  and 10 km s$^{-1}$.  The vertical dashed black lines show the
+  maximum outer orbital period P$_{\rm out}$ for which the outer
+  tertiary companion is Roche lobe-filling, assuming a stellar radius
+  of R$_{\rm 3} =$ 200 R$_{\odot}$ (CHANGE, POSSIBLY USING MESA
+  CALCULATIONS?!).  The horizontal dashed red line shows the observed
+  orbital period for Binary 7782, using its observed orbital period
+  and our assumed final inner companion masses (i.e., m$_{\rm 1} =$
+  m$_{\rm 2} =$ 1.4 M$_{\odot}$).  Finally, the thick solid horizontal
+  red line shows the parameter space for P$_{\rm out}$ allowed after
+  considering all of the aforementioned criteria.  \simon{I think that
+    the figure needs work. I like putting the parameter space in terms
+    of orbital periods, but the q=0.1 and q=10 constraints seems
+    not very practical. The red labels are not readable, and I am not
+    really sure how to read the figure. What about the alternative in
+    the next figure, which shows tertiary mass vs. orbital period?}
 \label{fig:fig2}}
 \end{figure}
+
+\begin{figure}[ht!]
+  \includegraphics[width=\columnwidth]{fig_minimumstablesize.pdf}
+\caption{Orbital separation as a function of the mass of the
+  Roche-lobe filling outer star. The red curves gives the size at the
+  first giant branch (thick curve) at at the AGB (thin curve). The
+  blue curve the orbital separation at the moment this giant fills its
+  Roche-lobe assuming a circular orbit and a total inner-binary mass
+  of 2.0\,\MSun. The green curves give, under these conditions, the
+  maximum orbital separation for a stable inner binary.
+\label{fig:tertiarymass_vs_size}}
+\end{figure}
+
+In Fig.\,\ref{fig:tertiarymass_vs_size} we present..
 
@@
 
-We use smoothed-particle hydrodynamics (SPH) simulations to compute the time evolution of the mass transfer process.
-We adopt the same initial particle masses as in Figure~\ref{fig:fig2}, namely initial component masses of m$_{\rm 1}$ = 1.1 M$_{\rm \odot}$ and m$_{\rm 2}$ = 0.9 M$_{\rm \odot}$ for the inner binary components, and m$_{\rm 3}$ is computed for the outer tertiary according to our assumed mass ratio, with our fiducial case corresponding to q $=$ 0.7.
-The initial orbital eccentricities are set to zero.
-The inner and outer binary orbital semi-major axes are set to 0.1 AU and 1 AU, respectively (CORRECT).
+We perform simulations of a triple star system of which the outer star
+overfills its Roche lobe while the inner binary remains detached. The
+calculations start by evolving the three stars to the same age, which
+is selected such that the outer-most star fills its Roche lobe.
+Constraints for the initial conditions are derived in the previous
+\S\, but in \S\,\ref{Sect:ICs} we summarize the adopted initial
+conditions for the simulations.
 
-\subsection{Initial Conditions} \label{ICs}
+RLOF in triples using a coupled integrator to follow the complex
+hydrodynamics of the mass transfer from the Roche-lobe filling outer
+star to the inner binary, while keeping track of the gravitational
+dynamics of the stars.  The equations of motion of the inner binary is
+solved using the semi-symplectic direct N-body integrator
+\texttt{Huayno} \citep{2012NewA...17..711P}. The hydrodynamics is
+performed with the smoothed-particles hydrodynamics code
+\texttt{Gadget2} \citep{2000ascl.soft03001S}, using an adiabatic
+equation of state.  The two inner binary stars are treated as point
+masses, but we allow them to accrete gas from the outer star.  This is
+realized using sink-particles that co-move with the mass points in the
+gravity code. While the inner two stars accrete mass, they also
+accrete the appropriate amoun of angular momentum from the gas.  and
+the the N-body integrator accounts of this appropriately.  For the
+radius of the sink particles we adopt $10 R_\odot$ for both stars.
 
-In this section, we describe and justify our choice of initial conditions for both our analytic calculations and smoothed-particle hydrodynamics simulations.
+The N-body code as well as the hydrodynamics solver operate using
+their own internal time-steps. The coupling between the two codes is
+realized using the \texttt{Bridge} method in the AMUSE framework
+\citep[see Sect.\.4.3.1 in][]{2013CoPhC.183..456P}.  This coupled
+integrator is based on the splitting of the Hamiltonian much in the
+same way as is done with two different gravity solvers by
+\cite{2007PASJ...59.1095F}. With the adopted scheme, the
+hydrodynamical solver is affected by the gravitational potential of
+its own particles, as well as the gravitational potential of the inner
+binary. The hydrodynamics, in particular the gas drag, in turn affects
+the orbits of the two inner stars. With \texttt{Bridge} we realize a
+second order coupling between the gravitational dynamics and the
+hydrodynamics.  The interval at which the gravity and hydrodynamics
+interact via \texttt{Bridge} depends on the parameters of the system
+we study, but typically we achieve converged solutions when this time
+step is about a fraction of 1/100 of the inner binary orbital period.
 
-We adopt initial component masses of m$_{\rm 1}$ = 1.1 M$_{\rm \odot}$ and m$_{\rm 2}$ = 0.9 M$_{\rm \odot}$ for the inner binary components, and m$_{\rm 3}$ = 1.4 M$_{\rm \odot}$ for the outer tertiary.
-This choice for the initial mass of the outer tertiary is critical since it ensures that the donor star during the mass transfer process will have a radiative envelope \citep[e.g.][]{maeder09}.
-In turn, this ensures that the mass transfer will be maximally conservative, such that the accretion stream will be maximally stable, accreting at a stable and constant rate \citep[e.g.][]{iben91}.
+\subsection{Initial Conditions} \label{Sect:ICs}
+
+We adopt initial component masses of m$_{\rm 1}$ = 1.1 M$_{\rm \odot}$
+and m$_{\rm 2}$ = 0.9 M$_{\rm \odot}$ for the inner binary components,
+and m$_{\rm 3}$ = 1.2 M$_{\rm \odot}$ for the tertiary star.  We
+evolved the 1.2\,\MSun\, star using the MESA stellar evolution code
+\cite{2011ApJS..192....3P} to a radius of about 255\,\RSun.  By this
+time the star has lost 0.13\,\MSun\, in a stellar wind.  With these
+parmeters the orbital separation of the outer binary becomes 3.86\,au,
+and the mass loss has driven a slight eccentricity from initiall
+circular orbit to about 0.0082 at the moment of Roche-lobe
+overflow. We chose a relative initial inclination of $i = 9^\circ$
+between the inner and the outer orbit.
+
+In fig.\,\ref{fig:topview_at_t0} we present a top view of the triple
+system at the onset of Roche-lobe overlofw.
+
+\begin{figure}[ht!]
+  \includegraphics[width=\columnwidth]{fig_t0_N80000_M012MSun1109MSun_a02au_e00_inc9deg.pdf}
+\caption{top view of the triple system in which the outer star
+  (represented by 80000\,sph particles and a core particle of
+  0.4\,\MSun (blue bullet). The two companion stars are represented as
+  red bullets (to the right).
+\label{fig:topview_at_t0}}
+\end{figure}
 
@@
 
+In fig.\,\ref{fig:topview_at_t1000day} we show the same triple at
+after 1000\,days of evolution.
+
+\begin{figure}[ht!]
+  \includegraphics[width=\columnwidth]{fig_t600_N80000_M012MSun1109MSun_a02au_e00_inc9deg.pdf}
+\caption{Same as Fig.\,\ref{fig:topview_at_t0} but at an age of $t
+  \simeq 996days$.
+\label{fig:topview_at_t1000day}}
+\end{figure}
+
+In fig.\,\ref{fig:mass_evolution_for_M1.2M1.1M0.9a02e00i09}
+
+\begin{figure}[ht!]
+  \includegraphics[width=\columnwidth]{fig_MvsTime_N80k_M012R100RSun1109MSun_a02au.pdf}
+\caption{Evolution of the masses (normalized to those at the moment of
+  Roche-lobe overflow) of each of the three stars as a function of
+  time for the first 1000\,days. (see Fig.\.\ref{fig:topview_at_t0}
+  for a face-on representation of the initial conditions and
+  fig.\,\ref{fig:topview_at_t1000day} for the final conditions}.  The
+green and orange dashed curves give the masses of the inner two stars,
+whereas the solid blue curve is the mass of the outer most star.
+\label{fig:mass_evolution_for_M1.2M1.1M0.9a02e00i09}
+\end{figure}
+
 \section{Summary and Discussion} \label{discussion}
+
+This
+choice for the initial mass of the outer tertiary is critical since it
+ensures that the donor star during the mass transfer process will have
+a radiative envelope \citep[e.g.][]{maeder09}.  In turn, this ensures
+that the mass transfer will be maximally conservative, such that the
+accretion stream will be maximally stable, accreting at a stable and
+constant rate \citep[e.g.][]{iben91}.
 
@@
 The NS companion would have a very comparable mass to the newly formed black hole progenitor at the time of explosion, and could potentially be used to constrain the maximum NS mass.
+More work needs to be done here to evaluate whether or not there is any parameter space for the products of this scenario that will allow for a mass determination for the original NS companion in the putative compact NS-NS binary.
 
@@
 
-N.W.C.L. acknowledges support from a Kalbfleisch Fellowship at the American Museum of Natural History.
+N.W.C.L. acknowledges support from a Kalbfleisch Fellowship at the
+American Museum of Natural History.  SPZ would like to thank Norm
+Murray and CITA for their hospitality during my long-term visit.
 
-\begin{thebibliography}{}
+\input /home/spz/Latex/lib/bib/references
 
-%\bibitem[\protect\citeauthoryear{Anderson et al.}{2008}]{anderson08}
-% Anderson J.,  Sarajedini A., Bedin L. R., King I. R., Piotto G.,
-%  Reid I. N., Siegel M., Majewski S. R., Paust N. E. Q., Aparicio A.,
-%  Milone A. P., Chaboyer B., Rosenberg A. 2008, AJ, 135, 2055
-%\bibitem[\protect\citeauthoryear{Artymowicz et al.}{1993}]{artymowicz93} Artymowicz P., Lin D. N. C., Wampler E. J. 1993, ApJ, 409, 592 
-%\bibitem[\protect\citeauthoryear{Bartos et al.}{2017}]{Bartos17} Bartos I., Kocsis B., Haiman Z. \& M\'{a}rka S., 2017, ApJ, 835, 165
-%\bibitem[\protect\citeauthoryear{Bartko et al.}{2009}]{Bartko09} Bartko H., Martins F., Trippe S., Fritz T.
-K., Genzel R., Ott T., Eisenhauer F., Gillessen S., Paumard T., Alexander T., Dodds-Eden K., Gerhard O., Levin Y., Mascetti L., Nayakshin S., Perets H.
-B., Perrin G., Pfuhl O., Reid M.
-J., Rouan D., Sternberg A., Trippe S., 2009, ApJ, 697, 1741
-%\bibitem[\protect\citeauthoryear{Bartko et al.}{2010}]{Bartko10} Bartko H., Martins F., Fritz T.
-K., Genzel R., Levin Y., Perets H.
-B., Paumard T., Nayakshin S., Gerhard O., Alexander T., Dodds-Eden K., Eisenhauer F., Gillessen S., Mascetti L., Ott T., Perrin G., Pfuhl O., Reid M.
-J., Rouan D., Zilka M., Sternberg A., 2010, ApJ, 708, 834
-%\bibitem[\protect\citeauthoryear{Baruteau et al.}{2011}]{Baruteau11} Baruteau C., Cuadra J. \& Lin D.N.C., 2011, ApJ, 726, 28
-%\bibitem[\protect\citeauthoryear{Bedin et al.}{2010}]{bedin10} Bedin L. R., Cassisi S., Castelli F., Piotto G., Anderson J., Salaris M., Momany Y., Pietrinferni A. 2010, MNRAS 357, 1038
-%\bibitem[\protect\citeauthoryear{Bender et al.}{2005}]{bender05} Bender R., Kormendy J., Bower G., et al. 2005, ApJ, 631, 280
-%\bibitem[\protect\citeauthoryear{Bruzual \& Charlot}{2003}]{bruzual03} Bruzual G., Charlot S. 2003, MNRAS, 344, 1000 
-%\bibitem[\protect\citeauthoryear{Casassus et al.}{2013}]{casassus13} Casassus S., Hales A., de Gregorio I., Dent B., Belloche A., G\"usten R., M\'enard F., Hughes A.
-M., Wilner D., Salinas V.
-2013, A\&A, 553, 64
-%\bibitem[\protect\citeauthoryear{Ceillier et al.}{2017}]{ceillier17} Ceillier T., Tayar J., Mathur S., Salabert D., Garc\'ia R.
-A., Stello D., Pinsonneault M.
-H., van Sanders J., Beck P.
-G., Bloemen S.
-2017, A\& A, 605, 111
-\bibitem[\protect\citeauthoryear{Chatterjee et al.}{2013}]{chatterjee13} Chatterjee S., Rasio F. A., Sills A., Glebbeek E. 2013, ApJ, 777, 106  
-\bibitem[\protect\citeauthoryear{Farris et al.}{2015}]{farris15} Farris B. D., Duffell P., MacFayden A. I., Haiman Z. 2014, ApJ, 783, 134 
-%\bibitem[\protect\citeauthoryear{Chen \& Amaro-Seoane}{2015}]{chen15} Chen X., Amaro-Seoane P. 2015, Classical and Quantum Gravity, 32, 6 
-%\bibitem[\protect\citeauthoryear{Dotter et al.}{2010}]{dotter10} Dotter, A., Sarajedini A., Anderson J., Aparicio A., Bedin L.
-R., Chaboyer B., Majewski S., Marin-Franch A., Milone A., Paust N., Piotto G., Reid N., Rosenberg A., Siegel M.
-2010, ApJ 708, 698
-%\bibitem[\protect\citeauthoryear{Dalessandro et al.}{2013}]{dalessandro13} Dalessandro E., Ferraro F.
-R., Massari D., Lanzoni B., Miocchi R.
-P., Beccari G., Bellini A., Sills A., Sigurdsson S., Mucciarelli A., Lovisi L.
-2013, ApJ, 778, 135
-%\bibitem[\protect\citeauthoryear{Eggleton}{1983}]{eggleton83} Eggleton P. P. 1983, ApJ, 268, 368 
-%\bibitem[\protect\citeauthoryear{Flock et al.}{2015}]{flock15} Flock M., Ruge J. P., Dzyurkevich N., Henning Th., Klahr H., Wolf S. 2015, A\&A, 574, 68
-%\bibitem[\protect\citeauthoryear{Ferraro et al.}{1997}]{ferraro97}
-%  Ferraro F. R., Paltrinieri B., Fusi Pecci F., Cacciari C., Dorman
-%  B., Rood R. T., Buonanno R., Corsi C. E., Burgarella D., Laget
-%  M. 1997, A\&A, 324, 915
-%\bibitem[\protect\citeauthoryear{Ferraro et al.}{1999}]{ferraro99}
-%  Ferraro F. R., Paltrinieri B., Rood R. T., Dorman B. 1999, ApJ, 522,
-%  983
-%\bibitem[\protect\citeauthoryear{Ferraro et al.}{2004}]{ferraro04}
-%  Ferraro F. R., Beccari G., Rood, R. T., Bellazzini M., Sills A.,
-%  Sabbi E. 2004, ApJ, 603, 127
-%\bibitem[\protect\citeauthoryear{Ferraro, Valenti \& Origlia}{2006}]{ferraro06} Ferraro F. R., Valenti E., Origlia L. 2006, ApJ, 649, 243
-%\bibitem[\protect\citeauthoryear{Ferraro et al.}{2009}]{ferraro09} Ferraro F.
-R., Beccari G., Dalessandro E., Lanzoni B., Sills A., Rood R.
-T., Pecci F.
-F., Karakas A.
-I., Miocchi P., Bovinelli S.
-2009, Nature, 462, 1028
-%\bibitem[\protect\citeauthoryear{Fregeau et al.}{2004}]{fregeau04} Fregeau J. M., Cheung P.,
-%  Portegies Zwart S. F., Rasio F. A. 2004, MNRAS, 352, 1
-%\bibitem[\protect\citeauthoryear{Fregeau, Ivanova \& Rasio}{2009}]{fregeau09} Fregeau J. M., Ivanova N.,
-%  Rasio F. A. 2009, ApJ, 707, 1533
-%\bibitem[\protect\citeauthoryear{Geller at al.}{2009}]{geller09}
-%  Geller A. M., Mathieu R. D., Harris H. C., McClure R. D., 2009,
-%  AJ, 137, 3743
-\bibitem[\protect\citeauthoryear{Geller \& Mathieu}{2011}]{geller11}
-  Geller A. M., Mathieu R. D. 2011, Nature, 478, 356
-\bibitem[\protect\citeauthoryear{Geller \& Mathieu}{2012}]{geller12} Geller A. M., Mathieu R. D. 2012, AJ, 144, 54
-\bibitem[\protect\citeauthoryear{Geller et al.}{2013a}]{geller13a} Geller A. M.,
-de Grijs R., Li C., Hurley J. R. 2013, ApJ, 779, 30
-\bibitem[\protect\citeauthoryear{Geller et al.}{2013b}]{geller13b} Geller A. M., Hurley J. R., Mathieu R. D. 2013, AJ, 145, 8
-\bibitem[\protect\citeauthoryear{Geller \& Leigh}{2015}]{geller15} Geller A. M., Leigh W. W. C. 2015, ApJL, 808, L25 
-%\bibitem[\protect\citeauthoryear{Ghez}{2008}]{ghez08} Ghez A.
-M., Salim S., Weinberg N.
-N., Lu J.
-R., Do T., Dunn J.
-K., Matthews K, Morris M.
-R., Yelda S., Becklin E.
-E., Kremenek T., Milosavlevic M., Naiman J., ApJ, 2008, 689, 1044
-%\bibitem[\protect\citeauthoryear{Ghez}{2008}]{ghez08}
-\bibitem[\protect\citeauthoryear{Gosnell et al.}{2014}]{gosnell14} Gosnell N. M., Mathieu R. D., Geller A. M., Sills A., Leigh N. W. C., Knigge C. 2014, ApJ, 783, 8
-\bibitem[\protect\citeauthoryear{Gosnell et al.}{2015}]{gosnell15} Gosnell N. M., Mathieu R. D., Geller A. M., Sills A., Leigh N. W. C., Knigge C. 2015, ApJ, 814, 163
-\bibitem[\protect\citeauthoryear{Haiman et al.}{2009}]{haiman09} Haiman Z., Kocsis B., Menou K. 2009, ApJ, 700, 1952  
-%\bibitem[\protect\citeauthoryear{Graham \& Spitler}{2009}]{Graham09} Graham A.W. \& Spitler L.R., 2009, MNRAS, 397, 2148
-%\bibitem[\protect\citeauthoryear{Harris et al.}{1996; 2010 update}]{harris96} Harris W. E. 1996, AJ, 112,
-%  1487; 2010 update
-%\bibitem[\protect\citeauthoryear{Heggie}{1975}]{heggie75} Heggie D. C. 1975, MNRAS, 173, 729
-%\bibitem[\protect\citeauthoryear{Heggie \& Hut}{2003}]{heggie03}
-%  Heggie D. C., Hut P. 2003, The Gravitational Million-Body Problem:
-%  A Multidisciplinary Approach to Sar Cluster Dynamics (Cambridge:
-%  Cambridge University Press)
-\bibitem[\protect\citeauthoryear{Hills}{1975}]{hills75} Hills J. G. 1975, AJ, 80, 809
-%\bibitem[\protect\citeauthoryear{Hurley et al.}{2005}]{hurley05}
-%  Hurley J. R., Pols O. R., Aarseth S. J., Tout C. A. 2005, MNRAS,
-%  363, 293
-%\bibitem[\protect\citeauthoryear{Hurley, Aarseth \&
-%    Shara}{2007}]{hurley07} Hurley J. R., Aarseth S. J., Shara M. M. 2007, ApJ, 665, 707
-%\bibitem[\protect\citeauthoryear{Hut \& Bahcall}{1983}]{hut83} Hut P., Bahcall J. N. 1983, ApJ,
-%  268, 319
-%\bibitem[\protect\citeauthoryear{Howarth}{1983}]{howarth83} Howarth I. D. 1983, MNRAS, 203, 301
-\bibitem[\protect\citeauthoryear{Hypki \& Giersz}{2013}]{hypki13} Hypki A., Giersz M. 2013,
-MNRAS, 429, 1221
-\bibitem[\protect\citeauthoryear{Iben}{1991}]{iben91}  Iben I., Jr. 1991, ApJS, 76, 55
-\bibitem[\protect\citeauthoryear{Kelley et al.}{2017}]{kelley17} Kelley L. Z., Blecha L., Hernquist L. 2017, MNRAS, 464, 3131 
-\bibitem[\protect\citeauthoryear{Knigge, Leigh \& Sills}{2009}]{knigge09} Knigge C., Leigh
-  N., Sills A. 2009, Nature, 457, 288
-%\bibitem[\protect\citeauthoryear{Laidler et al.}{2008}]{laidler08} Laidler et al. 2008, ``Synphot Data User's Guide'' (Baltimore, STScI)
-%\bibitem[\protect\citeauthoryear{Lanzoni et al.}{2007}]{lanzoni07} Lanzoni B., Dalessandro E., Ferraro F.
-R., Valenti E., Beccari G., Schiavon R.
-P., Rood R.
-T., Mapelli M., Sigurdsson S.
-2007, ApJ, 663, 1040
-%\bibitem[\protect\citeauthoryear{Kaluzny et al.}{1998}]{kaluzny98} Kaluzny J., Hilditch R. W., Clement C., Rucinski S. M. 1998, MNRAS, 296, 347
-%\bibitem[\protect\citeauthoryear{Kaluzny et al.}{2015}]{kaluzny15} Kaluzny J., Thompson I. B., Narloch W., Pych W., Rozyczka M. 2015, Acta Astronomica, 65, 267 
-\bibitem[\protect\citeauthoryear{Leigh, Sills \& Knigge}{2007}]{leigh07} Leigh
-  N. W. C., Sills A., Knigge C. 2007, ApJ, 661, 210
-%\bibitem[\protect\citeauthoryear{Leigh, Sills \& Knigge}{2008}]{leigh08} Leigh
-%  N. W., Sills A., Knigge C. 2008, ApJ, 678, 564
-%\bibitem[\protect\citeauthoryear{Leigh, Sills \& Knigge}{2009}]{leigh09} Leigh
-%  N. W., Sills A., Knigge C. 2009, MNRAS, 399, L179
-\bibitem[\protect\citeauthoryear{Leigh \& Sills}{2011}]{leigh11} Leigh N. W. C., Sills A. 2011, MNRAS, 410, 2370
-\bibitem[\protect\citeauthoryear{Leigh et al.}{2012}]{leigh12} Leigh N. W. C., Umbreit S.,
-Sills A., Knigge C., De Marchi G., Glebbeek E., Sarajedini A. 2012, MNRAS, 422, 1592
-\bibitem[\protect\citeauthoryear{Leigh et al.}{2013}]{leigh13} Leigh N. W. C., Knigge C.,
-Sills A., Perets H. B., Sarajedini A., Glebbeek E. 2013, MNRAS, 428, 897
-%\bibitem[\protect\citeauthoryear{Leigh et al.}{2014}]{leigh14} Leigh N. W. C., L\"utzgendorf N., 
-%Geller A. M., Maccarone T. J., Heinke C., Sesana A. 2014, MNRAS, 444, 29
-%\bibitem[\protect\citeauthoryear{Leigh et al.}{2016a}]{leigh16a} Leigh N. W. C., Antonini F., Stone N. C., Shara M. M., Merritt D. 2016a, MNRAS, 463, 1605
-%\bibitem[\protect\citeauthoryear{Leigh et al.}{2016b}]{leigh16b} Leigh N. W. C., Stone N. C., Geller A. M., Shara M. M., Muddu H., Solano-Oropeza D., Thomas Y. 2016b, MNRAS, 463, 3311 
-%\bibitem[\protect\citeauthoryear{Leigh et al.}{2016c}]{leigh16c} Leigh N. W. C., Geller A. M., Toonen S. 2016c, ApJ, 818, 21
-%\bibitem[\protect\citeauthoryear{Leigh et al.}{2016d}]{leigh16d} Leigh N. W. C., Shara M. M., Geller A. M. 2016d, MNRAS, 459, 1242
-\bibitem[\protect\citeauthoryear{Leonard}{1989}]{leonard89} Leonard
-  P. J. T. 1989, AJ, 98, 217
-%\bibitem[\protect\citeauthoryear{Leonard \& Linnell}{1992}]{leonard92}
-%  Leonard P. J. T., Linnell A. P. 1992, AJ, 103, 1928
-%\bibitem[\protect\citeauthoryear{Leonard \& Livio}{1995}]{leonard95} Leonard P. J. T., Livio M. 1995,
-%  ApJ, 447, L121
-%\bibitem[\protect\citeauthoryear{Lim, Diaz \& Laidler}{2015}]{lim15} Lim P. L., Diaz R. L., Laidler V. 2015, PySynphot User's Guide (Baltimore, MD: STScI)
-%\bibitem[\protect\citeauthoryear{Lovisi et al.}{2012}]{lovisi12} Lovisi L., Mucciarelli A., Lanzoni B., Ferraro F. R., Gratton R., Dalessandro E., Contreras R. R. 2012, ApJ, 754, 91
-\bibitem[\protect\citeauthoryear{Maeder}{2009}]{maeder09} Maeder A. 2009, 
-Physics, Formation and Evolution of Rotating Stars. Berlin: Springer-Verlag
-\bibitem[\protect\citeauthoryear{Mardling \& Aarseth}{1999}]{mardling99} Mardling R. A., Aarseth S. J. 1999, ASIC, 522, 385  
-%\bibitem[\protect\citeauthoryear{Mapelli et al.}{2006}]{mapelli06}
-%  Mapelli M., Sigurdsson S., Ferraro F. R., Colpi M., Possenti A., Lanzoni B. 2006,
-%  MNRAS, 373, 361
-\bibitem[\protect\citeauthoryear{Mathieu \& Geller}{2009}]{mathieu09}
-  Mathieu R. D., Geller A. R. 2009, Nature, 462, 1032
-\bibitem[\protect\citeauthoryear{McCrea}{1964}]{mccrea64} McCrea
-  W. H. 1964, MNRAS, 128, 147
-\bibitem[\protect\citeauthoryear{Moe \& Kratter}{2018}]{moe18} Moe M., Kratter K. M. 2018, ApJ, 854, 44 
-%\bibitem[\protect\citeauthoryear{Milone et al.}{2008}]{milone08}
-%  Milone A. P., Piotto G., Bedin L. R., Sarajedini A. 2008, MmSAI, 79,
-%  623
-%\bibitem[\protect\citeauthoryear{Milone et al.}{2012}]{milone12} Milone A. P., Piotto G.,
-%Bedin L. R., Aparicio A., Anderson J., Sarajedini A., Marino A. F., Moretti A.,
-%Davies M. B., Chaboyer B., Dotter A., Hempel M., Marin-Franch A., Majewski S.,
-%Paust N. E. Q., Reid I. N., Rosenberg A., Siegel M. 2012, A\&A, 540, 16
-\bibitem[\protect\citeauthoryear{Perets \& Fabrycky}{2009}]{perets09} Perets H. B., Fabrycky D. C. 2009, ApJ, 697, 1048
-%\bibitem[\protect\citeauthoryear{Pickles}{1998}]{pickles98} Pickles A. J. 1998, PASP, 110, 863
-\bibitem[\protect\citeauthoryear{Piotto et al.}{2004}]{piotto04}
-  Piotto G., De Angeli F., King I. R., Djorgovski S. G., Bono G.,
-  Cassisi S., Meylan G., Recio-Blanco A., Rich R. M., Davies M. B. 2004,
-  ApJ, 604, L109
-\bibitem[\protect\citeauthoryear{Rafikov}{2016}]{rafikov16} Rafikov R. R. 2016, ApJ, 827, 111 
-%\bibitem[\protect\citeauthoryear{Piotto et al.}{2007}]{piotto07}
-%Piotto G., Bedin L. R., Anderson J., King I. R., Cassisi S., Milone A. P., Villanova S., Pietrinferni A., Renzini A. 2007, ApJ, 661, L53
-%\bibitem[\protect\citeauthoryear{Piotto et al.}{2015}]{piotto15}
-%  Piotto G., Milone A.
-P., Bedin L.
-R., Anderson J., King I.
-R., Marino A.
-F., Nardiello D., Aparicio A., Barbuy B., Bellini A., Brown T.
-M., Cassisi S., Cool A.
-M., Cunial A., Dalessandro E., D'Antona F., Ferraro F.
-R., Hidalgo S., Lanzoni B., Monelli M., Ortolani S., Renzini A., Sarajedini A., van der Marel R.
-P., Vesperini E., Zoccali M.
-2015, AJ, 149, 91
-%\bibitem[\protect\citeauthoryear{Raghavan et al.}{2010}]{raghavan10} Raghavan D., McAlister H. A., Henry T. J, et al. 2010, ApJS, 190, 1 
-\bibitem[\protect\citeauthoryear{Sandquist et al.}{2003}]{sandquist03} Sandquist E. L., Latham D. W., Shetrone M. D., Milone A. A. E. 2003, AJ, 125, 810
-%\bibitem[\protect\citeauthoryear{Sarajedini et al.}{2007}]{sarajedini07}
-%  Sarajedini A., Bedin L. R., Chaboyer B., Dotter  A., Siegel M.,
-%  Anderson J., Aparicio A., King I., Majewski S., Marin-Franch A.,
-%  Piotto G., Reid  I. N., Rosenberg A., Steven M. 2007, AJ, 133, 1658
-%\bibitem[\protect\citeauthoryear{Sigurdsson \& Phinney}{1993}]{sigurdsson93} Sigurdsson S. \& Phinney S.L. 1993, ApJ, 415, 631 
-%\bibitem[\protect\citeauthoryear{Shara et al.}{1995}]{shara95} Shara
-%  M. M., Drissen L., Bergeron L. E.,  Paresce F. 1995, ApJ, 441, 617
-\bibitem[\protect\citeauthoryear{Shara, Saffer \&
-    Livio}{1997}]{shara97} Shara M. M., Saffer R. A., Livio M. 1997,
-  ApJ, 489, L59
-\bibitem[\protect\citeauthoryear{Sills et al.}{1997}]{sills97} Sills A., Lombardi J. C. Jr.,
-Bailyn C. D., Demarque P., Rasio F. A., Shapiro S. L. 1997, ApJ, 487, 290
-\bibitem[\protect\citeauthoryear{Sills \& Bailyn}{1999}]{sills99} Sills A., Bailyn C. D. 1999,
-  ApJ, 513, 428
-\bibitem[\protect\citeauthoryear{Sills et al.}{2001}]{sills01} Sills A. R., Faber J. A.,
-  Lombardi J. C., Rasio F. A., Waren A. R. 2001, ApJ, 548, 323
-\bibitem[\protect\citeauthoryear{Simunovic, Puzia \& Sills}{2014}]{simunovic14} Simunovic, M., Puzia, T. H., Sills, A. 2014, ApJL, 795, L10
-\bibitem[\protect\citeauthoryear{Simunovic \& Puzia}{2016}]{simunovic16} Simunovic M., Puzia T. H. 2016, MNRAS 462, 3401
-\bibitem[\protect\citeauthoryear{Tobin et al.}{2018}]{tobin18} Tobin J.
-J., Looney L.
-W., Li Z.-Y., Sadavoy S.
-I., Dunham M.
-M.
-Segura-Cox D., Kratter K., Chandler C.
-J., Melis C., Harris R.
-J., Perez L.
-2018, ApJ, 867, 43
-%\bibitem[\protect\citeauthoryear{Sirianni et al.}{2005}]{sirianni05} Sirianni M., Jee M.
-J., Benitez N., Blakeslee J.
-P., Martel A.
-R., Meurer G., Clampin M., De Marchi G., Ford H.
-C., Gilliland R., Hartig G.
-F., Illingworth G.
-D., Mack J., McCann W.
-J.
-2005, PASP, 117, 1049
-%\bibitem[\protect\citeauthoryear{Sollima et al.}{2007}]{sollima07}
-%  Sollima A., Beccari G., Ferraro F. R., Fusi Pecci F., Sarajedini
-%  A. 2008, MNRAS, 380, 781
-%\bibitem[\protect\citeauthoryear{Sollima et al.}{2008}]{sollima08}
-%  Sollima A., Beccari G., Ferraro F. R., Fusi Pecci F., Sarajedini
-%  A. 2007, A\&A, 481, 701
-%\bibitem[\protect\citeauthoryear{Soto et al.}{2017}]{soto17} Soto M., Belloni A., Anderson J., Piotto G., Bedin L.
-R., van der Marel R.
-P., Milone A.
-P., Brown T.
-M., Cool A.
-M., King I.
-R., Sarajedini A., Granata V., Cassisi S., Aparicio A., Hidalgo S., Ortolani S., Nardiello D.
-2017, AJ, 153, 19
-%\bibitem[\protect\citeauthoryear{Spitzer}{1969}]{spitzer69} Spitzer
-%  L. Jr. 1969, ApJ, 168, L139
-%\bibitem[\protect\citeauthoryear{Spitzer}{1987}]{spitzer87} Spitzer L. 1987, Dynamical Evolution of Globular Clusters (Princeton: Princeton University Press)
-%\bibitem[\protect\citeauthoryear{Tout et al.}{1996}]{tout96} Tout C. A., Pols O. R., Eggleton P. P., Han Z. 1996, MNRAS, 281, 257
-\bibitem[\protect\citeauthoryear{van den Berg et al.}{2001}]{vandenberg01} van den Berg M., Orosz J., Verbunt F., Stassun K. 2001, A\&A, 375, 375
-
-\end{thebibliography}
+%\bibliographystyle{/home/spz/Latex/lib/styles/elsevier/elsarticle-num} 
+%\bibliography{references}
 

### 2018-12-10 BSS7782.tex
updated text file, renamed files, and added makefile

--- 2018-12-10 apjl.tex
@@
   Roche-lobe overflow) of each of the three stars as a function of
-  time for the first 1000\,days. (see Fig.\.\ref{fig:topview_at_t0}
+  time for the first 1000\,days. (see Fig.\,\ref{fig:topview_at_t0}
   for a face-on representation of the initial conditions and
@@
 
-\input /home/spz/Latex/lib/bib/references
+\bibliographystyle{apj}
+\bibliography{BBS7782}
 
+%\input /home/spz/Latex/lib/bib/references
 %\bibliographystyle{/home/spz/Latex/lib/styles/elsevier/elsarticle-num} 

### 2018-12-10 compile.sh

@@ -1,0 +1,6 @@
+name=BSS7782
+pdflatex $name
+bibtex $name
+pdflatex $name
+pdflatex $name
+

### 2018-12-10 BSS7782.tex
Update BSS7782.tex

@@
 proposed mechanism should be more frequent in younger clusters with
-ages $\lesssim$ 4-6 Gyr, since the donor will have radiative envelope.
+ages $\lesssim$ 4-6 Gyr, since the donor will have a radiative envelope.
 
@@
 Even more curious, there exists in the old open cluster NGC 188 a
-double BS binary, called Binary 7782.  Specifically, \citet{mathieu09}
+double BS binary, called Binary 7782.
+More generally, the BS population in NGC 188 has a bi-modal period-eccentricity distribution.
+As discussed in \citet{leigh11}, this could be hinting at a triple origin for at least some subset of the total BS population.
+As for Binary 7782, \citet{mathieu09}
 observed a compact and mildly eccentric (i.e., e $\sim$ 0.1) binary
@@
 $10^{-2}$ \citep{leonard89,leigh11,leigh12}.  Typically, such binaries
-have long orbital periods. Dynamically, it difficult to form a
+have long orbital periods. Dynamically, it is difficult to form a
 short-period binary composed of two collision products during a
 collision interaction in a star cluster \citep{2011Sci...334.1380F}.
-So, how did Binary 7782 form?  MENTION BIMODAL P-E DISTRIBUTION, AND
-HOW THIS COULD BE SUGGESTIVE OF A TRIPLE ORIGIN FOR SOME OF THE SUBSET
-OF OBSERVED BSs.
+So, how did Binary 7782 form?
 
@@
   think that {\em moe18} and {\em tobin18} are not the right
-  references}.  This initial configuration for our assumed formation
+  references...NL:  Agreed.  Do you have others to recommend?  These were what came to mind, but 
+  I can do some digging to try to find the more appropriate refs.}.  This initial configuration for our assumed formation
 scenario for Binary 7782, described below, is depicted in
@@
 We consider a scenario where the outer star is filling its Roche lobe
-and is transfers mass to the inner binary.  The mass transfer stream
+and transfers mass to the inner binary.  The mass transfer stream
 gathers at the circularization radius a$_{\rm c}$, and forms a disk
@@
 from the center of mass corresponding to the outer tertiary companion
-defined by the Roche lobe is given by \citep{eggleton83}.
-\simon{Do we really need this eq?}
-\begin{equation}
-\label{eqn:roche}
-R_{\rm L} = \frac{0.49q^{2/3}}{0.6q^{2/3} + {\rm ln}(1 + q^{1/3})}a_{\rm out},
-\end{equation}
-where the mass ratio q is defined as q $=$ m$_{\rm 3}$/(m$_{\rm 1} +$
-m$_{\rm 2}$).  Combining Equation~\ref{eqn:roche} with
+defined by the Roche lobe is given by Equation 2 in \citep{eggleton83}.
+\simon{Do we really need this eq? - NL: Good call, no.  We can definitely remove this to save space, given that this is a Letter.  I have done so.}
+%\begin{equation}
+%\label{eqn:roche}
+%R_{\rm L} = \frac{0.49q^{2/3}}{0.6q^{2/3} + {\rm ln}(1 + q^{1/3})}a_{\rm out},
+%\end{equation}
+%where the mass ratio q is defined as q $=$ m$_{\rm 3}$/(m$_{\rm 1} +$
+%m$_{\rm 2}$).  
+Combining Equation 2 in \citet{eggleton83} (with mass ratio q $=$ m$_{\rm 3}$/(m$_{\rm 1} +$m$_{\rm 2}$)) with
 Equation~\ref{eqn:specangmom1}, we can solve for the circularization
@@
 which we require a$_{\rm c} >$ a$_{\rm in}$, \del{after folding in all
-  constraints from the requirements for dynamical stability}\simon{can
-  we not simply state the constraints?}, an outer tertiary that is
+  constraints from the requirements for dynamical stability (listed in the caption of Figure~\ref{fig:fig2})}\simon{can
+  we not simply state the constraints? - We do, but it is in the caption to save space.  It is all there anyways, so can be brought in to the main text if necessary.}, an outer tertiary that is
 Roche lobe-filling, and a dynamically hard outer tertiary orbit.  Note
 that the range of plotted orbital periods P$_{\rm in}$ corresponding
-to a contact state for the inner binary, assuming \simon{This looks
-  weird:} R$_{\rm 1} =$ R$_{\rm 2} =$ 1 R$_{\odot}$, lies outside the
-range of plotted values for P$_{\rm in}$, since it does not contribute
+to a contact state for the inner binary lies outside the
+range of plotted values for P$_{\rm in}$ (for components with radii of roughly 1 R$_{\odot}$), since it does not contribute
 significantly to constraining the outer orbital properties of a
@@
     transfer?}.  \simon{what is the purpose of extending q to 0.1 and
-    10?} We assume initial component masses of m$_{\rm 1}$ = 1.1
+    10?
+- NL: Fair enough.
+It was arbitrary, admittedly, but supposed to take in to account the fact that the mass ratio changes during MT.
+I suppose I thought it illustrated that nothing much changes upon changing q, hence the conclusions are robust over the entire extent of the MT process, during which the mass ratio of course changes.} We assume initial component masses of m$_{\rm 1}$ = 1.1
   M$_{\rm \odot}$ and m$_{\rm 2}$ = 0.9 M$_{\rm \odot}$ for the inner
@@
   tertiary according to our assumed mass ratio (with our fiducial case
-  corresponding to q $=$ 0.7.  We assume completely conservative mass
+  corresponding to q $=$ 0.7).  We assume completely conservative mass
   transfer for this exercise, and a final mass for the outer tertiary
@@
   Roche-lobe filling outer star. The red curves gives the size at the
-  first giant branch (thick curve) at at the AGB (thin curve). The
-  blue curve the orbital separation at the moment this giant fills its
-  Roche-lobe assuming a circular orbit and a total inner-binary mass
+  first giant branch (thick curve) at the AGB (thin curve). The
+  blue curve gives the orbital separation at the moment this giant fills its
+  Roche-lobe assuming a circular orbit and a total inner binary mass
   of 2.0\,\MSun. The green curves give, under these conditions, the

### 2018-12-10 BSS7782.tex
Update BSS7782.tex

@@
     really sure how to read the figure. What about the alternative in
-    the next figure, which shows tertiary mass vs. orbital period?}
+    the next figure, which shows tertiary mass vs.
+orbital period?
+- NL: I am fine with swapping out this figure for another, ultimately.
+It still does need work.
+Could you send me the files you have for radius as a function of primary mass?
+I can then update the figure with that, using your assumed initial masses for the simulations.
+That *would* basically finish everything I had intended with the figure, so if we still want to remove it after that, that is totally fine.}
 \label{fig:fig2}}
@@
 
-We perform simulations of a triple star system of which the outer star
+We perform simulations of a triple star system for which the outer star
 overfills its Roche lobe while the inner binary remains detached. The
@@
 
-RLOF in triples using a coupled integrator to follow the complex
+RLOF in triples is modeled using a coupled integrator to follow the complex
 hydrodynamics of the mass transfer from the Roche-lobe filling outer
 star to the inner binary, while keeping track of the gravitational
-dynamics of the stars.  The equations of motion of the inner binary is
+dynamics of the stars.  The equations of motion of the inner binary are 
 solved using the semi-symplectic direct N-body integrator
@@
 gravity code. While the inner two stars accrete mass, they also
-accrete the appropriate amoun of angular momentum from the gas.  and
-the the N-body integrator accounts of this appropriately.  For the
+accrete the corresponding amount of angular momentum from the gas.  
+The the N-body integrator accounts of this appropriately.  For the
 radius of the sink particles we adopt $10 R_\odot$ for both stars.
@@
 \citep[see Sect.\.4.3.1 in][]{2013CoPhC.183..456P}.  This coupled
-integrator is based on the splitting of the Hamiltonian much in the
+integrator is based on the splitting of the Hamiltonian, much in the
 same way as is done with two different gravity solvers by
@@
 and m$_{\rm 3}$ = 1.2 M$_{\rm \odot}$ for the tertiary star.  We
-evolved the 1.2\,\MSun\, star using the MESA stellar evolution code
+evolve the 1.2\,\MSun\, star using the MESA stellar evolution code
 \cite{2011ApJS..192....3P} to a radius of about 255\,\RSun.  By this
-time the star has lost 0.13\,\MSun\, in a stellar wind.  With these
-parmeters the orbital separation of the outer binary becomes 3.86\,au,
-and the mass loss has driven a slight eccentricity from initiall
+time the star has lost 0.13\,\MSun\, via a stellar wind.  With these
+parameters the orbital separation of the outer binary becomes 3.86\,au,
+and the mass loss has driven a slight eccentricity deviating from an initially
 circular orbit to about 0.0082 at the moment of Roche-lobe
-overflow. We chose a relative initial inclination of $i = 9^\circ$
-between the inner and the outer orbit.
+overflow. We choose a relative initial inclination of $i = 9^\circ$
+between the inner and the outer orbits.
+%NL: What are the initial orbital separations?
 
@@
   \includegraphics[width=\columnwidth]{fig_t0_N80000_M012MSun1109MSun_a02au_e00_inc9deg.pdf}
-\caption{top view of the triple system in which the outer star
+\caption{Top view of the simulated triple system in which the outer star over-fills its Roche-lobe
   (represented by 80000\,sph particles and a core particle of
@@
 
-In fig.\,\ref{fig:topview_at_t1000day} we show the same triple at
+In fig.\,\ref{fig:topview_at_t1000day} we show the same triple 
 after 1000\,days of evolution.
@@
 \caption{Evolution of the masses (normalized to those at the moment of
-  Roche-lobe overflow) of each of the three stars as a function of
-  time for the first 1000\,days. (see Fig.\,\ref{fig:topview_at_t0}
+  Roche-lobe overflow) for each of the three stars in the simulated triple as a function of
+  time for the first 1000\,days. (see fig.\,\ref{fig:topview_at_t0}
   for a face-on representation of the initial conditions and
@@
 \section{Summary and Discussion} \label{discussion}
-
-This
-choice for the initial mass of the outer tertiary is critical since it
-ensures that the donor star during the mass transfer process will have
-a radiative envelope \citep[e.g.][]{maeder09}.  In turn, this ensures
-that the mass transfer will be maximally conservative, such that the
-accretion stream will be maximally stable, accreting at a stable and
-constant rate \citep[e.g.][]{iben91}.
 
@@
 
-WHAT ELSE?  SOMETHING RELATED TO TIMESCALES AND THE PROBABiLitY OF OBSERVING THE WD?
-
 \end{enumerate}
 
+Our choice for the initial mass of the outer tertiary is critical since it
+ensures that the donor star during the mass transfer process will have
+a radiative envelope \citep[e.g.][]{maeder09}.  In turn, this ensures
+that the mass transfer will be maximally conservative, such that the
+accretion stream will be maximally stable, accreting at a stable and
+roughly constant rate \citep[e.g.][]{iben91}.
+
 Finally, in future work, we intend to explore the implications of the mechanism proposed here for other types of stellar triples.
-The results highlight that specific theoretical predictions can often be made.
+Our results highlight that specific theoretical predictions can often be made.
 For example, if two white dwarfs form the inner compact binary, than circumbinary accretion could push one of them above the Chandrasekhar mass limit.
@@
 This predicts hot hypervelocity WDs with masses very close to the Chandrasekhar mass limit for this scenario.
-Similarly, if the two WDs are replaced with two neutron stars (NSs), then one NS will likely accrete to surpass the critical supernova limit, upon which time it explodes to become a black hole and receives a strong natal kick.
+Similarly, if the two WDs are replaced with two neutron stars (NSs), then one NS could accrete to surpass the critical supernova limit, upon which time it explodes to become a black hole and receives a strong natal kick.
 The NS companion would have a very comparable mass to the newly formed black hole progenitor at the time of explosion, and could potentially be used to constrain the maximum NS mass.

### 2018-12-11 BSS7782.tex
Added Lagrangian radii figure

@@
 \begin{figure}[ht!]
-  \includegraphics[width=\columnwidth]{fig_t600_N80000_M012MSun1109MSun_a02au_e00_inc9deg.pdf}
+  \includegraphics[width=0.49\columnwidth]{lagrange_points_and_sph.pdf}
+~  \includegraphics[width=0.51\columnwidth]{fig_t600_N80000_M012MSun1109MSun_a02au_e00_inc9deg.pdf}
 \caption{Same as Fig.\,\ref{fig:topview_at_t0} but at an age of $t
-  \simeq 996days$.
+  \simeq 996days$. Left panel shows the equipotential surface of the
+  triple overplotted with the gas distribution, the right panel shows
+  just the gas and the stars as bullets.
 \label{fig:topview_at_t1000day}}

### 2018-12-11 src/lagrange_points_and_sph.py
added script to make figure

@@ -1,0 +1,132 @@
+import numpy
+from matplotlib import pyplot
+from amuse.plot import xlabel, ylabel, effective_iso_potential_plot
+from amuse.units import units, constants, nbody_system, quantities
+from amuse.community.hermite0.interface import Hermite
+from amuse.datamodel import Particles
+from amuse import plot as aplot
+from amuse.lab import *
+
+def read_files(filename):
+    b = read_set_from_file(filename+"_binary.amuse", "hdf5", close_file=True)
+    print b
+    c = read_set_from_file(filename+"_core.amuse", "hdf5", close_file=True)
+    print c
+    g = read_set_from_file(filename+"_gas.amuse", "hdf5", close_file=True)
+    print g
+    return b, c, g
+
+def setup_gravity_code(triple):
+    converter = nbody_system.nbody_to_si(1.0|units.MSun, 1.0|units.AU)
+    gravity = Hermite(converter)
+    gravity.particles.add_particles(triple)
+    return gravity
+
+def make_effective_iso_potential_plot(gravity_code, lim):
+    omega = (constants.G * gravity_code.particles.total_mass()
+              / (1.0|units.AU**3)).sqrt()
+    center_of_mass = gravity_code.particles.center_of_mass()[:2]
+
+    """
+    pyplot.rcParams.update({'font.size': 30})
+    figure = pyplot.figure(figsize = (12, 12))
+    ax = pyplot.gca()
+    ax.get_yaxis().get_major_formatter().set_useOffset(False)
+    ax.minorticks_on() 
+    """
+
+    lim = lim.value_in(units.au)
+    #current_axes = pyplot.subplot(1, 1, 1)
+    #current_axes.set_aspect("equal", adjustable = "box")
+    effective_iso_potential_plot(gravity_code, 
+                                 omega,
+                                 xlim = [-lim, lim] | units.AU,
+                                 ylim = [-lim, lim] | units.AU,
+                                 center_of_rotation = center_of_mass,
+                                 fraction_screen_filled=0.8,
+                                 resolution = [4000, 4000],
+                                 number_of_contours = 20)
+    
+#    xlabel('x [au]')
+#    ylabel('y [au]')
+    """
+    pyplot.text(0.6, -0.06, "$L_1$")
[…]

### 2018-12-12 BSS7782.tex
Update BSS7782.tex

@@
   think that {\em moe18} and {\em tobin18} are not the right
-  references...NL:  Agreed.  Do you have others to recommend?  These were what came to mind, but 
-  I can do some digging to try to find the more appropriate refs.}.  This initial configuration for our assumed formation
+  references - NL: I am fine with swapping out this figure for another, ultimately.
+It still does need work.
+Could you send me the files you have for radius as a function of primary mass?
+I can then update the figure with that, using your assumed initial masses for the simulations.
+That *would* basically finish everything I had intended with the figure, so if we still want to remove it after that, that is totally fine.}.
+This initial configuration for our assumed formation
 scenario for Binary 7782, described below, is depicted in

### 2018-12-12 BSS7782.tex
testing

@@
 observed a compact and mildly eccentric (i.e., e $\sim$ 0.1) binary
-star system with an orbital period of $\sim$ 10 days hosting two blue
+star system with an orbital period of $\sim$ 10 days hosting two roughly equal-mass blue
 stragglers.  During a given binary-binary interaction, the probability
@@
 \caption{Orbital separation as a function of the mass of the
-  Roche-lobe filling outer star. The red curves gives the size at the
-  first giant branch (thick curve) at the AGB (thin curve). The
-  blue curve gives the orbital separation at the moment this giant fills its
+  Roche-lobe filling outer star. The red curves gives the size r$_{\rm 3}$ at the
+  first giant branch (thick curve) and at the AGB (thin curve). The
+  blue curve gives the orbital separation a$_{\rm RLOF}$ at the moment this giant fills its
   Roche-lobe assuming a circular orbit and a total inner binary mass
   of 2.0\,\MSun. The green curves give, under these conditions, the
-  maximum orbital separation for a stable inner binary.
+  maximum orbital separation for a stable inner binary or a$_{\rm stable}$.
 \label{fig:tertiarymass_vs_size}}

### 2018-12-13 BSS7782.tex
testing

@@
 orbits, and co-planar triples only since this is what has been
-observed for low-mass tertiaries \cite{2010yCat..73890925T} \simon{I
+observed for low-mass tertiaries \cite{2010yCat..73890925T,moe18} \simon{I
   think that {\em moe18} and {\em tobin18} are not the right
-  references - NL: I am fine with swapping out this figure for another, ultimately.
-It still does need work.
-Could you send me the files you have for radius as a function of primary mass?
-I can then update the figure with that, using your assumed initial masses for the simulations.
-That *would* basically finish everything I had intended with the figure, so if we still want to remove it after that, that is totally fine.}.
+  references - NL: I checked and I think the moe18 reference, at least, is fine, so I added it back in.
+But feel free to remove it, if you prefer.}.
 This initial configuration for our assumed formation
@@
 overflow. We choose a relative initial inclination of $i = 9^\circ$
-between the inner and the outer orbits.
-%NL: What are the initial orbital separations?
+between the inner and the outer orbits, since observed stellar triples composed of low-mass stars have been observed to favor co-planar configurations \citep{moe18}.
+%NL: What are the initial orbital separations?  Why this choice of initial inclination? - I added a sentence and reference to justify it.
 
 In fig.\,\ref{fig:topview_at_t0} we present a top view of the triple
-system at the onset of Roche-lobe overlofw.
+system at the onset of Roche-lobe overflow.
 
@@
 \item The BSs in the inner binary should have roughly equal masses, independent of their initial masses.
-This is because it is the lowest mass object that typically accretes the fastest, since its orbital velocity and distance relative to the circumbinary disk is typically the lowest \citep[e.g.][]{haiman09,farris15,rafikov16,kelley17}.
+This is because it is the lowest mass object that typically accretes the fastest, since its orbital velocity and distance relative to the circumbinary disk is typically the lowest \citep[e.g.][]{kroupa95,bate97,bate00,haiman09,bate12,farris15,rafikov16,kelley17}.
 This quickly brings the mass ratio toward unity.

### 2018-12-19 BSS7782.tex
started working on the text

@@
 companion on to the inner binary via a circumbinary disk.  We apply
-our hypothetical scenario to the observed double blue straggler system
-Binary 7782 in the old open cluster NGC 188, and show that its
-observed properties are naturally reproduced within the context our
-proposed model.  Within the context of the hypothetical formation
-mechanism proposed here, the presented work predicts the following
-properties for the post-mass transfer double BS tertiary: (1) For the
-outer tertiary orbit, the initial orbital period should lie between
-220 days $\lesssim$ P$_{\rm out}$ $\lesssim$ 1100 days, assuming
+our scenario to the observed double blue straggler system Binary 7782
+in the old open cluster NGC 188, and show that its observed properties
+are naturally reproduced within the context our proposed model.
+Within the context of the hypothetical formation mechanism proposed
+here, the presented work predicts the following properties for the
+post-mass transfer double BS tertiary: (1) For the outer tertiary
+orbit, the initial orbital period should lie between 220 days
+$\lesssim$ P$_{\rm out}$ $\lesssim$ 1100 days \simon{Do you think that
+  the initial binary could be as large as 1400 days?}, assuming
 initial masses for the inner binary components of m$_{\rm 1} =$ 1.1
 M$_{\odot}$ and m$_{\rm 2} =$ 0.9 M$_{\odot}$ and an outer tertiary
-mass of m$_{\rm 3} =$ 1.4 M$_{\odot}$. (2) Larger final WD masses, and
-hence core masses for the donor at the time of mass transfer, should
-correspond to larger final outer orbital periods for the tertiary. (3)
-For the inner binary, the rotational axes of the BSs should be aligned
-with each other and the orbital plane of the outer tertiary WD. (4)
-The BSs in the inner binary should have roughly equal masses,
-independent of their initial masses.  This predicts that the initially
-lower mass MS star should accrete the most, and should hence be
-polluted more effectively by the accreted material.  This could be
-observable in the surface layers of a radiative star (i.e., He, C and
-O if the donor is an RGB star, and/or s-process elements if the donor
-is an AGB star). (5) Twin BSs in compact binaries formed from the
-proposed mechanism should be more frequent in younger clusters with
-ages $\lesssim$ 4-6 Gyr, since the donor will have a radiative envelope.
+mass of m$_{\rm 3} = 1.4$ M$_{\odot}$.  After Roche-lobe overflow, the
+outer star turns into a white dwarf (WD). There is a correlation
+bewteen the mass of this WD and the outer orbital period in the sense
+that a more massive white dwarfs will be on a wider orbit.  (3) The
+rotational axes of the BSs in the inner binary should be aligned with
+each other and the orbital plane of the outer tertiary WD. (4) The BSs
+in the inner binary should have roughly equal masses, independent of
+their initial masses.  This predicts that the initially lower mass MS
+star should accrete the most, and should hence be enriched more
+effectively by the accreted material.  This could be observable in the
+surface layers of a radiative star (i.e., He, C and O enrichment if
+the donor is an RGB star, and/or s-process elements if the donor is an
+AGB star). (5) Twin BSs in compact binaries formed from the proposed
+mechanism should be more frequent in younger clusters \simon{WHy not
+  in the field?} with ages $\lesssim$ 4-6 Gyr, since the donor will
+have a radiative envelope. (6) the orbital of the binary BS will be
+tight (typically $\aplt 0.3$\,au) and close to circular ($e \aplt
+0.2$).
 
@@
 main-sequence turn-off (MSTO) in a cluster colour-magnitude diagram
-(CMD) \citep[e.g.][]{1953AJ.....58...61S,simunovic14,simunovic16}.
-Two primary channels for BS formation have been proposed; mass
-transfer from an evolved donor on to a main-sequence star in a binary
-star system
+\citep[e.g.][]{1953AJ.....58...61S,simunovic14,simunovic16}.  Two
+primary channels for BS formation have been proposed; mass transfer
+from an evolved donor on to a main-sequence star in a binary star
+system
 \citep[e.g.][]{mccrea64,997A&A...328..143P,knigge09,mathieu09,leigh11,geller11,geller12,gosnell14,gosnell15},
-and direct stellar collisions involving main-sequence stars mediated
-via direct interactions involving binaries
+and direct stellar collisions involving main-sequence stars possibly
+mediated via binaries
 \citep[e.g.][]{hills75,1997A&A...328..130P,shara97,leigh07,leigh11,leigh13,hypki13,2018arXiv181100058P}.
@@
 of compact main-sequence binaries (ms, ms), and mergers of the inner
-binaries of hierarchical triple star systems induced by Lidov-Kozai
+binaries \cite{+++} of hierarchical triple star systems induced by Lidov-Kozai
 oscillations coupled with tidal damping \citep[e.g.][]{perets09}.
@@
 many BSs with observed properties that defy these simple scenarios.
-\del{For example, in the old open cluster M67, there lurks a candidate
-  triple system that is posited to host \textit{two} BSs
+For example, in the old open cluster M67, there lurks a candidate
+triple system that is posited to host two BSs
 \citep{vandenberg01,sandquist03}.  The observations suggest that the
-  outer tertiary is itself a BS, with a mass $\sim$ 1.7 M$_{\odot}$
-  and orbiting the inner binary with a period of 1188.5 days
-  \citep{sandquist03}.  The inner binary has a period of only 1.068
-  days \citep{vandenberg01}, and hosts a BS of mass 2.52 M$_{\odot}$.}
-In order to form this system after convolving its observed properties
-with its host cluster age, we require at least five stars in order to
-conserve the total system mass \citep{leigh11}.  As explained in
-\citet{leigh11}, this is strongly indicative of a dynamical origin for
-the system, and a single direct interaction involving a binary and a
-triple that resulted in two separate collision events is the most
-probable explanation for its origin (i.e., a single interaction
-involving two multiples with two or more stars is a more likely
-scenario to produce this system than two back-to-back direct
-binary-binary interactions) \citep{2004MNRAS.350..615G}.
+outer tertiary is itself a BS, with a mass $\sim$ 1.7 M$_{\odot}$ and
+orbiting the inner binary with a period of 1188.5 days
+\citep{sandquist03}.  The inner binary has a period of only 1.068 days
+\citep{vandenberg01}, and hosts a BS of mass 2.52 M$_{\odot}$.  In
+order to form this system \del{after convolving its observed
+  properties with its host cluster age,} we require at least five
+stars in order to conserve the total system mass \citep{leigh11}.  As
+explained in \citet{leigh11}, this is strongly indicative of a
+dynamical origin for the system, and a single direct interaction
+involving a binary and a triple that resulted in two separate
+collision events is the most probable explanation for its origin
+(i.e., a single interaction involving two multiples with two or more
+stars is a more likely scenario to produce this system than two
+back-to-back direct binary-binary interactions)
+\citep{2004MNRAS.350..615G}.  \simon{Maybe add something about the
+  curious binary AE Aurigae?}
 
 Even more curious, there exists in the old open cluster NGC 188 a
-double BS binary, called Binary 7782.
-More generally, the BS population in NGC 188 has a bi-modal period-eccentricity distribution.
-As discussed in \citet{leigh11}, this could be hinting at a triple origin for at least some subset of the total BS population.
-As for Binary 7782, \citet{mathieu09}
-observed a compact and mildly eccentric (i.e., e $\sim$ 0.1) binary
-star system with an orbital period of $\sim$ 10 days hosting two roughly equal-mass blue
-stragglers.  During a given binary-binary interaction, the probability
-that not one but two direct (ms, ms) collisions occur is less than
-$10^{-2}$ \citep{leonard89,leigh11,leigh12}.  Typically, such binaries
-have long orbital periods. Dynamically, it is difficult to form a
+double BS binary, called Binary 7782.  More generally, the BS
+population in NGC 188 has a bi-modal period-eccentricity distribution.
+As discussed in \citet{leigh11}, this could be hinting at a triple
+origin for at least some subset of the total BS population.  As for
+Binary 7782, \citet{mathieu09} observed a compact and mildly eccentric
+(i.e., $e \sim 0.1$) binary star system with an orbital period of
+$\sim$ 10 days hosting two roughly equal-mass blue stragglers.  During
+a given binary-binary interaction, the probability that not one but
+two direct (ms, ms) collisions occur is less than $10^{-2}$
+\citep{leonard89,leigh11,leigh12}.  Binaries with collision products
+typically have relatively long orbital periods
+\cite{2011Sci...334.1380F}. Dynamically, it is difficult to form a
 short-period binary composed of two collision products during a
@@
 binaries in general, which involves mass transfer from an outer
-tertiary companion on to an inner MS-MS binary.  In section~\ref{dyn},
-we constrain the range of initial (i.e., pre-mass transfer) orbital
-parameters for a hypothetical outer tertiary companion, using a
-combination of dynamical and stellar evolution-based constraints.  In
-Section~\ref{sims} we present the numerical simulations used to study
-the mass transfer process in our hypothetical triple system, computed
-using the \texttt{AMUSE}\cite{AMUSE} software package, in order to
-study the evolution of the inner and outer orbital parameters during
-mass transfer.  We summarize and discuss the implications of our
-results for compact double BS binaries and, more generally, mass
-transfer in stellar triples in Section~\ref{discussion}.
+tertiary companion on to an inner (ms, ms) binary.  In
+section~\ref{dyn}, we constrain the range of initial (i.e., pre-mass
+transfer) orbital parameters for a hypothetical outer tertiary
+companion, using a combination of dynamical and stellar
+evolution-based constraints.  In Section~\ref{sims} we present the
+numerical simulations used to study the mass transfer process in our
+hypothetical triple system, computed using the
+\texttt{AMUSE}\cite{AMUSE} software package, in order to study the
+evolution of the inner and outer orbital parameters during mass
+transfer.  We summarize and discuss the implications of our results
+for compact double BS binaries and, more generally, mass transfer in
+stellar triples in Section~\ref{discussion}.
 
@@
 semi-major axes are denoted a$_{\rm in}$ and a$_{\rm out}$,
-respectively.  We assume circular orbits for both the inner and outer
-orbits, and co-planar triples only since this is what has been
-observed for low-mass tertiaries \cite{2010yCat..73890925T,moe18} \simon{I
-  think that {\em moe18} and {\em tobin18} are not the right
-  references - NL: I checked and I think the moe18 reference, at least, is fine, so I added it back in.
-But feel free to remove it, if you prefer.}.
-This initial configuration for our assumed formation
-scenario for Binary 7782, described below, is depicted in
-Figure~\ref{fig:fig1}.
+respectively.  For clarity we now assume both orbits, the inner as
+well as the outer to have a small eccentricity and low inclination.
+These assumptions are also supported by the population of observed
+low-mass triples \cite{2010yCat..73890925T,moe18}.  This initial
+configuration for our assumed formation scenario for Binary 7782,
+described below, is depicted in Figure~\ref{fig:fig1}.
 
@@
   via Equation~\ref{eqn:ac}, and marks the mean separation of the
-  circumbinary disk.
+  circumbinary disk.\
+  \simon{Should we also indicate the accretion stream onto the two stars?}
 \label{fig:fig1}}
@@
 about the inner binary, this results in
-\simon{replaced lower case $r$ with upper case.}
 \begin{equation}
@@
 where R$_{\rm L}$ is the radius of the Roche lobe of the outer
-tertiary companion, a$_{\rm c}$ is the semi-major axis of the orbit
+tertiary companion, $a_{\rm c}$ is the semi-major axis of the orbit
 about the inner binary corresponding to the circularization radius and
-v$_{\rm orb,c}$ is the orbital velocity at a$_{\rm c}$.  The distance
+v$_{\rm orb,c}$ is the orbital velocity at $a_{\rm c}$.  The distance
 from the center of mass corresponding to the outer tertiary companion
 defined by the Roche lobe is given by Equation 2 in \citep{eggleton83}.
-\simon{Do we really need this eq? - NL: Good call, no.  We can definitely remove this to save space, given that this is a Letter.  I have done so.}
 %\begin{equation}
@@
   out}$-P$_{\rm in}$-plane for Binary 7782.  We assume initial
-component masses of m$_{\rm 1} =$ 1.1 M$_{\rm \odot}$ and m$_{\rm 2}
-=$ 0.9 M$_{\rm \odot}$ for the inner binary components, and m$_{\rm 3}
-=$ 1.4 M$_{\rm \odot}$ for the outer tertiary.  We compare the
+component masses of $m_{\rm 1} = 1.1$ M$_{\rm \odot}$ and $m_{\rm 2}
+= 0.9$ M$_{\rm \odot}$ for the inner binary components, and $m_{\rm 3}
+= 1.4 M$_{\rm \odot}$ for the outer tertiary.  We compare the
 circularization radius to the semi-major axis of the inner binary, for
-which we require a$_{\rm c} >$ a$_{\rm in}$, \del{after folding in all
-  constraints from the requirements for dynamical stability (listed in the caption of Figure~\ref{fig:fig2})}\simon{can
-  we not simply state the constraints? - We do, but it is in the caption to save space.  It is all there anyways, so can be brought in to the main text if necessary.}, an outer tertiary that is
-Roche lobe-filling, and a dynamically hard outer tertiary orbit.  Note
-that the range of plotted orbital periods P$_{\rm in}$ corresponding
-to a contact state for the inner binary lies outside the
-range of plotted values for P$_{\rm in}$ (for components with radii of roughly 1 R$_{\odot}$), since it does not contribute
-significantly to constraining the outer orbital properties of a
-hypothesized outer WD tertiary.  The thick horizontal solid red line
-shows the allowed range of outer semi-major axes, after folding in all
-of the aforementioned criteria.  As is clear, this makes a relatively
-narrow prediction for the allowed ranges of outer tertiary orbits,
-namely 2.2 $\times$ 10$^{2}$ days $\le$ P$_{\rm out}$ $\le$ 1.1
-$\times$ 10$^3$ days, for our assumed final donor mass.
+which we require $a_{\rm c} > a_{\rm in}$, after folding in all
+constraints from the requirements for dynamical stability (listed in
+the caption of Figure~\ref{fig:fig2}), an outer tertiary that is Roche
+lobe-filling, and a dynamically hard outer tertiary orbit.  Note that
+the range of plotted orbital periods P$_{\rm in}$ corresponding to a
+contact state for the inner binary lies outside the range of plotted
+values for $P_{\rm in}$ (for components with radii of roughly 1
+R$_{\odot}$), since it does not contribute significantly to
+constraining the outer orbital properties of a hypothesized outer WD
+tertiary.  The thick horizontal solid red line shows the allowed range
+of outer semi-major axes, after folding in all of the aforementioned
+criteria.  As is clear, this makes a relatively narrow prediction for
+the allowed ranges of outer tertiary orbits, namely 2.2 $\times$
+10$^{2}$ days $\le$ P$_{\rm out}$ $\le$ 1.1 $\times$ 10$^3$ days, for
+our assumed final donor mass.
 
@@
 
-RLOF in triples is modeled using a coupled integrator to follow the complex
-hydrodynamics of the mass transfer from the Roche-lobe filling outer
-star to the inner binary, while keeping track of the gravitational
-dynamics of the stars.  The equations of motion of the inner binary are 
-solved using the semi-symplectic direct N-body integrator
-\texttt{Huayno} \citep{2012NewA...17..711P}. The hydrodynamics is
-performed with the smoothed-particles hydrodynamics code
-\texttt{Gadget2} \citep{2000ascl.soft03001S}, using an adiabatic
+Roche-lobe overflow in triples is modeled using a coupled integrator
+to follow the complex hydrodynamics of the mass transfer from the
+Roche-lobe filling outer star to the inner binary, while keeping track
+of the gravitational dynamics of the stars.  The equations of motion
+of the inner binary are solved using the symplectic direct N-body
+integrator \texttt{Huayno} \citep{2012NewA...17..711P}. The
+hydrodynamics is performed with the smoothed-particles hydrodynamics
+code \texttt{Gadget2} \citep{2000ascl.soft03001S}, using an adiabatic
 equation of state.  The two inner binary stars are treated as point
@@
 The the N-body integrator accounts of this appropriately.  For the
-radius of the sink particles we adopt $10 R_\odot$ for both stars.
+radius of the sink particles we adopt $2 R_\odot$ for both stars.
 
@@
 its own particles, as well as the gravitational potential of the inner
-binary. The hydrodynamics, in particular the gas drag, in turn affects
-the orbits of the two inner stars. With \texttt{Bridge} we realize a
-second order coupling between the gravitational dynamics and the
-hydrodynamics.  The interval at which the gravity and hydrodynamics
-interact via \texttt{Bridge} depends on the parameters of the system
-we study, but typically we achieve converged solutions when this time
-step is about a fraction of 1/100 of the inner binary orbital period.
+binary. The hydrodynamics, in particular the interaction with the gas,
+in turn affects the orbits of the two inner stars. With
+\texttt{Bridge} we realize a second order coupling between the
+gravitational dynamics and the hydrodynamics.  The interval at which
+the gravity and hydrodynamics interact via \texttt{Bridge} depends on
+the parameters of the system we study, but typically we achieve
+converged solutions when this time step is about a fraction of 1/100
+of the inner binary orbital period.
+
+++++
 
@@
 
-We adopt initial component masses of m$_{\rm 1}$ = 1.1 M$_{\rm \odot}$
-and m$_{\rm 2}$ = 0.9 M$_{\rm \odot}$ for the inner binary components,
-and m$_{\rm 3}$ = 1.2 M$_{\rm \odot}$ for the tertiary star.  We
+We adopt initial component masses of $m_{\rm 1} = 1.1$ M$_{\rm \odot}$
+and $m_{\rm 2} = 0.9$ M$_{\rm \odot}$ for the inner binary components,
+and $m_{\rm 3} = 1.2$ M$_{\rm \odot}$ for the tertiary star.  We
 evolve the 1.2\,\MSun\, star using the MESA stellar evolution code
-\cite{2011ApJS..192....3P} to a radius of about 255\,\RSun.  By this
-time the star has lost 0.13\,\MSun\, via a stellar wind.  With these
-parameters the orbital separation of the outer binary becomes 3.86\,au,
-and the mass loss has driven a slight eccentricity deviating from an initially
-circular orbit to about 0.0082 at the moment of Roche-lobe
-overflow. We choose a relative initial inclination of $i = 9^\circ$
-between the inner and the outer orbits, since observed stellar triples composed of low-mass stars have been observed to favor co-planar configurations \citep{moe18}.
+\cite{2011ApJS..192....3P} to a radius of about 1\,au.  By this time
+the star has lost 0.13\,\MSun\, via a stellar wind.  We turned the
+stellar evolution model, structure and temperature composition, into a
+smoothed-particles representation using the module {\tt
+  StellarModelInSPH} in AMUSE (see chapter 4 in \cite{AMUSE}).  We
+replace the stellar core by a point mass to precent that all the
+resolution will be in the central portion of the star instead of the
+envelope. In a following step we relax the star using the
+hydrodynamics solver. This relaxation process is realized in 100 steps
+during which we reduce the velocity dispersion of individual SPH
+particles to a glasseas structure \citep[see, for example, \S\,3.3 on
+  page 40 in][]{1994astro.ph.10043W}.
+
+With these parameters the orbital separation of the outer binary
+becomes 3.86\,au, and the mass loss has driven a slight eccentricity
+deviating from an initially circular orbit to about 0.0082 at the
+moment of Roche-lobe overflow. We choose a relative initial
+inclination of $i = 9^\circ$ between the inner and the outer orbits,
+since observed stellar triples composed of low-mass stars have been
+observed to favor co-planar configurations \citep{moe18}.
 %NL: What are the initial orbital separations?  Why this choice of initial inclination? - I added a sentence and reference to justify it.
@@
 \caption{Evolution of the masses (normalized to those at the moment of
-  Roche-lobe overflow) for each of the three stars in the simulated triple as a function of
+  RLOF) for each of the three stars in the simulated triple as a function of
   time for the first 1000\,days. (see fig.\,\ref{fig:topview_at_t0}
@@
 \end{figure}
+
+The orbital evolution of the inner binary circumreferenced by a disk
+tends to evove by the accretion of mass and angular momentum. As a
+consequence, the two stars in the binary accumulate mass, and their
+orbit shrinks. The orbital evolution can be approximated, to first order, by:
+\begin{equation}
+  d\ln a \over dt   = - d\ln m_{\rm in} \over dt,
+\end{equation}
+where $a$ and $m_{\rm in}$ are the semimajor-axis and total mass in
+the inner binary.  In the simulations we measure ${\dln a \over dt}
+\simeq -0.0843$\,Myr$^{-1}$.
 
@@
 
-\item The BSs in the inner binary should have roughly equal masses, independent of their initial masses.
-This is because it is the lowest mass object that typically accretes the fastest, since its orbital velocity and distance relative to the circumbinary disk is typically the lowest \citep[e.g.][]{kroupa95,bate97,bate00,haiman09,bate12,farris15,rafikov16,kelley17}.
-This quickly brings the mass ratio toward unity.
-This predicts that the initially lower mass MS star should accrete the most, and should hence be polluted more significantly by any accreted material.
-This could be observable in the surface layers of a radiative star.
-If the donor is an RGB star, the accretor will be enriched in mostly carbon, oxygen and helium.
-If the donor is an AGB star, it will be enriched in mostly s-process elements.
+\item The BSs in the inner binary should have roughly equal masses,
+  independent of their initial masses.  This is because it is the
+  lowest mass object that typically accretes the fastest, since its
+  orbital velocity and distance relative to the circumbinary disk is
+  typically the lowest
+  \citep[e.g.][]{kroupa95,bate97,bate00,haiman09,bate12,farris15,rafikov16,kelley17}.
+  This quickly brings the mass ratio toward unity.  This predicts that
+  the initially lower mass MS star should accrete the most, and should
+  hence be enriched more by any accreted material.  This could be
+  observable in the surface layers of a radiative star.  If the donor
+  is an RGB star, the accretor will be enriched in mostly carbon,
+  oxygen and helium.  If the donor is an AGB star, it will be enriched
+  in mostly s-process elements.
 

### 2018-12-20 BSS7782.tex
some minor update. Regretfully, did not have the time to really get to the paper. Better tomorrow

@@
 \newcommand{\LSun}{\mbox{L$_\odot$}}
+
+\def\apgt{\ {\raise-.5ex\hbox{$\buildrel>\over\sim$}}\ }
+\def\aplt{\ {\raise-.5ex\hbox{$\buildrel<\over\sim$}}\ }
 
@@
   the initial binary could be as large as 1400 days?}, assuming
-initial masses for the inner binary components of m$_{\rm 1} =$ 1.1
-M$_{\odot}$ and m$_{\rm 2} =$ 0.9 M$_{\odot}$ and an outer tertiary
-mass of m$_{\rm 3} = 1.4$ M$_{\odot}$.  After Roche-lobe overflow, the
+initial masses for the inner binary components of $m_{\rm 1} = 1.1$
+M$_{\odot}$ and $m_{\rm 2} =$ 0.9 M$_{\odot}$ and an outer tertiary
+mass of $m_{\rm 3} = 1.4$ M$_{\odot}$.  After Roche-lobe overflow, the
 outer star turns into a white dwarf (WD). There is a correlation
@@
 system
-\citep[e.g.][]{mccrea64,997A&A...328..143P,knigge09,mathieu09,leigh11,geller11,geller12,gosnell14,gosnell15},
+\citep[e.g.][]{mccrea64,1997A&A...328..143P,knigge09,mathieu09,leigh11,geller11,geller12,gosnell14,gosnell15},
 and direct stellar collisions involving main-sequence stars possibly
@@
 Other possible, albeit related, formation mechanisms include mergers
-of compact main-sequence binaries (ms, ms), and mergers of the inner
-binaries \cite{+++} of hierarchical triple star systems induced by Lidov-Kozai
-oscillations coupled with tidal damping \citep[e.g.][]{perets09}.
+of close main-sequence binaries (ms, ms) \cite{2018arXiv181100058P},
+and mergers of the inner binaries of hierarchical triple star systems
+induced by Lidov-Kozai oscillations coupled with tidal damping
+\citep[e.g.][]{perets09}.
 
@@
 tertiary companion on to an inner (ms, ms) binary.  In
-section~\ref{dyn}, we constrain the range of initial (i.e., pre-mass
+section~\ref{sect:dyn}, we constrain the range of initial (i.e., pre-mass
 transfer) orbital parameters for a hypothetical outer tertiary
@@
 
-\section{Constraints on the present-day orbital parameters for a hypothesized tertiary companion in the compact BS Binary 7782} \label{dyn}
+\section{Constraints on the present-day orbital parameters for a hypothesized
+         tertiary companion in the compact BS Binary 7782} \label{sect:dyn}
 
-Consider a hierarchical triple system with component masses m$_{\rm
-  1}$ and m$_{\rm 2}$ for the inner binary, and mass m$_{\rm 3}$ for
+Consider a hierarchical triple system with component masses $m_{\rm
+  1}$ and $m_{\rm 2}$ for the inner binary, and mass $m_{\rm 3}$ for
 the outer tertiary companion.  The inner and outer binary orbital
@@
 from the center of mass corresponding to the outer tertiary companion
-defined by the Roche lobe is given by Equation 2 in \citep{eggleton83}.
-%\begin{equation}
-%\label{eqn:roche}
-%R_{\rm L} = \frac{0.49q^{2/3}}{0.6q^{2/3} + {\rm ln}(1 + q^{1/3})}a_{\rm out},
-%\end{equation}
-%where the mass ratio q is defined as q $=$ m$_{\rm 3}$/(m$_{\rm 1} +$
-%m$_{\rm 2}$).  
-Combining Equation 2 in \citet{eggleton83} (with mass ratio q $=$ m$_{\rm 3}$/(m$_{\rm 1} +$m$_{\rm 2}$)) with
+defined by the Roche lobe is given by Equation 2 in
+\citep{eggleton83}.  Combining Equation 2 in \citet{eggleton83} (with
+mass ratio q $=$ m$_{\rm 3}$/(m$_{\rm 1} +$m$_{\rm 2}$)) with
 Equation~\ref{eqn:specangmom1}, we can solve for the circularization
@@
 = 0.9$ M$_{\rm \odot}$ for the inner binary components, and $m_{\rm 3}
-= 1.4 M$_{\rm \odot}$ for the outer tertiary.  We compare the
+= 1.4 $M$_{\rm \odot}$ for the outer tertiary.  We compare the
 circularization radius to the semi-major axis of the inner binary, for
@@
 
-We perform simulations of a triple star system for which the outer star
-overfills its Roche lobe while the inner binary remains detached. The
-calculations start by evolving the three stars to the same age, which
-is selected such that the outer-most star fills its Roche lobe.
-Constraints for the initial conditions are derived in the previous
-\S\, but in \S\,\ref{Sect:ICs} we summarize the adopted initial
-conditions for the simulations.
+We perform simulations of a triple star system for which the outer
+star overfills its Roche lobe while the inner binary remains
+detached. The calculations start by evolving the three stars to the
+same age, which is selected such that the outer-most star fills its
+Roche lobe.  First order constraints for the initial conditions are
+derived in the previous \S\, but in \S\,\ref{Sect:ICs} we summarize
+the adopted initial conditions for the more detailed simulations.
 
@@
 equation of state.  The two inner binary stars are treated as point
-masses, but we allow them to accrete gas from the outer star.  This is
-realized using sink-particles that co-move with the mass points in the
-gravity code. While the inner two stars accrete mass, they also
-accrete the corresponding amount of angular momentum from the gas.
-The the N-body integrator accounts of this appropriately.  For the
-radius of the sink particles we adopt $2 R_\odot$ for both stars.
+masses, but we allow them to accrete mass and angular momentum from
+the gas liberated by the outer star.  This is realized using
+sink-particles that co-move with the mass points in the gravity
+code. While the inner two stars accrete mass, they also accrete the
+corresponding amount of angular momentum from the gas.  The the N-body
+integrator accounts of this appropriately.  For the radius of the sink
+particles we adopt $2 R_\odot$ for both stars.
 
@@
 
-++++
-
 \subsection{Initial Conditions} \label{Sect:ICs}
@@
 and $m_{\rm 2} = 0.9$ M$_{\rm \odot}$ for the inner binary components,
-and $m_{\rm 3} = 1.2$ M$_{\rm \odot}$ for the tertiary star.  We
-evolve the 1.2\,\MSun\, star using the MESA stellar evolution code
-\cite{2011ApJS..192....3P} to a radius of about 1\,au.  By this time
-the star has lost 0.13\,\MSun\, via a stellar wind.  We turned the
-stellar evolution model, structure and temperature composition, into a
-smoothed-particles representation using the module {\tt
-  StellarModelInSPH} in AMUSE (see chapter 4 in \cite{AMUSE}).  We
-replace the stellar core by a point mass to precent that all the
-resolution will be in the central portion of the star instead of the
-envelope. In a following step we relax the star using the
-hydrodynamics solver. This relaxation process is realized in 100 steps
-during which we reduce the velocity dispersion of individual SPH
+and between $m_{\rm 3} = 1.2$ and $m_{\rm 3} = 1.4$ M$_{\rm \odot}$
+for the tertiary star.  We evolve the tertiary star using the MESA
+stellar-evolution code \cite{2011ApJS..192....3P} to a radius of about
+1\,au.  By this time the star has lost 0.13\,\MSun\, via a stellar
+wind.  We subsequently turn the stellar-evolution model, structure,
+temperature and composition, into a smoothed-particles representation
+using the module {\tt StellarModelInSPH} in AMUSE (see chapter 4 in
+\cite{AMUSE}).  We replace the stellar core by a point mass to prevent
+that all the resolution will be in the central portion of the star
+instead of the envelope. In a following step we relax the star using
+the hydrodynamics solver. This relaxation process is realized in 100
+steps during which we reduce the velocity dispersion of individual SPH
 particles to a glasseas structure \citep[see, for example, \S\,3.3 on
-  page 40 in][]{1994astro.ph.10043W}.
+  page 40 in][]{1994astro.ph.10043W}. During this procedure the
+gaseous envelope of the star tends to expand by about 20\%.  To
+detemrine the radius of the eventual star we calculate Lagrangian
+radii and use the distance to the stellar center which contains 90\%
+of it's mass. This 90\% mass-radius we consider as the stellar radius,
+and match it with the Roche-lobe of the outer orbit.
 
 With these parameters the orbital separation of the outer binary
-becomes 3.86\,au, and the mass loss has driven a slight eccentricity
-deviating from an initially circular orbit to about 0.0082 at the
-moment of Roche-lobe overflow. We choose a relative initial
-inclination of $i = 9^\circ$ between the inner and the outer orbits,
-since observed stellar triples composed of low-mass stars have been
-observed to favor co-planar configurations \citep{moe18}.
-%NL: What are the initial orbital separations?  Why this choice of initial inclination? - I added a sentence and reference to justify it.
-
+becomes $\sim 3.86$\,au, and we adopt the outer orbit to be circular.
+We choose a relative initial inclination between the inner and the
+outer orbit of $i = 0^\circ$, $i = 9^\circ$ and $i = 180^\circ$.  The
+first two choices are motivated by observed stellar triples composed
+of low-mass stars which have been observed to favor co-planar
+configurations \citep{moe18}. To test the effect of a retrogade
+orbiting triple we include the $i = 180^\circ$ case.
+% NL: What are the initial orbital separations?  Why this choice of
+% initial inclination? - I added a sentence and reference to justify
+% it.
 In fig.\,\ref{fig:topview_at_t0} we present a top view of the triple
@@
 
-In fig.\,\ref{fig:mass_evolution_for_M1.2M1.1M0.9a02e00i09}
+In fig.\,\ref{fig:mass_vs_semimajor_axis}
 
 \begin{figure}[ht!]
-  \includegraphics[width=\columnwidth]{fig_MvsTime_N80k_M012R100RSun1109MSun_a02au.pdf}
-\caption{Evolution of the masses (normalized to those at the moment of
-  RLOF) for each of the three stars in the simulated triple as a function of
-  time for the first 1000\,days. (see fig.\,\ref{fig:topview_at_t0}
-  for a face-on representation of the initial conditions and
-  fig.\,\ref{fig:topview_at_t1000day} for the final conditions}.  The
-green and orange dashed curves give the masses of the inner two stars,
-whereas the solid blue curve is the mass of the outer most star.
-\label{fig:mass_evolution_for_M1.2M1.1M0.9a02e00i09}
+  \includegraphics[width=\columnwidth]{fig_mass_vs_semimajor_axis.pdf}
+  \caption{Evolution of the total mass of the inner binary as a
+    function of the orbital separation for four calculations with
+    somewhat different initial conditions (see legend).  The initial
+    binary for the orange curve is presented in
+    fig.\,\ref{fig:topview_at_t0}, and in
+    fig.\,\ref{fig:topview_at_t1000day} we present the final
+    conditions.
+\label{fig:mass_vs_semimajor_axis}}
 \end{figure}
@@
 \begin{equation}
-  d\ln a \over dt   = - d\ln m_{\rm in} \over dt,
+  {d\ln a \over dt}   = {-d\ln m_{\rm in} \over dt},
 \end{equation}
 where $a$ and $m_{\rm in}$ are the semimajor-axis and total mass in
-the inner binary.  In the simulations we measure ${\dln a \over dt}
+the inner binary.  In the simulations we measure ${d\ln a \over dt}
 \simeq -0.0843$\,Myr$^{-1}$.
@@
 
-\item For the predicted outer tertiary orbit, the present-day semi-major axis should lie between 220 days $\lesssim$ P$_{\rm out}$ $\lesssim$ 1100 days, assuming initial masses for the inner binary components of m$_{\rm 1} =$ 1.1 M$_{\odot}$ and m$_{\rm 2} =$ 0.9 M$_{\odot}$ and an outer tertiary mass of m$_{\rm 3} =$ 1.4 M$_{\odot}$.
+\item For the predicted outer tertiary orbit, the present-day semi-major axis should lie between 220 days $\lesssim$ P$_{\rm out}$ $\lesssim$ 1100 days, assuming initial masses for the inner binary components of $m_{\rm 1} = 1.1$ M$_{\odot}$ and $m_{\rm 2} = 0.9$ M$_{\odot}$ and an outer tertiary mass of $m_{\rm 3} = 1.4 $M$_{\odot}$.
 

### 2018-12-21 BSS7782.tex
Updated paper

@@
 for compact double BS binaries and, more generally, mass transfer in
-stellar triples in Section~\ref{discussion}.
+stellar triples in Section~\ref{sect:discussion}.
 
@@
 
-\subsection{AMUSE} \label{amuse}
-
 We perform simulations of a triple star system for which the outer
@@
 Roche lobe.  First order constraints for the initial conditions are
-derived in the previous \S\, but in \S\,\ref{Sect:ICs} we summarize
-the adopted initial conditions for the more detailed simulations.
+derived in the previous \S. In the following two sections we describe
+how we setup these simulations and then discuss the results. The
+calculations are performed using the
+
+\subsection{Setting-up the simulations}
+
+We adopt initial masses of $m_{\rm 1} = 1.1$ M$_{\rm \odot}$ and
+$m_{\rm 2} = 0.9$ M$_{\rm \odot}$ for the inner binary components, and
+between $m_{\rm 3} = 1.2$ and $m_{\rm 3} = 1.4$ M$_{\rm \odot}$ for
+the tertiary star.  We evolve the tertiary star using the MESA
+stellar-evolution code \cite{2011ApJS..192....3P} to a radius of about
+1\,au, at which point we assume it to overfill it's Roche lobe.  By
+this time the star has lost 0.13\,\MSun\, via a stellar wind.
+
+The stellar-evolution model, its structure, temperature and
+composition profiles are turned into a smoothed-particles
+representation using the module {\tt StellarModelInSPH} in AMUSE (see
+chapter 4 in \cite{AMUSE}).  We follow the same procedure as described
+in \cite{2014MNRAS.438.1909D} for simulating the future of the triple
+system \chi Tau (HD 97131) in which the outer-most star overfills it
+Roche lobe to an inner binary.  After generating the hydrodynamical
+representation of the donor star we replace the stellar core by a
+point mass to prevent the majority of the resolution to be confined in
+the star's central region.  In a following step we relax the star
+using the hydrodynamics solver. This relaxation process is realized in
+100 steps during which we reduce the velocity dispersion of individual
+SPH particles to a glasseas structure \citep[see, for example, \S\,3.3
+  on page 40 in][]{1994astro.ph.10043W}. During this procedure the
+gaseous envelope of the star tends to expand by about 20\%.  To
+detemrine the radius of the eventual star we calculate Lagrangian
+radii and use the distance to the stellar center which contains 90\%
+of it's mass. This 90\% mass-radius we consider as the stellar radius,
+and match it with the Roche-lobe of the outer orbit.
+
+With these parameters the orbital separation of the outer binary
+becomes $\sim 3.86$\,au, and we adopt the outer orbit to be circular.
+We choose a relative initial inclination between the inner and the
+outer orbit of $i = 0^\circ$, $i = 9^\circ$, $i = 90^\circ$ and $i =
+180^\circ$.  The first two choices are motivated by observed stellar
+triples composed of low-mass stars which have been observed to favor
+co-planar configurations \citep{moe18}. To test the effect of highly
+inclined and retrogade orbits we include the $i = 90^\circ$ and $i =
+180^\circ$ cases.  In fig.\,\ref{fig:topview_at_t0} we present a top
+view of the triple system at the onset of Roche-lobe overflow.
+
+\begin{figure}[ht!]
+  \includegraphics[width=\columnwidth]{fig_t0_N80000_M012MSun1109MSun_a02au_e00_inc9deg.pdf}
+\caption{Top view of the simulated triple system in which the outer
+  star over-fills its Roche-lobe (represented by 80000\,sph particles
+  and a core particle of 0.4\,\MSun (blue bullet). The two companion
+  stars are represented as red bullets (to the right).
+\label{fig:topview_at_t0}}
+\end{figure}
 
@@
 code. While the inner two stars accrete mass, they also accrete the
-corresponding amount of angular momentum from the gas.  The the N-body
-integrator accounts of this appropriately.  For the radius of the sink
-particles we adopt $2 R_\odot$ for both stars.
+corresponding amount of angular momentum from the gas (see chapter 5
+in \cite{AMUSE}).  The the N-body integrator accounts of this
+appropriately.  For the radius of the sink particles we adopt $10
+R_\odot$ for both stars.
 
@@
 
-\subsection{Initial Conditions} \label{Sect:ICs}
-
-We adopt initial component masses of $m_{\rm 1} = 1.1$ M$_{\rm \odot}$
-and $m_{\rm 2} = 0.9$ M$_{\rm \odot}$ for the inner binary components,
-and between $m_{\rm 3} = 1.2$ and $m_{\rm 3} = 1.4$ M$_{\rm \odot}$
-for the tertiary star.  We evolve the tertiary star using the MESA
-stellar-evolution code \cite{2011ApJS..192....3P} to a radius of about
-1\,au.  By this time the star has lost 0.13\,\MSun\, via a stellar
-wind.  We subsequently turn the stellar-evolution model, structure,
-temperature and composition, into a smoothed-particles representation
-using the module {\tt StellarModelInSPH} in AMUSE (see chapter 4 in
-\cite{AMUSE}).  We replace the stellar core by a point mass to prevent
-that all the resolution will be in the central portion of the star
-instead of the envelope. In a following step we relax the star using
-the hydrodynamics solver. This relaxation process is realized in 100
-steps during which we reduce the velocity dispersion of individual SPH
-particles to a glasseas structure \citep[see, for example, \S\,3.3 on
-  page 40 in][]{1994astro.ph.10043W}. During this procedure the
-gaseous envelope of the star tends to expand by about 20\%.  To
-detemrine the radius of the eventual star we calculate Lagrangian
-radii and use the distance to the stellar center which contains 90\%
-of it's mass. This 90\% mass-radius we consider as the stellar radius,
-and match it with the Roche-lobe of the outer orbit.
-
-With these parameters the orbital separation of the outer binary
-becomes $\sim 3.86$\,au, and we adopt the outer orbit to be circular.
-We choose a relative initial inclination between the inner and the
-outer orbit of $i = 0^\circ$, $i = 9^\circ$ and $i = 180^\circ$.  The
-first two choices are motivated by observed stellar triples composed
-of low-mass stars which have been observed to favor co-planar
-configurations \citep{moe18}. To test the effect of a retrogade
-orbiting triple we include the $i = 180^\circ$ case.
-% NL: What are the initial orbital separations?  Why this choice of
-% initial inclination? - I added a sentence and reference to justify
-% it.
-In fig.\,\ref{fig:topview_at_t0} we present a top view of the triple
-system at the onset of Roche-lobe overflow.
-
-\begin{figure}[ht!]
-  \includegraphics[width=\columnwidth]{fig_t0_N80000_M012MSun1109MSun_a02au_e00_inc9deg.pdf}
-\caption{Top view of the simulated triple system in which the outer star over-fills its Roche-lobe
-  (represented by 80000\,sph particles and a core particle of
-  0.4\,\MSun (blue bullet). The two companion stars are represented as
-  red bullets (to the right).
-\label{fig:topview_at_t0}}
-\end{figure}
-
 \section{Results} \label{results}
 
-In fig.\,\ref{fig:topview_at_t1000day} we show the same triple 
-after 1000\,days of evolution.
+In fig.\,\ref{fig:topview_at_t1000day} we show the same triple after
+1000\,days of evolution.
+
+\cite{2018arXiv181208175M}
 
@@
 
-\section{Summary and Discussion} \label{discussion}
+with the accretion of mass both stars in the inner binary also accrete
+angular momentum.  By the end of the simulation the spins of the two
+blue stragglers is aliened along the orbital angular momeumt axis with
+an angle of $90.0^\circ$ for the primary star and $93.4^\circ$ for the
+secondary star with respect to the argument of pericenter of the inner
+orbit.  By the end of the simulations the spin of the primary is about
+50.5 per day, and 41.5 per day for the secondary star. But by this
+time both stars have accreted only a small portion, and we expect that
+the final spins of both stars is close to break-up.
 
-In this Letter, we have proposed a formation scenario for double BS equal-mass compact binaries, as observed for Binary 7782 in the old open cluster NGC 188.
-The proposed scenario involves mass transfer from an evolved outer tertiary companion, which is accreted by the inner binary via a circumbinary disk.
-Our scenario makes several predictions for the observed properties of a hypothetical outer triple companion, now a WD.
-These are:
+\section{Discussion} \label{sect:discussion}
+
+In order to study the T-tauri binaries V4046 Sgr and DQ Tau
+\cite{2011MNRAS.413.2679D} perform a series of 2D hydrodynamical
+simulations of circum binary disks.  They studied the two observed
+T-tauri system V4046 Sgr and DQ~Tau.
+
+For V4046 Sgr, for which the two stars have comparable masses as in
+our calculation in an ciruclar orbit with a period of only 2.4 days
+they find tha the inner binary accretates at a rate of $\sim
+0.028$\,\MSun/Myr.  For DQ~Taur, which is composed of lower-mass stars
+($m_1 = m_2 \seimq 0.55$\,\MSun) in an eccentric ($e\simeq 0.556$)
+orbit of $\sim 15.8$\,days they find and accretion rate onto the inner
+binary of $\sim 0.027$\,\MSun/Myr.  These values are in the same range
+as in our calculations, which result in an accretion rate of the inner
+binary of 0.027--0.058\,\MSun/Myr (on average measurd over a period of
+about 3000 days).  The highest accretion rate we obtain for the
+simulations with an eccentric inner orbit. Here we applied a small
+correction to compensate for the larger accretion radii adopted for
+the two stars of 10\,\RSun\, compared to 6\,\RSun\, in
+\cite{2011MNRAS.413.2679D}. Interestingly, however,
+\cite{2011MNRAS.413.2679D} find that the primary star in V4046 Sgr
+accretes at an 8\% higher rate than the secondary star, whereas in our
+case the secondary star accretes at a higher rate than the primary
+star by about 1\% to 12\%.  Higher accretion rates in the secondary
+star are realized for eccentric and retrogade inner orbits.
+
+\section{Summary} \label{sect:conclusions}
+
+In this Letter, we have proposed a formation scenario for double BS
+equal-mass compact binaries, as observed for Binary 7782 in the old
+open cluster NGC 188.  The proposed scenario involves mass transfer
+from an evolved outer tertiary companion, which is accreted by the
+inner binary via a circumbinary disk.  Our scenario makes several
+predictions for the observed properties of a hypothetical outer triple
+companion, now a WD.  These are:
 
@@
 
-\item For the predicted outer tertiary orbit, the present-day semi-major axis should lie between 220 days $\lesssim$ P$_{\rm out}$ $\lesssim$ 1100 days, assuming initial masses for the inner binary components of $m_{\rm 1} = 1.1$ M$_{\odot}$ and $m_{\rm 2} = 0.9$ M$_{\odot}$ and an outer tertiary mass of $m_{\rm 3} = 1.4 $M$_{\odot}$.
+\item For the predicted outer tertiary orbit, the present-day
+  semi-major axis should lie between 220 days $\lesssim$ P$_{\rm out}$
+  $\lesssim$ 1100 days, assuming initial masses for the inner binary
+  components of $m_{\rm 1} = 1.1$ M$_{\odot}$ and $m_{\rm 2} = 0.9$
+  M$_{\odot}$ and an outer tertiary mass of $m_{\rm 3} = 1.4
+  $M$_{\odot}$.
 
-\item Larger final WD masses, and hence core masses for the donor at the time of mass transfer, should correspond to larger final outer orbital periods for the tertiary.
-This is because the Roche radius is larger for larger outer orbital periods, such that the donor must evolve to larger radii, and hence core masses, before the onset of mass transfer.
+\item Larger final WD masses, and hence core masses for the donor at
+  the time of mass transfer, should correspond to larger final outer
+  orbital periods for the tertiary.  This is because the Roche radius
+  is larger for larger outer orbital periods, such that the donor must
+  evolve to larger radii, and hence core masses, before the onset of
+  mass transfer.
 
-\item For the inner binary, the rotational axes of the BSs should be aligned with each other and the orbital plane of the outer tertiary WD.
-This is because accretion onto the BS progenitors proceeds via an accretion disk, that forms at the circularization radius and that has an orbital plane aligned with that of the outer tertiary.
+\item For the inner binary, the rotational axes of both the BSs should
+  be aligned with each other and the orbital plane of the outer
+  tertiary WD.  This is because accretion onto the BS progenitors
+  proceeds via an accretion disk, that forms at the circularization
+  radius and that has an orbital plane aligned with that of the outer
+  tertiary.
 
@@
 
-\item Twin BSs in compact binaries formed from the proposed mechanism should be more frequent in younger clusters with ages $\lesssim$ 4-6 Gyr.
-This is because clusters with a main-sequence turn-off mass $\lesssim$ 1.2 M$_{\odot}$ have convective envelopes \citep[e.g.][]{iben91,maedoer09}, and a radiative envelope for the donor in a mass transferring binary ensures stable accretion on to the accretor.
+\item Twin BSs in compact binaries formed from the proposed mechanism
+  should be more frequent in younger clusters with ages $\lesssim$ 4-6
+  Gyr.  This is because clusters with a main-sequence turn-off mass
+  $\lesssim$ 1.2 M$_{\odot}$ have convective envelopes
+  \citep[e.g.][]{iben91,maedoer09}, and a radiative envelope for the
+  donor in a mass transferring binary ensures stable accretion on to
+  the accretor.  \simon{Can we quantify this?}
 
@@
 
-Finally, in future work, we intend to explore the implications of the mechanism proposed here for other types of stellar triples.
-Our results highlight that specific theoretical predictions can often be made.
-For example, if two white dwarfs form the inner compact binary, than circumbinary accretion could push one of them above the Chandrasekhar mass limit.
-Upon explosion, its WD companion would be ejected at roughly the orbital velocity at the time of explosion, producing a hypervelocity WD.
-This predicts hot hypervelocity WDs with masses very close to the Chandrasekhar mass limit for this scenario.
-Similarly, if the two WDs are replaced with two neutron stars (NSs), then one NS could accrete to surpass the critical supernova limit, upon which time it explodes to become a black hole and receives a strong natal kick.
-The NS companion would have a very comparable mass to the newly formed black hole progenitor at the time of explosion, and could potentially be used to constrain the maximum NS mass.
-More work needs to be done here to evaluate whether or not there is any parameter space for the products of this scenario that will allow for a mass determination for the original NS companion in the putative compact NS-NS binary.
+\simon{Why would we try to sell already what we plan on doing. I'de prefer to keep this quet.}
+Finally, in future work, we intend to explore the implications of the
+mechanism proposed here for other types of stellar triples.  Our
+results highlight that specific theoretical predictions can often be
+made.  For example, if two white dwarfs form the inner compact binary,
+than circumbinary accretion could push one of them above the
+Chandrasekhar mass limit.  Upon explosion, its WD companion would be
+ejected at roughly the orbital velocity at the time of explosion,
+producing a hypervelocity WD.  This predicts hot hypervelocity WDs
+with masses very close to the Chandrasekhar mass limit for this
+scenario.  Similarly, if the two WDs are replaced with two neutron
+stars (NSs), then one NS could accrete to surpass the critical
+supernova limit, upon which time it explodes to become a black hole
+and receives a strong natal kick.  The NS companion would have a very
+comparable mass to the newly formed black hole progenitor at the time
+of explosion, and could potentially be used to constrain the maximum
+NS mass.  More work needs to be done here to evaluate whether or not
+there is any parameter space for the products of this scenario that
+will allow for a mass determination for the original NS companion in
+the putative compact NS-NS binary.
 
@@
 American Museum of Natural History.  SPZ would like to thank Norm
-Murray and CITA for their hospitality during my long-term visit.
+Murray and CITA for their hospitality during my long-term visit.  This
+work was supported by the Netherlands Research School for Astronomy
+(NOVA), NWO (grant \# 621.016.701 [LGM-II]).
 

### 2018-12-27 BSS7782.tex
corrected minor typo

@@
 in \cite{2014MNRAS.438.1909D} for simulating the future of the triple
-system \chi Tau (HD 97131) in which the outer-most star overfills it
+system \xi Tau (HD 97131) in which the outer-most star overfills it
 Roche lobe to an inner binary.  After generating the hydrodynamical

### 2018-12-29 BSS7782.tex
edited tex file

@@
 bewteen the mass of this WD and the outer orbital period in the sense
-that a more massive white dwarfs will be on a wider orbit.  (3) The
+that more massive white dwarfs will be on wider orbits.  (3) The
 rotational axes of the BSs in the inner binary should be aligned with
@@
 the donor is an RGB star, and/or s-process elements if the donor is an
-AGB star). (5) Twin BSs in compact binaries formed from the proposed
-mechanism should be more frequent in younger clusters \simon{WHy not
-  in the field?} with ages $\lesssim$ 4-6 Gyr, since the donor will
-have a radiative envelope. (6) the orbital of the binary BS will be
-tight (typically $\aplt 0.3$\,au) and close to circular ($e \aplt
+AGB star). (5) Relative to old dense clusters with high velocity dispersions, 
+twin BSs in compact binaries formed from the proposed 
+mechanism should be more frequent in the Galactic field and younger 
+open clusters with ages $\lesssim$ 4-6 Gyr, since then the donor will
+have a radiative envelope. (6) the orbit of the binary BS will be
+compact (typically $\aplt 0.3$\,au) and close to circular ($e \aplt
 0.2$).
@@
 \citep[e.g.][]{1953AJ.....58...61S,simunovic14,simunovic16}.  Two
-primary channels for BS formation have been proposed; mass transfer
+primary channels for BS formation have been proposed: mass transfer
 from an evolved donor on to a main-sequence star in a binary star
@@
 \citep[e.g.][]{hills75,1997A&A...328..130P,shara97,leigh07,leigh11,leigh13,hypki13,2018arXiv181100058P}.
-Other possible, albeit related, formation mechanisms include mergers
-of close main-sequence binaries (ms, ms) \cite{2018arXiv181100058P},
+Other possible, albeit related, formation mechanism includes mergers
+of close main-sequence binaries (MS-MS) \cite{2018arXiv181100058P},
 and mergers of the inner binaries of hierarchical triple star systems
@@
 \citep{2004MNRAS.350..615G}.  \simon{Maybe add something about the
-  curious binary AE Aurigae?}
+  curious binary AE Aurigae? - NL2: For sure.  I still don't know anything about it... But if I get time over the next few days I will do my research and write something.}
 
@@
 a given binary-binary interaction, the probability that not one but
-two direct (ms, ms) collisions occur is less than $10^{-2}$
-\citep{leonard89,leigh11,leigh12}.  Binaries with collision products
+two direct (MS-MS) collisions will occur is less than $10^{-2}$
+\citep{leonard89,leigh11,leigh12}.  Plus, binaries with collision products
 typically have relatively long orbital periods
@@
 short-period binary composed of two collision products during a
-collision interaction in a star cluster \citep{2011Sci...334.1380F}.
+collisional interaction in a star cluster \citep{2011Sci...334.1380F}.
 So, how did Binary 7782 form?
@@
 binaries in general, which involves mass transfer from an outer
-tertiary companion on to an inner (ms, ms) binary.  In
+tertiary companion on to an inner (MS-MS) binary.  In
 section~\ref{sect:dyn}, we constrain the range of initial (i.e., pre-mass
@@
 respectively.  For clarity we now assume both orbits, the inner as
-well as the outer to have a small eccentricity and low inclination.
+well as the outer, to have a small eccentricity and low inclination.
 These assumptions are also supported by the population of observed
@@
   circumbinary disk.\
-  \simon{Should we also indicate the accretion stream onto the two stars?}
+  \simon{Should we also indicate the accretion stream onto the two stars?
+- NL2:  I have now updated this plot to show two circumstellar disks, and the flow on to thiose.
+I can edit further, if you recommend it, but it's been tough with the down-sizing.
+Maybe if I make things bigger still...
+Anyways, happy to try more.}
 \label{fig:fig1}}
@@
 and transfers mass to the inner binary.  The mass transfer stream
-gathers at the circularization radius a$_{\rm c}$, and forms a disk
+gathers at the circularization radius a$_{\rm c}$, and forms a circumbinary disk
 around the inner binary.  Using conservation of angular momentum, we
@@
 constraining the outer orbital properties of a hypothesized outer WD
-tertiary.  The thick horizontal solid red line shows the allowed range
+tertiary).  The thick horizontal solid red line shows the allowed range
 of outer semi-major axes, after folding in all of the aforementioned
@@
   allowed for the hypothetical outer tertiary orbit of Binary 7782.
-  The solid diagonal black lines show the period corresponding to the
+  The solid diagonal black line shows the period corresponding to the
   circularization radius a$_{\rm c}$ for the mass transfer stream
-  coming from the outer star, for different values of the mass ratio,
-  namely q $=$ 0.1, 0.7, 1, 2 and 10 \simon{before or after mass
-    transfer?}.  \simon{what is the purpose of extending q to 0.1 and
+  coming from the outer star (i.e., at the onset of mass transfer), assuming a mass ratio of q $=$ 0.7 and component masses 
+  of m$_{\rm 1} =$ 0.9 M$_{\odot}$, m$_{\rm 2} =$ 1.1 M$_{\odot}$ and 
+  m$_{\rm 3} =$ 1.4 M$_{\odot}$. \simon{what is the purpose of extending q to 0.1 and
     10?
-- NL: Fair enough.
-It was arbitrary, admittedly, but supposed to take in to account the fact that the mass ratio changes during MT.
-I suppose I thought it illustrated that nothing much changes upon changing q, hence the conclusions are robust over the entire extent of the MT process, during which the mass ratio of course changes.} We assume initial component masses of m$_{\rm 1}$ = 1.1
+- NL2: I was originally thinking that q changes during MT, but I have now removed the other lines and just left the one corresponding to our test case.} We assume initial component masses of m$_{\rm 1}$ = 1.1
   M$_{\rm \odot}$ and m$_{\rm 2}$ = 0.9 M$_{\rm \odot}$ for the inner
@@
   tertiary companion is Roche lobe-filling, assuming a stellar radius
-  of R$_{\rm 3} =$ 200 R$_{\odot}$ (CHANGE, POSSIBLY USING MESA
-  CALCULATIONS?!).  The horizontal dashed red line shows the observed
+  of R$_{\rm 3} =$ 200 R$_{\odot}$.  The horizontal dashed red line shows the observed
   orbital period for Binary 7782, using its observed orbital period
@@
 orbital period?
-- NL: I am fine with swapping out this figure for another, ultimately.
-It still does need work.
-Could you send me the files you have for radius as a function of primary mass?
-I can then update the figure with that, using your assumed initial masses for the simulations.
-That *would* basically finish everything I had intended with the figure, so if we still want to remove it after that, that is totally fine.}
+- NL2: I have now edited this figure, removed the other q curves, increased font size, etc., but am okay with it if you want to remove it for something else.}
 \label{fig:fig2}}
@@
 
+%NL2: Can we also plot the radii at the terminal-age RGB and AGB, or some maximum radius during each evolutionary phase?  
+%I know this will make the plot busier, but these some more relevant to me for mass transfer than the zero-age RGB and 
+%AGB radii.  What do you think?
 \begin{figure}[ht!]
@@
 \caption{Orbital separation as a function of the mass of the
-  Roche-lobe filling outer star. The red curves gives the size r$_{\rm 3}$ at the
+  Roche-lobe filling outer star. The red curves give the stellar radius r$_{\rm 3}$ at the
   first giant branch (thick curve) and at the AGB (thin curve). The
-  blue curve gives the orbital separation a$_{\rm RLOF}$ at the moment this giant fills its
+  blue curves give the orbital separation a$_{\rm RLOF}$ at the moment this giant fills its
   Roche-lobe assuming a circular orbit and a total inner binary mass
   of 2.0\,\MSun. The green curves give, under these conditions, the
-  maximum orbital separation for a stable inner binary or a$_{\rm stable}$.
+  maximum orbital separation for a stable inner binary, or a$_{\rm stable}$.
 \label{fig:tertiarymass_vs_size}}
@@
 
-In Fig.\,\ref{fig:tertiarymass_vs_size} we present..
+%NL2: I tried to fill in the text below, but please go through and edit it as you see fit.
+Also, we need to decide which figures we are going to keep, since I am guessing there is a limit for ApJL.
+This of course relates to the current Figure 2, which you may feel should be removed and would be fine with me.
+In Fig.\,\ref{fig:tertiarymass_vs_size} we present several characteristic sizes and orbital separations for the problem at hand.  
+The red curves show the stellar radius upon reaching the first giant branch (thick curve) and the asymptotic 
+giant branch (thin curves).  The blue curves show the orbital separation at the moment of Roche-lobe overflow for each of the aforementioned giants, 
+assuming a circular orbit and a total inner binary mass of $0.9 + 1.1$ M$_{\odot}$ $=$ 2.0 M$_{\odot}$.  The green curves show 
+for these assumptions the maximum orbital separation for a stable inner binary pair.
 
@@
 
-The stellar-evolution model, its structure, temperature and
-composition profiles are turned into a smoothed-particles
+The stellar-evolution model, including the structure, temperature and
+composition profiles, are turned into a smoothed-particles
 representation using the module {\tt StellarModelInSPH} in AMUSE (see
@@
 in \cite{2014MNRAS.438.1909D} for simulating the future of the triple
-system \xi Tau (HD 97131) in which the outer-most star overfills it
-Roche lobe to an inner binary.  After generating the hydrodynamical
+system $\chi$ Tau (HD 97131) in which the outer-most star overfills its
+Roche lobe and trnsfers mass to an inner binary.  After generating the hydrodynamical
 representation of the donor star we replace the stellar core by a
 point mass to prevent the majority of the resolution to be confined in
-the star's central region.  In a following step we relax the star
+the star's central regions.  In a following step we relax the star
 using the hydrodynamics solver. This relaxation process is realized in
@@
 gaseous envelope of the star tends to expand by about 20\%.  To
-detemrine the radius of the eventual star we calculate Lagrangian
+detemrine the radius of the evolving star we calculate Lagrangian
 radii and use the distance to the stellar center which contains 90\%
-of it's mass. This 90\% mass-radius we consider as the stellar radius,
+of it's mass. From this 90\% mass-radius relation we obtain the stellar radius,
 and match it with the Roche-lobe of the outer orbit.
@@
 We choose a relative initial inclination between the inner and the
-outer orbit of $i = 0^\circ$, $i = 9^\circ$, $i = 90^\circ$ and $i =
-180^\circ$.  The first two choices are motivated by observed stellar
+outer orbits of $i = 0^\circ$, $i = 9^\circ$, $i = 90^\circ$ and $i =
+180^\circ$.  The first two choices are motivated by observed low-mass stellar
 triples composed of low-mass stars which have been observed to favor
@@
 inclined and retrogade orbits we include the $i = 90^\circ$ and $i =
-180^\circ$ cases.  In fig.\,\ref{fig:topview_at_t0} we present a top
-view of the triple system at the onset of Roche-lobe overflow.
+180^\circ$ cases.  In Fig.\,\ref{fig:topview_at_t0} we present a top
+view of the triple system in our simulations at the onset of Roche-lobe overflow.
 
@@
 Roche-lobe overflow in triples is modeled using a coupled integrator
-to follow the complex hydrodynamics of the mass transfer from the
+to follow the complex hydrodynamics of mass transfer from the
 Roche-lobe filling outer star to the inner binary, while keeping track
@@
 integrator \texttt{Huayno} \citep{2012NewA...17..711P}. The
-hydrodynamics is performed with the smoothed-particles hydrodynamics
+hydrodynamics are performed with the smoothed-particles hydrodynamics
 code \texttt{Gadget2} \citep{2000ascl.soft03001S}, using an adiabatic
@@
 corresponding amount of angular momentum from the gas (see chapter 5
-in \cite{AMUSE}).  The the N-body integrator accounts of this
-appropriately.  For the radius of the sink particles we adopt $10
+in \cite{AMUSE}).  The N-body integrator correctly accounts for this.  For the radius of the sink particles we adopt $10
 R_\odot$ for both stars.
@@
 1000\,days of evolution.
+%NL2:  We are labeling the figures differently in the text.
+You label with ``fig.\,\", whereas I use ``Figure~''.
+It doesn't matter to me which we use, just thought I'd highlight this so we come back to it right before submitting.
 
@@
 \simeq -0.0843$\,Myr$^{-1}$.
+%NL2:  The above equation seems incorrect to me, dimensionally.
+It can be fixed by saying the ``specific mass'' and ``dimensionless semi-major axis'', I suppose.
+But then I'd define how you make those parameters dimensionless.
 
-with the accretion of mass both stars in the inner binary also accrete
+With the accretion of mass, both stars in the inner binary also accrete
 angular momentum.  By the end of the simulation the spins of the two
-blue stragglers is aliened along the orbital angular momeumt axis with
+blue stragglers are aligned along the orbital angular momeumt axis with
 an angle of $90.0^\circ$ for the primary star and $93.4^\circ$ for the
@@
 orbit.  By the end of the simulations the spin of the primary is about
-50.5 per day, and 41.5 per day for the secondary star. But by this
-time both stars have accreted only a small portion, and we expect that
-the final spins of both stars is close to break-up.
+50.5 rotations per day, and 41.5 rotations per day for the secondary star. But by this
+time both stars have accreted only a small portion of mass, and we expect that
+the final spins of both stars will be close to break-up (ignoring any spin-down from magnetic braking effects).
+%NL2: I added the bit about magnetic braking above but it needs to be worded better, or removed.  Will come back to it, and feel free to edit it yourself as well..
 
@@
 
-In order to study the T-tauri binaries V4046 Sgr and DQ Tau
+In this Letter, we consider the formation of double blue straggler compct binaries formed 
+from mass transfer from an outer tertiary companion.  As illustrated via SPH simulations, 
+the mass transfer stream forms a circumbinary 
+disk, from which the inner binary components accrete, driving the inner binary toward a 
+mass ratio close to unity.  Our simulations suggest that the inner binary orbital separation 
+should decrease in response to mass accretion, for the assumed initial conditions adopted here.  A more 
+detailed study of the relevant parameter is worth performing in future work.  For example, under what circumstances 
+might the inner binary pair merge, forming a much more massive BS?  Conversely, if the orbital 
+separation of the inner binary \textit{increases} in response to mass transfer, this could 
+cause the triple to become dynamically unstable, subsequently undergoing a chaotic interaction, most likely 
+resulting in the ejection of the lowest mass object in the system.  If one of the two BSs formed in 
+this scenario are ejected, this would leave behind a BS binary with a WD companion.  Such systems 
+are assumed to solely be the result of mass transfer in binary systems, but the results presented here 
+suggest that such an assumption should be regarded with caution.
+
+In order to study the T-tauri binaries V4046 Sgr and DQ Tau, 
 \cite{2011MNRAS.413.2679D} perform a series of 2D hydrodynamical
-simulations of circum binary disks.  They studied the two observed
-T-tauri system V4046 Sgr and DQ~Tau.
+simulations of circumbinary disks.  These authors studied the two observed
+T-tauri systems V4046 Sgr and DQ~Tau, to which we compare our results here.
 
@@
 our calculation in an ciruclar orbit with a period of only 2.4 days
-they find tha the inner binary accretates at a rate of $\sim
-0.028$\,\MSun/Myr.  For DQ~Taur, which is composed of lower-mass stars
+they find that the inner binary accretes at a rate of $\sim
+0.028$\,\MSun/Myr.  For DQ~Tau, which is composed of lower-mass stars
 ($m_1 = m_2 \seimq 0.55$\,\MSun) in an eccentric ($e\simeq 0.556$)
-orbit of $\sim 15.8$\,days they find and accretion rate onto the inner
+orbit of $\sim 15.8$\,days they find an accretion rate onto the inner
 binary of $\sim 0.027$\,\MSun/Myr.  These values are in the same range
-as in our calculations, which result in an accretion rate of the inner
-binary of 0.027--0.058\,\MSun/Myr (on average measurd over a period of
-about 3000 days).  The highest accretion rate we obtain for the
+as in our calculations, which results in an accretion rate of the inner
+binary of 0.027--0.058\,\MSun/Myr (i.e., the average measured over a period of
+about 3000 days in our simulations).  The highest accretion rate we obtain for the
 simulations with an eccentric inner orbit.  Here we applied a small
@@
 star are realized for eccentric and retrogade inner orbits.
+%NL2:  Huh.
+This is interesting.
+Is the physical reason for it that apocenter for the secondary tends to be closer to the circumbinary disk?
+I don't get why retrograde wins though, since naively I'd have thought prograde should lead to lower relative velocities between the secondary and the gas flow, and hence to higher accretion rates.
+What am I missing?
+Is there momentum cancellation via colliding gas, shocks, etc.
+I am missing somewhere?
 
@@
   components of $m_{\rm 1} = 1.1$ M$_{\odot}$ and $m_{\rm 2} = 0.9$
-  M$_{\odot}$ and an outer tertiary mass of $m_{\rm 3} = 1.4
+  M$_{\odot}$ and an initial outer tertiary mass of $m_{\rm 3} = 1.4
   $M$_{\odot}$.
 
-\item Larger final WD masses, and hence core masses for the donor at
+\item Larger final WD masses, and hence larger core masses for the donor at
   the time of mass transfer, should correspond to larger final outer
@@
 
-\item Twin BSs in compact binaries formed from the proposed mechanism
+\item Twin BSs in compact binaries formed from the mechanism proposed here 
   should be more frequent in younger clusters with ages $\lesssim$ 4-6
@@
 
-Our choice for the initial mass of the outer tertiary is critical since it
+We emphasize in closing that our choice for the initial mass of the outer tertiary is critical since it
 ensures that the donor star during the mass transfer process will have
@@
 
-\simon{Why would we try to sell already what we plan on doing. I'de prefer to keep this quet.}
-Finally, in future work, we intend to explore the implications of the
-mechanism proposed here for other types of stellar triples.  Our
-results highlight that specific theoretical predictions can often be
-made.  For example, if two white dwarfs form the inner compact binary,
-than circumbinary accretion could push one of them above the
-Chandrasekhar mass limit.  Upon explosion, its WD companion would be
-ejected at roughly the orbital velocity at the time of explosion,
-producing a hypervelocity WD.  This predicts hot hypervelocity WDs
-with masses very close to the Chandrasekhar mass limit for this
-scenario.  Similarly, if the two WDs are replaced with two neutron
-stars (NSs), then one NS could accrete to surpass the critical
-supernova limit, upon which time it explodes to become a black hole
-and receives a strong natal kick.  The NS companion would have a very
-comparable mass to the newly formed black hole progenitor at the time
-of explosion, and could potentially be used to constrain the maximum
-NS mass.  More work needs to be done here to evaluate whether or not
-there is any parameter space for the products of this scenario that
-will allow for a mass determination for the original NS companion in
-the putative compact NS-NS binary.
+%\simon{Why would we try to sell already what we plan on doing.
+I'de prefer to keep this quet.
+- NL2: To be honest, the ideas came to me, seemed relevant, and I was more interested in if *you* thought they were interesting ideas worth pursuing.
+If that is the case, then yes let's pursue it ourselves and remove this paragraph (now done).
+Happy to work on these ideas, and actually have been in the WD+WD case with a student but it is going very slowly.
+I think this mechanism should tie in nicely with that project though, so I'd like to include you on that if the student gets what he needs to done...
+it might be a lot quicker for us to just do it though.
+:) }
+%Finally, in future work, we intend to explore the implications of the
+%mechanism proposed here for other types of stellar triples.  Our
+%results highlight that specific theoretical predictions can often be
+%made.  For example, if two white dwarfs form the inner compact binary,
+%than circumbinary accretion could push one of them above the
+%Chandrasekhar mass limit.  Upon explosion, its WD companion would be
+%ejected at roughly the orbital velocity at the time of explosion,
+%producing a hypervelocity WD.  This predicts hot hypervelocity WDs
+%with masses very close to the Chandrasekhar mass limit for this
+%scenario.  Similarly, if the two WDs are replaced with two neutron
+%stars (NSs), then one NS could accrete to surpass the critical
+%supernova limit, upon which time it explodes to become a black hole
+%and receives a strong natal kick.  The NS companion would have a very
+%comparable mass to the newly formed black hole progenitor at the time
+%of explosion, and could potentially be used to constrain the maximum
+%NS mass.  More work needs to be done here to evaluate whether or not
+%there is any parameter space for the products of this scenario that
+%will allow for a mass determination for the original NS companion in
+%the putative compact NS-NS binary.
 

### 2018-12-29 BSS7782.tex
included apj.bst and corrected few minor typos

@@
 0.028$\,\MSun/Myr.  For DQ~Tau, which is composed of lower-mass stars
-($m_1 = m_2 \seimq 0.55$\,\MSun) in an eccentric ($e\simeq 0.556$)
+($m_1 = m_2 \simeq 0.55$\,\MSun) in an eccentric ($e\simeq 0.556$)
 orbit of $\sim 15.8$\,days they find an accretion rate onto the inner
@@
 \bibliographystyle{apj}
-\bibliography{BBS7782}
+\bibliography{BSS7782}
 

### 2019-01-04 BSS7782.tex
fixed references to be in Simon's format

@@
 main-sequence turn-off (MSTO) in a cluster colour-magnitude diagram
-\citep[e.g.][]{1953AJ.....58...61S,simunovic14,simunovic16}.  Two
+\citep[e.g.][]{1953AJ.....58...61S,2014ApJ...782...49S}.  Two
 primary channels for BS formation have been proposed: mass transfer
@@
 system
-\citep[e.g.][]{mccrea64,1997A&A...328..143P,knigge09,mathieu09,leigh11,geller11,geller12,gosnell14,gosnell15},
+\citep[e.g.][]{1964MNRAS.128..147M,1997A&A...328..143P,2009Natur.457..288K,2011MNRAS.410.2370L,2011Natur.478..356G},
 and direct stellar collisions involving main-sequence stars possibly
 mediated via binaries
-\citep[e.g.][]{hills75,1997A&A...328..130P,shara97,leigh07,leigh11,leigh13,hypki13,2018arXiv181100058P}.
+\citep[e.g.][]{hills75,1997A&A...328..130P,2007ApJ...661..210L,2013MNRAS.428..897L,2013MNRAS.429.1221H,2018arXiv181100058P}.
 Other possible, albeit related, formation mechanism includes mergers
@@
 induced by Lidov-Kozai oscillations coupled with tidal damping
-\citep[e.g.][]{perets09}.
+\citep[e.g.][]{2009ApJ...697.1048P}.
 
@@
 triple system that is posited to host two BSs
-\citep{vandenberg01,sandquist03}.  The observations suggest that the
+\citep{2001A&A...375..375V,2003AJ....125..810S}.  The observations suggest that the
 outer tertiary is itself a BS, with a mass $\sim$ 1.7 M$_{\odot}$ and
 orbiting the inner binary with a period of 1188.5 days
-\citep{sandquist03}.  The inner binary has a period of only 1.068 days
-\citep{vandenberg01}, and hosts a BS of mass 2.52 M$_{\odot}$.  In
+\citep{{2003AJ....125..810S}.  The inner binary has a period of only 1.068 days
+\citep{2001A&A...375..375V}, and hosts a BS of mass 2.52 M$_{\odot}$.  In
 order to form this system \del{after convolving its observed
   properties with its host cluster age,} we require at least five
-stars in order to conserve the total system mass \citep{leigh11}.  As
-explained in \citet{leigh11}, this is strongly indicative of a
+stars in order to conserve the total system mass \citep{2011MNRAS.410.2370L}.  As
+explained in \citet{2011MNRAS.410.2370L}, this is strongly indicative of a
 dynamical origin for the system, and a single direct interaction
@@
 population in NGC 188 has a bi-modal period-eccentricity distribution.
-As discussed in \citet{leigh11}, this could be hinting at a triple
+As discussed in \citet{2011MNRAS.410.2370L}, this could be hinting at a triple
 origin for at least some subset of the total BS population.  As for
-Binary 7782, \citet{mathieu09} observed a compact and mildly eccentric
+Binary 7782, \citet{2009Natur.462.1032M} observed a compact and mildly eccentric
 (i.e., $e \sim 0.1$) binary star system with an orbital period of
@@
 two direct (MS-MS) collisions will occur is less than $10^{-2}$
-\citep{leonard89,leigh11,leigh12}.  Plus, binaries with collision products
+\citep{1989AJ.....98..217L,2011MNRAS.410.2370L,2012MNRAS.425.2369L}.  Plus, binaries with collision products
 typically have relatively long orbital periods
@@
 defined by the Roche lobe is given by Equation 2 in
-\citep{eggleton83}.  Combining Equation 2 in \citet{eggleton83} (with
+\citep{1983ApJ...268..368E}.  Combining Equation 2 in \citet{1983ApJ...268..368E} (with
 mass ratio q $=$ m$_{\rm 3}$/(m$_{\rm 1} +$m$_{\rm 2}$)) with
@@
   tertiary companion is Roche lobe-filling, assuming a stellar radius
-  of R$_{\rm 3} =$ 200 R$_{\odot}$.  The horizontal dashed red line shows the observed
+  of R$_{\rm 3} =$ 200 R$_{\odot}$ (which corresponds to the maximum stellar radius reached on the AGB for the range of tertiary masses of interest to us.
+The horizontal dashed red line shows the observed
   orbital period for Binary 7782, using its observed orbital period
@@
 triples composed of low-mass stars which have been observed to favor
-co-planar configurations \citep{moe18}. To test the effect of highly
+co-planar configurations \citep{2018ApJ...854...44M}. To test the effect of highly
 inclined and retrogade orbits we include the $i = 90^\circ$ and $i =
@@
   typically the lowest
-  \citep[e.g.][]{kroupa95,bate97,bate00,haiman09,bate12,farris15,rafikov16,kelley17}.
+  \citep[e.g.][]{1995MNRAS.277.1491K,1997MNRAS.285...33B,2000MNRAS.314...33B}.
   This quickly brings the mass ratio toward unity.  This predicts that
@@
   $\lesssim$ 1.2 M$_{\odot}$ have convective envelopes
-  \citep[e.g.][]{iben91,maedoer09}, and a radiative envelope for the
+  \citep[e.g.][]{1991ApJS...76...55I,2009pfer.book.....M}, and a radiative envelope for the
   donor in a mass transferring binary ensures stable accretion on to
@@
 ensures that the donor star during the mass transfer process will have
-a radiative envelope \citep[e.g.][]{maeder09}.  In turn, this ensures
+a radiative envelope \citep[e.g.][]{2009pfer.book.....M}.  In turn, this ensures
 that the mass transfer will be maximally conservative, such that the
 accretion stream will be maximally stable, accreting at a stable and
-roughly constant rate \citep[e.g.][]{iben91}.
+roughly constant rate \citep[e.g.][]{1991ApJS...76...55I}.
 

### 2019-01-14 BSS7782.tex
updated some figures

@@
 
-\title{A Triple Origin for Twin Blue Stragglers in Compact Binaries}
+\title{A Triple Origin for Twin Blue Stragglers in Close Binaries}
 
@@
 companion on to the inner binary via a circumbinary disk.  We apply
-our scenario to the observed double blue straggler system Binary 7782
+this scenario to the observed double blue straggler system Binary 7782
 in the old open cluster NGC 188, and show that its observed properties
-are naturally reproduced within the context our proposed model.
-Within the context of the hypothetical formation mechanism proposed
-here, the presented work predicts the following properties for the
-post-mass transfer double BS tertiary: (1) For the outer tertiary
-orbit, the initial orbital period should lie between 220 days
-$\lesssim$ P$_{\rm out}$ $\lesssim$ 1100 days \simon{Do you think that
-  the initial binary could be as large as 1400 days?}, assuming
-initial masses for the inner binary components of $m_{\rm 1} = 1.1$
-M$_{\odot}$ and $m_{\rm 2} =$ 0.9 M$_{\odot}$ and an outer tertiary
-mass of $m_{\rm 3} = 1.4$ M$_{\odot}$.  After Roche-lobe overflow, the
-outer star turns into a white dwarf (WD). There is a correlation
-bewteen the mass of this WD and the outer orbital period in the sense
-that more massive white dwarfs will be on wider orbits.  (3) The
-rotational axes of the BSs in the inner binary should be aligned with
-each other and the orbital plane of the outer tertiary WD. (4) The BSs
-in the inner binary should have roughly equal masses, independent of
-their initial masses.  This predicts that the initially lower mass MS
-star should accrete the most, and should hence be enriched more
-effectively by the accreted material.  This could be observable in the
-surface layers of a radiative star (i.e., He, C and O enrichment if
-the donor is an RGB star, and/or s-process elements if the donor is an
-AGB star). (5) Relative to old dense clusters with high velocity dispersions, 
-twin BSs in compact binaries formed from the proposed 
-mechanism should be more frequent in the Galactic field and younger 
-open clusters with ages $\lesssim$ 4-6 Gyr, since then the donor will
-have a radiative envelope. (6) the orbit of the binary BS will be
-compact (typically $\aplt 0.3$\,au) and close to circular ($e \aplt
-0.2$).
+are naturally reproduced within the context of the proposed model.
+Based on this model, we predict the following properties for twin blue
+stragglers: (1) For the outer tertiary orbit, the initial orbital
+period should lie between 220 days $\lesssim$ P$_{\rm out}$ $\lesssim$
+1100 days, assuming initial masses for the inner binary components of
+$m_{\rm 1} = 1.1$ M$_{\odot}$ and $m_{\rm 2} =$ 0.9 M$_{\odot}$ and an
+outer tertiary mass of $m_{\rm 3} = 1.4$ M$_{\odot}$.  After
+Roche-lobe overflow, the outer star turns into a white dwarf (WD) of
+0.43 to 0.54\,\MSun. There is a correlation between the mass of this
+WD and the outer orbital period in the sense that more massive white
+dwarfs will be on wider orbits.  (3) The rotational axes of both the
+BSs in the inner binary will be aligned with each other and the
+orbital plane of the outer tertiary WD. (4) The BSs in the inner
+binary will have roughly the same masses, independent of their initial
+masses.  This follows from the more copious accretion of mass onto the
+initially lower mass star.  This star should therefore be enriched
+more effectively by the accreted material.  As a result, one of the
+blue stragglers will appear to be more enriched by He, C and O
+if the donor started to overflow its Roche lobe at the red
+giant branch, or with s-process elements if the donor was on the
+asymptotic giant branch.  (5) Relative to old dense clusters with high
+velocity dispersions, twin BSs in close binaries formed from the
+proposed mechanism should be more frequent in the Galactic field and
+younger open clusters with ages $\lesssim$ 4-6 Gyr, since then the
+donor will have a radiative envelope. (6) the orbit of the binary BS
+will be close (typically $\aplt 0.3$\,au) and close to circular ($e
+\aplt 0.2$).
 
@@
 Blue straggler (BS) stars are brighter and bluer than the
-main-sequence turn-off (MSTO) in a cluster colour-magnitude diagram
+main-sequence turn-off in a cluster colour-magnitude diagram
 \citep[e.g.][]{1953AJ.....58...61S,2014ApJ...782...49S}.  Two
@@
 In spite of these specific predictions for the expected properties of
-BSs formed from each of the above production mechanisms, there exist
-many BSs with observed properties that defy these simple scenarios.
-For example, in the old open cluster M67, there lurks a candidate
-triple system that is posited to host two BSs
-\citep{2001A&A...375..375V,2003AJ....125..810S}.  The observations suggest that the
-outer tertiary is itself a BS, with a mass $\sim$ 1.7 M$_{\odot}$ and
-orbiting the inner binary with a period of 1188.5 days
-\citep{{2003AJ....125..810S}.  The inner binary has a period of only 1.068 days
-\citep{2001A&A...375..375V}, and hosts a BS of mass 2.52 M$_{\odot}$.  In
-order to form this system \del{after convolving its observed
-  properties with its host cluster age,} we require at least five
-stars in order to conserve the total system mass \citep{2011MNRAS.410.2370L}.  As
-explained in \citet{2011MNRAS.410.2370L}, this is strongly indicative of a
+BSs formed from each of the above production mechanisms, many BSs
+exist with observed properties that defy these simple scenarios.  For
+example, in the old open cluster M67, there lurks a candidate triple
+system that is posited to host two BSs
+\citep{2001A&A...375..375V,2003AJ....125..810S}.  The observations
+suggest that the outer tertiary is itself a BS, with a mass $\sim$ 1.7
+M$_{\odot}$ and orbiting the inner binary with a period of $\sim
+1188.5$ days \citep{2003AJ....125..810S}.  The inner binary has a
+period of only $\sim 1.068$ days \citep{2001A&A...375..375V}, and
+hosts a BS of mass $\sim 2.52$ M$_{\odot}$.  In order to form this
+system we require at least five stars in order to conserve the total
+mass in the system \citep{2011MNRAS.410.2370L}.  As explained in
+\citet{2011MNRAS.410.2370L}, this is strongly indicative of a
 dynamical origin for the system, and a single direct interaction
@@
 \citep{2004MNRAS.350..615G}.  \simon{Maybe add something about the
-  curious binary AE Aurigae? - NL2: For sure.  I still don't know anything about it... But if I get time over the next few days I will do my research and write something.}
+  curious binary AE Aurigae? - NL2: For sure.  I still don't know
+  anything about it... But if I get time over the next few days I will
+  do my research and write something.}
 
@@
 \begin{figure}[ht!]
-  \includegraphics[width=\columnwidth]{fig_mass_vs_semimajor_axis.pdf}
+  \includegraphics[width=\columnwidth]{fig_orbital_evolution_for_12MSun.pdf}
+  \includegraphics[width=\columnwidth]{fig_orbital_evolution_for_14MSun.pdf}
   \caption{Evolution of the total mass of the inner binary as a

### 2019-01-14 BSS7782.tex
new figures

@@
 back-to-back direct binary-binary interactions)
-\citep{2004MNRAS.350..615G}.  \simon{Maybe add something about the
-  curious binary AE Aurigae? - NL2: For sure.  I still don't know
-  anything about it... But if I get time over the next few days I will
-  do my research and write something.}
+\citep{2004MNRAS.350..615G}.
 
@@
   via Equation~\ref{eqn:ac}, and marks the mean separation of the
-  circumbinary disk.\
-  \simon{Should we also indicate the accretion stream onto the two stars?
-- NL2:  I have now updated this plot to show two circumstellar disks, and the flow on to thiose.
-I can edit further, if you recommend it, but it's been tough with the down-sizing.
-Maybe if I make things bigger still...
-Anyways, happy to try more.}
+  circumbinary disk.
 \label{fig:fig1}}
@@
 \caption{Parameter space in the P$_{\rm out}$-P$_{\rm in}$-plane
-  allowed for the hypothetical outer tertiary orbit of Binary 7782.
-  The solid diagonal black line shows the period corresponding to the
-  circularization radius a$_{\rm c}$ for the mass transfer stream
-  coming from the outer star (i.e., at the onset of mass transfer), assuming a mass ratio of q $=$ 0.7 and component masses 
-  of m$_{\rm 1} =$ 0.9 M$_{\odot}$, m$_{\rm 2} =$ 1.1 M$_{\odot}$ and 
-  m$_{\rm 3} =$ 1.4 M$_{\odot}$. \simon{what is the purpose of extending q to 0.1 and
-    10?
-- NL2: I was originally thinking that q changes during MT, but I have now removed the other lines and just left the one corresponding to our test case.} We assume initial component masses of m$_{\rm 1}$ = 1.1
-  M$_{\rm \odot}$ and m$_{\rm 2}$ = 0.9 M$_{\rm \odot}$ for the inner
-  binary components, and m$_{\rm 3}$ is computed for the outer
-  tertiary according to our assumed mass ratio (with our fiducial case
-  corresponding to q $=$ 0.7).  We assume completely conservative mass
-  transfer for this exercise, and a final mass for the outer tertiary
-  of 0.6 M$_{\rm \odot}$ once it has become a WD.  The dashed diagonal
-  black line shows a rough criterion for dynamical stability in the
-  triple, approximately following \citet{mardling99} (i.e., a$_{\rm
-    in} <$ 0.1a$_{\rm out}$ is required for long-term dynamical
-  stability in equal-mass co-planar triples).  The vertical solid red
-  lines show the outer orbital periods corresponding to the hard-soft
-  boundary assuming central velocity dispersions of $\sigma =$ 1, 5
-  and 10 km s$^{-1}$.  The vertical dashed black lines show the
-  maximum outer orbital period P$_{\rm out}$ for which the outer
-  tertiary companion is Roche lobe-filling, assuming a stellar radius
-  of R$_{\rm 3} =$ 200 R$_{\odot}$ (which corresponds to the maximum stellar radius reached on the AGB for the range of tertiary masses of interest to us.
-The horizontal dashed red line shows the observed
-  orbital period for Binary 7782, using its observed orbital period
-  and our assumed final inner companion masses (i.e., m$_{\rm 1} =$
-  m$_{\rm 2} =$ 1.4 M$_{\odot}$).  Finally, the thick solid horizontal
-  red line shows the parameter space for P$_{\rm out}$ allowed after
-  considering all of the aforementioned criteria.  \simon{I think that
-    the figure needs work. I like putting the parameter space in terms
-    of orbital periods, but the q=0.1 and q=10 constraints seems
-    not very practical. The red labels are not readable, and I am not
-    really sure how to read the figure. What about the alternative in
-    the next figure, which shows tertiary mass vs.
-orbital period?
-- NL2: I have now edited this figure, removed the other q curves, increased font size, etc., but am okay with it if you want to remove it for something else.}
+  allowed for the hypothetical outer tertiary orbit of Binary 7782
+  before Roche-lobe overflow.  The solid diagonal black line shows the
+  period corresponding to the circularization radius a$_{\rm c}$ for
+  the mass transfer stream coming from the outer star (i.e., at the
+  onset of mass transfer), assuming a mass ratio of q $=$ 0.7 and
+  component masses of m$_{\rm 1} =$ 0.9 M$_{\odot}$, m$_{\rm 2} =$ 1.1
+  M$_{\odot}$ and m$_{\rm 3} =$ 1.4 M$_{\odot}$.  We assume initial
+  component masses of m$_{\rm 1}$ = 1.1 M$_{\rm \odot}$ and m$_{\rm
+    2}$ = 0.9 M$_{\rm \odot}$ for the inner binary components, and
+  m$_{\rm 3}$ is computed for the outer tertiary according to our
+  assumed mass ratio (with our fiducial case corresponding to q $=$
+  0.7).  We assume completely conservative mass transfer for this
+  exercise, and a final mass for the outer tertiary of 0.6 M$_{\rm
+    \odot}$ once it has become a WD.  The dashed diagonal black line
+  shows a rough criterion for dynamical stability in the triple,
+  approximately following \citet{mardling99} (i.e., a$_{\rm in} <$
+  0.1a$_{\rm out}$ is required for long-term dynamical stability in
+  equal-mass co-planar triples).  The vertical solid red lines show
+  the outer orbital periods corresponding to the hard-soft boundary
+  assuming central velocity dispersions of $\sigma =$ 1, 5 and 10 km
+  s$^{-1}$.  The vertical dashed black lines show the maximum outer
+  orbital period P$_{\rm out}$ for which the outer tertiary companion
+  is Roche lobe-filling, assuming a stellar radius of R$_{\rm 3} =$
+  200 R$_{\odot}$ (which corresponds to the maximum stellar radius
+  reached on the AGB for the range of tertiary masses of interest to
+  us.  The horizontal dashed red line shows the observed orbital
+  period for Binary 7782, using its observed orbital period and our
+  assumed final inner companion masses (i.e., m$_{\rm 1} =$ m$_{\rm 2}
+  =$ 1.4 M$_{\odot}$).  Finally, the thick solid horizontal red line
+  shows the parameter space for P$_{\rm out}$ allowed after
+  considering all of the aforementioned criteria.  
 \label{fig:fig2}}
@@
 
-%NL2: Can we also plot the radii at the terminal-age RGB and AGB, or some maximum radius during each evolutionary phase?  
-%I know this will make the plot busier, but these some more relevant to me for mass transfer than the zero-age RGB and 
-%AGB radii.  What do you think?
 \begin{figure}[ht!]
-  \includegraphics[width=\columnwidth]{fig_minimumstablesize.pdf}
-\caption{Orbital separation as a function of the mass of the
-  Roche-lobe filling outer star. The red curves give the stellar radius r$_{\rm 3}$ at the
-  first giant branch (thick curve) and at the AGB (thin curve). The
-  blue curves give the orbital separation a$_{\rm RLOF}$ at the moment this giant fills its
-  Roche-lobe assuming a circular orbit and a total inner binary mass
-  of 2.0\,\MSun. The green curves give, under these conditions, the
-  maximum orbital separation for a stable inner binary, or a$_{\rm stable}$.
+  \includegraphics[width=\columnwidth]{fig_M14MSun_outerorbit.pdf}
+  \caption{Giant radius as a function of the mass of the core of the
+    Roche-lobe filling outer star (dark blue curve).  Here we adopted
+    a donor mass of 1.4\,\MSun, but for an 1.2\,\MSun\, donor curve is
+    quite similar (see dotted dark-blue curve).  The red squares in
+    the curve show the parameters for which we performed more detailed
+    gravitational-hydrodynamical simulations (see \S\,\ref{sims}).
+    The horizontal dashed line shows the orbital separation of the
+    observed twin blue stragger 7782.  The initial triple in which it
+    possibly formed must at least have been dynamically stable. The
+    minimal orbital separation for the inner binary for which the
+    triple is stable is given by the lower green colored curve.
+    Donors which are smaller than about 100\,\RSun\, (dark blue curve
+    indicated with a$_{\rm stable}$) result in a dynamically unstable
+    triple. The minimal core mass associated with a stable triple is
+    then indicated by the left-most vertikcal dotted line.  The
+    orbital separation at which the donor star overfills its Roche
+    lobe is indicated with the light-blue curve. The top curve (dark
+    red) shows an estimate of the final orbit separation of the outer
+    star, and therefore of the final orbit of the white dwarf around
+    the inner twin blue straggler.  For core masses $\apgt
+    0.5$\,\MSun\, the final orbital separataion, after mass transfer,
+    is smaller than the initial orbit.  Here we adopted an initial
+    inner binary mass of (1.0+0.9)\,\MSun\, and a final twin-blue
+    straggler mass of (1.4+1.4)\,\MSun.
 \label{fig:tertiarymass_vs_size}}
@@
 
-%NL2: I tried to fill in the text below, but please go through and edit it as you see fit.
-Also, we need to decide which figures we are going to keep, since I am guessing there is a limit for ApJL.
-This of course relates to the current Figure 2, which you may feel should be removed and would be fine with me.
-In Fig.\,\ref{fig:tertiarymass_vs_size} we present several characteristic sizes and orbital separations for the problem at hand.  
-The red curves show the stellar radius upon reaching the first giant branch (thick curve) and the asymptotic 
-giant branch (thin curves).  The blue curves show the orbital separation at the moment of Roche-lobe overflow for each of the aforementioned giants, 
-assuming a circular orbit and a total inner binary mass of $0.9 + 1.1$ M$_{\odot}$ $=$ 2.0 M$_{\odot}$.  The green curves show 
-for these assumptions the maximum orbital separation for a stable inner binary pair.
+In Fig.\,\ref{fig:tertiarymass_vs_size} we present several
+characteristic sizes and orbital separations for the problem at hand.
+The red curves show the stellar radius upon reaching the first giant
+branch (thick curve) and the asymptotic giant branch (thin curves).
+The blue curves show the orbital separation at the moment of
+Roche-lobe overflow for each of the aforementioned giants, assuming a
+circular orbit and a total inner binary mass of $0.9 + 1.1$
+M$_{\odot}$ $=$ 2.0 M$_{\odot}$.  The green curves show for these
+assumptions the maximum orbital separation for a stable inner binary
+pair.
 
@@
 \begin{figure}[ht!]
-  \includegraphics[width=\columnwidth]{fig_t0_N80000_M012MSun1109MSun_a02au_e00_inc9deg.pdf}
+  \includegraphics[width=\columnwidth]{fig_BBSS_gas_M14Msun_A010au_t0002.pdf}
 \caption{Top view of the simulated triple system in which the outer
@@
 \begin{figure}[ht!]
-  \includegraphics[width=0.49\columnwidth]{lagrange_points_and_sph.pdf}
-~  \includegraphics[width=0.51\columnwidth]{fig_t600_N80000_M012MSun1109MSun_a02au_e00_inc9deg.pdf}
+  \includegraphics[width=0.49\columnwidth]{fig_BBSS_Lgas_M14Msun_A010au_t3360.pdf}
+~  \includegraphics[width=0.51\columnwidth]{fig_BBSS_gas_M14Msun_A010au_t3360.pdf}
 \caption{Same as Fig.\,\ref{fig:topview_at_t0} but at an age of $t

### 2019-01-14 BSS7782.tex
updated text and figures

@@
 binaries in general, which involves mass transfer from an outer
-tertiary companion on to an inner (MS-MS) binary.  In
-section~\ref{sect:dyn}, we constrain the range of initial (i.e., pre-mass
-transfer) orbital parameters for a hypothetical outer tertiary
-companion, using a combination of dynamical and stellar
+tertiary companion on to an inner binary composed to two main-sequence
+stars.  In section~\ref{sect:dyn}, we constrain the range of initial
+(i.e., pre-mass transfer) orbital parameters for a hypothetical outer
+tertiary companion, using a combination of dynamical and stellar
 evolution-based constraints.  In Section~\ref{sims} we present the
-numerical simulations used to study the mass transfer process in our
-hypothetical triple system, computed using the
-\texttt{AMUSE}\cite{AMUSE} software package, in order to study the
-evolution of the inner and outer orbital parameters during mass
-transfer.  We summarize and discuss the implications of our results
-for compact double BS binaries and, more generally, mass transfer in
-stellar triples in Section~\ref{sect:discussion}.
+numerical simulations used to study the mass transfer process triple
+system with orbital parameters that, according to our expectations,
+for promising progenitors for the twin BS 7782.  The calculations are
+performed using the Astrophysical Multipurpose Software Environment
+(\texttt{AMUSE} for short) \cite{AMUSE} with a combination of stellar
+evolution, hydrodynamical and gravitational simulations.  with these
+calculations we further constrain the possible range of initial
+parameters that naturally lead to twin BS with orbital parameters
+similar to the 7782 system.  We summarize and discuss the implications
+of our results for compact double BS binaries and, more generally,
+mass transfer in stellar triples in Section~\ref{sect:discussion}.
 
@@
 
-Consider a hierarchical triple system with component masses $m_{\rm
-  1}$ and $m_{\rm 2}$ for the inner binary, and mass $m_{\rm 3}$ for
-the outer tertiary companion.  The inner and outer binary orbital
-semi-major axes are denoted a$_{\rm in}$ and a$_{\rm out}$,
-respectively.  For clarity we now assume both orbits, the inner as
-well as the outer, to have a small eccentricity and low inclination.
-These assumptions are also supported by the population of observed
-low-mass triples \cite{2010yCat..73890925T,moe18}.  This initial
-configuration for our assumed formation scenario for Binary 7782,
-described below, is depicted in Figure~\ref{fig:fig1}.
+In our scenario we start with a binary star with component masses
+$m_{\rm 1}$ and $m_{\rm 2}$ that is orbited tertiary of mass
+$m_3$. The inner and outer binary orbital semi-major axes are denoted
+a$_{\rm in}$ and a$_{\rm out}$, respectively.  For clarity we now
+assume both orbits, the inner as well as the outer, to have negligible
+eccentricity and low inclination.  These assumptions are also
+supported by the population of observed low-mass triples
+\cite{2010yCat..73890925T,moe18}.  This initial configuration for our
+assumed formation scenario for Binary 7782, described below, is
+depicted in Figure~\ref{fig:fig1}.
 
@@
 
-We consider a scenario where the outer star is filling its Roche lobe
-and transfers mass to the inner binary.  The mass transfer stream
-gathers at the circularization radius a$_{\rm c}$, and forms a circumbinary disk
-around the inner binary.  Using conservation of angular momentum, we
-equate the specific angular momentum of the accreted mass at the inner
-Lagrangian point of the (outer) donor star to the final specific
-angular momentum of the accretion stream at the circularization radius
-about the inner binary, this results in
+According to our scenario $m_3 > m_1 > m_2$ and the outer orbit is
+sufficiently small that the tertiary star is filling its Roche lobe
+and transfers mass to the inner binary before it leaves the asumptotic
+giant branch. We constrain the inner orbit by requiring the triple
+system to be dynamicall stable, for which we adopt eq.\,90 in
+\cite{2001MNRAS.321..398M}.  While transferring mass, the accretion
+stream gathers around the inner binary at the circularization radius
+a$_{\rm c}$, and forms a circumbinary disk.  Using conservation of
+angular momentum, we equate the specific angular momentum of the
+accreted mass at the inner Lagrangian point of the (outer) donor star
+to the final specific angular momentum of the accretion stream at the
+circularization radius about the inner binary, this results in
 \begin{equation}
@@
 v$_{\rm orb,c}$ is the orbital velocity at $a_{\rm c}$.  The distance
-from the center of mass corresponding to the outer tertiary companion
-defined by the Roche lobe is given by Equation 2 in
-\citep{1983ApJ...268..368E}.  Combining Equation 2 in \citet{1983ApJ...268..368E} (with
-mass ratio q $=$ m$_{\rm 3}$/(m$_{\rm 1} +$m$_{\rm 2}$)) with
-Equation~\ref{eqn:specangmom1}, we can solve for the circularization
+from the center of mass corresponding to the tertiary defined by the
+Roche lobe is given by Equation 2 in \citep{1983ApJ...268..368E}.
+Combining Equation 2 in \citet{1983ApJ...268..368E} (with mass ratio q
+$=$ m$_{\rm 3}$/(m$_{\rm 1} +$m$_{\rm 2}$)) with
+Equation~\ref{eqn:specangmom1}, we solve for the circularization
 radius as a function of a$_{\rm out}$ and the assumed stellar masses:
@@
   out}$-P$_{\rm in}$-plane for Binary 7782.  We assume initial
-component masses of $m_{\rm 1} = 1.1$ M$_{\rm \odot}$ and $m_{\rm 2}
-= 0.9$ M$_{\rm \odot}$ for the inner binary components, and $m_{\rm 3}
-= 1.4 $M$_{\rm \odot}$ for the outer tertiary.  We compare the
+component masses of $m_{\rm 1} = 1.1$ M$_{\rm \odot}$ and $m_{\rm 2} =
+0.9$ M$_{\rm \odot}$ for the inner binary components, and $m_{\rm 3} =
+1.4 $M$_{\rm \odot}$ for the outer tertiary.  We compare the
 circularization radius to the semi-major axis of the inner binary, for
@@
 the caption of Figure~\ref{fig:fig2}), an outer tertiary that is Roche
-lobe-filling, and a dynamically hard outer tertiary orbit.  Note that
-the range of plotted orbital periods P$_{\rm in}$ corresponding to a
-contact state for the inner binary lies outside the range of plotted
-values for $P_{\rm in}$ (for components with radii of roughly 1
-R$_{\odot}$), since it does not contribute significantly to
-constraining the outer orbital properties of a hypothesized outer WD
-tertiary).  The thick horizontal solid red line shows the allowed range
-of outer semi-major axes, after folding in all of the aforementioned
-criteria.  As is clear, this makes a relatively narrow prediction for
-the allowed ranges of outer tertiary orbits, namely 2.2 $\times$
+lobe-filling, and a dynamically hard outer tertiary orbit.  \simon{Why
+  do you consider it important to mention that the orbit is hard, and
+  for what environment did you consider this?}  Note that the range of
+plotted orbital periods P$_{\rm in}$ corresponding to a contact state
+for the inner binary lies outside the range of plotted values for
+$P_{\rm in}$ (for components with radii of roughly 1 R$_{\odot}$),
+since it does not contribute to constraining the outer orbital
+properties).  The thick horizontal solid red line shows the allowed
+range of outer semi-major axes, after folding in all of the
+aforementioned criteria.  These constraints result in a rather narrow
+range of initial conditions for the outer orbit, namely 2.2 $\times$
 10$^{2}$ days $\le$ P$_{\rm out}$ $\le$ 1.1 $\times$ 10$^3$ days, for
-our assumed final donor mass.
+which the tertiary star overfills its Roche lobe, the triple is (at
+least initially) dynamically stable and the accretion stream forms a
+gaseous ring around the inner binary.
 
@@
     orbital separation at which the donor star overfills its Roche
-    lobe is indicated with the light-blue curve. The top curve (dark
-    red) shows an estimate of the final orbit separation of the outer
-    star, and therefore of the final orbit of the white dwarf around
-    the inner twin blue straggler.  For core masses $\apgt
-    0.5$\,\MSun\, the final orbital separataion, after mass transfer,
-    is smaller than the initial orbit.  Here we adopted an initial
-    inner binary mass of (1.0+0.9)\,\MSun\, and a final twin-blue
-    straggler mass of (1.4+1.4)\,\MSun.
+    lobe is indicated with the light-blue curve. The top curve (brown)
+    shows an estimate of the final orbit separation of the outer star,
+    and therefore of the final orbit of the white dwarf around the
+    inner twin blue straggler.  For core masses $\apgt 0.5$\,\MSun\,
+    the final orbital separataion, after mass transfer, is smaller
+    than the initial orbit.  Here we adopted an initial inner binary
+    mass of (1.0+0.9)\,\MSun\, and a final twin-blue straggler mass of
+    (1.4+1.4)\,\MSun.
 \label{fig:tertiarymass_vs_size}}
@@
 
-In Fig.\,\ref{fig:tertiarymass_vs_size} we present several
-characteristic sizes and orbital separations for the problem at hand.
-The red curves show the stellar radius upon reaching the first giant
-branch (thick curve) and the asymptotic giant branch (thin curves).
-The blue curves show the orbital separation at the moment of
-Roche-lobe overflow for each of the aforementioned giants, assuming a
-circular orbit and a total inner binary mass of $0.9 + 1.1$
-M$_{\odot}$ $=$ 2.0 M$_{\odot}$.  The green curves show for these
-assumptions the maximum orbital separation for a stable inner binary
-pair.
+When adopting a mass of the tertiary star of $m_3 = 1.4$\,\MSun, we
+can estimate the initial parameters for the inner binary as well as
+the orbit of the outer star after mass transfer. We first calculate
+the stellar radius as a function of core mass. In
+figure\,\ref{fig:tertiarymass_vs_size} we present this relation
+calculated using the {\tt SeBa} stellar evolution code
+\cite{1996A&A...309..179P} (dark blue curve).  The interruption in
+this curve, aroung a core mass of $m_{\rm core} \sim 0.5$\,\MSun\, is
+a result of the evolution along the horizontal branch, where the core
+of the star continues to grow but the radius actually shrinks.
+
+Adopting masses for the inner binary $m_1=1.1$\,\MSun\, and
+$m_2=0.9$\,\MSun\, we can calculate the outer orbital separation at
+the onset of Roche-lobe overflow $a_{\rm out}$, and subsequently the
+maximum orbital separation for the inner binary for which the orbit is
+stable and a circum binary disk can form. These two limits are
+prosented as the light-blue and light green curves in
+figure\,\ref{fig:tertiarymass_vs_size}.  The alotted region of
+parameter space is then above the dahsed horizontal line and to the
+right of the vertical dotted line.
+
+With the adopted parameters, we can also estimate the final orbital
+period of the left-over core from the tertiary star.  The change in
+orbital separation due to non-conservative mass transfer can be
+expressed in terms of the mass of the outer star before and after mass
+transfer $m_3$ and $m'_3$, the total mass in the inner binary before
+($m_{\rm in}$) and after having accreted ($m'_{\rm in}$) and the
+amount of angular momentum lost per unit mass $\eta \simeq 3$
+\cite{1995A&A...296..691P}.
+\begin{equation}
+  {a \over a_0} = \left( {m'_3 m'_{\rm in} \over m_3 m_{\rm in}} \right)^{-2}
+  \left( {m'_3 + m'_{\rm in} \over m_3 + m_{\rm in}} \right)^{2\eta + 1}
+\end{equation}
+In figure\,\ref{fig:tertiarymass_vs_size} we present this relation
+with the top brown curve, which subsequently gives an estimate of the
+orbital separation of the white dwarf around the twin blue straggler
+7782.
 
@@
   and a core particle of 0.4\,\MSun (blue bullet). The two companion
-  stars are represented as red bullets (to the right).
+  stars are represented as black bullets (to the right).  The inner
+  binary is represented by the yellow and the red bullets for the
+  1.1\,\MSun\, primary and 0.9\,\MSun\, secondary stars in a circular
+  orbit of 0.1\,au. The 1.4\,\MSun\, giant star is presented to the
+  right in a circular orbit of $\sim 1.47$\,au in the plan of the
+  inner binary.
 \label{fig:topview_at_t0}}
@@
 \caption{Same as Fig.\,\ref{fig:topview_at_t0} but at an age of $t
-  \simeq 996days$. Left panel shows the equipotential surface of the
-  triple overplotted with the gas distribution, the right panel shows
-  just the gas and the stars as bullets.
+  \simeq 1091\,days$ after the start of the simulation. Left panel
+  shows the equipotential surface of the triple overplotted with the
+  gas distribution, the right panel shows just the gas and the stars
+  as bullets.
 \label{fig:topview_at_t1000day}}

### 2019-01-15 BSS7782.tex
worked on text

@@
 population in NGC 188 has a bi-modal period-eccentricity distribution.
-As discussed in \citet{2011MNRAS.410.2370L}, this could be hinting at a triple
-origin for at least some subset of the total BS population.  As for
-Binary 7782, \citet{2009Natur.462.1032M} observed a compact and mildly eccentric
-(i.e., $e \sim 0.1$) binary star system with an orbital period of
-$\sim$ 10 days hosting two roughly equal-mass blue stragglers.  During
-a given binary-binary interaction, the probability that not one but
-two direct (MS-MS) collisions will occur is less than $10^{-2}$
-\citep{1989AJ.....98..217L,2011MNRAS.410.2370L,2012MNRAS.425.2369L}.  Plus, binaries with collision products
-typically have relatively long orbital periods
-\cite{2011Sci...334.1380F}. Dynamically, it is difficult to form a
-short-period binary composed of two collision products during a
-collisional interaction in a star cluster \citep{2011Sci...334.1380F}.
-So, how did Binary 7782 form?
+As discussed in \citet{2011MNRAS.410.2370L}, this could be hinting at
+a triple origin for at least some subset of the total BS population.
+As for Binary 7782, \citet{2009Natur.462.1032M} observed a compact and
+mildly eccentric (i.e., $e \sim 0.1$) binary star system with an
+orbital period of $\sim$ 10 days hosting two roughly equal-mass blue
+stragglers.  During a given binary-binary interaction, the probability
+that not one but two direct (MS-MS) collisions will occur is less than
+$10^{-2}$
+\citep{1989AJ.....98..217L,2011MNRAS.410.2370L,2012MNRAS.425.2369L}.
+Plus, binaries with collision products typically have relatively long
+orbital periods \cite{2011Sci...334.1380F}. Dynamically, it is
+difficult to form a short-period binary composed of two collision
+products during a collisional interaction in a star cluster
+\citep{2011Sci...334.1380F}.  So, how did Binary 7782 form?
 
@@
 When adopting a mass of the tertiary star of $m_3 = 1.4$\,\MSun, we
-can estimate the initial parameters for the inner binary as well as
+can constrain the initial parameters for the inner binary as well as
 the orbit of the outer star after mass transfer. We first calculate
@@
 \cite{1996A&A...309..179P} (dark blue curve).  The interruption in
-this curve, aroung a core mass of $m_{\rm core} \sim 0.5$\,\MSun\, is
+this curve, around a core mass of $m_{\rm core} \sim 0.5$\,\MSun\, is
 a result of the evolution along the horizontal branch, where the core
 of the star continues to grow but the radius actually shrinks.
+Roche-lobe overflow in this phase is not expected to happen, because
+it would already have happened in an earlier evolutionary state of the
+donor star, when it was bigger.
 
@@
 maximum orbital separation for the inner binary for which the orbit is
-stable and a circum binary disk can form. These two limits are
-prosented as the light-blue and light green curves in
+stable and a circum-binary disk can form. These two limits are
+presented as the light-blue and light green curves in
 figure\,\ref{fig:tertiarymass_vs_size}.  The alotted region of
-parameter space is then above the dahsed horizontal line and to the
+parameter space is then above the dashed horizontal line and to the
 right of the vertical dotted line.
@@
 With the adopted parameters, we can also estimate the final orbital
-period of the left-over core from the tertiary star.  The change in
-orbital separation due to non-conservative mass transfer can be
-expressed in terms of the mass of the outer star before and after mass
-transfer $m_3$ and $m'_3$, the total mass in the inner binary before
-($m_{\rm in}$) and after having accreted ($m'_{\rm in}$) and the
-amount of angular momentum lost per unit mass $\eta \simeq 3$
-\cite{1995A&A...296..691P}.
+period of the left-over core from the tertiary star after the phase of
+mass transfer.  The change in orbital separation due to
+non-conservative mass transfer can be expressed in terms of the mass
+of the outer star before and after mass transfer $m_3$ and $m'_3$,
+respectively, the total mass in the inner binary before ($m_{\rm in}$)
+and after accretion ($m'_{\rm in}$) and the amount of angular momentum
+lost per unit mass $\eta \simeq 3$. Adopting the relation between the
+orbital separation before mass transfer ($a'$) and after mass transfer
+($a$) from \cite{1995A&A...296..691P}
 \begin{equation}
-  {a \over a_0} = \left( {m'_3 m'_{\rm in} \over m_3 m_{\rm in}} \right)^{-2}
-  \left( {m'_3 + m'_{\rm in} \over m_3 + m_{\rm in}} \right)^{2\eta + 1}
+  {a \over a'} = \left( {m'_3 m'_{\rm in} \over m_3 m_{\rm in}} \right)^{-2}
+  \left( {m'_3 + m'_{\rm in} \over m_3 + m_{\rm in}} \right)^{2\eta + 1},
 \end{equation}
-In figure\,\ref{fig:tertiarymass_vs_size} we present this relation
-with the top brown curve, which subsequently gives an estimate of the
-orbital separation of the white dwarf around the twin blue straggler
-7782.
+we arrive at the top brown curve in
+figure\,\ref{fig:tertiarymass_vs_size}. This curve provides an
+estimate of the orbital separation of the white dwarf around the twin
+blue straggler 7782. Tidal effects during the episode of mass tranfer
+have probably circularized the orbit, althoug some slight eccentricity
+due to turbulent motion in the outer layers of the donor star may have
+induces a small eccentricity of $e \ll 0.1$.
 

### 2019-01-16 BSS7782.tex
updated the paper

@@
 \def\aplt{\ {\raise-.5ex\hbox{$\buildrel<\over\sim$}}\ }
+%%\def\figure{\ {figure\,}}
 
@@
 We propose a formation mechanism for twin blue stragglers in compact
-binaries that involves mass transfer from an evolved outer tertiary
+binaries that involve mass transfer from an evolved outer tertiary
 companion on to the inner binary via a circumbinary disk.  We apply
@@
 masses.  This follows from the more copious accretion of mass onto the
-initially lower mass star.  This star should therefore be enriched
+initially lower mass star.  This star should, therefore, be enriched
 more effectively by the accreted material.  As a result, one of the
@@
 if the donor started to overflow its Roche lobe at the red
-giant branch, or with s-process elements if the donor was on the
-asymptotic giant branch.  (5) Relative to old dense clusters with high
-velocity dispersions, twin BSs in close binaries formed from the
+giant branch, or with s-process elements, if the donor was on the
+asymptotic giant branch.  (5) Relative to old dense clusters with high-velocity dispersions, twin BSs in close binaries formed from the
 proposed mechanism should be more frequent in the Galactic field and
@@
 main-sequence turn-off in a cluster colour-magnitude diagram
-\citep[e.g.][]{1953AJ.....58...61S,2014ApJ...782...49S}.  Two
-primary channels for BS formation have been proposed: mass transfer
-from an evolved donor on to a main-sequence star in a binary star
-system
+\citep[e.g.][]{1953AJ.....58...61S,2014ApJ...782...49S}.  Two primary
+channels for BS formation have been proposed: mass transfer from an
+evolved donor on to a main-sequence star in a binary star system
 \citep[e.g.][]{1964MNRAS.128..147M,1997A&A...328..143P,2009Natur.457..288K,2011MNRAS.410.2370L,2011Natur.478..356G},
@@
 mediated via binaries
-\citep[e.g.][]{hills75,1997A&A...328..130P,2007ApJ...661..210L,2013MNRAS.428..897L,2013MNRAS.429.1221H,2018arXiv181100058P}.
+\citep[e.g.][]{1975AJ.....80..809H,1997A&A...328..130P,2007ApJ...661..210L,2013MNRAS.428..897L,2013MNRAS.429.1221H,2018arXiv181100058P}.
 Other possible, albeit related, formation mechanism includes mergers
@@
 binaries in general, which involves mass transfer from an outer
-tertiary companion on to an inner binary composed to two main-sequence
+tertiary companion on to an inner binary composed of two main-sequence
 stars.  In section~\ref{sect:dyn}, we constrain the range of initial
@@
 
-In our scenario we start with a binary star with component masses
+In our scenario, we start with a binary star with component masses
 $m_{\rm 1}$ and $m_{\rm 2}$ that is orbited tertiary of mass
@@
 assumed formation scenario for Binary 7782, described below, is
-depicted in Figure~\ref{fig:fig1}.
+depicted in figure~\ref{fig:fig1}.
 
@@
 sufficiently small that the tertiary star is filling its Roche lobe
-and transfers mass to the inner binary before it leaves the asumptotic
+and transfers mass to the inner binary before it leaves the asymptotic
 giant branch. We constrain the inner orbit by requiring the triple
-system to be dynamicall stable, for which we adopt eq.\,90 in
-\cite{2001MNRAS.321..398M}.  While transferring mass, the accretion
+system to be dynamically stable, for which we adopt eq.\,1 in
+\cite{1999ASIC..522..385M,}.  While transferring mass, the accretion
 stream gathers around the inner binary at the circularization radius
-a$_{\rm c}$, and forms a circumbinary disk.  Using conservation of
-angular momentum, we equate the specific angular momentum of the
-accreted mass at the inner Lagrangian point of the (outer) donor star
-to the final specific angular momentum of the accretion stream at the
-circularization radius about the inner binary, this results in
+a$_{\rm c}$, and forms a circumbinary disk
+\citep{2002apa..book.....F}.  Using conservation of angular momentum,
+we equate the specific angular momentum of the accreted mass at the
+inner Lagrangian point of the (outer) donor star to the final specific
+angular momentum of the accretion stream at the circularization radius
+about the inner binary, this results in
 \begin{equation}
@@
 v$_{\rm orb,c}$ is the orbital velocity at $a_{\rm c}$.  The distance
-from the center of mass corresponding to the tertiary defined by the
+from the centre of mass corresponding to the tertiary defined by the
 Roche lobe is given by Equation 2 in \citep{1983ApJ...268..368E}.
@@
 properties).  The thick horizontal solid red line shows the allowed
-range of outer semi-major axes, after folding in all of the
-aforementioned criteria.  These constraints result in a rather narrow
+range of outer semi-major axes, after folding in all of 
+the aforementioned criteria.  These constraints result in a rather narrow
 range of initial conditions for the outer orbit, namely 2.2 $\times$
@@
     The horizontal dashed line shows the orbital separation of the
-    observed twin blue stragger 7782.  The initial triple in which it
+    observed twin blue straggler 7782.  The initial triple in which it
     possibly formed must at least have been dynamically stable. The
     minimal orbital separation for the inner binary for which the
-    triple is stable is given by the lower green colored curve.
+    triple is stable is given by the lower green coloured curve.
     Donors which are smaller than about 100\,\RSun\, (dark blue curve
@@
     triple. The minimal core mass associated with a stable triple is
-    then indicated by the left-most vertikcal dotted line.  The
+    then indicated by the left-most vertical dotted line.  The
     orbital separation at which the donor star overfills its Roche
@@
     inner twin blue straggler.  For core masses $\apgt 0.5$\,\MSun\,
-    the final orbital separataion, after mass transfer, is smaller
+    the final orbital separation, after mass transfer, is smaller
     than the initial orbit.  Here we adopted an initial inner binary
@@
 lost per unit mass $\eta \simeq 3$. Adopting the relation between the
-orbital separation before mass transfer ($a'$) and after mass transfer
-($a$) from \cite{1995A&A...296..691P}
+orbital separation before mass transfer ($a$) and after mass transfer
+($a'$) from \cite{1995A&A...296..691P}
 \begin{equation}
-  {a \over a'} = \left( {m'_3 m'_{\rm in} \over m_3 m_{\rm in}} \right)^{-2}
-  \left( {m'_3 + m'_{\rm in} \over m_3 + m_{\rm in}} \right)^{2\eta + 1},
+  {a' \over a} = \left( {m_3 m_{\rm in} \over m'_3 m'_{\rm in}} \right)^{-2}
+  \left( {m_3 + m_{\rm in} \over m'_3 + m'_{\rm in}} \right)^{2\eta + 1},
 \end{equation}
@@
 due to turbulent motion in the outer layers of the donor star may have
-induces a small eccentricity of $e \ll 0.1$.
+induces a small $e \ll 0.1$ eccentricity.
+
+Having limited parameter space for the formation of the twin blue
+straggler 7782, we continue by performing a series of simulations to
+investigate the accretion and changes to the inner orbits of triple
+systems in this range of parameters.
 
@@
 derived in the previous \S. In the following two sections we describe
-how we setup these simulations and then discuss the results. The
-calculations are performed using the
+how we set up these simulations and then discuss the results. The
+calculations are performed using the Astrophysical Multipurpose
+Software Environment using a combination of stellar evolution,
+gravitational dynamics and hydrodynamics.
 
@@
 stellar-evolution code \cite{2011ApJS..192....3P} to a radius of about
-1\,au, at which point we assume it to overfill it's Roche lobe.  By
-this time the star has lost 0.13\,\MSun\, via a stellar wind.
+100\,\RSun\, and 150\,\RSun, at which point we assume it to overfill
+it's Roche lobe (see red squared in
+figure~\ref{fig:tertiarymass_vs_size}).  We perform calculations for an
+inner orbital separation of $a_{\rm in} = 0.10$\,au, $a_{\rm in} =
+0.15$\,au and $a_{\rm in} = 0.20$\,au.  In total we performed 12
+calculations at a resolution of 40k SPH particles 12 at 80k.
 
 The stellar-evolution model, including the structure, temperature and
-composition profiles, are turned into a smoothed-particles
+composition profiles are turned into a smoothed-particles
 representation using the module {\tt StellarModelInSPH} in AMUSE (see
@@
 in \cite{2014MNRAS.438.1909D} for simulating the future of the triple
-system $\chi$ Tau (HD 97131) in which the outer-most star overfills its
-Roche lobe and trnsfers mass to an inner binary.  After generating the hydrodynamical
-representation of the donor star we replace the stellar core by a
-point mass to prevent the majority of the resolution to be confined in
-the star's central regions.  In a following step we relax the star
-using the hydrodynamics solver. This relaxation process is realized in
-100 steps during which we reduce the velocity dispersion of individual
-SPH particles to a glasseas structure \citep[see, for example, \S\,3.3
-  on page 40 in][]{1994astro.ph.10043W}. During this procedure the
-gaseous envelope of the star tends to expand by about 20\%.  To
-detemrine the radius of the evolving star we calculate Lagrangian
-radii and use the distance to the stellar center which contains 90\%
-of it's mass. From this 90\% mass-radius relation we obtain the stellar radius,
-and match it with the Roche-lobe of the outer orbit.
+system $\chi$ Tau (HD 97131) in which the outer-most star overfills
+its Roche lobe and transfers mass to an inner binary.  After
+generating the hydrodynamical representation of the donor star we
+replace the stellar core by a point mass to prevent the majority of
+the resolution to be confined in the star's central regions.  In a
+following step we relax the star using the hydrodynamics solver. This
+relaxation process is realized in 100 steps during which we reduce the
+velocity dispersion of individual SPH particles to a glasses
+structure \citep[see, for example, \S\,3.3 on page 40
+  in][]{1994astro.ph.10043W}. During this procedure, the gaseous
+envelope of the star tends to expand by about 20\%.  To determine the
+radius of the evolving star we calculate Lagrangian radii and use the
+distance to the stellar center which contains 90\% of its mass. From
+this 90\% mass-radius relation we obtain the stellar radius and match
+it with the Roche-lobe of the outer orbit.
 
 With these parameters the orbital separation of the outer binary
-becomes $\sim 3.86$\,au, and we adopt the outer orbit to be circular.
-We choose a relative initial inclination between the inner and the
-outer orbits of $i = 0^\circ$, $i = 9^\circ$, $i = 90^\circ$ and $i =
-180^\circ$.  The first two choices are motivated by observed low-mass stellar
-triples composed of low-mass stars which have been observed to favor
-co-planar configurations \citep{2018ApJ...854...44M}. To test the effect of highly
-inclined and retrogade orbits we include the $i = 90^\circ$ and $i =
-180^\circ$ cases.  In Fig.\,\ref{fig:topview_at_t0} we present a top
-view of the triple system in our simulations at the onset of Roche-lobe overflow.
+becomes $\sim 250$\,\RSun for the 100\,\RSun donor star and about
+430\,\RSun\, for the more evolved donor star.  We adopt the outer
+orbit to be circular and in the plane of the inner binary.
+%% We
+%% performed several additional calculations for inclined orbits (choosing
+%% a relative initial inclination $i = 9^\circ$, $i = 45^\circ$, $i =
+%% 90^\circ$ and $i = 180^\circ$, but we wi
+The low inclination is motivated by observed stellar triples composed
+of low-mass stars to favour co-planar configurations
+\citep{2018ApJ...854...44M}.
+%% To test the effect of highly inclined
+%% and retrogade orbits we include the $i = 90^\circ$ and $i = 180^\circ$
+%% cases.
+In figure~\ref{fig:topview_at_t0} we present a top view of the initial
+conditions for one of these calculations.
 
@@
   \includegraphics[width=\columnwidth]{fig_BBSS_gas_M14Msun_A010au_t0002.pdf}
-\caption{Top view of the simulated triple system in which the outer
-  star over-fills its Roche-lobe (represented by 80000\,sph particles
-  and a core particle of 0.4\,\MSun (blue bullet). The two companion
+\caption{Top view of the simulated triple system in which the
+  100\,\RSun\, outer star of 1.4\,\MSun\, that over-fills its
+  Roche-lobe.  the star is represented by 80000\,SPH particles and a
+  core particle of $\sim 0.4$\,\MSun (black bullet). The two companion
   stars are represented as black bullets (to the right).  The inner
@@
   orbit of 0.1\,au. The 1.4\,\MSun\, giant star is presented to the
-  right in a circular orbit of $\sim 1.47$\,au in the plan of the
+  right in a circular orbit of $\sim 250$\,\RSun\, in the plan of the
   inner binary.
@@
 
-Roche-lobe overflow in triples is modeled using a coupled integrator
+Roche-lobe overflow in triples is modelled using a coupled integrator
 to follow the complex hydrodynamics of mass transfer from the
@@
 masses, but we allow them to accrete mass and angular momentum from
-the gas liberated by the outer star.  This is realized using
+the gas liberated by the outer star.  This is realized using spherical
 sink-particles that co-move with the mass points in the gravity
@@
 corresponding amount of angular momentum from the gas (see chapter 5
-in \cite{AMUSE}).  The N-body integrator correctly accounts for this.  For the radius of the sink particles we adopt $10
-R_\odot$ for both stars.
+in \cite{AMUSE}).  The N-body integrator correctly accounts for this.
+For the radius of the sink particles, we adopt $2 R_\odot$ for both
+stars.
 
-The N-body code as well as the hydrodynamics solver operate using
+The N-body code, as well as the hydrodynamics solver, operate using
 their own internal time-steps. The coupling between the two codes is
@@
 its own particles, as well as the gravitational potential of the inner
-binary. The hydrodynamics, in particular the interaction with the gas,
-in turn affects the orbits of the two inner stars. With
+binary. The hydrodynamics, in particular, the interaction with the gas,
+in turn, affects the orbits of the two inner stars. With
 \texttt{Bridge} we realize a second order coupling between the
@@
 
-\section{Results} \label{results}
+\section{Results of the hydrodynamical simulations} \label{results}
 
-In fig.\,\ref{fig:topview_at_t1000day} we show the same triple after
-1000\,days of evolution.
-%NL2:  We are labeling the figures differently in the text.
-You label with ``fig.\,\", whereas I use ``Figure~''.
-It doesn't matter to me which we use, just thought I'd highlight this so we come back to it right before submitting.
+to test the hypotheses that (1) the secondary in the inner binary
+accretes more effectively than the primary star and to measure the
+change to the inner orbit due to the Roche-lobe overflow of the outer
+star, we perform a series of calculations in which we take the self
+gravity and the hydrodynamical effects of the triple into account.
+The results of these simulations are presented in
+figure~\ref{fig:topview_at_t1000day} and
+figure~\ref{fig:mass_vs_semimajor_axis}.  The first figure
+(figure~\ref{fig:topview_at_t1000day} shows the top view of the same
+initial realization for which we presented the initial conditions in
+figure~\ref{fig:topview_at_t0} but now at an age of 1091 days after
+the onset of mass transfer. To guide the eye we add, to the left panel,
+the equipotential surfaces in the orbital plane.
 
-\cite{2018arXiv181208175M}
+It is apparent that the mass transfer in the adopted triples leads to
+a rather untidy evolution, in particular, because much of the donor
+mass is lost through the second Lagrangian point to the right side of
+the donor star in figure~\ref{fig:topview_at_t1000day}. Much mass is
+also lost through the third Lagrangian point (to the left of the inner
+binary). One remaining question is how much mass is eventually ejected
+altogether from the triple system and is therefore not accreted to any
+of the two inner stars. This value is hard to estimate from the
+simulations, but an accretion efficiency of $\apgt 0.6$ is necessary to
+make the scenario feasible. Over the time scale for which we performed
+the calculations, this efficiency is reached, but it is not clear who
+the system responds at later stages.
 
@@
 ~  \includegraphics[width=0.51\columnwidth]{fig_BBSS_gas_M14Msun_A010au_t3360.pdf}
-\caption{Same as Fig.\,\ref{fig:topview_at_t0} but at an age of $t
+\caption{Same as figure~\ref{fig:topview_at_t0} but at an age of $t
   \simeq 1091\,days$ after the start of the simulation. Left panel
@@
 
-In fig.\,\ref{fig:mass_vs_semimajor_axis}
+The evolution of the inner orbit presented for several simulations in
+figure~\ref{fig:mass_vs_semimajor_axis}, is complicated.  This is
+caused by the complex transport of mass, energy and angular momentum
+through the accretion stream and throughout the system.  It is
+therefore hard to quantify distinct trends in the evolution of the
+triple system. In simulated of the response of an inner binary on
+accretion from a circumbinary disk, \cite{2018arXiv181208175M}
+conclude that the complexity of angular momentum transport between
+outer star, accretion stream to the individual inner stars, is
+complicated and without clear trends. For most of our calculations we
+agree with this statement, but in
+figure~\,\ref{fig:mass_vs_semimajor_axis} we nevertheless present the
+results of 6 of our calculations, three for and 1.2\,\MSun\, donor and
+three for a 1.4\,\MSun\, donor star. The various coloured curves give
+the resulting evolution of the inner orbit as a function of the total
+mass in the inner binary. While the inner two stars accrete the orbit
+in the case with a 1.2\,\MSun\, donor tends to shrink. These systems
+are expected to result in a contact binary, that eventually may merge
+to form a single blue straggler. The required evolution in order to
+explain the observed twin blue straggler 7782 are indicated with the
+three black curves, and the simulated path clearly deviates from
+these. We, therefore, argue that a 1.2\,\MSun\, donor has difficulty
+explaining the observed orbital separation of $\sim 0.13$\,au in BSS
+7782.
 
@@
 
-The orbital evolution of the inner binary circumreferenced by a disk
-tends to evove by the accretion of mass and angular momentum. As a
-consequence, the two stars in the binary accumulate mass, and their
-orbit shrinks. The orbital evolution can be approximated, to first order, by:
-\begin{equation}
-  {d\ln a \over dt}   = {-d\ln m_{\rm in} \over dt},
-\end{equation}
-where $a$ and $m_{\rm in}$ are the semimajor-axis and total mass in
-the inner binary.  In the simulations we measure ${d\ln a \over dt}
-\simeq -0.0843$\,Myr$^{-1}$.
-%NL2:  The above equation seems incorrect to me, dimensionally.
-It can be fixed by saying the ``specific mass'' and ``dimensionless semi-major axis'', I suppose.
-But then I'd define how you make those parameters dimensionless.
+In the lower panel in figure~\ref{fig:mass_vs_semimajor_axis} we
+present the evolution of the orbit for the 1.4\,\MSun\, donor. A more
+massive donor is more likely to be able to produce a twin blue
+straggler, simply because there is more mass available in the stellar
+envelope. On the other hand, a more massive donor may also result in a
+lower accretion efficiency, because the thermal time scale of the
+stellar envelope is smaller than for the lower mass donor at the same
+stellar radius. Such a shorter thermal time-scale eventually leads to
+a higher mass transfer rate, which again may lead to a lower accretion
+efficiency. However, the larger mass budget in the envelope appears to
+compensate.
 
-With the accretion of mass, both stars in the inner binary also accrete
-angular momentum.  By the end of the simulation the spins of the two
-blue stragglers are aligned along the orbital angular momeumt axis with
-an angle of $90.0^\circ$ for the primary star and $93.4^\circ$ for the
-secondary star with respect to the argument of pericenter of the inner
-orbit.  By the end of the simulations the spin of the primary is about
-50.5 rotations per day, and 41.5 rotations per day for the secondary star. But by this
-time both stars have accreted only a small portion of mass, and we expect that
-the final spins of both stars will be close to break-up (ignoring any spin-down from magnetic braking effects).
-%NL2: I added the bit about magnetic braking above but it needs to be worded better, or removed.  Will come back to it, and feel free to edit it yourself as well..
+The orbit of the inner binary expands in these cases as a result of
+the accretion onto the inner two stars. In all the three cases
+presented in figure~\ref{fig:mass_vs_semimajor_axis} expand by about
+the same rate (as function of the accretion onto the inner binary
+star). As a consequence, the inner binaries that start with $a =
+0.15$\,au and $a=0.20$\,au eventually become dynamically unstable.
+The binary with an initial separation of $0.10$\,au expands to reach a
+separation of about 0.126--0.145\,au for a mass of the inner two stars
+of 1.4\,\MSun, which is consistent with the observed twin blue
+straggler 7782. In our simulations the eccentricity of the inner
+binary grows to about $e \simeq 0.0028$.
+
+With the accretion of mass, both stars in the inner binary also
+accrete angular momentum.  By the end of the simulation the spins of
+the two blue stragglers are aligned along the orbital angular momentum
+axis with an angle of $90.0^\circ$ for the primary star and
+$93.4^\circ$ for the secondary star with respect to the argument of
+pericenter of the inner orbit.  By the end of the simulations the spin
+of the primary is about 50.5 rotations per day, and 41.5 rotations per
+day for the secondary star. But by this time both stars have accreted
+only a small portion of mass and we expect that the final spins of
+both stars will be close to break-up (ignoring any spin-down from
+magnetic braking effects).
 
@@
 
-In this Letter, we consider the formation of double blue straggler compct binaries formed 
-from mass transfer from an outer tertiary companion.  As illustrated via SPH simulations, 
-the mass transfer stream forms a circumbinary 
-disk, from which the inner binary components accrete, driving the inner binary toward a 
-mass ratio close to unity.  Our simulations suggest that the inner binary orbital separation 
-should decrease in response to mass accretion, for the assumed initial conditions adopted here.  A more 
-detailed study of the relevant parameter is worth performing in future work.  For example, under what circumstances 
-might the inner binary pair merge, forming a much more massive BS?  Conversely, if the orbital 
-separation of the inner binary \textit{increases} in response to mass transfer, this could 
-cause the triple to become dynamically unstable, subsequently undergoing a chaotic interaction, most likely 
-resulting in the ejection of the lowest mass object in the system.  If one of the two BSs formed in 
-this scenario are ejected, this would leave behind a BS binary with a WD companion.  Such systems 
-are assumed to solely be the result of mass transfer in binary systems, but the results presented here 
-suggest that such an assumption should be regarded with caution.
+We considered the formation of twin blue stragglers in tight binaries.
+These systems may form through mass transfer from an outer Roche-lobe
+filling tertiary star. Once this star ascends the giant branch, part
+of its envelope is transferred to the inner binary, and accreted by
+the two inner stars which are still on the main sequence.
+
+As illustrated via SPH simulations, the mass transfer stream forms a
+circumbinary disk, from which the inner binary stars accrete, driving
+the inner binary toward a mass ratio close to unity.  Our simulations
+suggest that the inner binary orbital separation can decrease or
+expand depending on the details of the transfer of mass and angular
+momentum. Regretfully, we do not really understand the details of this
+process, but then this process is hardly understood in binary
+evolution also.
+
+We summarize the results of these simulations as follows: for a
+1.2\,\MSun\, tertiary donor mass, we expect the inner two stars to
+eventually merge and form a single blue straggler. This reduces the
+system to a binary with a primary blue straggler and an outer white
+dwarf in a relatively wide orbit. Such a blue straggler will
+distinguish itself from other blue stragglers from potentially
+being more than twice the turn-off mass in a star cluster.  An
+example could be the $2.9\pm0.2$\,\MSun\, blue straggler S1237 in the
+Galactic cluster M67 \cite{2016ApJ...832L..13L}. It is the primary of
+a $\sim 698$\,day binary with an eccentric orbit of $\sim 0.10$.
+
+With an original outer star of $\sim 1.4$\,\MSun, the inner orbit
+tends to expand. For relatively wide inner orbit this eventually leads
+to a dynamically unstable system resulting either in a collision or in
+the ejection of (probably) the lowest mass star. This evolution could
+result in a single ejected blue straggler the other blue straggler in
+a relatively close and eccentric orbit with a white dwarf (the
+left-over core of the tertiary star).
+
+When we adopt an inner orbit of $0.10$\,au\, the expansion eventually
+matches the observed orbital separation of $0.13$\,au of the observed
+twin BSS 7782 and the observed masses of the two stars.
 
@@
 \cite{2011MNRAS.413.2679D} perform a series of 2D hydrodynamical
-simulations of circumbinary disks.  These authors studied the two observed
-T-tauri systems V4046 Sgr and DQ~Tau, to which we compare our results here.
+simulations of circumbinary disks.  These authors studied the two
+observed T-tauri systems V4046 Sgr and DQ~Tau, to which we compare our
+results here.  For V4046 Sgr, for which the two stars have comparable
+masses as in our calculation in an circular orbit with a period of
+only 2.4 days they find that the inner binary accretes at a rate of
+$\sim 0.028$\,\MSun/Myr.  For DQ~Tau, which is composed of lower-mass
+stars ($m_1 = m_2 \simeq 0.55$\,\MSun) in an eccentric ($e\simeq
+0.556$) orbit of $\sim 15.8$\,days they find an accretion rate onto
+the inner binary of $\sim 0.027$\,\MSun/Myr.  These values are in the
+same range as in our calculations, which results in an accretion rate
+of the inner binary of 0.027--0.058\,\MSun/Myr (i.e., the average
+measured over a period of about 3000 days in our simulations).
+Interestingly, however, \cite{2011MNRAS.413.2679D} find that the
+primary star in V4046 Sgr accretes at an 8\% higher rate than the
+secondary star, whereas in our case the secondary star accretes at a
+higher rate than the primary star by about 1\% to 12\%.  Higher
+accretion rates in the secondary star are realized for eccentric and
+retrogade inner orbits.
 
-For V4046 Sgr, for which the two stars have comparable masses as in
-our calculation in an ciruclar orbit with a period of only 2.4 days
-they find that the inner binary accretes at a rate of $\sim
-0.028$\,\MSun/Myr.  For DQ~Tau, which is composed of lower-mass stars
-($m_1 = m_2 \simeq 0.55$\,\MSun) in an eccentric ($e\simeq 0.556$)
-orbit of $\sim 15.8$\,days they find an accretion rate onto the inner
-binary of $\sim 0.027$\,\MSun/Myr.  These values are in the same range
-as in our calculations, which results in an accretion rate of the inner
-binary of 0.027--0.058\,\MSun/Myr (i.e., the average measured over a period of
-about 3000 days in our simulations).  The highest accretion rate we obtain for the
-simulations with an eccentric inner orbit.  Here we applied a small
-correction to compensate for the larger accretion radii adopted for
-the two stars of 10\,\RSun\, compared to 6\,\RSun\, in
-\cite{2011MNRAS.413.2679D}. Interestingly, however,
-\cite{2011MNRAS.413.2679D} find that the primary star in V4046 Sgr
-accretes at an 8\% higher rate than the secondary star, whereas in our
-case the secondary star accretes at a higher rate than the primary
-star by about 1\% to 12\%.  Higher accretion rates in the secondary
-star are realized for eccentric and retrogade inner orbits.
-%NL2:  Huh.
-This is interesting.
-Is the physical reason for it that apocenter for the secondary tends to be closer to the circumbinary disk?
-I don't get why retrograde wins though, since naively I'd have thought prograde should lead to lower relative velocities between the secondary and the gas flow, and hence to higher accretion rates.
-What am I missing?
-Is there momentum cancellation via colliding gas, shocks, etc.
-I am missing somewhere?
+%NL2: Huh.  This is interesting.  Is the physical reason for it that
+%apocenter for the secondary tends to be closer to the circumbinary
+%disk?  I don't get why retrograde wins though, since naively I'd have
+%thought prograde should lead to lower relative velocities between the
+%secondary and the gas flow, and hence to higher accretion rates.
+%What am I missing?  Is there momentum cancellation via colliding gas,
+%shocks, etc. I am missing somewhere?
+%% SPZ: I think that we do not have to add these extra simulations. I
+%% found the result sufficiently confusing to check and check
+%% again. Maybe we write another paper on these results, or a
+%% follow-up on accretion in triples. But maybe it is best to stick to
+%% the observed facts, and not try to explore parameter space in
+%% extensio. What do you think, Nathan?  At the moment, this last
+%% paragraph is a bit of an after though, but maybe it is worth
+%% mentioning that our results are consistent with those of others...
 
@@
 
-In this Letter, we have proposed a formation scenario for double BS
-equal-mass compact binaries, as observed for Binary 7782 in the old
-open cluster NGC 188.  The proposed scenario involves mass transfer
-from an evolved outer tertiary companion, which is accreted by the
-inner binary via a circumbinary disk.  Our scenario makes several
-predictions for the observed properties of a hypothetical outer triple
-companion, now a WD.  These are:
+We propose a formation scenario for twin blue stragglers of equal-mass
+in tight binaries, as observed for Binary 7782 in the old open cluster
+NGC 188.  The proposed scenario involves mass transfer from an evolved
+outer tertiary companion, which is accreted by the inner binary via a
+circumbinary disk.  Our scenario makes several predictions for the
+observed properties of a hypothetical outer triple companion, now a
+WD.  These are:
 
@@
 \item Larger final WD masses, and hence larger core masses for the donor at
-  the time of mass transfer, should correspond to larger final outer
-  orbital periods for the tertiary.  This is because the Roche radius
+  the time of mass transfer should correspond to larger final outer
+  orbital periods for the tertiary.  This is because of the Roche radius
   is larger for larger outer orbital periods, such that the donor must
@@
   be aligned with each other and the orbital plane of the outer
-  tertiary WD.  This is because accretion onto the BS progenitors
+  tertiary WD.  This is because of accretion onto the BS progenitors
   proceeds via an accretion disk, that forms at the circularization
@@
   should be more frequent in younger clusters with ages $\lesssim$ 4-6
-  Gyr.  This is because clusters with a main-sequence turn-off mass
+  Gyr.  This is because of clusters with a main-sequence turn-off mass
   $\lesssim$ 1.2 M$_{\odot}$ have convective envelopes
@@
 
-We emphasize in closing that our choice for the initial mass of the outer tertiary is critical since it
-ensures that the donor star during the mass transfer process will have
-a radiative envelope \citep[e.g.][]{2009pfer.book.....M}.  In turn, this ensures
-that the mass transfer will be maximally conservative, such that the
-accretion stream will be maximally stable, accreting at a stable and
-roughly constant rate \citep[e.g.][]{1991ApJS...76...55I}.
-
-%\simon{Why would we try to sell already what we plan on doing.
-I'de prefer to keep this quet.
-- NL2: To be honest, the ideas came to me, seemed relevant, and I was more interested in if *you* thought they were interesting ideas worth pursuing.
-If that is the case, then yes let's pursue it ourselves and remove this paragraph (now done).
-Happy to work on these ideas, and actually have been in the WD+WD case with a student but it is going very slowly.
-I think this mechanism should tie in nicely with that project though, so I'd like to include you on that if the student gets what he needs to done...
-it might be a lot quicker for us to just do it though.
-:) }
-%Finally, in future work, we intend to explore the implications of the
-%mechanism proposed here for other types of stellar triples.  Our
-%results highlight that specific theoretical predictions can often be
-%made.  For example, if two white dwarfs form the inner compact binary,
-%than circumbinary accretion could push one of them above the
-%Chandrasekhar mass limit.  Upon explosion, its WD companion would be
-%ejected at roughly the orbital velocity at the time of explosion,
-%producing a hypervelocity WD.  This predicts hot hypervelocity WDs
-%with masses very close to the Chandrasekhar mass limit for this
-%scenario.  Similarly, if the two WDs are replaced with two neutron
-%stars (NSs), then one NS could accrete to surpass the critical
-%supernova limit, upon which time it explodes to become a black hole
-%and receives a strong natal kick.  The NS companion would have a very
-%comparable mass to the newly formed black hole progenitor at the time
-%of explosion, and could potentially be used to constrain the maximum
-%NS mass.  More work needs to be done here to evaluate whether or not
-%there is any parameter space for the products of this scenario that
-%will allow for a mass determination for the original NS companion in
-%the putative compact NS-NS binary.
+We emphasize in closing that our choice for the initial mass of the
+outer tertiary is critical since it ensures that the donor star during
+the mass transfer process will have a radiative envelope
+\citep[e.g.][]{2009pfer.book.....M}.  In turn, this ensures that the
+mass transfer will be maximally conservative, such that the accretion
+stream will be maximally stable, accreting at a stable and roughly
+constant rate \citep[e.g.][]{1991ApJS...76...55I}.
 

### 2019-01-17 BSS7782.tex
updated tex file

@@
 \shorttitle{Compact Binaries of BS Twins from Stellar Triples}
-\shortauthors{Leigh \& Portegies Zwart}
+\shortauthors{Portegies Zwart \& Leigh}
 %%
@@
 
+\author{Simon Portegies Zwart}
+\affiliation{Leiden Observatory \\
+Leiden University \\
+PO Box 9513, 2300 RA \\
+Leiden, the Netherlands}
+
 \author{Nathan W. C. Leigh}
@@
 
-\author{Simon Portegies Zwart}
-\affiliation{Leiden Observatory \\
-Leiden University \\
-PO Box 9513, 2300 RA \\
-Leiden, the Netherlands}
+%\author{Simon Portegies Zwart}
+%\affiliation{Leiden Observatory \\
+%Leiden University \\
+%PO Box 9513, 2300 RA \\
+%Leiden, the Netherlands}
 
@@
 
-We propose a formation mechanism for twin blue stragglers in compact
-binaries that involve mass transfer from an evolved outer tertiary
+We propose a formation mechanism for twin blue stragglers (BSs) in compact
+binaries that involves mass transfer from an evolved outer tertiary
 companion on to the inner binary via a circumbinary disk.  We apply
-this scenario to the observed double blue straggler system Binary 7782
+this scenario to the observed double BS system Binary 7782
 in the old open cluster NGC 188, and show that its observed properties
 are naturally reproduced within the context of the proposed model.
-Based on this model, we predict the following properties for twin blue
-stragglers: (1) For the outer tertiary orbit, the initial orbital
+Based on this model, we predict the following properties for twin BSs: (1) For the outer tertiary orbit, the initial orbital
 period should lie between 220 days $\lesssim$ P$_{\rm out}$ $\lesssim$
@@
 0.43 to 0.54\,\MSun. There is a correlation between the mass of this
-WD and the outer orbital period in the sense that more massive white
-dwarfs will be on wider orbits.  (3) The rotational axes of both the
-BSs in the inner binary will be aligned with each other and the
-orbital plane of the outer tertiary WD. (4) The BSs in the inner
-binary will have roughly the same masses, independent of their initial
-masses.  This follows from the more copious accretion of mass onto the
-initially lower mass star.  This star should, therefore, be enriched
+WD and the outer orbital period: more massive WDs will be on wider orbits.  (3) The rotational axes of both 
+BSs will be aligned with each other and the
+orbital plane of the outer tertiary WD. (4) The BSs 
+will have roughly equal masses, independent of their initial
+masses (since the initially lower mass star accretes the most).  The dominant accretor should, therefore, be enriched
 more effectively by the accreted material.  As a result, one of the
-blue stragglers will appear to be more enriched by He, C and O
-if the donor started to overflow its Roche lobe at the red
-giant branch, or with s-process elements, if the donor was on the
-asymptotic giant branch.  (5) Relative to old dense clusters with high-velocity dispersions, twin BSs in close binaries formed from the
+BSs will appear to be more enriched by either He, C and O or by s-process elements, depending on 
+if the donor started to overflow its Roche lobe on, respectively, the red
+giant or asymptotic giant branch.  (5) Relative to old dense clusters with high-velocity dispersions, twin BSs in close binaries formed from the
 proposed mechanism should be more frequent in the Galactic field and
@@
 donor will have a radiative envelope. (6) the orbit of the binary BS
-will be close (typically $\aplt 0.3$\,au) and close to circular ($e
+will have a small semi-major axis (typically $\aplt 0.3$\,au) and be close to circular ($e
 \aplt 0.2$).
@@
 
-Blue straggler (BS) stars are brighter and bluer than the
-main-sequence turn-off in a cluster colour-magnitude diagram
+Blue straggler stars are brighter and bluer than the
+main-sequence (MS) turn-off in a cluster colour-magnitude diagram
 \citep[e.g.][]{1953AJ.....58...61S,2014ApJ...782...49S}.  Two primary
 channels for BS formation have been proposed: mass transfer from an
-evolved donor on to a main-sequence star in a binary star system
+evolved donor on to a MS star in a binary star system
 \citep[e.g.][]{1964MNRAS.128..147M,1997A&A...328..143P,2009Natur.457..288K,2011MNRAS.410.2370L,2011Natur.478..356G},
-and direct stellar collisions involving main-sequence stars possibly
+and direct stellar collisions involving MS stars possibly
 mediated via binaries
 \citep[e.g.][]{1975AJ.....80..809H,1997A&A...328..130P,2007ApJ...661..210L,2013MNRAS.428..897L,2013MNRAS.429.1221H,2018arXiv181100058P}.
-Other possible, albeit related, formation mechanism includes mergers
-of close main-sequence binaries (MS-MS) \cite{2018arXiv181100058P},
+Other possible, albeit related, formation mechanisms include mergers
+of close MS-MS binaries \cite{2018arXiv181100058P},
 and mergers of the inner binaries of hierarchical triple star systems
@@
 exist with observed properties that defy these simple scenarios.  For
-example, in the old open cluster M67, there lurks a candidate triple
+example, in the old open cluster (OC) M67, there lurks a candidate triple
 system that is posited to host two BSs
@@
 period of only $\sim 1.068$ days \citep{2001A&A...375..375V}, and
-hosts a BS of mass $\sim 2.52$ M$_{\odot}$.  In order to form this
-system we require at least five stars in order to conserve the total
-mass in the system \citep{2011MNRAS.410.2370L}.  As explained in
-\citet{2011MNRAS.410.2370L}, this is strongly indicative of a
+hosts a BS of mass $\sim 2.52$ M$_{\odot}$.  In order to reproduce the total system mass 
+we require at least five stars \citep{2011MNRAS.410.2370L}.  This is strongly indicative of a
 dynamical origin for the system, and a single direct interaction
 involving a binary and a triple that resulted in two separate
-collision events is the most probable explanation for its origin
-(i.e., a single interaction involving two multiples with two or more
-stars is a more likely scenario to produce this system than two
-back-to-back direct binary-binary interactions)
-\citep{2004MNRAS.350..615G}.
+collisions is the most probable explanation for its origin
+(instead of back-to-back direct binary-binary interactions)
+\citep{2004MNRAS.350..615G,2011MNRAS.410.2370L}.
 
-Even more curious, there exists in the old open cluster NGC 188 a
-double BS binary, called Binary 7782.  More generally, the BS
+Even more curious, there exists in the old OC NGC 188 a
+double BS binary, called Binary 7782.  The BS
 population in NGC 188 has a bi-modal period-eccentricity distribution.
@@
 mildly eccentric (i.e., $e \sim 0.1$) binary star system with an
-orbital period of $\sim$ 10 days hosting two roughly equal-mass blue
-stragglers.  During a given binary-binary interaction, the probability
+orbital period of $\sim$ 10 days hosting two roughly equal-mass BSs.  During a given binary-binary interaction, the probability
 that not one but two direct (MS-MS) collisions will occur is less than
@@
 binaries in general, which involves mass transfer from an outer
-tertiary companion on to an inner binary composed of two main-sequence
+tertiary companion on to an inner binary composed of two MS 
 stars.  In section~\ref{sect:dyn}, we constrain the range of initial
@@
 evolution-based constraints.  In Section~\ref{sims} we present the
-numerical simulations used to study the mass transfer process triple
-system with orbital parameters that, according to our expectations,
-for promising progenitors for the twin BS 7782.  The calculations are
+numerical simulations used to study the mass transfer process in this triple
+system. We adopt orbital parameters that, according to our expectations,
+are most promising for the progenitors of the twin BS 7782.  The calculations are
 performed using the Astrophysical Multipurpose Software Environment
@@
 calculations we further constrain the possible range of initial
-parameters that naturally lead to twin BS with orbital parameters
+parameters that naturally lead to twin BSs with orbital parameters
 similar to the 7782 system.  We summarize and discuss the implications
@@
 In our scenario, we start with a binary star with component masses
-$m_{\rm 1}$ and $m_{\rm 2}$ that is orbited tertiary of mass
+$m_{\rm 1}$ and $m_{\rm 2}$ that is orbited by a tertiary of mass
 $m_3$. The inner and outer binary orbital semi-major axes are denoted
-a$_{\rm in}$ and a$_{\rm out}$, respectively.  For clarity we now
+a$_{\rm in}$ and a$_{\rm out}$, respectively.  For clarity we 
 assume both orbits, the inner as well as the outer, to have negligible
@@
 from the centre of mass corresponding to the tertiary defined by the
-Roche lobe is given by Equation 2 in \citep{1983ApJ...268..368E}.
-Combining Equation 2 in \citet{1983ApJ...268..368E} (with mass ratio q
+Roche lobe is given by eq.\,2 in \citep{1983ApJ...268..368E}.
+Combining eq.\,2 in \citet{1983ApJ...268..368E} (with mass ratio q
 $=$ m$_{\rm 3}$/(m$_{\rm 1} +$m$_{\rm 2}$)) with
-Equation~\ref{eqn:specangmom1}, we solve for the circularization
+eq.~\ref{eqn:specangmom1}, we solve for the circularization
 radius as a function of a$_{\rm out}$ and the assumed stellar masses:
@@
 constraints from the requirements for dynamical stability (listed in
-the caption of Figure~\ref{fig:fig2}), an outer tertiary that is Roche
-lobe-filling, and a dynamically hard outer tertiary orbit.  \simon{Why
-  do you consider it important to mention that the orbit is hard, and
-  for what environment did you consider this?}  Note that the range of
+the caption of figure~\ref{fig:fig2}), and the assumption of an outer tertiary that is Roche
+lobe-filling.  
+%\simon{Why do you consider it important to mention that the orbit is hard, and for what environment did you consider this? - NL: Deleted.}  
+Note that the range of
 plotted orbital periods P$_{\rm in}$ corresponding to a contact state
 for the inner binary lies outside the range of plotted values for
-$P_{\rm in}$ (for components with radii of roughly 1 R$_{\odot}$),
+$P_{\rm in}$ (for components with radii of 1 R$_{\odot}$),
 since it does not contribute to constraining the outer orbital
-properties).  The thick horizontal solid red line shows the allowed
+properties.  The thick horizontal solid red line shows the allowed
 range of outer semi-major axes, after folding in all of 
@@
 range of initial conditions for the outer orbit, namely 2.2 $\times$
-10$^{2}$ days $\le$ P$_{\rm out}$ $\le$ 1.1 $\times$ 10$^3$ days, for
-which the tertiary star overfills its Roche lobe, the triple is (at
-least initially) dynamically stable and the accretion stream forms a
-gaseous ring around the inner binary.
+10$^{2}$ days $\le$ P$_{\rm out}$ $\le$ 1.1 $\times$ 10$^3$ days.
+%, for
+%which the tertiary star overfills its Roche lobe, the triple is (at
+%least initially) dynamically stable and the accretion stream forms a
+%gaseous ring around the inner binary.
 
@@
   reached on the AGB for the range of tertiary masses of interest to
-  us.  The horizontal dashed red line shows the observed orbital
+  us; see figure~\ref{fig:tertiarymass_vs_size}).  The horizontal dashed red line shows the observed orbital
   period for Binary 7782, using its observed orbital period and our
@@
   \caption{Giant radius as a function of the mass of the core of the
-    Roche-lobe filling outer star (dark blue curve).  Here we adopted
-    a donor mass of 1.4\,\MSun, but for an 1.2\,\MSun\, donor curve is
+    Roche-lobe filling outer star (dark blue curve).  Here we adopt
+    a donor mass of 1.4\,\MSun, but for an 1.2\,\MSun\, donor the curve is
     quite similar (see dotted dark-blue curve).  The red squares in
@@
     The horizontal dashed line shows the orbital separation of the
-    observed twin blue straggler 7782.  The initial triple in which it
+    observed twin BS 7782.  The initial triple in which it
     possibly formed must at least have been dynamically stable. The
@@
     lobe is indicated with the light-blue curve. The top curve (brown)
-    shows an estimate of the final orbit separation of the outer star,
-    and therefore of the final orbit of the white dwarf around the
-    inner twin blue straggler.  For core masses $\apgt 0.5$\,\MSun\,
+    shows an estimate of the final orbital separation of the outer star,
+    and therefore of the final orbit of the WD around the
+    inner twin BSs.  For core masses $\apgt 0.5$\,\MSun\,
     the final orbital separation, after mass transfer, is smaller
     than the initial orbit.  Here we adopted an initial inner binary
-    mass of (1.0+0.9)\,\MSun\, and a final twin-blue straggler mass of
+    mass of (1.0+0.9)\,\MSun\, and a final twin BS mass of
     (1.4+1.4)\,\MSun.
@@
 
-When adopting a mass of the tertiary star of $m_3 = 1.4$\,\MSun, we
+Adopting a mass for the tertiary star of $m_3 = 1.4$\,\MSun, we
 can constrain the initial parameters for the inner binary as well as
@@
 maximum orbital separation for the inner binary for which the orbit is
-stable and a circum-binary disk can form. These two limits are
-presented as the light-blue and light green curves in
+stable and a circumbinary disk can form. These two limits are
+presented as the light blue and light green curves in
 figure\,\ref{fig:tertiarymass_vs_size}.  The alotted region of
@@
 With the adopted parameters, we can also estimate the final orbital
-period of the left-over core from the tertiary star after the phase of
+period of the left-over core from the tertiary star after 
 mass transfer.  The change in orbital separation due to
@@
 we arrive at the top brown curve in
-figure\,\ref{fig:tertiarymass_vs_size}. This curve provides an
-estimate of the orbital separation of the white dwarf around the twin
-blue straggler 7782. Tidal effects during the episode of mass tranfer
-have probably circularized the orbit, althoug some slight eccentricity
+figure\,\ref{fig:tertiarymass_vs_size}. This curve provides a prediction for 
+the current orbital separation of the WD around the twin
+BS 7782. Tidal effects during mass tranfer
+have probably circularized the orbit, although some slight eccentricity
 due to turbulent motion in the outer layers of the donor star may have
@@
 
-Having limited parameter space for the formation of the twin blue
-straggler 7782, we continue by performing a series of simulations to
+Having limited parameter space for the formation of the twin BS 7782, we continue by performing a series of simulations to
 investigate the accretion and changes to the inner orbits of triple
@@
 100\,\RSun\, and 150\,\RSun, at which point we assume it to overfill
-it's Roche lobe (see red squared in
+it's Roche lobe (see red square in
 figure~\ref{fig:tertiarymass_vs_size}).  We perform calculations for an
@@
 0.15$\,au and $a_{\rm in} = 0.20$\,au.  In total we performed 12
-calculations at a resolution of 40k SPH particles 12 at 80k.
+calculations at a resolution of 40k SPH particles and 12 at 80k.
 
@@
 \caption{Top view of the simulated triple system in which the
-  100\,\RSun\, outer star of 1.4\,\MSun\, that over-fills its
-  Roche-lobe.  the star is represented by 80000\,SPH particles and a
+  100\,\RSun\, outer star of 1.4\,\MSun\, over-fills its
+  Roche-lobe.  The star is represented by 80000\,SPH particles and a
   core particle of $\sim 0.4$\,\MSun (black bullet). The two companion
   stars are represented as black bullets (to the right).  The inner
-  binary is represented by the yellow and the red bullets for the
+  binary is represented by the yellow and red bullets for, respectively, the
   1.1\,\MSun\, primary and 0.9\,\MSun\, secondary stars in a circular
   orbit of 0.1\,au. The 1.4\,\MSun\, giant star is presented to the
-  right in a circular orbit of $\sim 250$\,\RSun\, in the plan of the
+  right in a circular orbit of $\sim 250$\,\RSun\, in the plane of the
   inner binary.
@@
 its own particles, as well as the gravitational potential of the inner
-binary. The hydrodynamics, in particular, the interaction with the gas,
-in turn, affects the orbits of the two inner stars. With
+binary. The hydrodynamics affects the orbits of the two inner stars. With
 \texttt{Bridge} we realize a second order coupling between the
@@
 figure~\ref{fig:mass_vs_semimajor_axis}.  The first figure
-(figure~\ref{fig:topview_at_t1000day} shows the top view of the same
+(figure~\ref{fig:topview_at_t1000day}) shows the top view of the same
 initial realization for which we presented the initial conditions in
@@
 make the scenario feasible. Over the time scale for which we performed
-the calculations, this efficiency is reached, but it is not clear who
+the calculations, this efficiency is reached, but it is not clear how
 the system responds at later stages.
@@
   \simeq 1091\,days$ after the start of the simulation. Left panel
-  shows the equipotential surface of the triple overplotted with the
+  shows the equipotential surfaces of the triple overplotted with the
   gas distribution, the right panel shows just the gas and the stars
@@
 The evolution of the inner orbit presented for several simulations in
-figure~\ref{fig:mass_vs_semimajor_axis}, is complicated.  This is
+figure~\ref{fig:mass_vs_semimajor_axis} is complicated.  This is
 caused by the complex transport of mass, energy and angular momentum
@@
 therefore hard to quantify distinct trends in the evolution of the
-triple system. In simulated of the response of an inner binary on
+triple system. In simulations of the response of an inner binary on
 accretion from a circumbinary disk, \cite{2018arXiv181208175M}
 conclude that the complexity of angular momentum transport between
-outer star, accretion stream to the individual inner stars, is
+the outer star and the accretion stream onto the individual inner stars, is
 complicated and without clear trends. For most of our calculations we
@@
 figure~\,\ref{fig:mass_vs_semimajor_axis} we nevertheless present the
-results of 6 of our calculations, three for and 1.2\,\MSun\, donor and
-three for a 1.4\,\MSun\, donor star. The various coloured curves give
+results of 6 of our calculations, three for a 1.2\,\MSun\, donor star and
+three for a 1.4\,\MSun\, donor. The various coloured curves give
 the resulting evolution of the inner orbit as a function of the total
-mass in the inner binary. While the inner two stars accrete the orbit
-in the case with a 1.2\,\MSun\, donor tends to shrink. These systems
+mass in the inner binary. As the inner two stars accrete, the orbit shrinks 
+for a 1.2\,\MSun\, donor. These systems
 are expected to result in a contact binary, that eventually may merge
-to form a single blue straggler. The required evolution in order to
-explain the observed twin blue straggler 7782 are indicated with the
-three black curves, and the simulated path clearly deviates from
+to form a single BS. The required evolution in order to
+explain the observed twin BS 7782 is indicated by the
+three black curves; the simulated path clearly deviates from
 these. We, therefore, argue that a 1.2\,\MSun\, donor has difficulty
@@
     function of the orbital separation for four calculations with
-    somewhat different initial conditions (see legend).  The initial
-    binary for the orange curve is presented in
+    somewhat different initial conditions (see the legend).  The initial
+    binary shown by the orange curve is presented in
     fig.\,\ref{fig:topview_at_t0}, and in
@@
 present the evolution of the orbit for the 1.4\,\MSun\, donor. A more
-massive donor is more likely to be able to produce a twin blue
-straggler, simply because there is more mass available in the stellar
+massive donor is more likely to be able to produce a twin BS system, simply because there is more mass available in the stellar
 envelope. On the other hand, a more massive donor may also result in a
 lower accretion efficiency, because the thermal time scale of the
-stellar envelope is smaller than for the lower mass donor at the same
-stellar radius. Such a shorter thermal time-scale eventually leads to
+stellar envelope is smaller than for a lower mass donor at the same
+stellar radius. A shorter thermal time-scale eventually leads to
 a higher mass transfer rate, which again may lead to a lower accretion
@@
 The orbit of the inner binary expands in these cases as a result of
-the accretion onto the inner two stars. In all the three cases
-presented in figure~\ref{fig:mass_vs_semimajor_axis} expand by about
-the same rate (as function of the accretion onto the inner binary
-star). As a consequence, the inner binaries that start with $a =
+accretion onto the inner two stars. All three cases
+presented in figure~\ref{fig:mass_vs_semimajor_axis} expand at about
+the same rate. Consequently, the inner binaries that start with $a =
 0.15$\,au and $a=0.20$\,au eventually become dynamically unstable.
 The binary with an initial separation of $0.10$\,au expands to reach a
-separation of about 0.126--0.145\,au for a mass of the inner two stars
-of 1.4\,\MSun, which is consistent with the observed twin blue
-straggler 7782. In our simulations the eccentricity of the inner
+separation of about 0.126--0.145\,au for final masses for the inner two stars
+of 1.4\,\MSun, which is consistent with the observed twin BS 7782. In our simulations the eccentricity of the inner
 binary grows to about $e \simeq 0.0028$.
@@
 accrete angular momentum.  By the end of the simulation the spins of
-the two blue stragglers are aligned along the orbital angular momentum
+the two BSs are aligned along the orbital angular momentum
 axis with an angle of $90.0^\circ$ for the primary star and
@@
 
-We considered the formation of twin blue stragglers in tight binaries.
+In this paper, we consider the formation of twin BSs in tight binaries.
 These systems may form through mass transfer from an outer Roche-lobe
@@
 of its envelope is transferred to the inner binary, and accreted by
-the two inner stars which are still on the main sequence.
+the two inner stars which are still on the MS.
 
@@
 expand depending on the details of the transfer of mass and angular
-momentum. Regretfully, we do not really understand the details of this
-process, but then this process is hardly understood in binary
-evolution also.
+momentum.  More work is certainly needed in order to fully understand 
+mass transfer in triples.
+%Regretfully, we do not really understand the details of this
+%process, but then this process is hardly understood in binary
+%evolution also.
+%NL: I edited the above to be a kinder to us.
 
@@
 1.2\,\MSun\, tertiary donor mass, we expect the inner two stars to
-eventually merge and form a single blue straggler. This reduces the
-system to a binary with a primary blue straggler and an outer white
-dwarf in a relatively wide orbit. Such a blue straggler will
-distinguish itself from other blue stragglers from potentially
+eventually merge and form a single BS. This reduces the
+system to a binary with a primary BS and an outer WD in a relatively wide orbit. Such a BS will
+distinguish itself from other BSs by potentially
 being more than twice the turn-off mass in a star cluster.  An
-example could be the $2.9\pm0.2$\,\MSun\, blue straggler S1237 in the
+example could be the $2.9\pm0.2$\,\MSun\, BS S1237 in the
 Galactic cluster M67 \cite{2016ApJ...832L..13L}. It is the primary of
@@
 
-With an original outer star of $\sim 1.4$\,\MSun, the inner orbit
-tends to expand. For relatively wide inner orbit this eventually leads
+With an original outer star of mass $\sim 1.4$\,\MSun, the inner orbit
+tends to expand. This eventually leads
 to a dynamically unstable system resulting either in a collision or in
 the ejection of (probably) the lowest mass star. This evolution could
-result in a single ejected blue straggler the other blue straggler in
-a relatively close and eccentric orbit with a white dwarf (the
-left-over core of the tertiary star).
+result in a single ejected blue straggler, with the other BS left in
+a relatively close and eccentric orbit with a WD (the
+left-over core of the tertiary star).  These ``imposter'' BS-WD binaries 
+would in principle mimic what is expected theoretically for BSs formed 
+from mass transfer in binary stars.
 
 When we adopt an inner orbit of $0.10$\,au\, the expansion eventually
-matches the observed orbital separation of $0.13$\,au of the observed
-twin BSS 7782 and the observed masses of the two stars.
+matches the observed orbital separation (i.e., $0.13$\,au) of the observed
+twin BS 7782 and the observed masses of the two stars.
 
@@
 results here.  For V4046 Sgr, for which the two stars have comparable
-masses as in our calculation in an circular orbit with a period of
-only 2.4 days they find that the inner binary accretes at a rate of
+masses as in our calculation for a circular orbit with a period of
+only 2.4 days, they find that the inner binary accretes at a rate of
 $\sim 0.028$\,\MSun/Myr.  For DQ~Tau, which is composed of lower-mass
 stars ($m_1 = m_2 \simeq 0.55$\,\MSun) in an eccentric ($e\simeq
-0.556$) orbit of $\sim 15.8$\,days they find an accretion rate onto
+0.556$) orbit of $\sim 15.8$\,days, they find an accretion rate onto
 the inner binary of $\sim 0.027$\,\MSun/Myr.  These values are in the
 same range as in our calculations, which results in an accretion rate
-of the inner binary of 0.027--0.058\,\MSun/Myr (i.e., the average
+for the inner binary of 0.027--0.058\,\MSun/Myr (i.e., the average
 measured over a period of about 3000 days in our simulations).
@@
 
-We propose a formation scenario for twin blue stragglers of equal-mass
-in tight binaries, as observed for Binary 7782 in the old open cluster
+In this paper, we propose a formation scenario for twin equal-mass blue stragglers 
+in tight binaries, as observed for Binary 7782 in the old OC
 NGC 188.  The proposed scenario involves mass transfer from an evolved
@@
 
-\item For the predicted outer tertiary orbit, the present-day
-  semi-major axis should lie between 220 days $\lesssim$ P$_{\rm out}$
+\item For the predicted outer tertiary orbit, the initial 
+  orbital period should lie between 220 days $\lesssim$ P$_{\rm out}$
   $\lesssim$ 1100 days, assuming initial masses for the inner binary
@@
   M$_{\odot}$ and an initial outer tertiary mass of $m_{\rm 3} = 1.4
-  $M$_{\odot}$.
+  $M$_{\odot}$.  Hence, the present-day orbital period should be close to this range.
 
@@
   the time of mass transfer should correspond to larger final outer
-  orbital periods for the tertiary.  This is because of the Roche radius
+  orbital periods for the tertiary.  This is because the Roche radius
   is larger for larger outer orbital periods, such that the donor must
@@
   be aligned with each other and the orbital plane of the outer
-  tertiary WD.  This is because of accretion onto the BS progenitors
+  tertiary WD.  This is because accretion onto the BS progenitors
   proceeds via an accretion disk, that forms at the circularization
@@
   should be more frequent in younger clusters with ages $\lesssim$ 4-6
-  Gyr.  This is because of clusters with a main-sequence turn-off mass
+  Gyr.  This is because clusters with a MS turn-off mass
   $\lesssim$ 1.2 M$_{\odot}$ have convective envelopes

### 2019-01-18 BSS7782.tex
removed small bug
updated figs 1 and 2
Edited tex file

@@
 Roche-lobe overflow, the outer star turns into a white dwarf (WD) of
-0.43 to 0.54\,\MSun. There is a correlation between the mass of this
+mass 0.43 to 0.54\,\MSun. There is a correlation between the mass of this
 WD and the outer orbital period: more massive WDs will be on wider orbits.  (3) The rotational axes of both 
@@
 \citep[e.g.][]{1964MNRAS.128..147M,1997A&A...328..143P,2009Natur.457..288K,2011MNRAS.410.2370L,2011Natur.478..356G},
-and direct stellar collisions involving MS stars possibly
+and direct stellar collisions involving MS stars likely 
 mediated via binaries
 \citep[e.g.][]{1975AJ.....80..809H,1997A&A...328..130P,2007ApJ...661..210L,2013MNRAS.428..897L,2013MNRAS.429.1221H,2018arXiv181100058P}.
-Other possible, albeit related, formation mechanisms include mergers
+The first mechanism predicts BSs in binaries with WD companions, whereas the second predicts 
+MS companions and long orbital periods.  Other possible, albeit related, formation mechanisms include mergers
 of close MS-MS binaries \cite{2018arXiv181100058P},
@@
 products during a collisional interaction in a star cluster
-\citep{2011Sci...334.1380F}.  So, how did Binary 7782 form?
+\citep{2011MNRAS.410.2370L,2011Sci...334.1380F}.  So, how did Binary 7782 form?
 
@@
 (\texttt{AMUSE} for short) \cite{AMUSE} with a combination of stellar
-evolution, hydrodynamical and gravitational simulations.  with these
+evolution, hydrodynamical and gravitational simulations.  With these
 calculations we further constrain the possible range of initial
@@
 supported by the population of observed low-mass triples
-\cite{2010yCat..73890925T,moe18}.  This initial configuration for our
+\cite{2010yCat..73890925T,2018ApJ...854...44M}.  This initial configuration for our
 assumed formation scenario for Binary 7782, described below, is
@@
 \begin{figure}[ht!]
-\plotone{fig1.eps}
+\plotone{fig_doodle.eps}
 \caption{Cartoon depiction of our proposed scenario for the formation
@@
 \begin{figure}[ht!]
-\plotone{fig2.eps}
+\plotone{fig_parameterspace.eps}
 \caption{Parameter space in the P$_{\rm out}$-P$_{\rm in}$-plane
@@
   the mass transfer stream coming from the outer star (i.e., at the
-  onset of mass transfer), assuming a mass ratio of q $=$ 0.7 and
-  component masses of m$_{\rm 1} =$ 0.9 M$_{\odot}$, m$_{\rm 2} =$ 1.1
-  M$_{\odot}$ and m$_{\rm 3} =$ 1.4 M$_{\odot}$.  We assume initial
+  onset of mass transfer).  
+%, assuming a mass ratio of q $=$ 0.7.
+% and
+%  component masses of m$_{\rm 1} =$ 0.9 M$_{\odot}$, m$_{\rm 2} =$ 1.1
+%  M$_{\odot}$ and m$_{\rm 3} =$ 1.4 M$_{\odot}$.  
+We assume initial
   component masses of m$_{\rm 1}$ = 1.1 M$_{\rm \odot}$ and m$_{\rm
@@
     Roche-lobe filling outer star (dark blue curve).  Here we adopt
-    a donor mass of 1.4\,\MSun, but for an 1.2\,\MSun\, donor the curve is
+    a donor mass of 1.4\,\MSun, but for an 1.2\,\MSun\, the donor the curve is
     quite similar (see dotted dark-blue curve).  The red squares in
@@
 presented as the light blue and light green curves in
-figure\,\ref{fig:tertiarymass_vs_size}.  The alotted region of
+figure\,\ref{fig:tertiarymass_vs_size}.  The allotted region of
 parameter space is then above the dashed horizontal line and to the
@@
 non-conservative mass transfer can be expressed in terms of the mass
-of the outer star before and after mass transfer $m_3$ and $m'_3$,
+of the outer star before and after mass transfer, i.e. $m_3$ and $m'_3$
 respectively, the total mass in the inner binary before ($m_{\rm in}$)
@@
 due to turbulent motion in the outer layers of the donor star may have
-induces a small $e \ll 0.1$ eccentricity.
+induced a small $e \ll 0.1$ eccentricity.
 
@@
 \begin{figure}[ht!]
-  \includegraphics[width=\columnwidth]{fig_BBSS_gas_M14Msun_A010au_t0002.pdf}
+  \includegraphics[width=\columnwidth]{fig_BBSS_gas_M14Msun_A010au_t0002.png}
 \caption{Top view of the simulated triple system in which the
@@
   orbit of 0.1\,au. The 1.4\,\MSun\, giant star is presented to the
-  right in a circular orbit of $\sim 250$\,\RSun\, in the plane of the
+  right in a circular orbit with semi-major axis $\sim 250$\,\RSun\, in the plane of the
   inner binary.
@@
 the parameters of the system we study, but typically we achieve
-converged solutions when this time step is about a fraction of 1/100
+converged solutions when this time step is about 1/100 that 
 of the inner binary orbital period.
@@
 
-to test the hypotheses that (1) the secondary in the inner binary
+To test the hypotheses that (1) the secondary in the inner binary
 accretes more effectively than the primary star and to measure the
@@
 figure~\ref{fig:topview_at_t0} but now at an age of 1091 days after
-the onset of mass transfer. To guide the eye we add, to the left panel,
+the onset of mass transfer. We add, to the left panel,
 the equipotential surfaces in the orbital plane.
@@
 It is apparent that the mass transfer in the adopted triples leads to
-a rather untidy evolution, in particular, because much of the donor
+a rather untidy evolution, since much of the donor
 mass is lost through the second Lagrangian point to the right side of
-the donor star in figure~\ref{fig:topview_at_t1000day}. Much mass is
+the donor star in figure~\ref{fig:topview_at_t1000day}. Significant mass is
 also lost through the third Lagrangian point (to the left of the inner
@@
 the ejection of (probably) the lowest mass star. This evolution could
-result in a single ejected blue straggler, with the other BS left in
+result in a single ejected BS, with the other BS left in
 a relatively close and eccentric orbit with a WD (the
@@
   donor in a mass transferring binary ensures stable accretion on to
-  the accretor.  \simon{Can we quantify this?}
+  the accretor.  %\simon{Can we quantify this? - NL: The stability of the accretion...?}
 

### 2019-01-22 BSS7782.tex
updated refs, corrected small issues, and made some small changes to the text.

@@
 
-We propose a formation mechanism for twin blue stragglers (BSs) in compact
-binaries that involves mass transfer from an evolved outer tertiary
-companion on to the inner binary via a circumbinary disk.  We apply
-this scenario to the observed double BS system Binary 7782
-in the old open cluster NGC 188, and show that its observed properties
+We propose a formation mechanism for twin blue stragglers (BSs) in
+compact binaries that involves mass transfer from an evolved outer
+tertiary companion on to the inner binary via a circumbinary disk.  We
+apply this scenario to the observed double BS system Binary 7782 in
+the old open cluster NGC 188, and show that its observed properties
 are naturally reproduced within the context of the proposed model.
-Based on this model, we predict the following properties for twin BSs: (1) For the outer tertiary orbit, the initial orbital
-period should lie between 220 days $\lesssim$ P$_{\rm out}$ $\lesssim$
-1100 days, assuming initial masses for the inner binary components of
-$m_{\rm 1} = 1.1$ M$_{\odot}$ and $m_{\rm 2} =$ 0.9 M$_{\odot}$ and an
-outer tertiary mass of $m_{\rm 3} = 1.4$ M$_{\odot}$.  After
-Roche-lobe overflow, the outer star turns into a white dwarf (WD) of
-mass 0.43 to 0.54\,\MSun. There is a correlation between the mass of this
-WD and the outer orbital period: more massive WDs will be on wider orbits.  (3) The rotational axes of both 
-BSs will be aligned with each other and the
-orbital plane of the outer tertiary WD. (4) The BSs 
-will have roughly equal masses, independent of their initial
-masses (since the initially lower mass star accretes the most).  The dominant accretor should, therefore, be enriched
-more effectively by the accreted material.  As a result, one of the
-BSs will appear to be more enriched by either He, C and O or by s-process elements, depending on 
-if the donor started to overflow its Roche lobe on, respectively, the red
-giant or asymptotic giant branch.  (5) Relative to old dense clusters with high-velocity dispersions, twin BSs in close binaries formed from the
-proposed mechanism should be more frequent in the Galactic field and
-younger open clusters with ages $\lesssim$ 4-6 Gyr, since then the
-donor will have a radiative envelope. (6) the orbit of the binary BS
-will have a small semi-major axis (typically $\aplt 0.3$\,au) and be close to circular ($e
-\aplt 0.2$).
+Based on this model, we predict the following properties for twin BSs:
+(1) For the outer tertiary orbit, the initial orbital period should
+lie between 220 days $\lesssim$ P$_{\rm out}$ $\lesssim$ 1100 days,
+assuming initial masses for the inner binary components of $m_{\rm 1}
+= 1.1$ M$_{\odot}$ and $m_{\rm 2} =$ 0.9 M$_{\odot}$ and an outer
+tertiary mass of $m_{\rm 3} = 1.4$ M$_{\odot}$.  After Roche-lobe
+overflow, the outer star turns into a white dwarf (WD) of mass 0.43 to
+0.54\,\MSun. There is a correlation between the mass of this WD and
+the outer orbital period: more massive WDs will be on wider orbits.
+(3) The rotational axes of both BSs will be aligned with each other
+and the orbital plane of the outer tertiary WD. (4) The BSs will have
+roughly equal masses, independent of their initial masses (since the
+lower mass star accretes the most).  The dominant accretor should,
+therefore, be enriched more effectively by the accreted material.  As
+a result, one of the BSs will appear to be more enriched by either He,
+C and O or by s-process elements, depending on if the donor started to
+overflow its Roche lobe on, respectively, the red giant or asymptotic
+giant branch.  (5) Relative to old dense clusters with high-velocity
+dispersions, twin BSs in close binaries formed from the proposed
+mechanism should be more frequent in the Galactic field and younger
+open clusters with ages $\lesssim$ 4-6 Gyr, since then the donor will
+have a radiative envelope. (6) the orbit of the binary BS will have a
+small semi-major axis (typically $\aplt 0.3$\,au) and be close to
+circular ($e \aplt 0.2$).
 
@@
 
-Blue straggler stars are brighter and bluer than the
-main-sequence (MS) turn-off in a cluster colour-magnitude diagram
-\citep[e.g.][]{1953AJ.....58...61S,2014ApJ...782...49S}.  Two primary
-channels for BS formation have been proposed: mass transfer from an
-evolved donor on to a MS star in a binary star system
+Blue straggler stars are brighter and bluer than the main-sequence
+(MS) turn-off in a cluster colour-magnitude diagram
+\citep[e.g.][]{1953AJ.....58...61S,1989AJ.....98..217L,2014ApJ...782...49S}.
+Two primary channels for BS formation have been proposed: mass
+transfer from an evolved donor on to a MS star in a binary star system
 \citep[e.g.][]{1964MNRAS.128..147M,1997A&A...328..143P,2009Natur.457..288K,2011MNRAS.410.2370L,2011Natur.478..356G},
-and direct stellar collisions involving MS stars likely 
-mediated via binaries
-\citep[e.g.][]{1975AJ.....80..809H,1997A&A...328..130P,2007ApJ...661..210L,2013MNRAS.428..897L,2013MNRAS.429.1221H,2018arXiv181100058P}.
-The first mechanism predicts BSs in binaries with WD companions, whereas the second predicts 
-MS companions and long orbital periods.  Other possible, albeit related, formation mechanisms include mergers
-of close MS-MS binaries \cite{2018arXiv181100058P},
-and mergers of the inner binaries of hierarchical triple star systems
+and direct stellar collisions involving MS stars likely mediated via
+binaries
+\citep[e.g.][]{1975AJ.....80..809H,1997A&A...328..130P,2007ApJ...661..210L,2013MNRAS.428..897L,2013MNRAS.429.1221H, 2019A&A...621L..10P}.
+The first mechanism predicts BSs in binaries with WD companions,
+whereas the second predicts MS companions in a wide and eccentric
+binary.  Other possible, albeit related, formation mechanisms include
+mergers of close MS-MS binaries \citep{2019A&A...621L..10P}, and
+mergers of the inner binaries of hierarchical triple star systems
 induced by Lidov-Kozai oscillations coupled with tidal damping
@@
 binaries in general, which involves mass transfer from an outer
-tertiary companion on to an inner binary composed of two MS 
-stars.  In section~\ref{sect:dyn}, we constrain the range of initial
-(i.e., pre-mass transfer) orbital parameters for a hypothetical outer
+tertiary companion on to an inner binary composed of two MS stars.  In
+section~\ref{sect:dyn}, we constrain the range of initial (i.e.,
+pre-mass transfer) orbital parameters for a hypothetical outer
 tertiary companion, using a combination of dynamical and stellar
 evolution-based constraints.  In Section~\ref{sims} we present the
-numerical simulations used to study the mass transfer process in this triple
-system. We adopt orbital parameters that, according to our expectations,
-are most promising for the progenitors of the twin BS 7782.  The calculations are
-performed using the Astrophysical Multipurpose Software Environment
-(\texttt{AMUSE} for short) \cite{AMUSE} with a combination of stellar
+numerical simulations used to study the mass transfer process in this
+triple system. We adopt orbital parameters that, according to our
+expectations, are most promising for the progenitors of the twin BS
+7782.  The calculations are performed using the Astrophysical
+Multipurpose Software Environment \cite[\texttt{AMUSE} for short,
+  see][]{PortegiesZwart2013456,AMUSE} with a combination of stellar
 evolution, hydrodynamical and gravitational simulations.  With these
@@
 supported by the population of observed low-mass triples
-\cite{2010yCat..73890925T,2018ApJ...854...44M}.  This initial configuration for our
+\citep{2010yCat..73890925T,2018ApJ...854...44M}.  This initial configuration for our
 assumed formation scenario for Binary 7782, described below, is
@@
 system to be dynamically stable, for which we adopt eq.\,1 in
-\cite{1999ASIC..522..385M,}.  While transferring mass, the accretion
+\cite{1999ASIC..522..385M}.  While transferring mass, the accretion
 stream gathers around the inner binary at the circularization radius
@@
 from the centre of mass corresponding to the tertiary defined by the
-Roche lobe is given by eq.\,2 in \citep{1983ApJ...268..368E}.
+Roche lobe is given by eq.\,2 in \cite{1983ApJ...268..368E}.
 Combining eq.\,2 in \citet{1983ApJ...268..368E} (with mass ratio q
@@
 %  M$_{\odot}$ and m$_{\rm 3} =$ 1.4 M$_{\odot}$.  
-We assume initial
-  component masses of m$_{\rm 1}$ = 1.1 M$_{\rm \odot}$ and m$_{\rm
-    2}$ = 0.9 M$_{\rm \odot}$ for the inner binary components, and
-  m$_{\rm 3}$ is computed for the outer tertiary according to our
-  assumed mass ratio (with our fiducial case corresponding to q $=$
-  0.7).  We assume completely conservative mass transfer for this
-  exercise, and a final mass for the outer tertiary of 0.6 M$_{\rm
-    \odot}$ once it has become a WD.  The dashed diagonal black line
-  shows a rough criterion for dynamical stability in the triple,
-  approximately following \citet{mardling99} (i.e., a$_{\rm in} <$
-  0.1a$_{\rm out}$ is required for long-term dynamical stability in
-  equal-mass co-planar triples).  The vertical solid red lines show
-  the outer orbital periods corresponding to the hard-soft boundary
-  assuming central velocity dispersions of $\sigma =$ 1, 5 and 10 km
-  s$^{-1}$.  The vertical dashed black lines show the maximum outer
-  orbital period P$_{\rm out}$ for which the outer tertiary companion
-  is Roche lobe-filling, assuming a stellar radius of R$_{\rm 3} =$
-  200 R$_{\odot}$ (which corresponds to the maximum stellar radius
-  reached on the AGB for the range of tertiary masses of interest to
-  us; see figure~\ref{fig:tertiarymass_vs_size}).  The horizontal dashed red line shows the observed orbital
-  period for Binary 7782, using its observed orbital period and our
-  assumed final inner companion masses (i.e., m$_{\rm 1} =$ m$_{\rm 2}
-  =$ 1.4 M$_{\odot}$).  Finally, the thick solid horizontal red line
-  shows the parameter space for P$_{\rm out}$ allowed after
-  considering all of the aforementioned criteria.  
+We assume initial component masses of m$_{\rm 1}$ = 1.1 M$_{\rm
+  \odot}$ and m$_{\rm 2}$ = 0.9 M$_{\rm \odot}$ for the inner binary
+components, and m$_{\rm 3}$ is computed for the outer tertiary
+according to our assumed mass ratio (with our fiducial case
+corresponding to q $=$ 0.7).  We assume completely conservative mass
+transfer for this exercise, and a final mass for the outer tertiary of
+0.6 M$_{\rm \odot}$ once it has become a WD.  The dashed diagonal
+black line shows a rough criterion for dynamical stability in the
+triple, approximately following \citet{1999ASIC..522..385M} (i.e.,
+a$_{\rm in} <$ 0.1a$_{\rm out}$ is required for long-term dynamical
+stability in equal-mass co-planar triples).  The vertical solid red
+lines show the outer orbital periods corresponding to the hard-soft
+boundary assuming central velocity dispersions of $\sigma =$ 1, 5 and
+10 km s$^{-1}$.  The vertical dashed black lines show the maximum
+outer orbital period P$_{\rm out}$ for which the outer tertiary
+companion is Roche lobe-filling, assuming a stellar radius of R$_{\rm
+  3} =$ 200 R$_{\odot}$ (which corresponds to the maximum stellar
+radius reached on the AGB for the range of tertiary masses of interest
+to us; see figure~\ref{fig:tertiarymass_vs_size}).  The horizontal
+dashed red line shows the observed orbital period for Binary 7782,
+using its observed orbital period and our assumed final inner
+companion masses (i.e., m$_{\rm 1} =$ m$_{\rm 2} =$ 1.4 M$_{\odot}$).
+Finally, the thick solid horizontal red line shows the parameter space
+for P$_{\rm out}$ allowed after considering all of the aforementioned
+criteria.
 \label{fig:fig2}}
@@
   \caption{Giant radius as a function of the mass of the core of the
-    Roche-lobe filling outer star (dark blue curve).  Here we adopt
-    a donor mass of 1.4\,\MSun, but for an 1.2\,\MSun\, the donor the curve is
-    quite similar (see dotted dark-blue curve).  The red squares in
-    the curve show the parameters for which we performed more detailed
-    gravitational-hydrodynamical simulations (see \S\,\ref{sims}).
-    The horizontal dashed line shows the orbital separation of the
-    observed twin BS 7782.  The initial triple in which it
-    possibly formed must at least have been dynamically stable. The
-    minimal orbital separation for the inner binary for which the
-    triple is stable is given by the lower green coloured curve.
-    Donors which are smaller than about 100\,\RSun\, (dark blue curve
-    indicated with a$_{\rm stable}$) result in a dynamically unstable
-    triple. The minimal core mass associated with a stable triple is
-    then indicated by the left-most vertical dotted line.  The
-    orbital separation at which the donor star overfills its Roche
-    lobe is indicated with the light-blue curve. The top curve (brown)
-    shows an estimate of the final orbital separation of the outer star,
-    and therefore of the final orbit of the WD around the
-    inner twin BSs.  For core masses $\apgt 0.5$\,\MSun\,
-    the final orbital separation, after mass transfer, is smaller
-    than the initial orbit.  Here we adopted an initial inner binary
-    mass of (1.0+0.9)\,\MSun\, and a final twin BS mass of
-    (1.4+1.4)\,\MSun.
+    Roche-lobe filling outer star (dark blue curve).  Here we adopt a
+    donor mass of 1.4\,\MSun, but for an 1.2\,\MSun\, the donor the
+    curve is quite similar (see dotted dark-blue curve).  The red
+    squares in the curve show the parameters for which we performed
+    more detailed gravitational-hydrodynamical simulations (see
+    \S\,\ref{sims}).  The horizontal dashed line shows the orbital
+    separation of the observed twin BS 7782.  The initial triple in
+    which it possibly formed must at least have been dynamically
+    stable. The minimal orbital separation for the inner binary for
+    which the triple is stable is given by the lower green coloured
+    curve.  Donors which are smaller than about 100\,\RSun\,
+    (light-green curve indicated with a$_{\rm stable}$) result in a
+    dynamically unstable triple. The minimal core mass associated with
+    a stable triple is then indicated by the left-most vertical dotted
+    line.  The orbital separation at which the donor star overfills
+    its Roche lobe is indicated with the light-blue curve. The top
+    curve (brown) shows an estimate of the final orbital separation of
+    the outer star, and therefore of the final orbit of the WD around
+    the inner twin BSs.  For core masses $\apgt 0.5$\,\MSun\, the
+    final orbital separation, after mass transfer, is smaller than the
+    initial orbit.  Here we adopted an initial inner binary mass of
+    (1.0+0.9)\,\MSun\, and a final twin BS mass of (1.4+1.4)\,\MSun.
 \label{fig:tertiarymass_vs_size}}
@@
 
-Adopting a mass for the tertiary star of $m_3 = 1.4$\,\MSun, we
-can constrain the initial parameters for the inner binary as well as
-the orbit of the outer star after mass transfer. We first calculate
-the stellar radius as a function of core mass. In
+Adopting a mass for the tertiary star of $m_3 = 1.4$\,\MSun, we can
+constrain the initial parameters for the inner binary as well as the
+orbit of the outer star after mass transfer. We first calculate the
+stellar radius as a function of core mass. In
 figure\,\ref{fig:tertiarymass_vs_size} we present this relation
 calculated using the {\tt SeBa} stellar evolution code
-\cite{1996A&A...309..179P} (dark blue curve).  The interruption in
-this curve, around a core mass of $m_{\rm core} \sim 0.5$\,\MSun\, is
-a result of the evolution along the horizontal branch, where the core
-of the star continues to grow but the radius actually shrinks.
+\citep{1996A&A...309..179P} as the dark blue curve.  The interruption
+in this curve, around a core mass of $m_{\rm core} \sim 0.5$\,\MSun\,
+is a result of the evolution along the horizontal branch, where the
+core of the star continues to grow but the radius actually shrinks.
 Roche-lobe overflow in this phase is not expected to happen, because
@@
 relaxation process is realized in 100 steps during which we reduce the
-velocity dispersion of individual SPH particles to a glasses
-structure \citep[see, for example, \S\,3.3 on page 40
-  in][]{1994astro.ph.10043W}. During this procedure, the gaseous
+velocity dispersion of individual SPH particles to a glasses structure
+\citep[see, for example, \S\,3.3 on page 40
+  in][]{1995LesHouchesSWhite}. During this procedure, the gaseous
 envelope of the star tends to expand by about 20\%.  To determine the
@@
 %% 90^\circ$ and $i = 180^\circ$, but we wi
-The low inclination is motivated by observed stellar triples composed
-of low-mass stars to favour co-planar configurations
-\citep{2018ApJ...854...44M}.
+%% The low inclination is motivated by observed stellar triples composed
+%% of low-mass stars to favour co-planar configurations
+%% \citep{2018ApJ...854...44M}.
 %% To test the effect of highly inclined
@@
 %% cases.
+%%SPZ: I removed the notion of low-inclination, because we already said as such in the intro.
 In figure~\ref{fig:topview_at_t0} we present a top view of the initial
@@
 its own particles, as well as the gravitational potential of the inner
-binary. The hydrodynamics affects the orbits of the two inner stars. With
+binary. The hydrodynamics affects the orbits of the two inner stars
+and the accretion onto the two stars affects the hydrodynamics. With
 \texttt{Bridge} we realize a second order coupling between the
@@
 the parameters of the system we study, but typically we achieve
-converged solutions when this time step is about 1/100 that 
-of the inner binary orbital period.
+converged solutions when this time step is about 1/100 that of the
+inner binary orbital period.
 
@@
 It is apparent that the mass transfer in the adopted triples leads to
-a rather untidy evolution, since much of the donor
-mass is lost through the second Lagrangian point to the right side of
-the donor star in figure~\ref{fig:topview_at_t1000day}. Significant mass is
-also lost through the third Lagrangian point (to the left of the inner
-binary). One remaining question is how much mass is eventually ejected
-altogether from the triple system and is therefore not accreted to any
-of the two inner stars. This value is hard to estimate from the
-simulations, but an accretion efficiency of $\apgt 0.6$ is necessary to
-make the scenario feasible. Over the time scale for which we performed
-the calculations, this efficiency is reached, but it is not clear how
-the system responds at later stages.
+a rather untidy evolution, since much of the donor mass is lost
+through the second Lagrangian point to the right side of the donor
+star in figure~\ref{fig:topview_at_t1000day}. A considerable amount of
+mass is also lost through the third Lagrangian point (to the left of
+the inner binary), although it is hard to actually quantize the amount
+of material los, becuase an appreciable fraction is expected to rain
+back onto the triple system.  One remaining question is how much mass
+is eventually ejected altogether from the triple system and is
+therefore not accreted to any of the two inner stars. This value is
+hard to estimate from the simulations, but an accretion efficiency of
+$\apgt 0.6$ is necessary to make the scenario feasible. Over the time
+scale for which we performed the calculations, this efficiency is
+reached, but it is not clear how the system responds at later stages.
 
-\begin{figure}[ht!]
-  \includegraphics[width=0.49\columnwidth]{fig_BBSS_Lgas_M14Msun_A010au_t3360.pdf}
-~  \includegraphics[width=0.51\columnwidth]{fig_BBSS_gas_M14Msun_A010au_t3360.pdf}
+\begin{figure*}[ht!]
+  \includegraphics[width=0.5\columnwidth]{fig_BBSS_Lgas_M14Msun_A010au_t3360.pdf}
+~  \includegraphics[width=0.5\columnwidth]{fig_BBSS_gas_M14Msun_A010au_t3360.pdf}
 \caption{Same as figure~\ref{fig:topview_at_t0} but at an age of $t
@@
 \label{fig:topview_at_t1000day}}
-\end{figure}
+\end{figure*}
 
@@
 accretion from a circumbinary disk, \cite{2018arXiv181208175M}
-conclude that the complexity of angular momentum transport between
-the outer star and the accretion stream onto the individual inner stars, is
-complicated and without clear trends. For most of our calculations we
-agree with this statement, but in
+conclude that the complexity of angular momentum transport between the
+outer star and the accretion stream onto the individual inner stars,
+is complicated and without clear trends. For most of our calculations
+we agree with this statement, but in
 figure~\,\ref{fig:mass_vs_semimajor_axis} we nevertheless present the
-results of 6 of our calculations, three for a 1.2\,\MSun\, donor star and
-three for a 1.4\,\MSun\, donor. The various coloured curves give
+results of 6 of our calculations, three for a 1.2\,\MSun\, donor star
+and three for a 1.4\,\MSun\, donor. The various coloured curves give
 the resulting evolution of the inner orbit as a function of the total
-mass in the inner binary. As the inner two stars accrete, the orbit shrinks 
-for a 1.2\,\MSun\, donor. These systems
-are expected to result in a contact binary, that eventually may merge
-to form a single BS. The required evolution in order to
-explain the observed twin BS 7782 is indicated by the
-three black curves; the simulated path clearly deviates from
-these. We, therefore, argue that a 1.2\,\MSun\, donor has difficulty
-explaining the observed orbital separation of $\sim 0.13$\,au in BSS
-7782.
+mass in the inner binary. As the inner two stars accrete, the orbit
+shrinks for a 1.2\,\MSun\, donor. These systems are expected to result
+in a contact binary, that eventually may merge to form a single BS
+with a mass more than twice the turn off. The required evolution in
+order to explain the observed twin BS 7782 is indicated by the three
+black curves; the simulated path clearly deviates from these. We,
+therefore, argue that a 1.2\,\MSun\, donor has difficulty explaining
+the observed orbital separation of $\sim 0.13$\,au in BSS 7782.
 
-\begin{figure}[ht!]
-  \includegraphics[width=\columnwidth]{fig_orbital_evolution_for_12MSun.pdf}
-  \includegraphics[width=\columnwidth]{fig_orbital_evolution_for_14MSun.pdf}
-  \caption{Evolution of the total mass of the inner binary as a
-    function of the orbital separation for four calculations with
-    somewhat different initial conditions (see the legend).  The initial
-    binary shown by the orange curve is presented in
+\begin{figure*}[ht!]
+  \includegraphics[width=0.51\columnwidth]{fig_orbital_evolution_for_12MSun.pdf}
+~  \includegraphics[width=0.49\columnwidth]{fig_orbital_evolution_for_14MSun.pdf}
+  \caption{Evolution of the orbital separation as a function of the
+    total mass of the inner binary for six calculations with somewhat
+    different initial conditions (see the legend). The left panel
+    shows the result for a 1.2\,\MSun\, donor star and the right panel
+    for a 1.4\,\MSun\, donor. The initial binary shown by the blue
+    curve of the right-hand panel is presented in
     fig.\,\ref{fig:topview_at_t0}, and in
     fig.\,\ref{fig:topview_at_t1000day} we present the final
-    conditions.
+    conditions of this system.  The black curves give the expected
+    evolution of the orbital separation of the inner binary assuming
+    that the binary evolved towards to observed orbital separation of
+    0.13\,au at a total binary mass of 2.8\,\MSun.
 \label{fig:mass_vs_semimajor_axis}}
-\end{figure}
+\end{figure*}
 
-In the lower panel in figure~\ref{fig:mass_vs_semimajor_axis} we
-present the evolution of the orbit for the 1.4\,\MSun\, donor. A more
-massive donor is more likely to be able to produce a twin BS system, simply because there is more mass available in the stellar
-envelope. On the other hand, a more massive donor may also result in a
-lower accretion efficiency, because the thermal time scale of the
-stellar envelope is smaller than for a lower mass donor at the same
-stellar radius. A shorter thermal time-scale eventually leads to
-a higher mass transfer rate, which again may lead to a lower accretion
-efficiency. However, the larger mass budget in the envelope appears to
-compensate.
+In the right-hand panel in figure~\ref{fig:mass_vs_semimajor_axis} we
+present the evolution of the orbit for the 1.4\,\MSun\, donor for
+several initial orbits of the inner binary. A more massive donor
+appears to be more effective in producing a twin BS with parameters
+consistent with the observed system 7782. There is more mass available
+in the envelope of the donor star, and the orbital evolution of the
+inner binary matches better with the anticipated evolution.  A more
+massive donor may therefore have a lower accretion efficiency while
+still accomodating the observed constraints.  The longer thermal time
+scale of the stellar envelope of the higher-mass donor at the same
+stellar radius eventually leads to a higher mass-transfer rate, and
+therefore to a lower accretion efficiency. However, the larger mass
+budget in the envelope appears to compensate.
 
 The orbit of the inner binary expands in these cases as a result of
-accretion onto the inner two stars. All three cases
-presented in figure~\ref{fig:mass_vs_semimajor_axis} expand at about
-the same rate. Consequently, the inner binaries that start with $a =
-0.15$\,au and $a=0.20$\,au eventually become dynamically unstable.
-The binary with an initial separation of $0.10$\,au expands to reach a
-separation of about 0.126--0.145\,au for final masses for the inner two stars
-of 1.4\,\MSun, which is consistent with the observed twin BS 7782. In our simulations the eccentricity of the inner
-binary grows to about $e \simeq 0.0028$.
+accretion onto the inner two stars. All three cases for the
+1.4\,\MSun\, donor presented in
+figure~\ref{fig:mass_vs_semimajor_axis} the inner orbit expands at
+about the same rate. Consequently, the inner binaries that start with
+$a = 0.15$\,au and $a=0.20$\,au eventually become dynamically
+unstable.  The binary with an initial separation of $0.10$\,au expands
+to reach a separation of about 0.126--0.145\,au for final masses for
+the inner two stars of 1.4\,\MSun, which is consistent with the
+observed twin BS 7782. In our simulations the eccentricity of the
+inner binary grows to about $e \simeq 0.0028$.
 
@@
 accrete angular momentum.  By the end of the simulation the spins of
-the two BSs are aligned along the orbital angular momentum
-axis with an angle of $90.0^\circ$ for the primary star and
-$93.4^\circ$ for the secondary star with respect to the argument of
-pericenter of the inner orbit.  By the end of the simulations the spin
-of the primary is about 50.5 rotations per day, and 41.5 rotations per
-day for the secondary star. But by this time both stars have accreted
-only a small portion of mass and we expect that the final spins of
-both stars will be close to break-up (ignoring any spin-down from
-magnetic braking effects).
+the two BSs are aligned along the orbital angular momentum axis with
+an angle of $90.0^\circ$ for the primary star and $93.4^\circ$ for the
+secondary star with respect to the argument of pericenter of the inner
+orbit.  By the end of the simulations the spin of the primary is about
+50.5 rotations per day, and 41.5 rotations per day for the secondary
+star.
+%% But by this time both stars have accreted
+%% only a small portion of mass and we expect that the final spins of
+%% both stars will be close to break-up (ignoring any spin-down from
+%% magnetic braking effects).
 
@@
 the inner binary toward a mass ratio close to unity.  Our simulations
-suggest that the inner binary orbital separation can decrease or
+indicate that the inner binary orbital separation can decrease or
 expand depending on the details of the transfer of mass and angular
@@
 1.2\,\MSun\, tertiary donor mass, we expect the inner two stars to
-eventually merge and form a single BS. This reduces the
-system to a binary with a primary BS and an outer WD in a relatively wide orbit. Such a BS will
-distinguish itself from other BSs by potentially
-being more than twice the turn-off mass in a star cluster.  An
-example could be the $2.9\pm0.2$\,\MSun\, BS S1237 in the
-Galactic cluster M67 \cite{2016ApJ...832L..13L}. It is the primary of
-a $\sim 698$\,day binary with an eccentric orbit of $\sim 0.10$.
+eventually merge and form a single BS. This reduces the system to a
+binary with a primary BS and an outer WD in a relatively wide
+orbit. Such a BS will distinguish itself from other BSs by potentially
+being more than twice the turn-off mass in a star cluster.  An example
+could be the $2.9\pm0.2$\,\MSun\, BS S1237 in the Galactic cluster M67
+\citep{2016ApJ...832L..13L}. It is the primary of a $\sim 698$\,day
+binary with an eccentric orbit of $\sim 0.10$.
 
 With an original outer star of mass $\sim 1.4$\,\MSun, the inner orbit
-tends to expand. This eventually leads
-to a dynamically unstable system resulting either in a collision or in
-the ejection of (probably) the lowest mass star. This evolution could
-result in a single ejected BS, with the other BS left in
-a relatively close and eccentric orbit with a WD (the
-left-over core of the tertiary star).  These ``imposter'' BS-WD binaries 
-would in principle mimic what is expected theoretically for BSs formed 
-from mass transfer in binary stars.
+tends to expand. This eventually leads to a dynamically unstable
+system resulting either in a collision or in the ejection of
+(probably) the lowest mass star. This evolution could result in a
+single ejected BS, with the other BS left in a relatively close and
+eccentric orbit with a WD (the left-over core of the tertiary star).
+These ``imposter'' BS-WD binaries would in principle mimic what is
+expected theoretically for BSs formed from mass transfer in binary
+stars. If such a dynamical instability engages relatively late in the
+mass-tranfer phase, the white dwarf (maybe with a little left-over
+envelope) is expected to be ejected. This would lead to a relatively
+wide twin blue-straggler binary and a single low-mass white dwarf.
 
 When we adopt an inner orbit of $0.10$\,au\, the expansion eventually
-matches the observed orbital separation (i.e., $0.13$\,au) of the observed
-twin BS 7782 and the observed masses of the two stars.
+matches the observed orbital separation (i.e., $0.13$\,au) of the
+observed twin BS 7782 and the observed masses of the two stars of
+about 1.4\,\MSun.
 
@@
 accretion rates in the secondary star are realized for eccentric and
-retrogade inner orbits.
+retrogade inner orbits. We performed an extra series of calculations
+to further study this, but they all lead to the merger of the inner
+binary.
 
@@
 
-In this paper, we propose a formation scenario for twin equal-mass blue stragglers 
-in tight binaries, as observed for Binary 7782 in the old OC
-NGC 188.  The proposed scenario involves mass transfer from an evolved
-outer tertiary companion, which is accreted by the inner binary via a
-circumbinary disk.  Our scenario makes several predictions for the
-observed properties of a hypothetical outer triple companion, now a
-WD.  These are:
+In this paper, we propose a formation scenario for twin equal-mass
+blue stragglers in tight binaries, as observed for Binary 7782 in the
+old OC NGC 188.  The proposed scenario involves mass transfer from an
+evolved outer tertiary companion, part of this mass is accreted by the
+inner binary via a circumbinary disk the rest escapes through the
+second and third Lagrangian points in the potential of the triple
+system.  Our scenario makes several predictions for the observed
+properties of a hypothetical outer triple companion, now a WD.  These
+are:
 
@@
 
-\item For the predicted outer tertiary orbit, the initial 
-  orbital period should lie between 220 days $\lesssim$ P$_{\rm out}$
+\item For the predicted outer tertiary orbit, the initial orbital
+  period should lie between 220 days $\lesssim$ P$_{\rm out}$
   $\lesssim$ 1100 days, assuming initial masses for the inner binary
@@
   M$_{\odot}$ and an initial outer tertiary mass of $m_{\rm 3} = 1.4
-  $M$_{\odot}$.  Hence, the present-day orbital period should be close to this range.
+  $M$_{\odot}$.
 
-\item Larger final WD masses, and hence larger core masses for the donor at
-  the time of mass transfer should correspond to larger final outer
-  orbital periods for the tertiary.  This is because the Roche radius
-  is larger for larger outer orbital periods, such that the donor must
-  evolve to larger radii, and hence core masses, before the onset of
-  mass transfer.
+\item Larger final WD masses, and hence larger core masses for the
+  donor at the time of mass transfer should correspond to larger final
+  outer orbital periods for the tertiary.  This is because the Roche
+  radius is larger for larger outer orbital periods, such that the
+  donor must evolve to larger radii, and hence core masses, before the
+  onset of mass transfer. We expect the orbital separation to range
+  from $\apgt 6.4$\,yr for a $\sim 0.42$\,\MSun\, white dwarf to
+  $\apgt 11.2$\,yr for a $\sim 0.48$\,\MSun\, white dwarf.
 
@@
   typically the lowest
-  \citep[e.g.][]{1995MNRAS.277.1491K,1997MNRAS.285...33B,2000MNRAS.314...33B}.
-  This quickly brings the mass ratio toward unity.  This predicts that
-  the initially lower mass MS star should accrete the most, and should
-  hence be enriched more by any accreted material.  This could be
-  observable in the surface layers of a radiative star.  If the donor
-  is an RGB star, the accretor will be enriched in mostly carbon,
-  oxygen and helium.  If the donor is an AGB star, it will be enriched
-  in mostly s-process elements.
+%% \citep[e.g.][]{1995MNRAS.277.1491K,1997MNRAS.285...33B,2000MNRAS.314...33B}.
+  \citep[e.g.][]{2000MNRAS.314...33B,2012ApJ...749..118S,2017MNRAS.466.1170M}.
+  The mass ratio of the inner binary, therefore grows to unity.  As a
+  consequence, the initially lower mass MS star should accrete the
+  most, and therefore be more enriched by accreted material.  This
+  could be observable in the surface layers of a radiative star.  If
+  the donor is an RGB star, the accretors will be enriched in mostly
+  carbon, oxygen and helium, but if the donor is an AGB star the
+  enrichment will be mostly in s-process elements.
 
-\item Twin BSs in compact binaries formed from the mechanism proposed here 
-  should be more frequent in younger clusters with ages $\lesssim$ 4-6
-  Gyr.  This is because clusters with a MS turn-off mass
-  $\lesssim$ 1.2 M$_{\odot}$ have convective envelopes
-  \citep[e.g.][]{1991ApJS...76...55I,2009pfer.book.....M}, and a radiative envelope for the
-  donor in a mass transferring binary ensures stable accretion on to
-  the accretor.  %\simon{Can we quantify this? - NL: The stability of the accretion...?}
+\item We expect twin BSs in compact binaries formed from the mechanism
+  proposed here to be more frequent in younger clusters with ages
+  $\lesssim$ 4-6 Gyr.  This is because clusters with a MS turn-off
+  mass $\lesssim$ 1.2 M$_{\odot}$ have convective envelopes
+  \citep[e.g.][]{1991ApJS...76...55I,2009pfer.book.....M}, and a
+  radiative envelope for the donor in a mass transferring binary
+  ensures stable accretion on to the accretor.  Note that part of the
+  mass liberated from the triple system through the second and third
+  Lagrangian points may eventually be accreted back onto the system.
+  This could have interesting consequences for the enrichment of the
+  low-mass white dwarf.
+
+  %\simon{Can we quantify this? - NL: The stability of the accretion...?}
 
@@
 
-We emphasize in closing that our choice for the initial mass of the
-outer tertiary is critical since it ensures that the donor star during
-the mass transfer process will have a radiative envelope
-\citep[e.g.][]{2009pfer.book.....M}.  In turn, this ensures that the
-mass transfer will be maximally conservative, such that the accretion
-stream will be maximally stable, accreting at a stable and roughly
-constant rate \citep[e.g.][]{1991ApJS...76...55I}.
+We emphasize, in closing, that the choice for the initial mass of the
+outer tertiary may be rather critical.  Mass transfer in our proposed
+scenario proceeds from the most massive tertiary to a binary of lower
+total mass. This may result in an unstable phase of mass transfer, in
+particular if the donor has a convective envelope
+\citep[e.g.][]{2009pfer.book.....M}. A radiative envelope of the donor
+ensures that the mass transfer will be maximally conservative, such
+that the accretion stream will be maximally stable, accreting at a
+stable and roughly constant rate \citep[e.g.][]{1991ApJS...76...55I}.
+This stability regime may also be of interest for explaining very
+massive twins, of $\apgt 20$\,\MSun\, which could be promising sources
+for gravitational wave detectors once both twins evolve to a binary
+black hole \citep{2016MNRAS.460.3545D}.
 
@@
 work was supported by the Netherlands Research School for Astronomy
-(NOVA), NWO (grant \# 621.016.701 [LGM-II]).
+(NOVA). 
+%%
+In this work we use the matplotlib
+\citep{2007CSE.....9...90H}, numpy
+\citep{Oliphant2006ANumPy}, AMUSE
+\citep{portegies_zwart_simon_2018_1443252}, SeBa
+\citep{2012ascl.soft01003P}, Huayno \citep{2012NewA...17..711P}, MESA
+\citep{2010ascl.soft10083P}, and GadGet2 \citep{2000ascl.soft03001S}
+packages. The calculations ware performed using the LGM-II (NWO grant
+\# 621.016.701) and the Dutch National Supercomputer at SURFSara
+(grant \# 15520).
 

### 2019-01-22 BSS7782.tex
change to 2 column format

@@
 %% using aastex version 6.2
-\documentclass{aastex62}
+%%\documentclass{aastex62}
+\documentclass[twocolumn]{aastex62}
 
@@
 \begin{figure*}[ht!]
-  \includegraphics[width=0.5\columnwidth]{fig_BBSS_Lgas_M14Msun_A010au_t3360.pdf}
-~  \includegraphics[width=0.5\columnwidth]{fig_BBSS_gas_M14Msun_A010au_t3360.pdf}
+  \includegraphics[width=0.5\linewidth]{fig_BBSS_Lgas_M14Msun_A010au_t3360.pdf}
+~  \includegraphics[width=0.5\linewidth]{fig_BBSS_gas_M14Msun_A010au_t3360.pdf}
 \caption{Same as figure~\ref{fig:topview_at_t0} but at an age of $t
@@
 \begin{figure*}[ht!]
-  \includegraphics[width=0.51\columnwidth]{fig_orbital_evolution_for_12MSun.pdf}
-~  \includegraphics[width=0.49\columnwidth]{fig_orbital_evolution_for_14MSun.pdf}
+  \includegraphics[width=0.51\linewidth]{fig_orbital_evolution_for_12MSun.pdf}
+~  \includegraphics[width=0.49\linewidth]{fig_orbital_evolution_for_14MSun.pdf}
   \caption{Evolution of the orbital separation as a function of the

### 2019-02-20 BSS7782.tex
edited tex file slightly for consistency with new figures

@@
 \begin{figure}[ht!]
-\plotone{fig_doodle.eps}
+%\plotone{fig_doodle.eps}
+\includegraphics[width=\columnwidth]{fig_doodle.pdf}
 \caption{Cartoon depiction of our proposed scenario for the formation
@@
 \begin{figure}[ht!]
-\plotone{fig_parameterspace.eps}
+%\plotone{fig_parameterspace.eps}
+\includegraphics[width=\columnwidth]{fig_parameterspace.pdf}
 \caption{Parameter space in the P$_{\rm out}$-P$_{\rm in}$-plane
@@
 boundary assuming central velocity dispersions of $\sigma =$ 1, 5 and
-10 km s$^{-1}$.  The vertical dashed black lines show the maximum
+10 km s$^{-1}$.  The vertical dashed black line show the maximum
 outer orbital period P$_{\rm out}$ for which the outer tertiary
@@
 velocity dispersion of individual SPH particles to a glasses structure 
-\citep[see, for example, \S\,3.3 on page 40
-  in][]{1995LesHouchesSWhite}. During this procedure, the gaseous
+%\citep[see, for example, \S\,3.3 on page 40 in][]{1995LesHouchesSWhite}. 
+(see, for example, \S\,3.3 on page 40 in White (1995)).  During this procedure, the gaseous
 envelope of the star tends to expand by about 20\%.  To determine the
@@
 \begin{figure*}[ht!]
-  \includegraphics[width=0.5\linewidth]{fig_BBSS_Lgas_M14Msun_A010au_t3360.pdf}
-~  \includegraphics[width=0.5\linewidth]{fig_BBSS_gas_M14Msun_A010au_t3360.pdf}
+  \includegraphics[width=0.5\linewidth]{fig_BBSS_Lgas_M14Msun_A010au_t3360.png}
+~  \includegraphics[width=0.5\linewidth]{fig_BBSS_gas_M14Msun_A010au_t3360.png}
 \caption{Same as figure~\ref{fig:topview_at_t0} but at an age of $t

### 2019-02-23 BSS7782.tex
Add files via upload

@@
 tertiary companion on to the inner binary via a circumbinary disk.  We
-apply this scenario to the observed double BS system Binary 7782 in
+apply this scenario to the observed double BS binary WOCS 7782 in
 the old open cluster NGC 188, and show that its observed properties
@@
 = 1.1$ M$_{\odot}$ and $m_{\rm 2} =$ 0.9 M$_{\odot}$ and an outer
-tertiary mass of $m_{\rm 3} = 1.4$ M$_{\odot}$.  After Roche-lobe
+tertiary mass of $m_{\rm 3} = 1.4$ M$_{\odot}$.  \textbf{(2)} After Roche-lobe
 overflow, the outer star turns into a white dwarf (WD) of mass 0.43 to
@@
 
-Blue straggler stars are brighter and bluer than the main-sequence
+\textbf{Most} blue straggler stars are brighter and bluer than the main-sequence
 (MS) turn-off in a cluster colour-magnitude diagram
@@
 \citep[e.g.][]{1975AJ.....80..809H,1997A&A...328..130P,2007ApJ...661..210L,2013MNRAS.428..897L,2013MNRAS.429.1221H, 2019A&A...621L..10P}.
-The first mechanism predicts BSs in binaries with WD companions,
+\textbf{The first mechanism predicts BSs in binaries with WD companions,
 whereas the second predicts MS companions in a wide and eccentric
-binary.  Other possible, albeit related, formation mechanisms include
+binary.}  Other possible, albeit related, formation mechanisms include
 mergers of close MS-MS binaries \citep{2019A&A...621L..10P}, and
@@
 induced by Lidov-Kozai oscillations coupled with tidal damping
-\citep[e.g.][]{2009ApJ...697.1048P}.
+\citep[e.g.][]{2009ApJ...697.1048P}.  \textbf{The latter predicts no binary companion, whereas the former predicts a MS companion in a wide binary.}
 
@@
 system that is posited to host two BSs
-\citep{2001A&A...375..375V,2003AJ....125..810S}.  The observations
-suggest that the outer tertiary is itself a BS, with a mass $\sim$ 1.7
-M$_{\odot}$ and orbiting the inner binary with a period of $\sim
-1188.5$ days \citep{2003AJ....125..810S}.  The inner binary has a
-period of only $\sim 1.068$ days \citep{2001A&A...375..375V}, and
-hosts a BS of mass $\sim 2.52$ M$_{\odot}$.  In order to reproduce the total system mass 
-we require at least five stars \citep{2011MNRAS.410.2370L}.  This is strongly indicative of a
-dynamical origin for the system, and a single direct interaction
+\citep{2001A&A...375..375V,2003AJ....125..810S}; one in the inner binary and one as the outer triple companion \citep{2003AJ....125..810S,2001A&A...375..375V}.  
+%The observations
+%suggest that the outer tertiary is itself a BS, with a mass $\sim$ 1.7
+%M$_{\odot}$ and orbiting the inner binary with a period of $\sim
+%1188.5$ days \citep{2003AJ....125..810S}.  The inner binary has a
+%period of only $\sim 1.068$ days \citep{2001A&A...375..375V}, and
+%hosts a BS of mass $\sim 2.52$ M$_{\odot}$.  
+In order to reproduce the total system mass 
+at least five stars are needed \citep{2011MNRAS.410.2370L}, which is strongly indicative of a
+dynamical origin for the system; a single direct interaction
 involving a binary and a triple that resulted in two separate
@@
 Even more curious, there exists in the old OC NGC 188 a
-double BS binary, called Binary 7782.  The BS
+double BS binary, called WOCS 7782 \citep{geller08}.  The BS
 population in NGC 188 has a bi-modal period-eccentricity distribution.
@@
 a triple origin for at least some subset of the total BS population.
-As for Binary 7782, \citet{2009Natur.462.1032M} observed a compact and
+As for WOCS 7782, \citet{2009Natur.462.1032M} observed a compact and
 mildly eccentric (i.e., $e \sim 0.1$) binary star system with an
@@
 products during a collisional interaction in a star cluster
-\citep{2011MNRAS.410.2370L,2011Sci...334.1380F}.  So, how did Binary 7782 form?
-
-We propose a formation channel for Binary 7782, and compact double BS
+\citep{2011MNRAS.410.2370L,2011Sci...334.1380F}.  So, how did WOCS 7782 form?
+
+We propose a formation channel for WOCS 7782, and compact double BS
 binaries in general, which involves mass transfer from an outer
@@
 \section{Constraints on the present-day orbital parameters for a hypothesized
-         tertiary companion in the compact BS Binary 7782} \label{sect:dyn}
+         tertiary companion in the compact BS binary WOCS 7782} \label{sect:dyn}
 
@@
 \citep{2010yCat..73890925T,2018ApJ...854...44M}.  This initial configuration for our
-assumed formation scenario for Binary 7782, described below, is
+assumed formation scenario for WOCS 7782, described below, is
 depicted in figure~\ref{fig:fig1}.
@@
 \caption{Cartoon depiction of our proposed scenario for the formation
-  of Binary 7782, specifically mass transfer from an evolved outer
+  of WOCS 7782, specifically mass transfer from an evolved outer
   tertiary companion on to a compact inner binary via a circumbinary
@@
 Figure~\ref{fig:fig2} shows the parameter space in the P$_{\rm
-  out}$-P$_{\rm in}$-plane for Binary 7782.  We assume initial
+  out}$-P$_{\rm in}$-plane for WOCS 7782.  We assume initial
 component masses of $m_{\rm 1} = 1.1$ M$_{\rm \odot}$ and $m_{\rm 2} =
@@
 range of initial conditions for the outer orbit, namely 2.2 $\times$
-10$^{2}$ days $\le$ P$_{\rm out}$ $\le$ 1.1 $\times$ 10$^3$ days.
+10$^{2}$ days $\le$ P$_{\rm out}$ $\le$ 1.1 $\times$ 10$^3$ days, \textit{which also directly translate into constraints on the final outer tertiary orbit.}
 %, for
@@
 
+\textbf{Finally, we compute the timescales for our hypothesized triple to undergo a direct interaction with another single or binary star.
+Using the same assumptions for the host cluster properties of NGC 188 outlined in Section 3.2 of \citet{leigh11} (right-hand column), we find upon setting the single-triple (1+3) and binary-triple (2+3) timescales equal to the expected duration of the mass transfer phase (i.e., $\sim$ 1 Myr) critical outer orbital periods for triples of, respectively, 8.1 $\times$ 10$^8$ and 2.4 $\times$ 10$^9$ days.
+These critical outer tertiary orbital periods, which correspond to the times for a \textit{specific} triple to undergo an interaction, correspond to 1+3 and 2+3 interaction times that are much longer than the maximum predicted outer orbital period of the hypothesized white dwarf tertiary in our scenario.
+Hence, we do not expect the mass transfer process to be interrupted by either 1+3 and 2+3 interactions.}
+
 \begin{figure}[ht!]
@@
 \caption{Parameter space in the P$_{\rm out}$-P$_{\rm in}$-plane
-  allowed for the hypothetical outer tertiary orbit of Binary 7782
+  allowed for the hypothetical outer tertiary orbit of WOCS 7782
   before Roche-lobe overflow.  The solid diagonal black line shows the
@@
 to us; see figure~\ref{fig:tertiarymass_vs_size}).  The horizontal
-dashed red line shows the observed orbital period for Binary 7782,
+dashed red line shows the observed orbital period for WOCS 7782,
 using its observed orbital period and our assumed final inner
@@
     evolution of the orbital separation of the inner binary assuming
-    that the binary evolved towards to observed orbital separation of
+    that the binary evolved towards the observed orbital separation of
     0.13\,au at a total binary mass of 2.8\,\MSun.
@@
 In this paper, we propose a formation scenario for twin equal-mass
-blue stragglers in tight binaries, as observed for Binary 7782 in the
+blue stragglers in tight binaries, as observed for WOCS 7782 in the
 old OC NGC 188.  The proposed scenario involves mass transfer from an
@@
   proposed here to be more frequent in younger clusters with ages
-  $\lesssim$ 4-6 Gyr.  This is because clusters with a MS turn-off
+  $\lesssim$ 4-6 Gyr.  This is because \textbf{stars in clusters} with a MS turn-off
   mass $\lesssim$ 1.2 M$_{\odot}$ have convective envelopes

### 2019-02-24 BSS7782.tex
Add files via upload

@@
 the old open cluster NGC 188, and show that its observed properties
-are naturally reproduced within the context of the proposed model.
+\textbf{can be} reproduced within the context of the proposed model.
 Based on this model, we predict the following properties for twin BSs:
@@
 products during a collisional interaction in a star cluster
-\citep{2011MNRAS.410.2370L,2011Sci...334.1380F}.  So, how did WOCS 7782 form?
+\citep{2011MNRAS.410.2370L,2011Sci...334.1380F}, \textit{and the timescale for exchanging another BS into a pre-existing BS-MS or BS-WD binary is much longer than the expected BS lifetime (see \citet{2011MNRAS.410.2370L} and the end of Section~\ref{sect:dyn} below)}.
+So, how did WOCS 7782 form?
 
@@
 $m_3$. The inner and outer binary orbital semi-major axes are denoted
-a$_{\rm in}$ and a$_{\rm out}$, respectively.  For clarity we 
+a$_{\rm in}$ and a$_{\rm out}$, respectively.  \textbf{For specificty,} we 
 assume both orbits, the inner as well as the outer, to have negligible
-eccentricity and low inclination.  These assumptions are also
+eccentricity and low inclination, \textbf{which minimizes chaotic effects during the mass transfer process, facilitates more stable mass transfer and ultimately allows us to simulate our target system for longer while also maximizing the amount of mass transferred}.
+These assumptions are also
 supported by the population of observed low-mass triples
@@
 the caption of figure~\ref{fig:fig2}), and the assumption of an outer tertiary that is Roche
-lobe-filling.  
+lobe-filling \textbf{(see \citet{2014MNRAS.438.1909D} for more details)}.  
 %\simon{Why do you consider it important to mention that the orbit is hard, and for what environment did you consider this? - NL: Deleted.}  
@@
 range of initial conditions for the outer orbit, namely 2.2 $\times$
-10$^{2}$ days $\le$ P$_{\rm out}$ $\le$ 1.1 $\times$ 10$^3$ days, \textit{which also directly translate into constraints on the final outer tertiary orbit.}
+10$^{2}$ days $\le$ P$_{\rm out}$ $\le$ 1.1 $\times$ 10$^3$ days, \textit{which also directly translates into constraints on the final outer tertiary orbit.}
 %, for
@@
 \textbf{Finally, we compute the timescales for our hypothesized triple to undergo a direct interaction with another single or binary star.
-Using the same assumptions for the host cluster properties of NGC 188 outlined in Section 3.2 of \citet{leigh11} (right-hand column), we find upon setting the single-triple (1+3) and binary-triple (2+3) timescales equal to the expected duration of the mass transfer phase (i.e., $\sim$ 1 Myr) critical outer orbital periods for triples of, respectively, 8.1 $\times$ 10$^8$ and 2.4 $\times$ 10$^9$ days.
+Using the same assumptions for the host cluster properties of NGC 188 outlined in Section 3.2 of \citet{2011MNRAS.410.2370L} (right-hand column), we find upon setting the single-triple (1+3) and binary-triple (2+3) timescales equal to the expected duration of the mass transfer phase (i.e., $\sim$ 1 Myr) critical outer orbital periods for triples of, respectively, 8.1 $\times$ 10$^8$ and 2.4 $\times$ 10$^9$ days.
 These critical outer tertiary orbital periods, which correspond to the times for a \textit{specific} triple to undergo an interaction, correspond to 1+3 and 2+3 interaction times that are much longer than the maximum predicted outer orbital period of the hypothesized white dwarf tertiary in our scenario.
@@
 the current orbital separation of the WD around the twin
-BS 7782. Tidal effects during mass tranfer
+BS 7782. Tidal effects during mass \textbf{transfer}
 have probably circularized the orbit, although some slight eccentricity
@@
 100\,\RSun\, and 150\,\RSun, at which point we assume it to overfill
-it's Roche lobe (see red square in
+it's Roche lobe (see red \textbf{squares} in
 figure~\ref{fig:tertiarymass_vs_size}).  We perform calculations for an
@@
 With these parameters the orbital separation of the outer binary
-becomes $\sim 250$\,\RSun for the 100\,\RSun donor star and about
+becomes $\sim 250$ R$_{\rm \odot}$ for the 100 R$_{\rm \odot}$ donor star and about
 430\,\RSun\, for the more evolved donor star.  We adopt the outer
@@
 
-To test the hypotheses that (1) the secondary in the inner binary
+To test the \textbf{hypothesis that the} secondary in the inner binary
 accretes more effectively than the primary star and to measure the
@@
 mass is also lost through the third Lagrangian point (to the left of
-the inner binary), although it is hard to actually quantize the amount
-of material los, becuase an appreciable fraction is expected to rain
+the inner binary), although it is hard to actually \textbf{quantify the amount
+of material lost}, becuase an appreciable fraction is expected to rain
 back onto the triple system.  One remaining question is how much mass
@@
 in the envelope of the donor star, and the orbital evolution of the
-inner binary matches better with the anticipated evolution.  A more
+inner binary matches better with the anticipated evolution \textbf{needed to reproduce the observed parameters of WOCS 7782.}  A more
 massive donor may therefore have a lower accretion efficiency while
@@
 The orbit of the inner binary expands in these cases as a result of
-accretion onto the inner two stars. All three cases for the
+accretion onto the inner two stars. \textbf{In all} three cases for the
 1.4\,\MSun\, donor presented in
@@
 secondary star with respect to the argument of pericenter of the inner
-orbit.  By the end of the simulations the spin of the primary is about
+orbit.
+\textbf{This supports our naive prediction that the spin angular momenta of the two stars in the inner binary should be more or less aligned post-mass transfer, due to the non-negligible amount of mass accreted.} By the end of the simulations the spin of the primary is about
 50.5 rotations per day, and 41.5 rotations per day for the secondary
 star.
+\textbf{Such high spin rates immediately post-mass transfer are supported by other work (see, for example, \citet{2014MNRAS.438.1909D}), which could then subsequently spin down due to, for example, magnetic braking, bringing them closer to the actually observed spin rates.}
 %% But by this time both stars have accreted
@@
 \section{Discussion} \label{sect:discussion}
+
+In this paper, we propose a formation scenario for twin equal-mass
+blue stragglers in tight binaries, as observed for WOCS 7782 in the
+old OC NGC 188.  The proposed scenario involves mass transfer from an
+evolved outer tertiary companion\textbf{. Part} of this mass is accreted by the
+inner binary via a circumbinary disk\textbf{, while} the rest escapes through the
+second and third Lagrangian points in the potential of the triple
+system.  Our scenario makes several predictions for the observed
+properties of a hypothetical outer triple companion, now a WD.  These
+are:
+
+\begin{enumerate}
+
+\item For the predicted outer tertiary orbit, the initial orbital
+  period should lie between 220 days $\lesssim$ P$_{\rm out}$
+  $\lesssim$ 1100 days, assuming initial masses for the inner binary
+  components of $m_{\rm 1} = 1.1$ M$_{\odot}$ and $m_{\rm 2} = 0.9$
+  M$_{\odot}$ and an initial outer tertiary mass of $m_{\rm 3} = 1.4          
+  $M$_{\odot}$.
+\textbf{These initial orbitl periods should match closely to the final periods we expected for the outer tertiary, since remaining within this range is needed to ensure Roche lobe overflow and we do not expect much subsequent orbital evolution post-mass transfer due to mass loss from stellar evolution.}
+
+\item Larger final WD masses, and hence larger core masses for the
+  donor at the time of mass transfer should correspond to larger final
+  outer orbital periods for the tertiary.  This is because the Roche
+  radius is larger for larger outer orbital periods, such that the
+  donor must evolve to larger radii, and hence core masses, before the
+  onset of mass transfer. We expect the orbital separation to range
+  from $\apgt 6.4$\,yr for a $\sim 0.42$\,\MSun\, white dwarf to
+  $\apgt 11.2$\,yr for a $\sim 0.48$\,\MSun\, white dwarf.
+
+\item For the inner binary, the rotational axes of both the BSs should
+  be aligned with each other and the orbital plane of the outer
+  tertiary WD.  This is because accretion onto the BS progenitors
+  proceeds via an accretion disk, that forms at the circularization
+  radius and that has an orbital plane aligned with that of the outer
+  tertiary.
+
+\item The BSs in the inner binary should have roughly equal masses,
+  independent of their initial masses.  This is because it is the
+  lowest mass object that typically accretes the fastest, since its
+  orbital velocity and distance relative to the circumbinary disk is
+  typically the lowest
+%% \citep[e.g.][]{1995MNRAS.277.1491K,1997MNRAS.285...33B,2000MNRAS.314...33B\
+%%}.                                                                            
+  \citep[e.g.][]{2000MNRAS.314...33B,2012ApJ...749..118S,2017MNRAS.466.1170M}.
+  The mass ratio of the inner binary, therefore grows to unity.
+
+\item As a consequence of the above, the initially lower mass MS star should accrete the
+  most, and therefore be more enriched by accreted material.  This
+  could be observable in the surface layers of a radiative star.  If
+  the donor is an RGB star, the accretors will be enriched in mostly
+  carbon, oxygen and helium, but if the donor is an AGB star the
+  enrichment will be mostly in s-process elements.  \textbf{Note that part of the
+  mass liberated from the triple system through the second and third
+  Lagrangian points may eventually be accreted back onto the system.
+  This could also have interesting consequences for the enrichment of the
+  low-mass white dwarf.}
+
+\item We expect twin BSs in compact binaries formed from the mechanism
+  proposed here to be more frequent in younger clusters with ages
+  $\lesssim$ 4-6 Gyr.  This is because \textbf{stars in clusters} with a MS turn-off
+  mass $\lesssim$ 1.2 M$_{\odot}$ have convective envelopes
+  \citep[e.g.][]{1991ApJS...76...55I,2009pfer.book.....M}, and a
+  radiative envelope for the donor in a mass transferring binary
+  ensures stable accretion on to the accretor.
+
+\end{enumerate}
+
+Finally, we emphasize that the choice for the initial mass of the
+outer tertiary may be rather critical.  Mass transfer in our proposed
+scenario proceeds from the most massive tertiary to a binary of lower
+total mass. This may result in an unstable phase of mass transfer, in
+particular if the donor has a convective envelope
+\citep[e.g.][]{2009pfer.book.....M}. A radiative envelope of the donor
+ensures that the mass transfer will be maximally conservative, such
+that the accretion stream will be maximally stable, accreting at a
+stable and roughly constant rate \citep[e.g.][]{1991ApJS...76...55I}.
+This stability regime may also be of interest for explaining very
+massive twins, of $\apgt 20$\,\MSun\, which could be promising sources
+for gravitational wave detectors once both twins evolve to a binary
+black hole \citep{2016MNRAS.460.3545D}.
+
+\section{Summary} \label{sect:conclusions}
 
@@
 mass transfer in triples.
-%Regretfully, we do not really understand the details of this
-%process, but then this process is hardly understood in binary
-%evolution also.
-%NL: I edited the above to be a kinder to us.
 
@@
 
-%NL2: Huh.  This is interesting.  Is the physical reason for it that
-%apocenter for the secondary tends to be closer to the circumbinary
-%disk?  I don't get why retrograde wins though, since naively I'd have
-%thought prograde should lead to lower relative velocities between the
-%secondary and the gas flow, and hence to higher accretion rates.
-%What am I missing?  Is there momentum cancellation via colliding gas,
-%shocks, etc. I am missing somewhere?
-%% SPZ: I think that we do not have to add these extra simulations. I
-%% found the result sufficiently confusing to check and check
-%% again. Maybe we write another paper on these results, or a
-%% follow-up on accretion in triples. But maybe it is best to stick to
-%% the observed facts, and not try to explore parameter space in
-%% extensio. What do you think, Nathan?  At the moment, this last
-%% paragraph is a bit of an after though, but maybe it is worth
-%% mentioning that our results are consistent with those of others...
-
-\section{Summary} \label{sect:conclusions}
-
-In this paper, we propose a formation scenario for twin equal-mass
-blue stragglers in tight binaries, as observed for WOCS 7782 in the
-old OC NGC 188.  The proposed scenario involves mass transfer from an
-evolved outer tertiary companion, part of this mass is accreted by the
-inner binary via a circumbinary disk the rest escapes through the
-second and third Lagrangian points in the potential of the triple
-system.  Our scenario makes several predictions for the observed
-properties of a hypothetical outer triple companion, now a WD.  These
-are:
-
-\begin{enumerate}
-
-\item For the predicted outer tertiary orbit, the initial orbital
-  period should lie between 220 days $\lesssim$ P$_{\rm out}$
-  $\lesssim$ 1100 days, assuming initial masses for the inner binary
-  components of $m_{\rm 1} = 1.1$ M$_{\odot}$ and $m_{\rm 2} = 0.9$
-  M$_{\odot}$ and an initial outer tertiary mass of $m_{\rm 3} = 1.4
-  $M$_{\odot}$.
-
-\item Larger final WD masses, and hence larger core masses for the
-  donor at the time of mass transfer should correspond to larger final
-  outer orbital periods for the tertiary.  This is because the Roche
-  radius is larger for larger outer orbital periods, such that the
-  donor must evolve to larger radii, and hence core masses, before the
-  onset of mass transfer. We expect the orbital separation to range
-  from $\apgt 6.4$\,yr for a $\sim 0.42$\,\MSun\, white dwarf to
-  $\apgt 11.2$\,yr for a $\sim 0.48$\,\MSun\, white dwarf.
-
-\item For the inner binary, the rotational axes of both the BSs should
-  be aligned with each other and the orbital plane of the outer
-  tertiary WD.  This is because accretion onto the BS progenitors
-  proceeds via an accretion disk, that forms at the circularization
-  radius and that has an orbital plane aligned with that of the outer
-  tertiary.
-
-\item The BSs in the inner binary should have roughly equal masses,
-  independent of their initial masses.  This is because it is the
-  lowest mass object that typically accretes the fastest, since its
-  orbital velocity and distance relative to the circumbinary disk is
-  typically the lowest
-%% \citep[e.g.][]{1995MNRAS.277.1491K,1997MNRAS.285...33B,2000MNRAS.314...33B}.
-  \citep[e.g.][]{2000MNRAS.314...33B,2012ApJ...749..118S,2017MNRAS.466.1170M}.
-  The mass ratio of the inner binary, therefore grows to unity.  As a
-  consequence, the initially lower mass MS star should accrete the
-  most, and therefore be more enriched by accreted material.  This
-  could be observable in the surface layers of a radiative star.  If
-  the donor is an RGB star, the accretors will be enriched in mostly
-  carbon, oxygen and helium, but if the donor is an AGB star the
-  enrichment will be mostly in s-process elements.
-
-\item We expect twin BSs in compact binaries formed from the mechanism
-  proposed here to be more frequent in younger clusters with ages
-  $\lesssim$ 4-6 Gyr.  This is because \textbf{stars in clusters} with a MS turn-off
-  mass $\lesssim$ 1.2 M$_{\odot}$ have convective envelopes
-  \citep[e.g.][]{1991ApJS...76...55I,2009pfer.book.....M}, and a
-  radiative envelope for the donor in a mass transferring binary
-  ensures stable accretion on to the accretor.  Note that part of the
-  mass liberated from the triple system through the second and third
-  Lagrangian points may eventually be accreted back onto the system.
-  This could have interesting consequences for the enrichment of the
-  low-mass white dwarf.
-
-  %\simon{Can we quantify this? - NL: The stability of the accretion...?}
-
-\end{enumerate}
-
-We emphasize, in closing, that the choice for the initial mass of the
-outer tertiary may be rather critical.  Mass transfer in our proposed
-scenario proceeds from the most massive tertiary to a binary of lower
-total mass. This may result in an unstable phase of mass transfer, in
-particular if the donor has a convective envelope
-\citep[e.g.][]{2009pfer.book.....M}. A radiative envelope of the donor
-ensures that the mass transfer will be maximally conservative, such
-that the accretion stream will be maximally stable, accreting at a
-stable and roughly constant rate \citep[e.g.][]{1991ApJS...76...55I}.
-This stability regime may also be of interest for explaining very
-massive twins, of $\apgt 20$\,\MSun\, which could be promising sources
-for gravitational wave detectors once both twins evolve to a binary
-black hole \citep{2016MNRAS.460.3545D}.
-
 \acknowledgments

### 2019-02-25 response_to_referees.txt
updated paper from refeee report.

Response to Reviewer Reports for Manuscript ID AAS15718

Dear Reviewers,

	Thank you very kindly for these suggestions for improvement.
	We have done our best to address each of them in detail.
	Below, we respond to each point, indicated in bold-faced font.
	We have also indicated edits to our manuscript with bold-faced
	font, which we point to below.  We hope that you will agree
	that our manuscript now meets the criteria for acceptance in
	ApJL.

Kindest regards,

Simon Portegies Zwart
Nathan Leigh

Reviewer #1:

The authors propose a novel formation mechanism for twin blue stragglers in compact binaries that involves mass transfer from a third companion in a triple system. They apply this new scenario to the observed double blue straggler system Binary 7782 in the old open cluster NGC 188. The idea in the paper is novel and the process described very interesting. Therefore, I would recommend the letter for publication once the following issues have been addressed.

Main:

1) The dynamical analysis performed to constrain the properties of the triple system should also include the typical timescale for triple-single stars and triple-binary stars interactions. Maybe these additional timescale will not put additional constraints in Fig.2 , but they should be at least mentioned and calculated under reasonable assumptions.

SPZ/NL: This is a good and important point.  We have now quantified
the possible effects of the 1+3 and 2+3 timescales, by setting these
timescales equal to the cluster lifetime as well as the expected total
duration of the mass transfer phase and solving for the critical outer
tertiary orbital period for such interactions.  Using the same
assumptions for the host cluster properties of NGC 188 outlined in
Section 3.2 of Leigh & Sills 2011 (right-hand column), we find upon
setting the 1+3 and 2+3 timescales equal to the cluster lifetime
(i.e., 4 Gyr) critical outer orbital periods for triples of 52.5 and
157.8 days, respectively.  However, these critical orbital periods
correspond to the times for any triple to undergo, respectively, a 1+3
or 2+3 interaction.  Hence, all this really tells us is that a
non-negligible fraction of primordial triples will have experienced
such an interaction within the cluster lifetime (but likely not all).
Meanwhile, triples could also form dynamically due to binary-binary
interactions, which have even shorter interaction timescales.

For comparison, if we compute the critical orbital periods
corresponding to the timescales for a specific triple to undergo
either a 1+3 or 2+3 interaction, and if we set the 1+3 and 2+3
timescales equal to the typical duration expected for mass transfer,
which is of order 1 Myr (i.e., corresponding to the expected duration
of the RGB phase, which is longer than is expected for the AGB phase),
then we obtain critical orbital periods of, respectively, 8.1 x 108
and 2.4 x 109 days.  The critical outer tertiary orbital periods
corresponding to such short interaction times are much longer than the
maximum predicted outer orbital period of the hypothesized white dwarf
tertiary in our scenario, and fall outside of the current range of
orbital periods shown on the x-axis in figure 2.  Hence, we do not
expect the mass transfer process to be interrupted by either 1+3 and
2+3 interactions.  Rather than include these critical orbital periods
in figure 2, we have included a paragraph on this in the text,
indicated in bold-faced font.

SIMON: I am happy to include these critical orbital periods in Figure
2, but do you think we should (I would argue not), and should assume 1
Myr for the duration of the MT process?  If I recall my stellar
evolution, this corresponds roughly the timescale for the RGB phase,
and I believe the AGB phase is much shorter.  As it is, I have added a
paragraph to the end of Section 2, but it takes up space, and I think
can ultimately be removed for that reason.

NATHAN: I agree. What counts here is the thermal time scale of the
Roche-lobe filling star, which is even shorter than 1Myr, but rather
something like a few thens of thousands of years. Much shorter than
any dynamical timescale in the cluster.

2) The authors fix the amount of angular momentum lost per unit mass to eta=3. How did they estimate this number? Please, provide some additional information and references. Could the value of this number be the reason of the discrepancy between the theoretical expectations and the simulation results in Fig. 6?

SPZ/NL: Indeed, this is one of these magic parameters that have
received relatively little attention in the recent literature, even
though it's value is very important. We adopt the approach as
advocated in Pols etal 1991 and Portegies Zwart 1995 with further
suport by the analysis of Pols 2007 and Krticka etal 2011. We do not
really know how much angular momentum is lost per unit mass in a
non-conservative binary system, but interestingly enough our analysis
in this paper appears to be consistent with these earlier findings.
We comment on this in the main text in the added sentence near Eq. 3.

3) The authors should elaborate more on the reason why there is a large discrepancy in the plots shown in Fig. 6. What could be the main reasons? And why for a donor of 1.2 Msun the discrepancy is larger?

SPZ/NL: Let's first point out that the trends are rather
consistent. The 1.2 Msun donor's seem to be doing something similar as
the 1.4Msun donors. Except that the more massive donors follow the
required trend in order to be able to explain the observed system.
Then, the inner orbits of the 1.2MSun donors tend to shrink, whereas
the more massive donors drive the expansion of the inner orbit.

4) The authors adopt an initial inner binary of 0.9 Msun-1.1 Msun. I understand that the calculations may be long and complicated, but they should present results for an additional run where they change the masses of the inner binary, as they have already done in the case of the third companion. These would make stronger their claim that the inner binary would evolve towards a mass ratio of unity.

SPZ/NL: As we pointed out in the manuscript, we do not really
understand the subtleties of angular momentum transport in
non-conservatively evolving binaries. In triples additional
complications are introduced by the third component. I fear that this
process require much more study, which we think, would be really
interesting to persue. However, for this manuscript we prefer to focus
on the initial conditions that are most likely to reproduce the
observe twin blue straggler, and for that discussion we think that the
1.2Msun donor does not lead to final parameters that are consistent
with this observed system.

5) Other interesting plots would be the evolution in time of the
masses of the three stars and their spins, and, more importantly of
the inner binary eccentricity.

SPZ/NL: The eccentricity of the inner binary remains small. It remains
below 0.02 for an inner orbital separation of 0.2au, and below 0.01
for the tighter inner orbits. We add a comment to this effect in the
paper.

For the evolution of the masses of the three stars we have figure 6.
to allow for a discussion on the initial mass-ratio of the inner
binary, we add a new figure (7), in which we present the mass ratio of
the inner binary as a function of the total mass of the inner binary
(both normalized). Here we demonstrate that the inner binary star
grows gradually to more equal masses, and that this effect is stronger
when the initial inner mass ratio is smaller. Interestingly, the an
initial mass-ratio of 0.9MSun/1.1MSun appears to be less favorable for
growing to two equal mass stars, when when we start with alower
initial mass ratio, for example using 0.7MSun/1.1MSun. We may refine
our conclusion that maybe a lower initial mass ratio for the inner
binary is favored over an initially more equal mass binary. However,
the observational constraints are insufficient to boltser this
conclusions at this point.

Minor:

1) In the abstract, the authors are missing the point "(2)" somewhere in the text.

SPZ/NL:  Fixed.  Thank you for catching this.

2) In the line after Eq. 2, the mentioned semi-major axes are not in a latex math style. Please, check this throughout the paper.

SPZ/NL: fixed

3) Figure 1 is maybe a bit small and readers would benefit from having a bigger figure.

SPZ/NL:  Fixed, for both figures 1 and 2.

4) The caption of Fig. 6 left panel needs attention. There are typos like "10 AU" instead of "0.10 AU", and so on.

SPZ/NL:  Ow. that is rather sloppy. Apologies. fixed.

5) In the summary section, there is "clusters with a MS turn-off" instead of "stars with a MS turn-off" (point 5 of the summary).

SPZ/NL:  Fixed.

====================================
Reviewer #2:

It has been my pleasure to review the manuscript A Triple Origin for Twin Blue Stragglers in Close Binaries by Portegies Zwart and Leigh. This paper reports a new and well-executed idea regarding the formation of a binary star that includes two blue stragglers. This system challenges the usually proposed blue straggler formation mechanisms.

This paper is certainly interesting and the work well done. Particularly impressive is the integration of a wide array of numerical tools to simulate the equally wide array of processes and scales in the problem. It is a powerful demonstration of the AMUSE framework into which so much effort has been invested. Of course there are always caveats in the results of each numerical tool, but even so the work certainly merits publication.

Whether it constitutes high-impact astronomical research meriting rapid publication as an ApJ Letter is less clear. The broad concept of mass transfer from a tertiary or a circumbinary disk onto a binary is not new, and so I don't think that the paper will have broad high-impact. However, the predictions of the paper may immediately influence the work of observers in the field, and on that basis I would lean toward publication in ApJ Letters.

Specific notes in the main text; suggested changes in [brackets]:

[Most] blue straggler stars are brighter and bluer than the main-sequence - the blue straggler domain has been opened wider by observations in recent years.

SPZ/NL:  Fixed.

It would be worth noting the expected (or not) companions to the two merger mechanisms, since the presence/nature of a companion is key to the story of this manuscript.

SPZ/NL:  Fixed – please see the first paragraph of the Introduction.

I think the introductory text on S1082 is rather long and unnecessary given that it has no relevance to this paper. I would suggest condensing to 1-2 sentences.

SPZ/NL:  Fixed.

called [WOCS] 7782 - here and throughout; cite Geller et al. 2008 if you wish.

SPZ/NL:  Fixed throughout the manuscript.

Important - "Dynamically, it is difficult to form a short-period binary composed of two collision products during a collisional interaction in a star cluster." I am not clear if by this statement the authors are excluding an exchange into a BS-[WD or MS] binary of another BS, creating 7782. This scenario has been posed previously. More broadly, with one stroke of this sentence, the authors are ruling out a host of other pathways to this binary. If that is their intent, this merits more justification. (To be clear, I don't think that they need to rule out all other scenarios for their scenario to be interesting.)

SPZ/NL:  This is of course a very valid point.  We do not intend to concretely rule out other formation channels, but rather to highlight that a purely dynamical formation channel likely has a low probability of occurring.  This is because, as explained in Leigh & Sills (2011), the energetics of a 1+2 interaction involving a BS and a pre-existing BS-MS or BS-WD system with a long orbital period are such that it is unlikely that the result will be a BS-BS binary with a short orbital period as is observed for WOCS 7782. And, as shown in Mathieu & Geller (2009), there are only two short-period BS binaries in NGC 188, such that the relevant 1+2 interaction time should be for a specific short-period BS binary, which increases the expected interaction time considerably such that it will exceed the expected BS lifetime.  To save on space, we have included a very brief mention of this in the draft.

before it leaves the asymptotic giant branch. - At this point in the paper, it is not evident why this needs to be AGB mass transfer and not RG mass transfer. That is, at this point it is not "according to this scenario"?

SPZ/NL: We ware not very clear about this.  the scenario only works
for donors on the giant branch. Not on the Hertzsprung-gap and not on
the AGB. We made that clear now in fig. 3 by painting these parts of
the curve indicating the stellar radius orange.

Important - "For clarity we assume both orbits, the inner as well as the outer, to have negligible eccentricity and low inclination." Might I suggest "For specificity"?

Yes, we do that now.

SPZ/NL:  Fixed.

More importantly, what is the significance of these assumptions? Is the goal of this paper simply to show that the proposed scenario can happen, in which case my last question is not as important. But if the goal is more generality, than these assumptions do matter.

SPZ/NL: Our prime objective is to demonstrate that this scenario
works. We do not really desire to cover parameter space or indicate in
which part of parameter space this scenario works. This may be very
interestsing, but for a future paper.

"We assume initial component masses of m1=1.1M⊙ and m2=0.9M⊙ for the inner binary components, and m3 = 1.4M⊙ for the outer tertiary." - Where did these assumptions for m2 and m3 come from? What is there motivation? And essentially the same question for exploring the range of 1.2⊙ < m3 < 1.4⊙ in Section 3.1. (As an aside, the way this is written, I first thought that these assumptions were being made for the entire paper, not just this section of the paper, which caused me some concern. This was not clarified/resolved (at least for m3) until Sections 3.1 and 4.
Perhaps the authors might want to make clearer here that here these assumptions are only for parameter delineation?)

SPZ/NL: These are good points, and yes this is effectively our choice
for parameter delineation that we expected to work best for a “proof
of concept” illustration via our simulations.  For instance, if the
initial mass ratio of the inner binary is too large, then it can occur
that not enough mass can be transferred to bring the inner binary
toward a mass ratio of unity. We added an explanation to the text to
express and motivate our rather explicite choice of parameters.

and the amount of angular momentum lost per unit mass η ≃ 3. Again, this number comes out of the blue?

SPZ/NL: Indeed, this is one of these magic parameters that have
received relatively little attention in the recent literature, even
though it's value is very important. We adopt the approach as
advocated in Pols etal 1991 and Portegies Zwart 1995 with further
suport by the analysis of Pols 2007 and Krticka etal 2011. We do not
really know how much angular momentum is lost per unit mass in a
non-conservative binary system, but interestingly enough our analysis
in this paper appears to be consistent with these earlier findings.
We comment on this in the main text in the added sentence near Eq. 3.

Tidal effects during mass tran[s]fer have probably circularized the orbit, although some slight 
SPZ?NL:  Fixed.

eccentricity due to turbulent motion in the outer layers of the donor star may have induced a small e ≪ 0.1 eccentricity - This has been the canonical assumption, but in fact observations don't support it (e.g., Mathieu & Geller 2009) and recent theoretical papers indicate why it might not happen. If the authors wish to stipulate this as yet another assumption of the paper, that is fine, but should be noted as such.

SPZ/NL: we leave out the remark about the low eccentricity of the outer orbit.

see red square[s]

SPZ/NL:  Fixed.

We follow the same procedure as described in de Vries et al. (2014) for simulating the future of the triple system χ Tau (HD 97131) in which the outer-most star overfills its Roche lobe and transfers mass to an inner binary. - Wouldn't it be appropriate to reference this paper (and perhaps other work - Mosta et al, others unknown to me) at the beginning of the last paragraph of the introduction? The idea being suggested here has a prior history.

SPZ/NL:  Done.

250 R⊙[ ]for the 100 R⊙[ ]donor star

SPZ/NL:  Fixed.

If length is an issue, I think Figure 4 could be sacrificed. In any case, it should be zoomed in so that the system itself is more easily seen. (To be honest, I am totally perplexed by "The two companion stars are represented as black bullets (to the right).")

SPZ/NL: We removed figure 4. the referee is right that it does not really add much to the paper.
The "black bullets to the right" was a typo, left over after meny iterations of refinement.

To test the hypotheses that (1) the secondary in the inner binary accretes more effectively than the primary star and to measure the change to the inner orbit due to the Roche-lobe overflow of the outer star, we perform a series of calculations in which we take the self gravity and the hydrodynamical effects of the triple into account. - I am perplexed as to the meaning of (1) when there is no (2)? More broadly, this seems like an oddly specific issue with which to start this section. The next sentence in the paragraph seems like the more reasonable starting point?

SPZ/NL:  This text has now been edited accordingly.

quanti[fy] the amount of material los[s], 
SPZ/NL:  Fixed.

This value is hard to estimate from the simulations, but an accretion efficiency of ∼> 0.6 is necessary to make the scenario feasible. - Please clarify what is meant by "feasible"? Does this mean feasible technically, or feasible in making the two blue stragglers, or ... ?

SPZ/NL: This means feasible in terms of being able to reproduce the
observed parameters of the system (or at least parameters consistent
with the available observational data), such as sufficient mass
accretion to drive both stars in the inner binary toward a mass ratio
of unity. The most extreme mass ratio of 1.1+ 0.5Msun for the inner
binary with an 1.4MSun donor could in principle lead to two 1.4MSun
blue stragglers, but in that case mass transfer has to be
conservative. In our simulations, only a fraction of the mass lost
from the donor is accreted by the two companion stars. We cannot
exclude the possibility that even mass that appears to be ejected from
the system eventually falls back. However, our simulations did not
last sufficiently long to validate this point. We prefer to remain
somewhat conservative (no pun intended).

and the orbital evolution of the inner binary matches better with the anticipated evolution. - I'm not following the meaning of "anticipated evolution"? Does this mean matching the observed binary?

SPZ/NL:  Yes, this was our intended meaning, and we have now included a phrase highlighted in bold-faced font to better indicate this.

[In a]ll three cases for the 1.4 M⊙ donor presented in figure 6 the inner orbit expands at about the same rate. By the end of the simulation the spins of the two BSs are aligned along the orbital angular momentum axis with an angle of 90.0◦ for the primary star and 93.4◦ for the secondary star with respect to the argument of pericenter of the inner orbit. - I'm a bit confused about the significance of this outcome, and why it is being reported. Earlier the text mentions "low inclination", but I believe that is the only information we are given about the original spin and orbital alignments. Resolving these comments is also important for the third prediction in the Summary.

SPZ/NL:  Fixed the typo.  We made a prediction that the spin angular momenta of the stars should become more or less aligned post-mass transfer, given that non-negligible mass is accreted.  This was to highlight that the simulations do indeed reproduce this basic expectation.  We have now included a brief sentence better explaining this prediction and result.

"By the end of the simulations the spin of the primary is about 50.5 rotations per day, and 41.5 rotations per day for the secondary star." - The authors might want to reference Leiner et al. 2018 for observational "confirmation" of these spin rates early in the lifetime of mass transfer products. Similarly, the current stars are not spinning this fast. Some explanation is merited.

SPZ/NL:  We do not have sufficient space to elaborate on these points in great detail, but magnetic braking has been proposed to explain the spin-down of the accretors post-mass transfer, which could render their “final” spin rates in better agreement with the observations.  We have included a brief sentence to better explain this, and referenced Leiner et al. 2018 to support it.

The first three paragraphs of Section 5: Discussion are a summary, not a discussion. They should be integrated into Section 6: Summary. Alternatively, and perhaps better, the predictions of Section 6: Summary might more appropriately be the Discussion, while these first three paragraphs might become the Summary.

SPZ:NL:  We have now edited the Discussion and Summary as recommended, but note than we do not highlight this change in bold-faced font for ease of reading.

The remaining two points of the current Section 5: Discussion are mildly interesting, but could be removed if length is an issue.

SPZ/NL:   We may want to leave this to the editor to decide.

The proposed scenario involves mass transfer from an evolved outer tertiary companion[. P]art of this mass is accreted by the inner binary via a circumbinary disk[, while] the rest escapes through the second and third Lagrangian points in the potential of the triple system.

SPZ/NL:  Fixed.

"Our scenario makes several predictions for the observed properties of a hypothetical outer triple companion, now a WD." - Kudos to the authors for making predictions regarding the tertiary in order to test their hypothesis for 7782. But I am a bit puzzled about their first bullet, which isn't in fact a testable prediction?

SPZ/NL:  We have included a sentence here explaining how this relates directly to a prediction for a comparable final orbital period for the proposed outer tertiary.

"Note that part of the mass liberated from the triple system through the second and third Lagrangian points may eventually be accreted back onto the system. This could have interesting consequences for the enrichment of the low-mass white dwarf." - This seems more relevant to point 4? I might even suggest that point 4 be split into two predictions, one having to do with the mass ratio and one having to do with enrichment.

SPZ/NL: Very interesting point. Thanks for pointing this out.
We have edited both of these bullet points as recommended.

Specific notes on the abstract:

Broadly speaking, the abstract is rather unusual in that it is not at all an abstract of the paper but rather a restatement of the predictions in the current Summary. As I wrote above, it is very good that the authors are making explicit predictions. But an abstract is intended to permit a reader to be informed about the entire essential content of a paper, and as such this abstract does not seem appropriately constructed.

SPZ/NL: We think that abstract maybe a bit controversial in comparison
with other abstracts, but we think that it covers the content of the
paper and the presented work.

"are naturally reproduced" - this is an overstatement given the tuning and uncertainties of the simulations; please change to "can be reproduced".

SPZ/NL:  Fixed.

### 2019-02-25 BSS7782.tex
updated paper from refeee report.

@@
 tertiary companion on to the inner binary via a circumbinary disk.  We
-apply this scenario to the observed double BS binary WOCS 7782 in
-the old open cluster NGC 188, and show that its observed properties
+apply this scenario to the observed double BS binary WOCS 7782 in the
+old open cluster NGC 188, and show that its observed properties
 \textbf{can be} reproduced within the context of the proposed model.
@@
 = 1.1$ M$_{\odot}$ and $m_{\rm 2} =$ 0.9 M$_{\odot}$ and an outer
-tertiary mass of $m_{\rm 3} = 1.4$ M$_{\odot}$.  \textbf{(2)} After Roche-lobe
-overflow, the outer star turns into a white dwarf (WD) of mass 0.43 to
-0.54\,\MSun. There is a correlation between the mass of this WD and
-the outer orbital period: more massive WDs will be on wider orbits.
-(3) The rotational axes of both BSs will be aligned with each other
-and the orbital plane of the outer tertiary WD. (4) The BSs will have
-roughly equal masses, independent of their initial masses (since the
-lower mass star accretes the most).  The dominant accretor should,
-therefore, be enriched more effectively by the accreted material.  As
-a result, one of the BSs will appear to be more enriched by either He,
-C and O or by s-process elements, depending on if the donor started to
-overflow its Roche lobe on, respectively, the red giant or asymptotic
-giant branch.  (5) Relative to old dense clusters with high-velocity
-dispersions, twin BSs in close binaries formed from the proposed
-mechanism should be more frequent in the Galactic field and younger
-open clusters with ages $\lesssim$ 4-6 Gyr, since then the donor will
-have a radiative envelope. (6) the orbit of the binary BS will have a
-small semi-major axis (typically $\aplt 0.3$\,au) and be close to
-circular ($e \aplt 0.2$).
+tertiary mass of $m_{\rm 3} = 1.4$ M$_{\odot}$.  \textbf{(2)} After
+Roche-lobe overflow, the outer star turns into a white dwarf (WD) of
+mass 0.43 to 0.54\,\MSun. There is a correlation between the mass of
+this WD and the outer orbital period: more massive WDs will be on
+wider orbits.  (3) The rotational axes of both BSs will be aligned
+with each other and the orbital plane of the outer tertiary WD. (4)
+The BSs will have roughly equal masses, independent of their initial
+masses (since the lower mass star accretes the most).  The dominant
+accretor should, therefore, be enriched more effectively by the
+accreted material.  As a result, one of the BSs will appear to be more
+enriched by either He, C and O or by s-process elements, depending on
+if the donor started to overflow its Roche lobe on, respectively, the
+red giant or {\bf early} asymptotic giant branch.  (5) Relative to old
+dense clusters with high-velocity dispersions, twin BSs in close
+binaries formed from the proposed mechanism should be more frequent in
+the Galactic field and younger open clusters with ages $\lesssim$ 4-6
+Gyr, since then the donor will have a radiative envelope. (6) the
+orbit of the binary BS will have a small semi-major axis (typically
+$\aplt 0.3$\,au) and be close to circular ($e \aplt 0.2$).
 
@@
 $m_3$. The inner and outer binary orbital semi-major axes are denoted
-a$_{\rm in}$ and a$_{\rm out}$, respectively.  \textbf{For specificty,} we 
-assume both orbits, the inner as well as the outer, to have negligible
-eccentricity and low inclination, \textbf{which minimizes chaotic effects during the mass transfer process, facilitates more stable mass transfer and ultimately allows us to simulate our target system for longer while also maximizing the amount of mass transferred}.
-These assumptions are also
-supported by the population of observed low-mass triples
-\citep{2010yCat..73890925T,2018ApJ...854...44M}.  This initial configuration for our
-assumed formation scenario for WOCS 7782, described below, is
-depicted in figure~\ref{fig:fig1}.
+a$_{\rm in}$ and a$_{\rm out}$, respectively.  \textbf{For
+  specificty,} we assume both orbits, the inner as well as the outer,
+\textbf{to be circular and in the same plane, which minimizes chaotic
+  effects during the mass transfer process, facilitates more stable
+  mass transfer and ultimately allows us to simulate our target system
+  for longer while also maximizing the amount of mass transferred}.
+These assumptions are also supported by the population of observed
+low-mass triples \citep{2010yCat..73890925T,2018ApJ...854...44M}.
+This initial configuration for our assumed formation scenario for WOCS
+7782, described below, is depicted in figure~\ref{fig:fig1}.
 
@@
 sufficiently small that the tertiary star is filling its Roche lobe
-and transfers mass to the inner binary before it leaves the asymptotic
+and transfers mass to the inner binary before it {\bf reaches} the asymptotic
 giant branch. We constrain the inner orbit by requiring the triple
@@
 In order for a circumbinary disk to form around the inner binary, we
-require that a$_{\rm in} <$ a$_{\rm c}$.
+require that $a_{\rm in} < a_{\rm c}$.
 
 Figure~\ref{fig:fig2} shows the parameter space in the P$_{\rm
-  out}$-P$_{\rm in}$-plane for WOCS 7782.  We assume initial
-component masses of $m_{\rm 1} = 1.1$ M$_{\rm \odot}$ and $m_{\rm 2} =
-0.9$ M$_{\rm \odot}$ for the inner binary components, and $m_{\rm 3} =
-1.4 $M$_{\rm \odot}$ for the outer tertiary.  We compare the
+  out}$-P$_{\rm in}$-plane for WOCS 7782.  \textbf{Here we adopted,
+  for clarity,} initial component masses of $m_{\rm 1} = 1.1$ M$_{\rm
+  \odot}$ and $m_{\rm 2} = 0.9$ M$_{\rm \odot}$ for the inner binary
+components, and $m_{\rm 3} = 1.4 $M$_{\rm \odot}$ for the outer
+tertiary.  \textbf{The scenario worked out is general, but we opt for
+  these specific parameters because they appear to naturally result in
+  a system with parameters similar to WOCS 7782.}  We compare the
 circularization radius to the semi-major axis of the inner binary, for
@@
 constraints from the requirements for dynamical stability (listed in
-the caption of figure~\ref{fig:fig2}), and the assumption of an outer tertiary that is Roche
-lobe-filling \textbf{(see \citet{2014MNRAS.438.1909D} for more details)}.  
+the caption of figure~\ref{fig:fig2}), and the assumption of an outer
+tertiary that is Roche lobe-filling \textbf{(see
+  \citet{2014MNRAS.438.1909D} for more details)}.
 %\simon{Why do you consider it important to mention that the orbit is hard, and for what environment did you consider this? - NL: Deleted.}  
@@
   \caption{Giant radius as a function of the mass of the core of the
-    Roche-lobe filling outer star (dark blue curve).  Here we adopt a
+    Roche-lobe filling outer star (dark blue curve).  {\bf The first
+      and last parts of this curve are orange to indicate that the
+      star at these masses and radii is on the Hertzsprung-gap (to the
+      left) or after core helium burning stage (to the right).  Only
+      when the donor is on the giant branch (dark blue) Roche-lobe
+      overflow will lead to a binary blue straggler.}  Here we adopt a
     donor mass of 1.4\,\MSun, but for an 1.2\,\MSun\, the donor the
@@
 With the adopted parameters, we can also estimate the final orbital
-period of the left-over core from the tertiary star after 
-mass transfer.  The change in orbital separation due to
-non-conservative mass transfer can be expressed in terms of the mass
-of the outer star before and after mass transfer, i.e. $m_3$ and $m'_3$
-respectively, the total mass in the inner binary before ($m_{\rm in}$)
-and after accretion ($m'_{\rm in}$) and the amount of angular momentum
-lost per unit mass $\eta \simeq 3$. Adopting the relation between the
-orbital separation before mass transfer ($a$) and after mass transfer
-($a'$) from \cite{1995A&A...296..691P}
+period of the left-over core from the tertiary star after mass
+transfer.  The change in orbital separation due to non-conservative
+mass transfer can be expressed in terms of the mass of the outer star
+before and after mass transfer, i.e. $m_3$ and $m'_3$ respectively,
+the total mass in the inner binary before ($m_{\rm in}$) and after
+accretion ($m'_{\rm in}$) and the amount of angular momentum lost per
+unit mass $\eta \simeq 3$.  {\bf The value of $\eta = 3$ was derived
+  in \cite{1991A&A...241..419P,1995A&A...296..691P} by matching the
+  orbital evolution and birthrate of Be-type x-ray binaries that
+  experience non-considervative mass transfer. This value of
+  consistent with the analysis for non-conservative evolution of type
+  B mass transfer in \cite{2011A&A...527A..84K} and further
+  constrained in \cite{2007ASPC..367..387P} to understand the mass
+  transfer in the 100-day orbital period binary V379 Cep.}  Adopting
+the relation between the orbital separation before mass transfer ($a$)
+and after mass transfer ($a'$) from \cite{1995A&A...296..691P}
 \begin{equation}
@@
 the current orbital separation of the WD around the twin
-BS 7782. Tidal effects during mass \textbf{transfer}
-have probably circularized the orbit, although some slight eccentricity
-due to turbulent motion in the outer layers of the donor star may have
-induced a small $e \ll 0.1$ eccentricity.
+BS 7782.
+%% Tidal effects during mass \textbf{transfer}
+%% have probably circularized the orbit, although some slight eccentricity
+%% due to turbulent motion in the outer layers of the donor star may have
+%% induced a small $e \ll 0.1$ eccentricity.
 
@@
 %%SPZ: I removed the notion of low-inclination, because we already said as such in the intro.
-In figure~\ref{fig:topview_at_t0} we present a top view of the initial
-conditions for one of these calculations.
-
-\begin{figure}[ht!]
-  \includegraphics[width=\columnwidth]{fig_BBSS_gas_M14Msun_A010au_t0002.png}
-\caption{Top view of the simulated triple system in which the
-  100\,\RSun\, outer star of 1.4\,\MSun\, over-fills its
-  Roche-lobe.  The star is represented by 80000\,SPH particles and a
-  core particle of $\sim 0.4$\,\MSun (black bullet). The two companion
-  stars are represented as black bullets (to the right).  The inner
-  binary is represented by the yellow and red bullets for, respectively, the
-  1.1\,\MSun\, primary and 0.9\,\MSun\, secondary stars in a circular
-  orbit of 0.1\,au. The 1.4\,\MSun\, giant star is presented to the
-  right in a circular orbit with semi-major axis $\sim 250$\,\RSun\, in the plane of the
-  inner binary.
-\label{fig:topview_at_t0}}
-\end{figure}
+%% In figure~\ref{fig:topview_at_t0} we present a top view of the initial
+%% conditions for one of these calculations.
+
+%% \begin{figure}[ht!]
+%%   \includegraphics[width=\columnwidth]{fig_BBSS_gas_M14Msun_A010au_t0002.png}
+%% \caption{Top view of the simulated triple system in which the
+%%   100\,\RSun\, outer star of 1.4\,\MSun\, over-fills its
+%%   Roche-lobe.  The star is represented by 80000\,SPH particles and a
+%%   core particle of $\sim 0.4$\,\MSun (black bullet). The two companion
+%%   stars are represented as black bullets (to the right).  The inner
+%%   binary is represented by the yellow and red bullets for, respectively, the
+%%   1.1\,\MSun\, primary and 0.9\,\MSun\, secondary stars in a circular
+%%   orbit of 0.1\,au. The 1.4\,\MSun\, giant star is presented to the
+%%   right in a circular orbit with semi-major axis $\sim 250$\,\RSun\, in the plane of the
+%%   inner binary.
+%% \label{fig:topview_at_t0}}
+%% \end{figure}
 
@@
 gravity and the hydrodynamical effects of the triple into account.
-The results of these simulations are presented in
-figure~\ref{fig:topview_at_t1000day} and
-figure~\ref{fig:mass_vs_semimajor_axis}.  The first figure
-(figure~\ref{fig:topview_at_t1000day}) shows the top view of the same
-initial realization for which we presented the initial conditions in
-figure~\ref{fig:topview_at_t0} but now at an age of 1091 days after
-the onset of mass transfer. We add, to the left panel,
-the equipotential surfaces in the orbital plane.
+The results of \textbf{one of} these simulations (1091 days after
+the onset of mass transfer) is presented in
+figure~\ref{fig:mass_vs_semimajor_axis}.
+%% figure~\ref{fig:topview_at_t1000day} and
+%% The first figure
+%% (figure~\ref{fig:topview_at_t1000day}) shows the top view of the same
+%% initial realization for which we presented the initial conditions in
+%% figure~\ref{fig:topview_at_t0} but now at an age of 1091 days after
+%% the onset of mass transfer. We add, to the left panel,
+%% the equipotential surfaces in the orbital plane.
 
@@
 ~  \includegraphics[width=0.5\linewidth]{fig_BBSS_gas_M14Msun_A010au_t3360.png}
-\caption{Same as figure~\ref{fig:topview_at_t0} but at an age of $t
-  \simeq 1091\,days$ after the start of the simulation. Left panel
-  shows the equipotential surfaces of the triple overplotted with the
-  gas distribution, the right panel shows just the gas and the stars
-  as bullets.
+  \caption{ Top view of one of the simulated triple systems at an age
+    of $t \simeq 1091\,days$ after the start of the simulation when
+    the 100\,\RSun\, outer star of 1.4\,\MSun\, over-fills its
+    Roche-lobe.  The star is represented by 80000\,SPH particles and a
+    core particle of $\sim 0.4$\,\MSun (black bullet in the middle of
+    the right-most yellow blob). The inner binary \textbf{(to the
+      left)} is represented by the yellow and red bullets for,
+    respectively, the 1.1\,\MSun\, primary and 0.9\,\MSun\, secondary
+    stars in a circular orbit of 0.1\,au. The 1.4\,\MSun\, giant star
+    is presented to the right in a circular orbit with semi-major axis
+    $\sim 250$\,\RSun\, in the plane of the inner binary.  Left panel
+    shows the equipotential surfaces of the triple overplotted with
+    the gas distribution, the right panel shows just the gas and the
+    stars as bullets.
 \label{fig:topview_at_t1000day}}
@@
     curve of the right-hand panel is presented in
-    fig.\,\ref{fig:topview_at_t0}, and in
     fig.\,\ref{fig:topview_at_t1000day} we present the final
@@
   M$_{\odot}$ and an initial outer tertiary mass of $m_{\rm 3} = 1.4
-  $M$_{\odot}$.
-\textbf{These initial orbitl periods should match closely to the final periods we expected for the outer tertiary, since remaining within this range is needed to ensure Roche lobe overflow and we do not expect much subsequent orbital evolution post-mass transfer due to mass loss from stellar evolution.}
+  $M$_{\odot}$. \textbf{The final orbital period of the white dwarf
+    around the binary blue straggler should exceeds the initiall
+    orbit, but be smaller than $\sim 4100$\,days.}
 
@@
 
-\item As a consequence of the above, the initially lower mass MS star should accrete the
-  most, and therefore be more enriched by accreted material.  This
-  could be observable in the surface layers of a radiative star.  If
-  the donor is an RGB star, the accretors will be enriched in mostly
-  carbon, oxygen and helium, but if the donor is an AGB star the
-  enrichment will be mostly in s-process elements.  \textbf{Note that part of the
-  mass liberated from the triple system through the second and third
-  Lagrangian points may eventually be accreted back onto the system.
-  This could also have interesting consequences for the enrichment of the
-  low-mass white dwarf.}
+\item As a consequence of the above, the initially lower mass MS star
+  should accrete the most, and therefore be more enriched by accreted
+  material.  This could be observable in the surface layers of a
+  radiative star.  If the donor is an RGB star, the accretors will be
+  enriched in mostly carbon, oxygen and helium, but if the donor is an
+  AGB star the enrichment will be mostly in s-process elements.
+  \textbf{Note that part of the mass liberated from the triple system
+    through the second and third Lagrangian points may eventually be
+    accreted back onto the system.  This could also have interesting
+    consequences for the enrichment of the low-mass white dwarf.  Such
+    a debris disk was recently found around the white dwarf SDSS
+    J122859.93+104032.9 \cite{Manseretal2019}.
+  }
 

### 2019-02-25 BSS7782.tex
small typo corrected

@@
 in the envelope of the donor star, and the orbital evolution of the
-inner binary matches better with the anticipated evolution \textbf{needed to reproduce the observed parameters of WOCS 7782.}  A more
-massive donor may therefore have a lower accretion efficiency while
-still accomodating the observed constraints.  The longer thermal time
-scale of the stellar envelope of the higher-mass donor at the same
-stellar radius eventually leads to a higher mass-transfer rate, and
-therefore to a lower accretion efficiency. However, the larger mass
-budget in the envelope appears to compensate.
+inner binary matches better with the anticipated evolution
+\textbf{needed to reproduce the observed parameters of WOCS 7782.}  A
+more massive donor may therefore have a lower accretion efficiency
+while still accomodating the observed constraints.  The longer thermal
+time scale of the stellar envelope of the higher-mass donor at the
+same stellar radius eventually leads to a higher mass-transfer rate,
+and therefore to a lower accretion efficiency. However, the larger
+mass budget in the envelope appears to compensate.
 
@@
 secondary star with respect to the argument of pericenter of the inner
-orbit.
-\textbf{This supports our naive prediction that the spin angular momenta of the two stars in the inner binary should be more or less aligned post-mass transfer, due to the non-negligible amount of mass accreted.} By the end of the simulations the spin of the primary is about
-50.5 rotations per day, and 41.5 rotations per day for the secondary
-star.
-\textbf{Such high spin rates immediately post-mass transfer are supported by other work (see, for example, \citet{2014MNRAS.438.1909D}), which could then subsequently spin down due to, for example, magnetic braking, bringing them closer to the actually observed spin rates.}
+orbit.  \textbf{This supports our naive prediction that the spin
+  angular momenta of the two stars in the inner binary should be more
+  or less aligned post-mass transfer, due to the non-negligible amount
+  of mass accreted.} By the end of the simulations the spin of the
+primary is about 50.5 rotations per day, and 41.5 rotations per day
+for the secondary star.  \textbf{Such high spin rates immediately
+  post-mass transfer are supported by other work (see, for example,
+  \citet{2014MNRAS.438.1909D}), which could then subsequently spin
+  down due to, for example, magnetic braking, bringing them closer to
+  the actually observed spin rates.}
 %% But by this time both stars have accreted

### 2019-03-04 BSS7782.tex
after referee report

@@
 assuming initial masses for the inner binary components of $m_{\rm 1}
-= 1.1$ M$_{\odot}$ and $m_{\rm 2} =$ 0.9 M$_{\odot}$ and an outer
-tertiary mass of $m_{\rm 3} = 1.4$ M$_{\odot}$.  \textbf{(2)} After
-Roche-lobe overflow, the outer star turns into a white dwarf (WD) of
-mass 0.43 to 0.54\,\MSun. There is a correlation between the mass of
-this WD and the outer orbital period: more massive WDs will be on
-wider orbits.  (3) The rotational axes of both BSs will be aligned
+= 1.1$ M$_{\odot}$ and $m_{\rm 2} = 0.7$ to $0.9$M$_{\odot}$ and an
+outer tertiary mass of $m_{\rm 3} = 1.4$ M$_{\odot}$.  \textbf{(2)}
+After Roche-lobe overflow, the outer star turns into a white dwarf
+(WD) of mass 0.43 to 0.54\,\MSun. There is a correlation between the
+mass of this WD and the outer orbital period: more massive WDs will be
+on wider orbits.  (3) The rotational axes of both BSs will be aligned
 with each other and the orbital plane of the outer tertiary WD. (4)
@@
 enriched by either He, C and O or by s-process elements, depending on
-if the donor started to overflow its Roche lobe on, respectively, the
-red giant or {\bf early} asymptotic giant branch.  (5) Relative to old
-dense clusters with high-velocity dispersions, twin BSs in close
+whether the donor started to overflow its Roche lobe on, respectively,
+the red giant or {\bf early} asymptotic giant branch.  (5) Relative to
+old dense clusters with high-velocity dispersions, twin BSs in close
 binaries formed from the proposed mechanism should be more frequent in
@@
 orbit of the binary BS will have a small semi-major axis (typically
-$\aplt 0.3$\,au) and be close to circular ($e \aplt 0.2$).
+$\aplt 0.3$\,au) and be close to circular ($e \aplt 0.1$).
 
@@
 
-Even more curious, there exists in the old OC NGC 188 a
-double BS binary, called WOCS 7782 \citep{geller08}.  The BS
+Even more curious, there exists in the old OC NGC 188 a double BS
+binary, called WOCS 7782 \citep{2009AJ....137.3743G}.  The BS
 population in NGC 188 has a bi-modal period-eccentricity distribution.
@@
 mildly eccentric (i.e., $e \sim 0.1$) binary star system with an
-orbital period of $\sim$ 10 days hosting two roughly equal-mass BSs.  During a given binary-binary interaction, the probability
-that not one but two direct (MS-MS) collisions will occur is less than
-$10^{-2}$
+orbital period of $\sim$ 10 days hosting two roughly equal-mass BSs.
+During a given binary-binary interaction, the probability that not one
+but two direct (MS-MS) collisions will occur is less than $10^{-2}$
 \citep{1989AJ.....98..217L,2011MNRAS.410.2370L,2012MNRAS.425.2369L}.
 Plus, binaries with collision products typically have relatively long
-orbital periods \cite{2011Sci...334.1380F}. Dynamically, it is
+orbital periods \citep{2011Sci...334.1380F}. Dynamically, it is
 difficult to form a short-period binary composed of two collision
 products during a collisional interaction in a star cluster
-\citep{2011MNRAS.410.2370L,2011Sci...334.1380F}, \textit{and the timescale for exchanging another BS into a pre-existing BS-MS or BS-WD binary is much longer than the expected BS lifetime (see \citet{2011MNRAS.410.2370L} and the end of Section~\ref{sect:dyn} below)}.
-So, how did WOCS 7782 form?
+\citep{2011MNRAS.410.2370L,2011Sci...334.1380F}, \textbf{and the
+  timescale for exchanging another BS into a pre-existing BS-MS or
+  BS-WD binary is much longer than the expected BS lifetime (see
+  \citet{2011MNRAS.410.2370L} and the end of Section~\ref{sect:dyn}
+  below)}.  So, how did WOCS 7782 form?
 
@@
 %\simon{Why do you consider it important to mention that the orbit is hard, and for what environment did you consider this? - NL: Deleted.}  
-Note that the range of
-plotted orbital periods P$_{\rm in}$ corresponding to a contact state
-for the inner binary lies outside the range of plotted values for
-$P_{\rm in}$ (for components with radii of 1 R$_{\odot}$),
-since it does not contribute to constraining the outer orbital
-properties.  The thick horizontal solid red line shows the allowed
-range of outer semi-major axes, after folding in all of 
-the aforementioned criteria.  These constraints result in a rather narrow
+Note that the range of plotted orbital periods P$_{\rm in}$
+corresponding to a contact state for the inner binary lies outside the
+range of plotted values for $P_{\rm in}$ (for components with radii of
+1 R$_{\odot}$), since it does not contribute to constraining the outer
+orbital properties.  The thick horizontal solid red line shows the
+allowed range of outer semi-major axes, after folding in all of the
+aforementioned criteria.  These constraints result in a rather narrow
 range of initial conditions for the outer orbit, namely 2.2 $\times$
-10$^{2}$ days $\le$ P$_{\rm out}$ $\le$ 1.1 $\times$ 10$^3$ days, \textit{which also directly translates into constraints on the final outer tertiary orbit.}
+10$^{2}$ days $\le$ P$_{\rm out}$ $\le$ 1.1 $\times$ 10$^3$ days,
+\textbf{which also directly translates into constraints on the final
+  outer tertiary orbit.}
 %, for
@@
 
-\textbf{Finally, we compute the timescales for our hypothesized triple to undergo a direct interaction with another single or binary star.
-Using the same assumptions for the host cluster properties of NGC 188 outlined in Section 3.2 of \citet{2011MNRAS.410.2370L} (right-hand column), we find upon setting the single-triple (1+3) and binary-triple (2+3) timescales equal to the expected duration of the mass transfer phase (i.e., $\sim$ 1 Myr) critical outer orbital periods for triples of, respectively, 8.1 $\times$ 10$^8$ and 2.4 $\times$ 10$^9$ days.
-These critical outer tertiary orbital periods, which correspond to the times for a \textit{specific} triple to undergo an interaction, correspond to 1+3 and 2+3 interaction times that are much longer than the maximum predicted outer orbital period of the hypothesized white dwarf tertiary in our scenario.
-Hence, we do not expect the mass transfer process to be interrupted by either 1+3 and 2+3 interactions.}
+\textbf{Finally, we compute the timescales for our hypothesized triple
+  to undergo a direct interaction with another single or binary star.
+  Using the same assumptions for the host cluster properties of NGC
+  188 outlined in Section 3.2 of \citet{2011MNRAS.410.2370L}
+  (right-hand column), we find upon setting the single-triple (3+1)
+  and binary-triple (3+2) timescales equal to the expected duration of
+  the mass transfer phase (i.e., $\sim 1$\, Myr) critical outer
+  orbital periods for triples for $\gg 1$\,Myr.  These critical outer
+  tertiary orbital periods, which correspond to the times for a
+  specific triple to undergo an interaction, correspond to 3+1 and 3+2
+  interaction times that are much longer than the maximum predicted
+  outer orbital period of the hypothesized white dwarf tertiary in our
+  scenario.  We therefore do not expect the mass transfer process to
+  be interrupted by a dynamical interaction in the cluster center.}
 
@@
 \end{equation}
-we arrive at the top brown curve in
+we arrive at the top red curve in
 figure\,\ref{fig:tertiarymass_vs_size}. This curve provides a prediction for 
@@
 We adopt initial masses of $m_{\rm 1} = 1.1$ M$_{\rm \odot}$ and
-$m_{\rm 2} = 0.9$ M$_{\rm \odot}$ for the inner binary components, and
-between $m_{\rm 3} = 1.2$ and $m_{\rm 3} = 1.4$ M$_{\rm \odot}$ for
-the tertiary star.  We evolve the tertiary star using the MESA
-stellar-evolution code \cite{2011ApJS..192....3P} to a radius of about
-100\,\RSun\, and 150\,\RSun, at which point we assume it to overfill
-it's Roche lobe (see red \textbf{squares} in
-figure~\ref{fig:tertiarymass_vs_size}).  We perform calculations for an
-inner orbital separation of $a_{\rm in} = 0.10$\,au, $a_{\rm in} =
+$m_{\rm 2} = 0.7$ M$_{\rm \odot}$ or 0.9\,M$_{\rm \odot}$ for the
+inner binary components, and between $m_{\rm 3} = 1.2$ and $m_{\rm 3}
+= 1.4$ M$_{\rm \odot}$ for the tertiary star.  We evolve the tertiary
+star using the MESA stellar-evolution code \cite{2011ApJS..192....3P}
+to a radius of about 100\,\RSun\, and 150\,\RSun, at which point we
+assume it to overfill it's Roche lobe (see red \textbf{squares} in
+figure~\ref{fig:tertiarymass_vs_size}).  We perform calculations for
+an inner orbital separation of $a_{\rm in} = 0.10$\,au, $a_{\rm in} =
 0.15$\,au and $a_{\rm in} = 0.20$\,au.  In total we performed 12
@@
 mass is also lost through the third Lagrangian point (to the left of
-the inner binary), although it is hard to actually \textbf{quantify the amount
-of material lost}, becuase an appreciable fraction is expected to rain
-back onto the triple system.  One remaining question is how much mass
-is eventually ejected altogether from the triple system and is
+the inner binary), although it is hard to actually \textbf{quantify
+  the amount of material lost}, becuase an appreciable fraction may to
+rain back onto the triple system.  One remaining question is how much
+mass is eventually ejected altogether from the triple system and is
 therefore not accreted to any of the two inner stars. This value is
 hard to estimate from the simulations, but an accretion efficiency of
-$\apgt 0.6$ is necessary to make the scenario feasible. Over the time
+$\apgt 0.8$ is necessary to make the scenario feasible. Over the time
 scale for which we performed the calculations, this efficiency is
@@
 in a contact binary, that eventually may merge to form a single BS
-with a mass more than twice the turn off. The required evolution in
-order to explain the observed twin BS 7782 is indicated by the three
-black curves; the simulated path clearly deviates from these. We,
-therefore, argue that a 1.2\,\MSun\, donor has difficulty explaining
-the observed orbital separation of $\sim 0.13$\,au in BSS 7782.
+with a mass more than twice the turn off in orbit around a low-mass
+white dwarf. The required evolution in order to explain the observed
+twin BS 7782 is indicated by the three black curves; the simulated
+path clearly deviates from these. We, therefore, argue that a
+1.2\,\MSun\, donor has difficulty explaining the observed orbital
+separation of $\sim 0.13$\,au in BSS 7782.
 
@@
 
+  \textbf{ We further validated this statement by performing an
+    additional series of calculations in which we vary the mass of the
+    tertiary star in the initial triple from 0.5\,\MSun\, to
+    0.7\,\MSun\, and 0.9\,\MSun. In
+    fig.\,\ref{fig:mass_ratio_evolution_for_14MSun} we present the
+    evolution of the normalized mass ratio in these binaries. with
+    these calculations we demonstrate that a low-mass ratio initially
+    tends to evolve towards an equal mass ratio.  }
+
+  \begin{figure}[ht!]
+  \includegraphics[width=\columnwidth]{fig_mass_ratio_evolution_for_14MSun.pdf}
+  \caption{Evolution of the mass ratio for initial triples with an
+    inner orbital separation of 0.1\,au (orange dotted curve) and
+    0.2\,au (all other curves). The initial primary mass was
+    1.4\,\MSun\, overfilling it's Roche lobe at a radius of
+    100\,\RSun. the companion masses are $m_2= 0.9$\,\MSun\, and the
+    mass of the tertiary is indicated in the legend. The dotted black
+    line indicates the required mass-ratio evolution in order to
+    eventually reach an equal mass-ratio blue-straggler binary.
+\label{fig:mass_ratio_evolution_for_14MSun}}
+\end{figure}
+
 \item As a consequence of the above, the initially lower mass MS star
@@
     a debris disk was recently found around the white dwarf SDSS
-    J122859.93+104032.9 \cite{Manseretal2019}.
-  }
+    J122859.93+104032.9 \citep{Manseretal2019}.  }
 
@@
 eccentric orbit with a WD (the left-over core of the tertiary star).
-These ``imposter'' BS-WD binaries would in principle mimic what is
-expected theoretically for BSs formed from mass transfer in binary
-stars. If such a dynamical instability engages relatively late in the
+Such a close BS-WD binary would be hard to explain in another way.
+%% These ``imposter'' BS-WD binaries would in principle mimic what is
+%% expected theoretically for BSs formed from mass transfer in binary
+%% stars.
+If such a dynamical instability engages relatively late in the
 mass-tranfer phase, the white dwarf (maybe with a little left-over

### 2019-03-04 response_to_referees.txt
minor edits for submission

@@
 
-SIMON: I am happy to include these critical orbital periods in Figure
-2, but do you think we should (I would argue not), and should assume 1
-Myr for the duration of the MT process?  If I recall my stellar
-evolution, this corresponds roughly the timescale for the RGB phase,
-and I believe the AGB phase is much shorter.  As it is, I have added a
-paragraph to the end of Section 2, but it takes up space, and I think
-can ultimately be removed for that reason.
-
-NATHAN: I agree. What counts here is the thermal time scale of the
-Roche-lobe filling star, which is even shorter than 1Myr, but rather
-something like a few thens of thousands of years. Much shorter than
-any dynamical timescale in the cluster.
-
 2) The authors fix the amount of angular momentum lost per unit mass to eta=3.
@@
 though it's value is very important. We adopt the approach as
-advocated in Pols etal 1991 and Portegies Zwart 1995 with further
-suport by the analysis of Pols 2007 and Krticka etal 2011. We do not
+advocated in Pols et al 1991 and Portegies Zwart 1995 with further
+support from the analysis of Pols 2007 and Krticka etal 2011. We do not
 really know how much angular momentum is lost per unit mass in a
@@
 understand the subtleties of angular momentum transport in
-non-conservatively evolving binaries. In triples additional
+non-conservatively evolving binaries. In triples, additional
 complications are introduced by the third component. I fear that this
 process require much more study, which we think, would be really
-interesting to persue. However, for this manuscript we prefer to focus
+interesting to pursue. However, for this manuscript we prefer to focus
 on the initial conditions that are most likely to reproduce the
-observe twin blue straggler, and for that discussion we think that the
+observed twin blue straggler, and for that discussion we think that the
 1.2Msun donor does not lead to final parameters that are consistent
@@
 grows gradually to more equal masses, and that this effect is stronger
-when the initial inner mass ratio is smaller. Interestingly, the an
+when the initial inner mass ratio is smaller. Interestingly, the 
 initial mass-ratio of 0.9MSun/1.1MSun appears to be less favorable for
-growing to two equal mass stars, when when we start with alower
+growing two equal mass stars, when we start with a lower
 initial mass ratio, for example using 0.7MSun/1.1MSun. We may refine
@@
 binary is favored over an initially more equal mass binary. However,
-the observational constraints are insufficient to boltser this
-conclusions at this point.
+the observational constraints are insufficient to bolster this
+conclusion at this point.
 
@@
 
-SPZ/NL: fixed
+SPZ/NL: Fixed.
 
@@
 
-SPZ/NL:  Ow. that is rather sloppy. Apologies. fixed.
+SPZ/NL:  Ow. that is rather sloppy. Apologies. Fixed.
 
@@
 
-SPZ/NL: We ware not very clear about this.  the scenario only works
-for donors on the giant branch. Not on the Hertzsprung-gap and not on
-the AGB. We made that clear now in fig. 3 by painting these parts of
+SPZ/NL: Our apologies, since we were not very clear about this.  The scenario only works for donors on the giant branch; not on the Hertzsprung-gap and not on
+the AGB. We have now made that clear in fig. 3 by painting these parts of
 the curve indicating the stellar radius orange.
@@
 Important - "For clarity we assume both orbits, the inner as well as the outer, to have negligible eccentricity and low inclination." Might I suggest "For specificity"?
-
-Yes, we do that now.
 
@@
 which part of parameter space this scenario works. This may be very
-interestsing, but for a future paper.
+interesting, but for a future paper.
 
@@
 toward a mass ratio of unity. We added an explanation to the text to
-express and motivate our rather explicite choice of parameters.
+express and motivate our rather explicit choice of parameters.
 
@@
 though it's value is very important. We adopt the approach as
-advocated in Pols etal 1991 and Portegies Zwart 1995 with further
-suport by the analysis of Pols 2007 and Krticka etal 2011. We do not
+advocated in Pols et al 1991 and Portegies Zwart 1995 with further
+support coming from the analysis of Pols 2007 and Krticka etal 2011. We do not
 really know how much angular momentum is lost per unit mass in a
@@
 Tidal effects during mass tran[s]fer have probably circularized the orbit, although some slight
-SPZ?NL:  Fixed.
+
+SPZ/NL:  Fixed.
 
@@
 
-SPZ/NL: we leave out the remark about the low eccentricity of the outer orbit.
+SPZ/NL: We have left out the remark about the low eccentricity of the outer orbit.
 
@@
 
-SPZ/NL: We removed figure 4. the referee is right that it does not really add much to the paper.
-The "black bullets to the right" was a typo, left over after meny iterations of refinement.
+SPZ/NL: We removed figure 4. The referee is right that it does not really add much to the paper.  The "black bullets to the right" was a typo, left over after many iterations of refinement.
 
@@
 quanti[fy] the amount of material los[s],
+
 SPZ/NL:  Fixed.
@@
 
-SPZ/NL: We think that abstract maybe a bit controversial in comparison
+SPZ/NL: We think that the abstract maybe a bit controversial in comparison
 with other abstracts, but we think that it covers the content of the

### 2019-03-25 BSS7782.tex
minor edits for submission
some update

@@
 tertiary companion on to the inner binary via a circumbinary disk.  We
-apply this scenario to the observed double BS binary WOCS 7782 in the
-old open cluster NGC 188, and show that its observed properties
+apply this scenario to the observed double BS-binary WOCS~7782 in the
+old open cluster NGC~188, and show that its observed properties
 \textbf{can be} reproduced within the context of the proposed model.
@@
 
-N.W.C.L. acknowledges support from a Kalbfleisch Fellowship at the
+The authors kindly thank two anonymous reviewers for their considerable insight and 
+suggestions for improvement.  N.W.C.L. acknowledges support from a Kalbfleisch Fellowship at the
 American Museum of Natural History.  SPZ would like to thank Norm

### 2019-03-25 BSS7782_prev.tex
added previous version to the git.

--- 2019-03-25 BSS7782.tex
@@
 old open cluster NGC~188, and show that its observed properties
-\textbf{can be} reproduced within the context of the proposed model.
+can be reproduced within the context of the proposed model.
 Based on this model, we predict the following properties for twin BSs:
@@
 = 1.1$ M$_{\odot}$ and $m_{\rm 2} = 0.7$ to $0.9$M$_{\odot}$ and an
-outer tertiary mass of $m_{\rm 3} = 1.4$ M$_{\odot}$.  \textbf{(2)}
+outer tertiary mass of $m_{\rm 3} = 1.4$ M$_{\odot}$.  (2)
 After Roche-lobe overflow, the outer star turns into a white dwarf
@@
 whether the donor started to overflow its Roche lobe on, respectively,
-the red giant or {\bf early} asymptotic giant branch.  (5) Relative to
+the red giant or early asymptotic giant branch.  (5) Relative to
 old dense clusters with high-velocity dispersions, twin BSs in close
@@
 
-\textbf{Most} blue straggler stars are brighter and bluer than the main-sequence
+Most blue straggler stars are brighter and bluer than the main-sequence
 (MS) turn-off in a cluster colour-magnitude diagram
@@
 \citep[e.g.][]{1975AJ.....80..809H,1997A&A...328..130P,2007ApJ...661..210L,2013MNRAS.428..897L,2013MNRAS.429.1221H, 2019A&A...621L..10P}.
-\textbf{The first mechanism predicts BSs in binaries with WD companions,
+The first mechanism predicts BSs in binaries with WD companions,
 whereas the second predicts MS companions in a wide and eccentric
-binary.}  Other possible, albeit related, formation mechanisms include
+binary.  Other possible, albeit related, formation mechanisms include
 mergers of close MS-MS binaries \citep{2019A&A...621L..10P}, and
@@
 induced by Lidov-Kozai oscillations coupled with tidal damping
-\citep[e.g.][]{2009ApJ...697.1048P}.  \textbf{The latter predicts no binary companion, whereas the former predicts a MS companion in a wide binary.}
+\citep[e.g.][]{2009ApJ...697.1048P}.  The latter predicts no binary companion, whereas the former predicts a MS companion in a wide binary.
 
@@
 products during a collisional interaction in a star cluster
-\citep{2011MNRAS.410.2370L,2011Sci...334.1380F}, \textbf{and the
-  timescale for exchanging another BS into a pre-existing BS-MS or
-  BS-WD binary is much longer than the expected BS lifetime (see
+\citep{2011MNRAS.410.2370L,2011Sci...334.1380F}, and the timescale for
+exchanging another BS into a pre-existing BS-MS or BS-WD binary is
+much longer than the expected BS lifetime (see
 \citet{2011MNRAS.410.2370L} and the end of Section~\ref{sect:dyn}
-  below)}.  So, how did WOCS 7782 form?
+below).  So, how did WOCS 7782 form?
 
@@
 $m_3$. The inner and outer binary orbital semi-major axes are denoted
-a$_{\rm in}$ and a$_{\rm out}$, respectively.  \textbf{For
-  specificty,} we assume both orbits, the inner as well as the outer,
-\textbf{to be circular and in the same plane, which minimizes chaotic
-  effects during the mass transfer process, facilitates more stable
-  mass transfer and ultimately allows us to simulate our target system
-  for longer while also maximizing the amount of mass transferred}.
-These assumptions are also supported by the population of observed
-low-mass triples \citep{2010yCat..73890925T,2018ApJ...854...44M}.
-This initial configuration for our assumed formation scenario for WOCS
-7782, described below, is depicted in figure~\ref{fig:fig1}.
+a$_{\rm in}$ and a$_{\rm out}$, respectively.  For specificty, we
+assume both orbits, the inner as well as the outer, to be circular and
+in the same plane, which minimizes chaotic effects during the mass
+transfer process, facilitates more stable mass transfer and ultimately
+allows us to simulate our target system for longer while also
+maximizing the amount of mass transferred.  These assumptions are also
+supported by the population of observed low-mass triples
+\citep{2010yCat..73890925T,2018ApJ...854...44M}.  This initial
+configuration for our assumed formation scenario for WOCS 7782,
+described below, is depicted in figure~\ref{fig:fig1}.
 
@@
 sufficiently small that the tertiary star is filling its Roche lobe
-and transfers mass to the inner binary before it {\bf reaches} the asymptotic
+and transfers mass to the inner binary before it reaches the asymptotic
 giant branch. We constrain the inner orbit by requiring the triple
@@
 Figure~\ref{fig:fig2} shows the parameter space in the P$_{\rm
-  out}$-P$_{\rm in}$-plane for WOCS 7782.  \textbf{Here we adopted,
-  for clarity,} initial component masses of $m_{\rm 1} = 1.1$ M$_{\rm
-  \odot}$ and $m_{\rm 2} = 0.9$ M$_{\rm \odot}$ for the inner binary
-components, and $m_{\rm 3} = 1.4 $M$_{\rm \odot}$ for the outer
-tertiary.  \textbf{The scenario worked out is general, but we opt for
-  these specific parameters because they appear to naturally result in
-  a system with parameters similar to WOCS 7782.}  We compare the
-circularization radius to the semi-major axis of the inner binary, for
-which we require $a_{\rm c} > a_{\rm in}$, after folding in all
-constraints from the requirements for dynamical stability (listed in
-the caption of figure~\ref{fig:fig2}), and the assumption of an outer
-tertiary that is Roche lobe-filling \textbf{(see
-  \citet{2014MNRAS.438.1909D} for more details)}.
+  out}$-P$_{\rm in}$-plane for WOCS 7782.  Here we adopted, for
+clarity, initial component masses of $m_{\rm 1} = 1.1$ M$_{\rm \odot}$
+and $m_{\rm 2} = 0.9$ M$_{\rm \odot}$ for the inner binary components,
+and $m_{\rm 3} = 1.4 $M$_{\rm \odot}$ for the outer tertiary.  The
+scenario worked out is general, but we opt for these specific
+parameters because they appear to naturally result in a system with
+parameters similar to WOCS 7782.  We compare the circularization
+radius to the semi-major axis of the inner binary, for which we
+require $a_{\rm c} > a_{\rm in}$, after folding in all constraints
+from the requirements for dynamical stability (listed in the caption
+of figure~\ref{fig:fig2}), and the assumption of an outer tertiary
+that is Roche lobe-filling (see \citet{2014MNRAS.438.1909D} for more
+details).
 %\simon{Why do you consider it important to mention that the orbit is hard, and for what environment did you consider this? - NL: Deleted.}  
@@
 10$^{2}$ days $\le$ P$_{\rm out}$ $\le$ 1.1 $\times$ 10$^3$ days,
-\textbf{which also directly translates into constraints on the final
-  outer tertiary orbit.}
+which also directly translates into constraints on the final
+  outer tertiary orbit.
 %, for
@@
 
-\textbf{Finally, we compute the timescales for our hypothesized triple
-  to undergo a direct interaction with another single or binary star.
-  Using the same assumptions for the host cluster properties of NGC
-  188 outlined in Section 3.2 of \citet{2011MNRAS.410.2370L}
-  (right-hand column), we find upon setting the single-triple (3+1)
-  and binary-triple (3+2) timescales equal to the expected duration of
-  the mass transfer phase (i.e., $\sim 1$\, Myr) critical outer
-  orbital periods for triples for $\gg 1$\,Myr.  These critical outer
-  tertiary orbital periods, which correspond to the times for a
-  specific triple to undergo an interaction, correspond to 3+1 and 3+2
-  interaction times that are much longer than the maximum predicted
-  outer orbital period of the hypothesized white dwarf tertiary in our
-  scenario.  We therefore do not expect the mass transfer process to
-  be interrupted by a dynamical interaction in the cluster center.}
+Finally, we compute the timescales for our hypothesized triple to
+undergo a direct interaction with another single or binary star.
+Using the same assumptions for the host cluster properties of NGC 188
+outlined in Section 3.2 of \citet{2011MNRAS.410.2370L} (right-hand
+column), we find upon setting the single-triple (3+1) and
+binary-triple (3+2) timescales equal to the expected duration of the
+mass transfer phase (i.e., $\sim 1$\, Myr) critical outer orbital
+periods for triples for $\gg 1$\,Myr.  These critical outer tertiary
+orbital periods, which correspond to the times for a specific triple
+to undergo an interaction, correspond to 3+1 and 3+2 interaction times
+that are much longer than the maximum predicted outer orbital period
+of the hypothesized white dwarf tertiary in our scenario.  We
+therefore do not expect the mass transfer process to be interrupted by
+a dynamical interaction in the cluster center.
 
@@
   \caption{Giant radius as a function of the mass of the core of the
-    Roche-lobe filling outer star (dark blue curve).  {\bf The first
-      and last parts of this curve are orange to indicate that the
-      star at these masses and radii is on the Hertzsprung-gap (to the
-      left) or after core helium burning stage (to the right).  Only
-      when the donor is on the giant branch (dark blue) Roche-lobe
-      overflow will lead to a binary blue straggler.}  Here we adopt a
-    donor mass of 1.4\,\MSun, but for an 1.2\,\MSun\, the donor the
-    curve is quite similar (see dotted dark-blue curve).  The red
-    squares in the curve show the parameters for which we performed
-    more detailed gravitational-hydrodynamical simulations (see
-    \S\,\ref{sims}).  The horizontal dashed line shows the orbital
-    separation of the observed twin BS 7782.  The initial triple in
-    which it possibly formed must at least have been dynamically
-    stable. The minimal orbital separation for the inner binary for
-    which the triple is stable is given by the lower green coloured
-    curve.  Donors which are smaller than about 100\,\RSun\,
-    (light-green curve indicated with a$_{\rm stable}$) result in a
-    dynamically unstable triple. The minimal core mass associated with
-    a stable triple is then indicated by the left-most vertical dotted
-    line.  The orbital separation at which the donor star overfills
-    its Roche lobe is indicated with the light-blue curve. The top
-    curve (brown) shows an estimate of the final orbital separation of
-    the outer star, and therefore of the final orbit of the WD around
-    the inner twin BSs.  For core masses $\apgt 0.5$\,\MSun\, the
-    final orbital separation, after mass transfer, is smaller than the
-    initial orbit.  Here we adopted an initial inner binary mass of
-    (1.0+0.9)\,\MSun\, and a final twin BS mass of (1.4+1.4)\,\MSun.
+    Roche-lobe filling outer star (dark blue curve).  The first and
+    last parts of this curve are orange to indicate that the star at
+    these masses and radii is on the Hertzsprung-gap (to the left) or
+    after core helium burning stage (to the right).  Only when the
+    donor is on the giant branch (dark blue) Roche-lobe overflow will
+    lead to a binary blue straggler.  Here we adopt a donor mass of
+    1.4\,\MSun, but for an 1.2\,\MSun\, the donor the curve is quite
+    similar (see dotted dark-blue curve).  The red squares in the
+    curve show the parameters for which we performed more detailed
+    gravitational-hydrodynamical simulations (see \S\,\ref{sims}).
+    The horizontal dashed line shows the orbital separation of the
+    observed twin BS 7782.  The initial triple in which it possibly
+    formed must at least have been dynamically stable. The minimal
+    orbital separation for the inner binary for which the triple is
+    stable is given by the lower green coloured curve.  Donors which
+    are smaller than about 100\,\RSun\, (light-green curve indicated
+    with a$_{\rm stable}$) result in a dynamically unstable
+    triple. The minimal core mass associated with a stable triple is
+    then indicated by the left-most vertical dotted line.  The orbital
+    separation at which the donor star overfills its Roche lobe is
+    indicated with the light-blue curve. The top curve (brown) shows
+    an estimate of the final orbital separation of the outer star, and
+    therefore of the final orbit of the WD around the inner twin BSs.
+    For core masses $\apgt 0.5$\,\MSun\, the final orbital separation,
+    after mass transfer, is smaller than the initial orbit.  Here we
+    adopted an initial inner binary mass of (1.0+0.9)\,\MSun\, and a
+    final twin BS mass of (1.4+1.4)\,\MSun.
 \label{fig:tertiarymass_vs_size}}
@@
 accretion ($m'_{\rm in}$) and the amount of angular momentum lost per
-unit mass $\eta \simeq 3$.  {\bf The value of $\eta = 3$ was derived
+unit mass $\eta \simeq 3$.  The value of $\eta = 3$ was derived
   in \cite{1991A&A...241..419P,1995A&A...296..691P} by matching the
@@
   constrained in \cite{2007ASPC..367..387P} to understand the mass
-  transfer in the 100-day orbital period binary V379 Cep.}  Adopting
+  transfer in the 100-day orbital period binary V379 Cep.  Adopting
 the relation between the orbital separation before mass transfer ($a$)
@@
 to a radius of about 100\,\RSun\, and 150\,\RSun, at which point we
-assume it to overfill it's Roche lobe (see red \textbf{squares} in
+assume it to overfill it's Roche lobe (see red squares in
 figure~\ref{fig:tertiarymass_vs_size}).  We perform calculations for
@@
 
-To test the \textbf{hypothesis that the} secondary in the inner binary
+To test the hypothesis that the secondary in the inner binary
 accretes more effectively than the primary star and to measure the
@@
 gravity and the hydrodynamical effects of the triple into account.
-The results of \textbf{one of} these simulations (1091 days after
+The results of one of these simulations (1091 days after
 the onset of mass transfer) is presented in
@@
 mass is also lost through the third Lagrangian point (to the left of
-the inner binary), although it is hard to actually \textbf{quantify
-  the amount of material lost}, becuase an appreciable fraction may to
+the inner binary), although it is hard to actually quantify
+  the amount of material lost, becuase an appreciable fraction may to
 rain back onto the triple system.  One remaining question is how much
@@
     core particle of $\sim 0.4$\,\MSun (black bullet in the middle of
-    the right-most yellow blob). The inner binary \textbf{(to the
-      left)} is represented by the yellow and red bullets for,
+    the right-most yellow blob). The inner binary (to the
+      left) is represented by the yellow and red bullets for,
     respectively, the 1.1\,\MSun\, primary and 0.9\,\MSun\, secondary
@@
 inner binary matches better with the anticipated evolution
-\textbf{needed to reproduce the observed parameters of WOCS 7782.}  A
+needed to reproduce the observed parameters of WOCS 7782.  A
 more massive donor may therefore have a lower accretion efficiency
@@
 The orbit of the inner binary expands in these cases as a result of
-accretion onto the inner two stars. \textbf{In all} three cases for the
+accretion onto the inner two stars. In all three cases for the
 1.4\,\MSun\, donor presented in
@@
 secondary star with respect to the argument of pericenter of the inner
-orbit.  \textbf{This supports our naive prediction that the spin
+orbit.  This supports our naive prediction that the spin
   angular momenta of the two stars in the inner binary should be more
   or less aligned post-mass transfer, due to the non-negligible amount
-  of mass accreted.} By the end of the simulations the spin of the
+  of mass accreted. By the end of the simulations the spin of the
 primary is about 50.5 rotations per day, and 41.5 rotations per day
-for the secondary star.  \textbf{Such high spin rates immediately
+for the secondary star.  Such high spin rates immediately
   post-mass transfer are supported by other work (see, for example,
@@
   down due to, for example, magnetic braking, bringing them closer to
-  the actually observed spin rates.}
+  the actually observed spin rates.
 %% But by this time both stars have accreted
@@
 old OC NGC 188.  The proposed scenario involves mass transfer from an
-evolved outer tertiary companion\textbf{. Part} of this mass is accreted by the
-inner binary via a circumbinary disk\textbf{, while} the rest escapes through the
+evolved outer tertiary companion. Part of this mass is accreted by the
+inner binary via a circumbinary disk, while the rest escapes through the
 second and third Lagrangian points in the potential of the triple
@@
   M$_{\odot}$ and an initial outer tertiary mass of $m_{\rm 3} = 1.4
-  $M$_{\odot}$. \textbf{The final orbital period of the white dwarf
+  $M$_{\odot}$. The final orbital period of the white dwarf
     around the binary blue straggler should exceeds the initiall
-    orbit, but be smaller than $\sim 4100$\,days.}
+    orbit, but be smaller than $\sim 4100$\,days.
 
@@
 
-  \textbf{ We further validated this statement by performing an
+  We further validated this statement by performing an
     additional series of calculations in which we vary the mass of the
@@
     these calculations we demonstrate that a low-mass ratio initially
-    tends to evolve towards an equal mass ratio.  }
+    tends to evolve towards an equal mass ratio.
 
@@
   AGB star the enrichment will be mostly in s-process elements.
-  \textbf{Note that part of the mass liberated from the triple system
+  Note that part of the mass liberated from the triple system
     through the second and third Lagrangian points may eventually be
@@
     a debris disk was recently found around the white dwarf SDSS
-    J122859.93+104032.9 \citep{Manseretal2019}.  }
+    J122859.93+104032.9 \citep{Manseretal2019}.
 
@@
   proposed here to be more frequent in younger clusters with ages
-  $\lesssim$ 4-6 Gyr.  This is because \textbf{stars in clusters} with a MS turn-off
+  $\lesssim$ 4-6 Gyr.  This is because stars in clusters with a MS turn-off
   mass $\lesssim$ 1.2 M$_{\odot}$ have convective envelopes

### 2019-04-01 BSS7782.tex
updates for referee report #3

@@
 
-We propose a formation mechanism for twin blue stragglers (BSs) in
-compact binaries that involves mass transfer from an evolved outer
-tertiary companion on to the inner binary via a circumbinary disk.  We
-apply this scenario to the observed double BS-binary WOCS~7782 in the
-old open cluster NGC~188, and show that its observed properties
-\textbf{can be} reproduced within the context of the proposed model.
-Based on this model, we predict the following properties for twin BSs:
-(1) For the outer tertiary orbit, the initial orbital period should
-lie between 220 days $\lesssim$ P$_{\rm out}$ $\lesssim$ 1100 days,
-assuming initial masses for the inner binary components of $m_{\rm 1}
-= 1.1$ M$_{\odot}$ and $m_{\rm 2} = 0.7$ to $0.9$M$_{\odot}$ and an
-outer tertiary mass of $m_{\rm 3} = 1.4$ M$_{\odot}$.  \textbf{(2)}
-After Roche-lobe overflow, the outer star turns into a white dwarf
-(WD) of mass 0.43 to 0.54\,\MSun. There is a correlation between the
-mass of this WD and the outer orbital period: more massive WDs will be
-on wider orbits.  (3) The rotational axes of both BSs will be aligned
-with each other and the orbital plane of the outer tertiary WD. (4)
-The BSs will have roughly equal masses, independent of their initial
-masses (since the lower mass star accretes the most).  The dominant
-accretor should, therefore, be enriched more effectively by the
-accreted material.  As a result, one of the BSs will appear to be more
-enriched by either He, C and O or by s-process elements, depending on
-whether the donor started to overflow its Roche lobe on, respectively,
-the red giant or {\bf early} asymptotic giant branch.  (5) Relative to
-old dense clusters with high-velocity dispersions, twin BSs in close
-binaries formed from the proposed mechanism should be more frequent in
-the Galactic field and younger open clusters with ages $\lesssim$ 4-6
-Gyr, since then the donor will have a radiative envelope. (6) the
-orbit of the binary BS will have a small semi-major axis (typically
-$\aplt 0.3$\,au) and be close to circular ($e \aplt 0.1$).
+We propose that twin blue stragglers (BSs) in compact binaries evolve
+through a phase of mass transfer from a giant outer tertiary companion
+on to the inner binary.  We apply this scenario to the twin-BS binary
+WOCS~ID~7782 in the old open cluster NGC~188.  This binary has two
+comparable-mass main-sequence stars in an almost circular ($e \aplt
+0.1$) orbit of $\aplt 10$\,days.  Our theoretical arguments are
+supported by simulations of an inner binary that accretes from a outer
+Roche-lobe overfilling star using the Astrophysicsal Multipurpose
+Software Environment. At least 80\,\% of the mass liberated by the
+tertiary star goes through a circum-binary disk before it is accreted
+by in the inner binary, causing the two stars to turn into blue
+stragglers.  In order to acquire relatively stable phase of mass
+transfer the donor should be about 1.4\,\MSun\, and over-fill it's
+Roche lobe before ascending the asymptotic giant-branch.  The outer
+star eventually turns into a 0.43 to 0.54\,\MSun\, white dwarf in a
+relatively wide $\apgt 5.8\,yr$ orbit.  Although, the scenario is
+generic, it requires some fine-tuning to achieve parameters comparable
+to the observed twin WOCS~ID~7782.  This system is best reproduced
+when starting with a $m_{\rm 3} = 1.4$ M$_{\odot}$ outer star in an
+220 to 1100~day orbit around an inner binary composed of an
+1.1\,\,MSun\, primary and a $m_{\rm 2}=0.7$ to $0.9$M$_{\odot}$
+secondary star in an 8.6 to 24\,day orbit.  Based on our simulations
+and theoretical arguments we predict that twin blue-stragglers that
+formed through mass transfer from a Roche-lobe over-filling outer star
+are generally comparable in mass, have aligned spins which again are
+algined with the orbit of the tertiary white-dwarf star.  If the two
+inner stars ware initially unequal in mass the less massive star will
+have accreted more material from the tertiary star, which therefore is
+more enhanced in CNO-processed material.
 
@@
 parameters that naturally lead to twin BSs with orbital parameters
-similar to the 7782 system.  We summarize and discuss the implications
-of our results for compact double BS binaries and, more generally,
-mass transfer in stellar triples in Section~\ref{sect:discussion}.
+similar to the 7782 system, without exhaustively covering parameter
+space.  We summarize and discuss the implications of our results for
+compact double BS binaries and, more generally, mass transfer in
+stellar triples in Section~\ref{sect:discussion}.
 
@@
   \caption{Giant radius as a function of the mass of the core of the
-    Roche-lobe filling outer star (dark blue curve).  {\bf The first
-      and last parts of this curve are orange to indicate that the
-      star at these masses and radii is on the Hertzsprung-gap (to the
-      left) or after core helium burning stage (to the right).  Only
-      when the donor is on the giant branch (dark blue) Roche-lobe
-      overflow will lead to a binary blue straggler.}  Here we adopt a
-    donor mass of 1.4\,\MSun, but for an 1.2\,\MSun\, the donor the
-    curve is quite similar (see dotted dark-blue curve).  The red
-    squares in the curve show the parameters for which we performed
-    more detailed gravitational-hydrodynamical simulations (see
-    \S\,\ref{sims}).  The horizontal dashed line shows the orbital
-    separation of the observed twin BS 7782.  The initial triple in
-    which it possibly formed must at least have been dynamically
-    stable. The minimal orbital separation for the inner binary for
-    which the triple is stable is given by the lower green coloured
-    curve.  Donors which are smaller than about 100\,\RSun\,
-    (light-green curve indicated with a$_{\rm stable}$) result in a
-    dynamically unstable triple. The minimal core mass associated with
-    a stable triple is then indicated by the left-most vertical dotted
-    line.  The orbital separation at which the donor star overfills
-    its Roche lobe is indicated with the light-blue curve. The top
-    curve (brown) shows an estimate of the final orbital separation of
-    the outer star, and therefore of the final orbit of the WD around
-    the inner twin BSs.  For core masses $\apgt 0.5$\,\MSun\, the
-    final orbital separation, after mass transfer, is smaller than the
-    initial orbit.  Here we adopted an initial inner binary mass of
-    (1.0+0.9)\,\MSun\, and a final twin BS mass of (1.4+1.4)\,\MSun.
+    Roche-lobe filling outer star (dark blue curve).  The first and
+    last parts of this curve are orange to indicate that the star at
+    these masses and radii is on the Hertzsprung-gap (to the left) or
+    after core helium burning stage (to the right).  When the
+    donor is on the giant branch (dark blue) Roche-lobe overflow will
+    lead to a binary blue straggler.  Here we adopt a donor mass of
+    1.4\,\MSun, but for an 1.2\,\MSun\, the donor the curve is quite
+    similar (see dotted dark-blue curve).  The red squares in the
+    curve show the parameters for which we performed more detailed
+    gravitational-hydrodynamical simulations (see \S\,\ref{sims}).
+    The horizontal dashed line shows the orbital separation of the
+    observed twin BS 7782.  The initial triple in which it possibly
+    formed must at least have been dynamically stable. The minimal
+    orbital separation for the inner binary for which the triple is
+    stable is given by the lower green coloured curve.  Donors which
+    are smaller than about 100\,\RSun\, (light-green curve indicated
+    with a$_{\rm stable}$) result in a dynamically unstable
+    triple. The minimal core mass associated with a stable triple is
+    then indicated by the left-most vertical dotted line.  The orbital
+    separation at which the donor star overfills its Roche lobe is
+    indicated with the light-blue curve. The top curve (brown) shows
+    an estimate of the final orbital separation of the outer star, and
+    therefore of the final orbit of the WD around the inner twin BSs.
+    For core masses $\apgt 0.5$\,\MSun\, the final orbital separation,
+    after mass transfer, is smaller than the initial orbit.  Here we
+    adopted an initial inner binary mass of (1.0+0.9)\,\MSun\, and a
+    final twin BS mass of (1.4+1.4)\,\MSun.
 \label{fig:tertiarymass_vs_size}}
@@
 mass is also lost through the third Lagrangian point (to the left of
-the inner binary), although it is hard to actually \textbf{quantify
-  the amount of material lost}, becuase an appreciable fraction may to
-rain back onto the triple system.  One remaining question is how much
-mass is eventually ejected altogether from the triple system and is
-therefore not accreted to any of the two inner stars. This value is
-hard to estimate from the simulations, but an accretion efficiency of
-$\apgt 0.8$ is necessary to make the scenario feasible. Over the time
-scale for which we performed the calculations, this efficiency is
-reached, but it is not clear how the system responds at later stages.
+the inner binary), although it is hard to actually quantify the amount
+of material lost, becuase an appreciable fraction may to rain back
+onto the triple system.  One remaining question is how much mass is
+eventually ejected altogether from the triple system and is therefore
+not accreted to any of the two inner stars.  In our simulations the
+accretion efficiency on the inner binary has to exceeds $\sim 80$\,\%
+for the two blue straggers to reach masses comparable to those
+observed in WOCS~ID~7782.  Over the relatively short time scale for
+which we performed the calculations this efficiency is achieved, but
+it is not clear how the system responds at later stages.
 
@@
 secondary star with respect to the argument of pericenter of the inner
-orbit.  \textbf{This supports our naive prediction that the spin
-  angular momenta of the two stars in the inner binary should be more
-  or less aligned post-mass transfer, due to the non-negligible amount
-  of mass accreted.} By the end of the simulations the spin of the
-primary is about 50.5 rotations per day, and 41.5 rotations per day
-for the secondary star.  \textbf{Such high spin rates immediately
-  post-mass transfer are supported by other work (see, for example,
-  \citet{2014MNRAS.438.1909D}), which could then subsequently spin
-  down due to, for example, magnetic braking, bringing them closer to
-  the actually observed spin rates.}
+orbit.  This supports our naive prediction that the spin angular
+momenta of the two stars in the inner binary should be more or less
+aligned post-mass transfer, due to the non-negligible amount of mass
+accreted. By the end of the simulations the spin of the primary is
+about 50.5 rotations per day, and 41.5 rotations per day for the
+secondary star.  Such high spin rates immediately post-mass transfer
+are supported by other work (see, for example,
+\citet{2014MNRAS.438.1909D}), but the twin blue stragglers in
+WOCS~ID~7782 are not observed to be spinning that fast
+\cite{2018ApJ...869L..29L}.  Rapdily spinning stars may slow due to,
+for example, magnetic braking, bringing them closer to the actually
+observed spin rates \cite{2018arXiv181202181L}.
+
 %% But by this time both stars have accreted
@@
   M$_{\odot}$ and an initial outer tertiary mass of $m_{\rm 3} = 1.4
-  $M$_{\odot}$. \textbf{The final orbital period of the white dwarf
-    around the binary blue straggler should exceeds the initiall
-    orbit, but be smaller than $\sim 4100$\,days.}
+  $M$_{\odot}$. The final orbital period of the white dwarf
+    around the binary blue straggler should exceeds the initial
+    orbit, but be smaller than $\sim 4100$\,days.
 
@@
 \end{figure}
-
-\item As a consequence of the above, the initially lower mass MS star
-  should accrete the most, and therefore be more enriched by accreted
-  material.  This could be observable in the surface layers of a
-  radiative star.  If the donor is an RGB star, the accretors will be
-  enriched in mostly carbon, oxygen and helium, but if the donor is an
-  AGB star the enrichment will be mostly in s-process elements.
-  \textbf{Note that part of the mass liberated from the triple system
-    through the second and third Lagrangian points may eventually be
-    accreted back onto the system.  This could also have interesting
-    consequences for the enrichment of the low-mass white dwarf.  Such
-    a debris disk was recently found around the white dwarf SDSS
-    J122859.93+104032.9 \citep{Manseretal2019}.  }
-
-\item We expect twin BSs in compact binaries formed from the mechanism
-  proposed here to be more frequent in younger clusters with ages
-  $\lesssim$ 4-6 Gyr.  This is because \textbf{stars in clusters} with a MS turn-off
-  mass $\lesssim$ 1.2 M$_{\odot}$ have convective envelopes
-  \citep[e.g.][]{1991ApJS...76...55I,2009pfer.book.....M}, and a
-  radiative envelope for the donor in a mass transferring binary
-  ensures stable accretion on to the accretor.
 

### 2019-04-08 BSS7782.tex
updated

@@
 0.1$) orbit of $\aplt 10$\,days.  Our theoretical arguments are
-supported by simulations of an inner binary that accretes from a outer
-Roche-lobe overfilling star using the Astrophysicsal Multipurpose
+supported by simulations of an inner binary that accretes from an outer
+Roche-lobe overfilling star using the Astrophysical Multipurpose
 Software Environment. At least 80\,\% of the mass liberated by the
@@
 by in the inner binary, causing the two stars to turn into blue
-stragglers.  In order to acquire relatively stable phase of mass
+stragglers.  In order to acquire a relatively stable phase of mass
 transfer the donor should be about 1.4\,\MSun\, and over-fill it's
@@
 220 to 1100~day orbit around an inner binary composed of an
-1.1\,\,MSun\, primary and a $m_{\rm 2}=0.7$ to $0.9$M$_{\odot}$
+1.1\,\MSun\, primary and a $m_{\rm 2}=0.7$ to $0.9$M$_{\odot}$
 secondary star in an 8.6 to 24\,day orbit.  Based on our simulations
-and theoretical arguments we predict that twin blue-stragglers that
-formed through mass transfer from a Roche-lobe over-filling outer star
-are generally comparable in mass, have aligned spins which again are
-algined with the orbit of the tertiary white-dwarf star.  If the two
-inner stars ware initially unequal in mass the less massive star will
-have accreted more material from the tertiary star, which therefore is
+and theoretical arguments we predict that twin BSs that
+formed through mass transfer from a Roche-lobe over-filling outer tertiary
+are generally comparable in mass and have aligned spins, which are in turn 
+aligned with the orbit of the tertiary white-dwarf star.  If the two
+inner stars were initially unequal in mass the less massive star will
+have accreted more material from the tertiary star, and should therefore be 
 more enhanced in CNO-processed material.
@@
 is a result of the evolution along the horizontal branch, where the
-core of the star continues to grow but the radius actually shrinks.
+core of the star continues to grow but the stellar radius actually shrinks.
 Roche-lobe overflow in this phase is not expected to happen, because
@@
 the inner two stars of 1.4\,\MSun, which is consistent with the
-observed twin BS 7782. In our simulations the eccentricity of the
+observed twin BS WOCS 7782. In our simulations the eccentricity of the
 inner binary grows to about $e \simeq 0.0028$.
@@
 WOCS~ID~7782 are not observed to be spinning that fast
-\cite{2018ApJ...869L..29L}.  Rapdily spinning stars may slow due to,
+\cite{2018ApJ...869L..29L}.  Rapidly spinning stars may slow due to,
 for example, magnetic braking, bringing them closer to the actually
@@
   $M$_{\odot}$. The final orbital period of the white dwarf
-    around the binary blue straggler should exceeds the initial
+    around the binary blue straggler should exceed the initial
     orbit, but be smaller than $\sim 4100$\,days.
@@
 
-  We further validated this statement by performing an
-    additional series of calculations in which we vary the mass of the
-    tertiary star in the initial triple from 0.5\,\MSun\, to
-    0.7\,\MSun\, and 0.9\,\MSun. In
-    fig.\,\ref{fig:mass_ratio_evolution_for_14MSun} we present the
-    evolution of the normalized mass ratio in these binaries. with
-    these calculations we demonstrate that a low-mass ratio initially
-    tends to evolve towards an equal mass ratio.
+    We further validated this statement by performing an additional
+    series of calculations in which we vary the mass of the tertiary
+    star in the initial triple from 0.5\,\MSun\, to 0.7\,\MSun\, and
+    0.9\,\MSun. In fig.\,\ref{fig:mass_ratio_evolution_for_14MSun} we
+    present the evolution of the normalized mass ratio in these
+    binaries. With these calculations we demonstrate that a low-mass
+    ratio initially tends to evolve towards an equal mass ratio.
 
@@
     1.4\,\MSun\, overfilling it's Roche lobe at a radius of
-    100\,\RSun. the companion masses are $m_2= 0.9$\,\MSun\, and the
-    mass of the tertiary is indicated in the legend. The dotted black
+    100\,\RSun. The companion masses are $m_2= 0.9$\,\MSun\, and the
+    mass of the tertiary are indicated in the legend. The dotted black
     line indicates the required mass-ratio evolution in order to
-    eventually reach an equal mass-ratio blue-straggler binary.
+    eventually reach an equal mass-ratio blue straggler binary.
 \label{fig:mass_ratio_evolution_for_14MSun}}
@@
 scenario proceeds from the most massive tertiary to a binary of lower
-total mass. This may result in an unstable phase of mass transfer, in
+mass. This may result in an unstable phase of mass transfer, in
 particular if the donor has a convective envelope
@@
 eccentric orbit with a WD (the left-over core of the tertiary star).
-Such a close BS-WD binary would be hard to explain in another way.
+As discussed in Section~\ref{intro}, BS-WD binaries are predicted to be the products of the binary mass transfer hypothesis (ignoring a common envelope phase) for BS formation.
+However, this mechanism tends to predict wide orbits, which is consistent with the observed BS-WD systems in NGC 188.
 %% These ``imposter'' BS-WD binaries would in principle mimic what is
@@
 %% stars.
-If such a dynamical instability engages relatively late in the
+If, on the other hand, such a dynamical instability engages relatively late in the
 mass-tranfer phase, the white dwarf (maybe with a little left-over
@@
 matches the observed orbital separation (i.e., $0.13$\,au) of the
-observed twin BS 7782 and the observed masses of the two stars of
+observed twin BS WOCS 7782 and the observed masses of the two stars of
 about 1.4\,\MSun.
